### 2023-09-11 article.tex
Start of notes from TBL dairy

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notes for this article! %
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% references to check:

%%%%
% A triple bottom line planning tool for measuring sustainability; A systems approach to sustinability using the Australian dairy industry as a case study.

% Capra, 1996; 
% Johnson and Mengersen, 2012)

% Define: Self-organising systems.

### 2023-09-12 data_prep.py
data_prep

@@ -1,0 +1,27 @@
+from carbon_converter import *
+
+import pandas as pd
+
+df = pd.read_feather("df.feather")
+df = df[df["giregion"]=="McLaren Vale"]
+
+###################################
+# We insert values for emissions
+#
+# We convert the use of fuels into CO2E
+# This includes both scope1 and scope 2 in the totals, as well as separate columns for comparison.
+df["irrigation_energy_diesel"] = df["irrigation_energy_diesel"].div(1000).apply(diesel_irrigation)
+df["diesel_vineyard"] = df["diesel_vineyard"].div(1000).apply(diesel_vehicle)
+df["petrol_vineyard"] = df["petrol_vineyard"].div(1000).apply(petrol_vehicle)
+df["lpg_vineyard"] = df["lpg_vineyard"].div(1000).apply(lpg_vehicle)
+df["biodiesel_vineyard"] = df["biodiesel_vineyard"].div(1000).apply(biodiesel_vehicle)
+
+df["scope1"] = df["irrigation_energy_diesel"]\
+    + df["diesel_vineyard"]\
+    + df["petrol_vineyard"]\
+    + df["lpg_vineyard"]\
+    + df["biodiesel_vineyard"]
+
+df = df[["area_harvested", "tonnes_grapes_harvested", "water_used", "scope1"]]
+
+df.to_csv("df.csv")

### 2023-09-13 data_prep.py
mclaren vale example

@@ -1,9 +1,12 @@
 from carbon_converter import *
 
+import numpy as np
 import pandas as pd
 
 df = pd.read_feather("df.feather")
 df = df[df["giregion"]=="McLaren Vale"]
+# df = df[df["giregion"]=="Barossa Valley"]
+# df = df[df["data_year_id"]=="2021/2022"]
 
 ###################################
 # We insert values for emissions
@@ -23,5 +26,73 @@ df["scope1"] = df["irrigation_energy_diesel"]\
     + df["biodiesel_vineyard"]
 
 df = df[["area_harvested", "tonnes_grapes_harvested", "water_used", "scope1"]]
+
+#################
+# area_harvested:
+
+#  count    1196.000000
+# mean       28.203892
+# std        98.008156
+# min     -2639.000000
+# 25%         6.150000
+# 50%        13.000000
+# 75%        27.630000
+# max       603.000000
+# Name: area_harvested, dtype: float64
+
+#########################
+# tonnes_grapes_harvested:
+
+#  count    1196.000000
+# mean      207.696812
+# std       378.606458
+# min         0.000000
+# 25%        34.747500
+# 50%        79.675000
+# 75%       196.260000
+# max      3600.000000
+# Name: tonnes_grapes_harvested, dtype: float64
+
+##############
+# water_used:
+
+#  count     1196.000000
+# mean       115.856636
+# std       1475.894398
+# min          0.000000
+# 25%          5.800000
+# 50%         14.278500
+# 75%         35.312500
+# max      47086.000000
+# Name: water_used, dtype: float64
+
+#########
+# scope1:
+
+#  count      1196.000000
+# mean      15645.899814
+# std       35327.725501
+# min           0.000000
+# 25%        1154.825490
+# 50%        4354.729749
+# 75%       12018.837443
+# max      335636.600238
+# Name: scope1, dtype: float64
+
+# log transform
+df = (df+1).apply(np.log)
+
+decs = {}
+for col in df.columns:
+    decs[col] = {"mean": df[col].mean(), "std": df[col].std()}
+
+# Scale and centre
+df = df - df.mean()
+df = df/df.std()
+
+for col in df.columns:
+    print("\n\n")
+    print("{} mean: {}".format(col, np.exp(decs[col]["mean"])))
+    print("{} std: {}".format(col, np.exp(decs[col]["std"])))
 
 df.to_csv("df.csv")

### 2023-09-13 example_linear_models.r

@@ -1,0 +1,17 @@
+
+df <- read.csv("df.csv")
+
+print(summary(lm(
+    tonnes_grapes_harvested ~
+    area_harvested + water_used + scope1
+    , data = df)))
+
+print(summary(lm(
+    water_used ~
+    area_harvested
+    , data = df)))
+
+print(summary(lm(
+    scope1 ~
+    area_harvested + water_used
+    , data = df)))

### 2023-09-19 straw_man_values.py
needs fixing but saving for now

@@ -1,0 +1,236 @@
+df = pd.read_feather("df.csv")
+
+# We do the ones relating to cover crops differently!
+
+len(df[
+    (df["bare_soil"]/df["area_harvested"]>.5)
+    ].index)/length
+# 0.05204399934329338
+
+len(df[
+    (df["permanent_cover_crop_native"]/df["area_harvested"]>.5)
+    ].index)/length
+# 0.11361024462321458
+
+len(df[
+    (df["permanent_cover_crop_non_native"]/df["area_harvested"]>.5)
+    ].index)/length
+# 0.220325069775078
+
+len(df[
+    (df["permanent_cover_crop_volunteer_sward"]/df["area_harvested"]>.5)
+    ].index)/length
+# 0.4014119192250862
+
+len(df[
+    (df["annual_cover_crop"]>.5)
+    ].index)/length
+# 0.23033984567394516
+
+##############
+# First Water
+
+len(df[
+    (df["water_used"].div(df["area_harvested"])<df["water_used"].div(df["area_harvested"]).median()) & 
+    (df["bare_soil"]>0.5)
+    ].index)/length
+# 0.04876046626169759
+
+len(df[
+    (df["water_used"].div(df["area_harvested"])<df["water_used"].div(df["area_harvested"]).median()) & 
+    (df["permanent_cover_crop_native"]>0)
+    ].index)/length
+# 0.07437202429814481
+
+len(df[
+    (df["water_used"].div(df["area_harvested"])<df["water_used"].div(df["area_harvested"]).median()) & 
+    (df["permanent_cover_crop_non_native"]>0)
+    ].index)/length
+# 0.16368412411755048
+
+len(df[
+    (df["water_used"].div(df["area_harvested"])<df["water_used"].div(df["area_harvested"]).median()) & 
+    (df["permanent_cover_crop_volunteer_sward"]>0)
+    ].index)/length
+# 0.24150385815137088
+
+len(df[
+    (df["water_used"].div(df["area_harvested"])<df["water_used"].div(df["area_harvested"]).median()) & 
+    (df["annual_cover_crop"]>.5)
+    ].index)/length
+# 0.11344606796913478
+
+
+##############
+# Lastly Fuel
+
+len(df[
+    ((df["petrol_vineyard"].div(df["area_harvested"])<df["petrol_vineyard"].div(df["area_harvested"]).median()) | 
[…]

### 2023-09-20 straw_man_values.py
updated with more down to earth values.

@@ -1,236 +1,527 @@
-df = pd.read_feather("df.csv")
+"""This is a script to prepare values for the strawman model
 
-# We do the ones relating to cover crops differently!
+We want these values to be based in some sense of reality so that the discussion can ensue in a reasonable course. That way people have the potential to agree with some of the values compared to just disagreeing completely with everything.
+
+It is also important that we establish some sense of validity to our resesarch. That the values we can derive are based in reality and somewhat defensible, however the workshop acts to strengthen both our understanding of these values and our ability to model the reality of affects and outcomes in vineyards.
+"""
+
+####################
+# Data preparation #
+####################
+# We being with similar data preparation to the the linear models data prep.
+
+from carbon_converter import *
+
+import pandas as pd
+import numpy as np
+
+df = pd.read_feather("df.feather")
+
+df["irrigation_energy_diesel"] = df["irrigation_energy_diesel"].div(1000).apply(diesel_irrigation)
+df["diesel_vineyard"] = df["diesel_vineyard"].div(1000).apply(diesel_vehicle)
+df["petrol_vineyard"] = df["petrol_vineyard"].div(1000).apply(petrol_vehicle)
+df["lpg_vineyard"] = df["lpg_vineyard"].div(1000).apply(lpg_vehicle)
+df["biodiesel_vineyard"] = df["biodiesel_vineyard"].div(1000).apply(biodiesel_vehicle)
+
+df["scope1"] = df["irrigation_energy_diesel"]\
+    + df["diesel_vineyard"]\
+    + df["petrol_vineyard"]\
+    + df["lpg_vineyard"]\
+    + df["biodiesel_vineyard"]
+
+df["area_harvested"] = df["area_harvested"]*10000
+
+df_floats = df.select_dtypes(float)
+df_o = df.select_dtypes("O")
+df_int = df.select_dtypes(int)
+
+for col in df_floats.columns:
+    #We make an exception for gross margin as people can lose money
+    if col == "gross_margin": 
+        continue
+    df_floats.loc[df_floats[col]<1, col] = np.nan 
+
+######
+# NOTE
+#
+# We have exceptional difference here.
[…]

### 2023-10-08 bn.py
sprinkler example as bn start using pymc

@@ -1,0 +1,17 @@
+# sprinkler.py
+import pylab as pl
+import pymc as mc
+ 
+G_obs = [1.]
+N = len(G_obs)
+ 
+R = mc.Bernoulli('R', .2, value=pl.ones(N))
+ 
+p_S = mc.Lambda('p_S', lambda R=R: pl.where(R, .01, .4),
+                doc='Pr[S|R]')
+S = mc.Bernoulli('S', p_S, value=pl.ones(N))
+ 
+p_G = mc.Lambda('p_G', lambda S=S, R=R:
+                pl.where(S, pl.where(R, .99, .9), pl.where(R, .8, 0.)),
+                doc='Pr[G|S,R]')
+G = mc.Bernoulli('G', p_G, value=G_obs, observed=True)

### 2023-10-29 straw_man_values.py
Added functions instead of manually slicing

@@ -73,203 +73,129 @@ df = pd.concat([df_floats, df_o, df_int], axis=1)
 # as singular pandas operations but at least a bit more
 # verbose as to what is going on and easier to check.
 
+def pr_root_node(df, node):
+    # We set nans to -10 to show that they are less than 0.
+    df = df.replace({np.nan: -10})
+    high = len(df[
+    (df[node]>0)
+    ].index)/len(df)
+    return {
+        "high": high
+    , "low": 1-high
+    }
+
+
+def pr_child_node(df: pd.DataFrame, node: str, parent: str):
+    ok = df[df[node].notnull()] 
+    length = len(ok[ok[parent].notnull()])
+    return {
+        "high": 
+        len(ok[
+        (
+            (ok[node]>0) # H
+        ) & 
+        (
+            (ok[parent].notnull())
+        )
+        ])/length
+        , "low": len(ok[
+        (
+            (ok[node]<0)
+        ) & 
+        (
+            (ok[parent].notnull())
+        )
+        ])/length
+    }
+
 ###############
 # Cover Crops #
 ###############
-length = len(df)
-# We set nans to -10 to show that they are less than 0.
-df = df.replace({np.nan: -10})
+# length = len(df)
+
 # this is sanity checked there are no values of -10 in the dataframe
 
 # we will reset this after cover crops as a nan here represents not utilising that type of cover crop!
+cover_crops = [
+    "bare_soil"
+    , "permanent_cover_crop_native"
+    , "permanent_cover_crop_non_native"
+    , "permanent_cover_crop_volunteer_sward"
+    , "annual_cover_crop"
+]
 
-len(df[
-    (df["bare_soil"]>0) # High
-    ].index)/length
-# 0.06386471843703825
-
-len(df[
-    (df["permanent_cover_crop_native"]>0) # high
-    ].index)/length
-# 0.10868494500082089
-
-len(df[
-    (df["permanent_cover_crop_non_native"]>0) # High
-    ].index)/length
-# 0.19947463470694468
-
-len(df[
-    (df["permanent_cover_crop_volunteer_sward"]>0) # High
-    ].index)/length
-# 0.3401740272533246
-
-len(df[
-    (df["annual_cover_crop"]>0) # high
-    ].index)/length
[…]

### 2023-10-29 article.tex
notes and definitions
research question and structural questions.
added papers to review from OIV
added draft questions
added notes from prior article that are more relevant here.
adding more notes
notes on defencible methods

@@
+%%%%%%%%%%%%%%%
+% Paper setup %
+%%%%%%%%%%%%%%%
+
+% What is your topic?
+% What is the context for your reserach?
+% What do you want to achieve?
+% Are there any relationships you want to explore?
+
+%%%%%%%%%%%%%%%%
+% Working title
+%
+\title{Measuring sustainability with Australian vine growers using a Bayesian Network}
+
+% Description
+% NB Avoid titles along the lines of: “Effects of ...”, “The role of ...”, etc.  Be specific about the effect and its significance so that your reader knows what is on offer.
+
+% For example, rather than write a title like “The effect of factor X on astrophysical properties of green cheese.”,
+
+% be specific about the effect and write something more like ...
+
+% “Factor X halves the lunar thermal diffusivity of  green cheese”.
+
+% You will usually find it easier to write an effective title if you make your title a sentence.
+
+% Notes
+% N/a
+
+%%%%%%%%%%%%%%%%%%%%
+% Intended readers
+%
+% David Klassen (wine maker Taylors)
+% Dpt Agriculture - EL worker
+        % They would like to know for policy
+% Lawson - asked about OOBNs
+% Winegrower - Someone from the limestones coast. The guy from Robe was interested.
+
+% Description:
+% Name 4 or 5 potential readers - give their names and why they would be interested  (e.g.
+“Ichabod Crane, paleo-fudgologist interested in polygalactic fudginomiality”, not “assorted paleo-fudgologists”).
+
+% Your readers should be outside your institution.
+
+% Notes
+% Many viticulturalists I know of are on the panel. It makes it hard to get one in particular.
+
+%%%%%%%%%%%%%%%%%%%%%
+% Anticipated Journal
+%
+% OIV Congress 2024
+
+% Descrption
+% Ensure that all readers are likely to read the nominated journal  (e.g.  few non-researchers read refereed academic journals; politicians simply don’t read).
+
+% Notes
+% Strangely this is less likely to be other researchers. Unless they are interested in Wine.
+
+%%%%%%%%%%%%
+% Question %
+%%%%%%%%%%%%
+
+% TODO: review the following questions:
+% What are the key factors/indicators of sustainability in the australian winegrowing industry?
+%  How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
+
+% Things to consider
+%
+% Why is the knowledge important?
+% What is the significance?
+% How will the findings be utilised?
+% What improvements may be derived from this result?
+% Are the terms well defined?
+% Is it doable? (cost & ethics)
+%       Can you finish it in time?
+% Do experts think your question is important/relevant/doable?
+
+% What is the nature of your question?
+%         who, what, where, when, why, how?
+
+% You can have more than one question.
+
+% What is the most important question your paper will pose?
+%
+% NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.
+
+% Why is the question/issue/problem worth examining?
+%
+% Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.
+“Nothing much is known” is not sufficient justification by itself.
+You have to show why the gap in knowledge is important.
+Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
+
+%%%%%%%%%%
+% Answer %
+%%%%%%%%%%
+
+% What is the answer to question
+%
+% 
+% NB  You must give a direct answer to the question posed.
+% Notes
+
+% Will the findings be considered significant?
+
+% How did you gather the evidence? 
+%
+% Briefly outline the methods you used to gather your evidence.
+
+% What is the main evidence?
+%
+% Briefly outline the key results.  Focus on outcomes.
+
+% What can you add to theory?
+%  
+% A research paper has to add to broader understanding. What will yours contribute?  Think about how your results and conclusions will change how people see the world.
+%
+% Many people have trouble with this section.
+Do not recycle the results.
+Focus on the conceptual models that explain why your results are as they are, or why they are different from what might have been expected.
+Your contribution may be something new or it may be confirmation of something already known but in a slightly different context.
+%
+% Sometimes the contribution to theory is not a simple answer but a better understanding of the questions that ought to be asked in future.
+%
+% Again, expect to draw heavily on the literature in framing your answer, but cite the literature only sparingly here (you can go into full detail when you prepare your discussion).
+
+% What can you add to practice?
+%
+% Superior research also has practical consequences.
+What are the consequences of your work?
+Think about how your results and conclusions might change what people do.
+Do not merely restate your results.
+
+%%%%%%%%%%%%%%%
+% Future work %
+%%%%%%%%%%%%%%%
+
+% What remains unresolved?
+% 
+% You may or may not have a lot to say here.  Some of it may be useful in your discussion.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%       Workshop ideas      %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Ice breaker
+% - who are you what are you involved in.
+% Who knows who?
+%
+
+% Ask the expert team to nominate scenarios of interest then enter evidence into the BN to represent these scenarios.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+% The creation of the model was done in the following stages (this is on page xxiv):
+
+%  + The conceptual model
+%  + key sustainability indicators
+%  + Connection of key indicators to available measurable variables
+
+% The identified measurable variables were:
+
+% Econoomy (Farm to gate was used):
+%  + Economics
+        % + Debt
+        % + Assets
+        % + Investment
+%  + profitability
+        % + Interest
+        % + Income
+        % + Competitiveness
+% %  + Work force
+%         + Employment
+%         + Productivity
+%         + Management
+%  + market
+        % + Commodity prices
+        % + Supply
+        % + Risks
+%  + physicals
+        % + Efficiency
+        % + Resource
+        % + Inputs
+%  + commodity prices
+%  + Supply and risks
+
+% Social (across farm, factory and market)
+%  + employment
+        % + Labour
+        % + Training
+        % + Management
+%  + legal and ethics
+        % + Discrimination
+        % + Compliance (regulatory)
+%  + community
+        % + Culture
+        % + Value
+        % + Cohesion (participation/social responsibility)
+%  + health and safety
+        % + Animal welfare
+        % + occupational
+        % + Consumer
+%  + product
+        % + Nutrition
+        % + marketing
+
+% Environment
+%  + Reource Efficiency
+%         + Water
+%         + Energy & emissions
+%         + land and soil
+%  + Waste
+%         + Water Waste
+%         + Solid Waste
+
+% A high | low | medium score was used
+
+%%%%%%%%%%%%%%
+
+% The research for this project has identified that there is no uniform
+% way to measure sustainability, no uniform agreement on indicators
+% that could be used for measurement and even less agreement on
+% which metrics should be used to quantify these indicators. This is
+% best demonstrated that of the 72 triple bottom line frameworks, the
+% indicator water occurred in 64 of these frameworks, although there
+% appeared to be no standard metric identified to measure how water
+% was measured. This is an endemic problem with sustainability
+% measurement.
+
+% The forces which drive the social, economic and environmental sectors, the decision-makers who have the power or influence to accept or reject change, cannot be ignored, if change is to be achieved (van Kerkhoff and Lebel, 2006).It may be that part of the problem with the progress of sustainable development in the past has been the traditional divide between those undertaking the systematic research and those on the ground required to take up and act on the results of such.
+The dissemination of research results has usually only occurred on completion, in a unidirectional, linear communication (van Kerkhoff and Lebel, 2006), whereas, as grounded researchers explain, the ownership of ideas and a willingness to implement these relies on a more collaborative approach from the outset, before research has even commenced.
+It requires acknowledging that experts exist in all spheres and need to be able to share information and debate, in order to come to agreement on issues, assessment tools, priorities for remediation and an optimal approach to solving problems (Corbin and Strauss, 2008; Johnson and Mengersen, 2009), e.g.
+improving sustainability.
+
+% The sustainability Bayesian network model was constructed using
+% open source software and has been delivered as a software package.
+% A future project could focus on making it easier for a wider range of
+% relevant stakeholders to engage with the model. For example a
+% graphical user interface to the model could be developed and
+% then web-enabled so that stakeholders can readily interact with the
+% model and run scenarios.
+
+% The concept of sustainability has been described as the most
+% challenging policy concept ever developed (Spangenberg, 2004).
+% There are more than 100 definitions of sustainability and sustainable
+% development (Labuschagne et al., 2005). The most frequently cited
+% definition comes from the pivotal 1987 World Commission on
+% Environment and Development ‘Brundtland Report’, ‘development
+% that meets the needs of the present without compromising the ability
+% of future generations to meet their own needs’ (WCED, 1987).
+
+% It is necessary to understand the impacts of each system on one another, for example, the impact of industries on climate change, diminishing resources, economic shifts and social change.
+In turn, it is necessary to understand the impact of variables such as these on an industry, its future viability, its surrounding communities and the economies they feed or depend on (Brundtland, 2007).
+Thus, a tool is required that can measure complexity within and between systems and model how changes in one element, positive or negative, might flow on to others.
+Only then can strategies for sustainability be developed with reduced risk of unintended negative consequences (Johnson and Mengersen, 2012).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % references to check:
+
+% https://www.sciencedirect.com/science/article/pii/S1462901122003872
 
@@
 
-% Define: Self-organising systems.
+% Murphy (2002)
+%  A diagram of graphical models!
+
+% The below references are from the previous OIV conference
+%       Interestingly the theme was sustainability.
+
+% 2023-3134: A DIGITAL TWIN APPLICATION FOR VINEYARDS SUSTAINABLE MANAGEMENT
+% Vittorio Faluomi: Tecnovine srl, Italy, vittorio.faluomi@tecnovine.com
+
+% 2023-3299: SUSTAINABLE PRODUCTION OF GRAPEVINE AND WINE IN TEXAS
+% Amit Dhingra: Department of Horticultural Sciences, USA, amit.dhingra@ag.tamu.edu
+
+% 2023-2958: DO SUSTAINABILITY CREDENTIALS NO LONGER SERVE AS A COMPETITIVE ADVANTAGE? - THE
+% QUEST FOR COMPETITIVE PARITY WITH REGARD TO SUSTAINABILITY IN THE WINE INDUSTRY
+% Barbara Richter: Hochschule Geisenheim University, Germany, barbara.richter@hs-gm.de
+
+% 2023-3028: THE BLOCKCHAIN FOR THE SUSTAINABILITY OF DESIGNATIONS OF ORIGIN AND QUALITY AGRI-
+% FOOD DISTRICTS: THE CASE OF VERMENTINO DI GALLURA D.O.C.G.
+% Graziella Benedetto, Forleo Marina: University of Sassari, Italy, gbenedet@uniss.it
+
+%  **************** This one looks super relavent
+% 2023-3044: SUSTAINABILITY ASSESSMENT: TESTING AND VALIDATING A HIERARCHICAL FRAMEWORK IN THE
+% PORTUGUESE WINE SECTOR CONTEXT.
+% Ana Trigo, Ana Marta-Costa, Rui Fragoso: Centre for Transdisciplinary Development Studies (CETRAD), University of Trás-
+% os-Montes e Alto Douro (UTAD)., Portugal, anatrigo@utad.pt
+
+% 2023-3146: USER-GENERATED CONTENT AND RELEVANCE OF SUSTAINABILITY ATTRIBUTES FOR WINE
+% CONSUMERS
+% Miguel-Ángel Gómez-Borja, Inmaculada Carrasco, Juan-Sebastián Castillo: Universidad de Castilla-La Mancha, Spain,
+% miguelangel.gborja@uclm.es
+
+% 2023-2844: THE JOURNEY TO FARMLAND SOIL RESTORATION: UNDERSTANDING AND MEASURING
+% PROGRESS TOWARDS SUSTAINABILITY
+% Alberto Acedo: Biome Makers, Spain, acedo@biomemakers.com
+
+% 2023-3239: ECOLOGICAL CRITERIA FOR A SUSTAINABILITY ASSESSMENT USING THE EXAMPLE OF THE ONLINE
+% CERTIFICATION "NACHHALTIG AUSTRIA" (SUSTAINABLE AUSTRIA)
+% Franz Rosner, Barbara Richter: Federal College and Research Institute for Viticulture and Pomology Klosterneuburg,
+% Austria, franz.rosner@weinobst.at
+
+% 2023-3084: THE IMPORTANCE OF RURAL EXTENSION AND ADVISORY SERVICES TO ACHIEVE A SUSTAINABLE
+% VITICULTURE IN A CLIMATE CHANGE SCENARIO
+% Ana Chambel: AVIPE, Portugal, ana.chambel@avipe.pt
+
+% 2023-3220: EXPLORING BAYESIAN BELIEF NETWORK TO SUPPORT SUSTAINABLE VINEYARD IRRIGATION IN
+% BRAZILIAN SEMI-ARID
+% Luiz Gustavo Lovato: UNICAMP, Brazil, luizglovato@gmail.com
+
+% PO-302
+% 2023-2856: DATA DRIVEN APPROACH TO ENERGY EFFICIENCY IN WINERIES
+% Gellio Ciotti, Marco Bietresato, Alessandro Zironi, Roberto Zironi, Rino Gubiani: Università degli Studi di Udine, Italy,
+% gellio.ciotti@uniud.it
+
+%%%%%%%%%%%%
+% Definitions:
+
+%%
+% Iterative Bayesian network developement cycle
+%
+% \autocite{johnsonIntegratedBayesianNetwork2009}
+% This article  illustrates a proposed integrated Bayesiannetwork  modeling  approach  using OOBNs within theiterative Bayesian network development cycle (IBNDC
+% ^ This is a really comprehensive and well written definition of object orientated bayesian networks!
+% 
+%
+%
+
+%%
+% integrated Bayesian networks
+%
+% The complex nature of environmental issues makes themideal case studies for the use of Bayesian networks as anintegration tool (Varis and Kuikka 1999; Uusitalo 2007;Barton et al. 2008), 
+%
+% Integrated models incorporate other types of tools like regression etc - it is literally what we are doing here.
+I would ask for a better definition from kerrie though.
+The term is used a lot but I cannot find an explicit definition.
+%
+
+%%
+% Self-organising systems.
+%
+% Sustainability is one such complex system.
+It comprises complex interacting factors and processes (e.g.
+in the context of the dairy study: farm, factory and market processes; and environmental, social and economic factors).
+It is self-organising; it does not require external intervention to thrive or deteriorate (e.g.
+an ecosystem can be sustainable through self-organisation).
+It can also exhibit emergent behaviour, since intervening in one part of the sustainability system can have unintended and quite extreme effects in seemingly unrelated parts of the system (Johnson and Mengersen, 2012).
+%
+% These systems are exactly what you think they are. It is described in physics, chemistry, social sciences and philosophy.
+% 
+% The wiki is quite informative.
+%https://en.wikipedia.org/wiki/Self-organization
+
+% Initiatives to improve the environmental impacts of the Australian Wine industry have been ongoing since the 1990s; with recommendations to implement strategies for national programs that would help educate industry members in sustainable practices (Keith Jones, 2002).
+The first legislative initiative to support national programs was the Environmental Management Guidelines for Vineyards in Western Australia during 2002 (Nind, 2002).
+The first national program was the Australian Wine Industry Stewardship, beginning shortly after, during 2004 (WFA, 2009).
+This program was replaced multiple times during the 2000s, first by the Australian Wine Environmental Stewardship, and then by EnviroWine, finally becoming EntWine in 2009.
+The period in the 2000s was further influenced by several key researchers and program leaders, where concurrently multiple regions developed approaches to sustainable management tied to sustainability programs (SWA, 2023).
+EntWine was eventually acquired by the Australian Wine Research Institute and Australian Grape & Wine during 2015; which would lead to its redevelopment into Sustainable Winegrowing Australia (SWA) during 2019/2020 (SWA, 2023).
+%             2.1.2. Previous Research and Motivation
+% During the period of 2010 to 2023 data was collected voluntarily from wine industry members through the national sustainability programs, ultimately being in SWA possession as of 2023.
+The data set was used in 2020 to analyse sustainable practices, resulting in the development of a Resource Intensity Score (RIS); where the RIS was a summary indicator value of a vineyard’s energy use, emissions and water use (Nayak et al., 2020).
+The analysis then fit vineyards’ RIS values to 55 variables sourced from 23 separate wine regions during the period of 2015 to 2018 through the use of Stepwise Regression modelling.
+It was found that the top 10% gross margin vineyards had a lower operating cost and a lower RIS score than vineyards in the bottom 10% gross margin.
+% The motivation for this thesis is to investigate the differences between the top 10% gross margin vineyards and those of the bottom 10%, hoping to uncover what the key differences were and to relate them to sustainable practices; as there is a known gap in the literature due to the difficulty to evaluate relationships using empirical evidence of both the environmental and economic impacts of sustainable practices in viticulture.
+This difficulty stems from data scarcity, industry complexity and transparency.
+While there have been attempts to fill these gaps, methodologies and indicators have lacked in ability to compare different regions and scales (Baiano, 2021).
+%             2.1.3. Economic Pressures
+% Historically strong demands for Australian wine have helped to create a thriving industry, however recently sharp reductions in exports to mainland China due to significant deposit tariffs have caused  a decline of 19% in Australian export value during the 2021-2022 financial year (see Figure 1) (Wine Australia, 2022).
+The pressure brought on by the drop in export value has been exacerbated by loss of tourism and labour due to the COVID-19 pandemic, global freight crisis, war in Europe and rising inflation (Wine Australia, 2021a, 2020).
+These pressures within the wine industry have trickled down to vineyards, where winemakers retain unwanted wine, creating an oversupply of grapes.
+Currently the proposed strategy to soften pressures proposed by Wine Australia includes initiatives focused on market diversification, and sustainability to build resilience in the coming years.
+% Figure 1:  The exports of Australian wine over time in Australian Dollars Free On Board, comparing exports between China and the rest of the world.
+This graphic is taken from the Wine Australia Annual Report of 2020-21(Wine Australia, 2022).
+%             2.1.4. Environmental Pressures
+% There are several environmental concerns that affect viticulture, including loss of soil quality, lack of rain, hail, disease, fire, and frost; with climate change exacerbating these issues.
+In 2020, 40,000 tonnes of grapes were lost across 18 different wine regions due to bush fires and smoke taint; the predicted incidence of wildfires is expected to increase (Canadell et al., 2021).
+In comparison to countrywide pressures such as drought, this damage made up only 3% of the total amount of grapes for that year; although acknowledged as a considerable loss on an individual basis, it was deemed to be only a minor national concern by Wine Australia when compared to other environmental pressures such as drought (Wine Australia, 2020).
+
+%
+%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
+% What the hell is a regional strategy
+% And how do you define, or know what trategy each region is using?
+%
+% Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.
+
+% This does not really address what the methods are - aside from classisifcation trees in the most vague sense.
+% What are the results briefly? why should someone read this article?
+% What is interesting - what will be discussed in the article with regard to these results? What makes me want to read the article?
+% And what is the take away point of the article? If I cant be bothered to read this article, what piece of knowledge can you leave mewiwth that I could recommend the article to someone else with?
+
+\section{Methods}
+
+% These are transcribed notes from Korb & Nicholson:
+
+Korb & Nicholson describe Knowledge Engineering with Bayesian Networks (KEBN) as ocurring in stages:
+- Generating Arc Structure
+- Parametarisation
+- dealing with utilities
+
+Pitchforth agrees with this style of structure naming these steps as:
+- Structure
+- Discretisation
+- Parametarisation
+- Model behaviour
+- Validation
+
+Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)
+
+With validation incorporating the expert scrutiny of the models begaviour for scenarios, as well as comparing this to both data and other literature.
+
+\citep{korbBayesianArtificialIntelligence2011}

### 2023-10-29 straw_man_values.py
Just adding a note

@@ -203,6 +203,8 @@ pr_root_node(df_slice, "electricity")
 # operating cost #
 ##################
 
+#  TODO: We could make a node structure and use recursive functions...
+
 ok = df[df["total_operating_costs"].notnull()]
 
 ok["petrol_vineyard"] = ok["petrol_vineyard"].replace({np.nan: 0})

### 2023-10-31 article.tex
quick back up mid Korb&Nicholsons notes.

@@
 
-Korb & Nicholson describe Knowledge Engineering with Bayesian Networks (KEBN) as ocurring in stages:
+Korb & Nicholson describe three major issues in the creation of Bayesian Networks though knowledge Engineering:
 - Generating Arc Structure
@@
 
-Pitchforth agrees with this style of structure naming these steps as:
+Korb and Nicholson also describe 8 common problems that occur during the construction of Bayesian. Korb and Nicholson suggest methods for overcoming this similarly to Pitchforth:
+\subsection{The process}
+\subsubsection{Parameterizing before evaluating the structure}
+\begin{enumerate}
+        \item Are the nodes in the BN the right ones?
+        \item Are the state spaces (values) for each node correct?
+        \item Are the arcs right?
+\end{enumerate}
+If the answer to any of the above questions is no; then the structure will not be sufficiently defined for the parametarisation of the CPT.
+In this paper we explicitly defined the structure of the BN prior to CPT parametarisation.
+This involved:
+\begin{enumerate}
+        \item exposing the panel to a strawman model in an intial workshop
+        \item Describing the model and the process invovled in defining the structure of a BN
+        \item The expert panel reviewing possible nodes and arcs, defining their own structures prior to a second workshop (with correspondence between expert panel members prior to the next workshop)
+        \item A second workshop to agree upon the final structure of the model
+\end{enumerate}
+\subsubsection{Trying to build the full model all at once}
+Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
+\begin{enumerate}
+        \item dividing models into subcomponents
+        \item breaking down the problem into a single target variable
+        \item reducing the scope of the problem
+        \item Setting a single time frame for the problem
+\end{enumerate}
+The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
+Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards.
+This also reduced the BN to a single terminal node.
+It was further decided to create the BN as a single season to limit its complexity.
+
+\subsection{The problem}
+\subsubsection{Not understanding the problem context, complexity without value.}
+It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
+\begin{enumerate}
+        \item what do you want to reason about?
+        \item What dont you know?
+        \item What infomration do you have?
+        \item What do you know?
+These questions are well addressed in prior research.
+The creation of baseline models showed strong linear relationships between many variables.
+The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability.
+here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
+\end{enumerate}
+\subsection{Structure - Nodes}
+\subsubsection{Getting the node values wrong. An exhaustive list below}
+\begin{enumerate}
+        \item Node values aren't exhaustive
+        \item Node values aren't exhaustive
+        \item Node values aren't mutually exclusive
+        \item Incorrect modelling of mutually exclusive outcomes
+        \item Trying to model fuzzy categories
+        \item Confusing state and Probability
+        \item Confusion about what the node represents
+\end{enumerate}
+Two major strategies were employed to overcome these problems.
+Tying nodes explicitly to a data source that corroberated the definition and state in some manner as the node.
+For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
+\subsection{Structure Arcs}
+\subsubsection{Getting the arc directions wrong}
+Arc directions are commonly wrong for the following reasons:
+\begin{enumerate}
+        \item Modelling reasoning rather than causation
+        \item Inverting cause and effect
+        \item Missing variables
+\end{enumerate}
+To note: Korb and Nicholson do not actually suggest a method for overcoming these problems.
+There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation.
+It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
+\subsubsection{Too many parents}
+Sometimes it is unavoidable that a node is affected by many factors, or other nodes.
+There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child.
+This technique was employed in the creation of the structure of the BN with the expert panel.
+\subsection{Parameters}
+\subsubsection{Experts estimates of probabilities are biased}
+-       -       - overconfidence
+-       -       - Anchoring
+-       -       - Availability
+-       -       - Inconsistent "filling in" of large CPTs
+\subsubsection{Incoherent probabilities (not summing to 1)}
+-       -       - Being dead certain.
+
+-
+
+Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:
+- Bayesian Network Structure
+- Probability Parameters
+- Decision Structure
+- Utilities Preference
+
+Pitchforth \citep{pitchforthProposedValidationFramework2013} agrees with this style of structure naming these steps as:
 - Structure
@@
 
+Korb & Nicholson have a similar view to Pitchforth. utilising a waterfall style developemental approach which include 5 stages:
+- Building the BN
+-       - Structure
+-       - Parameters
+-       - Preferences
+- Validation
+-       - Sensitivity Analysis
+-       - Accuracy testing
+- Field testing
+-       - Alpha/Beta testing
+-       - Acceptance testing
+- Industrial use
+-       - Collection of Statistics
+- Refinement
+-       - Updating procedures
+-       - Regression testing
+
 Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)

### 2023-10-31 article.tex
Notes for Korb & Nicholson about KEBN

@@
 
-Korb & Nicholson describe three major issues in the creation of Bayesian Networks though knowledge Engineering:
+\citep{korbBayesianArtificialIntelligence2011} Korb & Nicholson describe three major issues in the creation of Bayesian Networks though knowledge Engineering:
 - Generating Arc Structure
@@
 \subsubsection{Experts estimates of probabilities are biased}
--       -       - overconfidence
--       -       - Anchoring
--       -       - Availability
--       -       - Inconsistent "filling in" of large CPTs
-\subsubsection{Incoherent probabilities (not summing to 1)}
+\begin{enumerate}
+        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
+        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
+        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison.
+"Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
+        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.
+
+\end{enumerate}
+We have attempted to overcome this with two methods.
+A diverse and varried expert panel.
+Those participanting have experience in multiple vineyards as managers and other duties as well as the panel itself having varied manager/owners from different regions and scale.
+With some experts being more specialised in specific areas such as agro-chemicals.
+\subsubsection{Incoherent/Incoherent probabilities}
+The collection of probabilities for when the CPT is large can result in inconsistent probabilities.
+The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
+The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}.
+In this study we overcame this through the use of worded response such as high and low.
+We then assigned probabilities to those broader cases.
+We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
+% \item Inconsistent "filling in" of large CPTs:
 -       -       - Being dead certain.
 
+\citep{morganUncertaintyGuideDealing1990}
+Two attributes of good elicitation process are:
+\begin{enumerate}
+        \item The expert should be apprised of what is known about the process, especially the nearly universal tendency to overcomefidence and other forms of bias.
+In order to avoid some problems, values should be elicited in random order and the expert not given feedback on how the different values fit together until a complet set has been elicited.
+        \item The elicitation process is not simply one of requesting and recording numbers but also one of the refining the definitions of variables and terms to be used in the model.
+What values are elicited depends directly upon the interpretation of terms and these should be made as explicit as possible and recorded during the elicitation.
+This is part of the process management described earlier.
+\end{enumerate}
 -
 
+\citep{Boneh2021} Boneh, T.
+(2010).
+Ontology and Bayesian decision networks for supporting the meterological forecasting process.
+Ph.
+D thesis, Clayton School of infomration technology, Monash university
 Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:

### 2023-10-31 article.tex
Korb an dNicholson notes done!

@@
 
-Korb and Nicholson also describe 8 common problems that occur during the construction of Bayesian. Korb and Nicholson suggest methods for overcoming this similarly to Pitchforth:
+Korb and Nicholson also describe 16 common problems that occur during the construction of Bayesian. Korb and Nicholson suggest methods for overcoming this similarly to Pitchforth:
 \subsection{The process}
@@
         \item What dont you know?
-        \item What infomration do you have?
+        \item What information do you have?
         \item What do you know?
@@
 here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
+\subsubsection{Complexity without value}
+A very common impulse, when something isk nown about thep roblem, is to want to put it in the model.
+But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value).
+Instead, the knowledge engineer must focus on the problem:
+"Which of the known variables are most relevant to the problem?"
+- This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential probelsm that will come with a cumbersome model.
 \end{enumerate}
 \subsection{Structure - Nodes}
-\subsubsection{Getting the node values wrong. An exhaustive list below}
+The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
 \begin{enumerate}
-        \item Node values aren't exhaustive
+        \item Getting the node values wrong
         \item Node values aren't exhaustive
@@
 With some experts being more specialised in specific areas such as agro-chemicals.
-\subsubsection{Incoherent/Incoherent probabilities}
+\subsubsection{Inconsistent probabilities}
 The collection of probabilities for when the CPT is large can result in inconsistent probabilities.
@@
 -       -       - Being dead certain.
+\subsubsection{Incoherent probabilities (not summing to 1)}
+We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
+\subsubsection{Being dead certain}
+It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
+Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.
 

### 2023-10-31 article.tex
adding reference recomendation to methods.
added list of definitions and minor update sto article

@@
 \section{Methods}
-
+\citep{mayfieldDesigningExpertledBayesian2023} -> this reference also uses a similar method which we can cite alongside everything else.
 % These are transcribed notes from Korb & Nicholson:
@@
 Two major strategies were employed to overcome these problems.
-Tying nodes explicitly to a data source that corroberated the definition and state in some manner as the node.
+Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node.
 For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.

### 2024-02-08 article.tex
abstract (and other files not uploaded?)

@@
 \citep{korbBayesianArtificialIntelligence2011}
+
+% Abstract
+
+Title:
+A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.
+
+Abstract:
+
+The assessment of environmental sustainability in the Australian winegrowing industry remains a complex issue involving changing and compounding factors.
+To address this, we developed a Bayesian Network (BN) using data and expert elicitation to summarise the key factors, their relationships, and how they come together to influence vineyards' environmental outcomes.
+The study leveraged diverse expert perspectives to mitigate biases in probability estimations and promote discourse.
+
+The development of the BN involved an iterative process, including variable selection and definition, the defining of model structure and variable relationships, and finally the determining of relationship significance through probabilities.
+Expert input was pivotal in structuring the BN model, ensuring relevance to industry, and how a variables influence changed across regions and scenarios.
+
+Due to the possible variation in any given vineyard scenario the BN model was expanded to review a case study of the Coonawarra wine region in South Australia.
+This highlighted regional differences between growers whilst also maintaining the significance of industry-wide concerns such as the use of agrochemicals.
+To promote accessibility and scrutiny the BN was further developed into an application, allowing the possibility of further industry and stakeholder feedback; enabling a systematic re-evaluation of significant factors to the wine growing industry and how they change over time.

### 2024-02-08 cpt.py

@@ -1,13 +1,19 @@
 import itertools
 import numpy as np
 
+# Edge ranking method
+# We give each edge a ranking and normalise from best to worst scenario.
+
 def calculate_LH(x_L, x_H, weights):
     """Given the best and worst case scenarios, x_L and x_H, we calculate the unit weight for the CPT."""
     return x_L/sum(weights), x_H/sum(weights)
 
+def combinations(num_weights):
+    return list(itertools.product([False, True], repeat=num_weights))
+
 def create_boolean_matrix(x_L, x_H, num_weights):
     # Generate all possible combinations of True and False for the given number
-    all_combinations = list(itertools.product([False, True], repeat=num_weights))
+    all_combinations = combinations(num_weights)
     # Create a boolean matrix with each combination as a row
     boolean_matrix = [[x_L if bit else x_H for bit in combination] for combination in all_combinations]
 
@@ -21,8 +27,16 @@ def calculate_CPT(weights, x_L, x_H):
 
     return sum(np.transpose(np.array([weights]*len(boolean_matrix))*boolean_matrix))
 
+# Counts method:
+# We give everything the same weighting and determine the
+# COT through the number of occurences of Low/Highs
+def counts_CPT(weights: dict):
+    # For this example we are count the number of occurences of low/bad/no/etc
+    all_combinations = combinations(len(weights)-1)
+    return [weights.get(value, value) for value in sum(np.transpose(np.array(all_combinations)))]
+
 if __name__ == "__main__":
-    weights = [1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11]
+    weights = [1, 2]
     x_L = 0.1
     x_H = 0.9
     matrix = calculate_CPT(weights, x_L, x_H)

### 2024-02-29 CPT_calculation.tex
writing backup

This method utilises interpolation between two tethered ends. The ends represent the two cases, all factors being true/contributing and all factors being false/not contributing. Each factor is attributed a weight that indicates its overall influence; for this application the participants decided to score a factors influence out of 10.

Using this method, we calculate any given probability, using

\begin{equation}
p=x\sum_{i}^{n} + y\sum_{m}^{i} 
\end{equation},

for n number of true or contributing factors and m false or not contributing factors. We know the solutions when there are only true ($p_t$) or only false ($p_f$). Where,

\begin{equation}
p_t=x\sum_{i}^{n} 
\text{ and }
p_f=y\sum_{m}^{i}
\end{equation}.

From here we derive values for $x$ and $y$ using the sum of the provided weights. For example if the weights were 2, 3 and 5. And, $p_t=0.6$ and $p_f=0.5$. We have:

\begin{equation}
p_t=x\sum_{i}^{n}\\
0.6=x(2+3+5)
x=0.05\\
\text{ and }
p_t=x\sum_{i}^{n}
0.6=x(2+3+5)
x=0.05
\end{equation}

### 2024-02-29 article.tex
writing backup

@@
 % What is your topic?
+The topic of this paper is the environmental sustainability of vineyards within Australia.
 % What is the context for your reserach?
+The context of this research is that the Australian wine sector in general has gone through many tribulations due to economic, environmental and social pressures.
+Previously we attempted to highlight areas of concern through the use of statistical models, which were able to show strong correlations between various environmental and economic factors.
+However, discussions with industry and experts helped to identify that these relationships were not entirely causal, with some management and process of winegrowers obfuscating effects by directly contracting them.
+A key example of this was the lack of water use change during drought periods due to various methods that were used to obtain either more water or to circumvent the detrimental effects of lacking water resources.
 % What do you want to achieve?
+The identification of key factors; and their relation and contribution, direct or indirect, to the environmental sustainability of Australian winegrowing.
 % Are there any relationships you want to explore?
+This is key to this study. The relationships are in many ways more important to the research than the effects.
 
@@
 %
-\title{Measuring sustainability with Australian vine growers using a Bayesian Network}
+\title{Measuring environmental sustainability with Australian vine growers using Bayesian Networks}
 
@@
 % TODO: review the following questions:
-% What are the key factors/indicators of sustainability in the australian winegrowing industry?
-%  How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
+What are the key factors/indicators of environmental  sustainability in the australian winegrowing industry?
+How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
+What are the key factors that relate directly to environmental sustainability, and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?
 
@@
 % Why is the knowledge important?
+This was identified as a gap within our own prior research and is helpful in creating a basis for scenario assessment and comparison.
+This will allow a greater understanding of how these factors change within different scenarios; whether that be climate, region, business goal.
 % What is the significance?
+The significance is to bridge the gap between correlations and data to causal relationships.
+To inform growers using factors that are within their control, or how factors within their control are indfuenced by natural phenomenon.
 % How will the findings be utilised?
+These findings will be used to help inform the wider winegrowing community of what factors are most significant to environmental outcomes, and how they interact with one another.
+In practice this study aids a grower through informing them of how decisions impact environmental outcomes and how changing circumstance contribute to these factors and outcomes.
 % What improvements may be derived from this result?
+A wider more informed understanding of contributing factors to environmental impact and how different factors relate to one another to contribute to these findings.
 % Are the terms well defined?
-% Is it doable? (cost & ethics)
-%       Can you finish it in time?
+The terms are well defined. This was a key outcome of this project.
 % Do experts think your question is important/relevant/doable?
+Experts helped to guide this decision, and changed the trajectory of this project in response to data presented and how well they believed they could inform the study.
 
@@
 %         who, what, where, when, why, how?
-
+What are the key factors that contribute to environmental impact within the Australian winegrowing industry?
+How do these key factors relate to each other and what are the factors that influence them?
+What are the decision that can be made by growers that can change the environmental outcomes of their vineyards?
+How do these factors chagne across well understood scenarios?
 % You can have more than one question.
@@
 % What is the most important question your paper will pose?
-%
+What are the key factors to environmental impact within the Australian winegrowing industry, and how are these factors related?
 % NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.
@@
 % Why is the question/issue/problem worth examining?
-%
+By examining the key and relevant factors to vineyards' environmental impacts we can better prepare for future changes in climate pressure, economic restrictions; that is we can better use this model to assess the potential environmental outcomes of the wine industry, as informed by experts, given potential upcoming challenges or changes.
 % Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.
@@
 Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
-
+The collection of data and subsequent statistical analytics can only go so far as to fill the gap between cause and effects within wiengrowing.
+This research helps to fully understand the relevant decisions being made, how they are informed and what the known outcomes are.
+This helps to align these results to data collected to show stronger causal relationships than pure correlative, or hypothetical postulations of statistical analysis.
 %%%%%%%%%%
@@
 \section{Methods}
+
+Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being a common approach \citep{gehringerMappingSustainabilityMeasurement2024}.
+Other approaches utilise the identification of key factors use their measurements as a proxy to indicate the impact to or health of the consequent environment #TODO:Ref.
+The use of sustainability
+\citep{klemesAssessingMeasuringEnvironmental2015}
+measurement systems and tools can help to manage risk and promote resilience for industries through identifying sustainable goals and the key factors of interest that contribute to the success of these goals.
+\citep{beckerSustainabilityScienceManaging2024}.
+Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment.
+
+In agriculture, the consideration of environment is critical to the success of the industry.
+The question of environmental sustainability has continued to grow in importance as further pressures such as climate change impact the industry.
+TODO:reference
+When sustainability is considered with reference to the environment perspectives can vary, not only due to physical differences but also due to priorities driven by a myriad of perspectives such as consumers, government and industry.
+It is important to consider many perspectives or be explicit about the perspectives consulted.
+It is shown that in Switz that the use of collaborative appraoches in which people can come to agreeance on particular significances and their effects it is helpful to \autocite{dichiaraCollaborativeApproachAchieving2024}
+In Australia, views of both industry and consumer are united in their tendency towards the priority to improve/regulate resource inputs such as chemical use and be mindful of \autocite{dumbrellComparingAustralianPublic2024}
+
+To include perspectives from industry experts and to maintain a causal structure we used Bayesian Networks.
+This allows the illustration of the model in a graphical sense as well as the ability to incorporate data and abstractions from experts together.
+
+A Bayesian Network is a graphical model, being comprised of nodes and edges.
+Uniquely, Bayesian Networks contain the operation within the nodes themselves instead of across the edges.
+This is done in the form probability tables, which are informed by the edges.
+There is simplicity within the calculations done within a node, as it is fundamentally achieved through sum and division operations; however great complexity is introduced when a node is informed by many parents, of which may also have many parents.
+The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes.
+The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.
+
+\subsection{Elicitation}
+
+The Bayesian Network was constructed using a mixture of data and expert elliciation.
+
+The structure of the
+
 \citep{mayfieldDesigningExpertledBayesian2023} -> this reference also uses a similar method which we can cite alongside everything else.
@@
 Korb and Nicholson also describe 16 common problems that occur during the construction of Bayesian. Korb and Nicholson suggest methods for overcoming this similarly to Pitchforth:
-\subsection{The process}
+\subsubsection{The process}
 \subsubsection{Parameterizing before evaluating the structure}
@@
 
+\subsection{Structure and Conditional Probabilities}
+
+\subsection{Validation}
+
 \citep{korbBayesianArtificialIntelligence2011}
@@
 
-Title:
+1. Introduction to Methodology
+
+    Brief overview of the research approach and the rationale behind using a Bayesian Network (BN) model for sustainability assessment in viticulture.
+    Mention of the collaborative expert elicitation process and the sequential workshops that shaped the model development.
+
+2. Identification of Sustainability Indicators
+
+    Description of the process for selecting sustainability indicators, including the use of data from Sustainable Wine Australia.
+    Criteria for indicator selection, focusing on relevance to environmental, economic, and social dimensions of sustainability in winegrowing.
+
+3. Expert Elicitation Process
+
+    Overview of the expert panel composition and the expertise represented.
+    Objectives and structure of the expert elicitation process, highlighting the series of workshops conducted.
+
+Workshop 1: Variable Review and Straw Man Model Introduction
+
+    Objectives: To agree on the sustainability indicators and introduce the initial straw man model.
+    Activities: Discussion on indicator relevance and definitions; presentation of the straw man model.
+    Outcomes: Agreement on initial set of variables and conceptual understanding of the model's direction.
+
+Workshop 2: Model Structure Refinement and Interpolation Method Introduction
+
+    Objectives: To refine the model's structure and address the complexity of CPTs through an interpolation method.
+    Activities: Examination of variable relationships; identification of complex CPTs; proposal of the linear interpolation method.
+    Outcomes: Revised model structure; decision to develop and implement the interpolation method for complex CPTs.
+
+Workshop 3: Finalization of CPTs and Case Study Selection
+
+    Objectives: To finalize CPT values using the interpolation method and select a case study for model application.
+    Activities: Presentation and application of the interpolation method; finalization of CPT values; selection of the Coonawarra wine region for the case study.
+    Outcomes: Completion of model parameterization; selection of case study region emphasizing the model's practical application.
+
+4. Development and Implementation of the Interpolation Method
+
+    Detailed explanation of the linear interpolation method developed to manage the complexity of CPTs for variables with extensive connections.
+    Justification for choosing this method and its anticipated impact on the model's usability and accuracy.
+
+5. Case Study Application: Coonawarra Wine Region
+
+    Rationale for selecting the Coonawarra wine region as a case study to apply and test the BN model.
+    Brief description of how the model was applied to this specific context, including any regional data used and adjustments made for the case study.
+
+6. Model Validation
+
+    Overview of the validation process employed to ensure the accuracy and reliability of the BN model.
+    Description of internal and external validation measures, including expert review and comparison with independent datasets.
+
+7. Conclusion
+
+    Summary of the methodological approach, emphasizing the collaborative expert elicitation process and the innovative solutions developed for model construction and parameterization.
+    Brief mention of the significance of the methodology for sustainability assessment in viticulture and potential implications for future research and practice.
+
+\section{Title}
 A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.
 
-Abstract:
+\section{Abstract}
 

### 2024-03-07 article.tex
start of the methods.

@@
 
-Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being a common approach \citep{gehringerMappingSustainabilityMeasurement2024}.
-Other approaches utilise the identification of key factors use their measurements as a proxy to indicate the impact to or health of the consequent environment #TODO:Ref.
-The use of sustainability
-\citep{klemesAssessingMeasuringEnvironmental2015}
-measurement systems and tools can help to manage risk and promote resilience for industries through identifying sustainable goals and the key factors of interest that contribute to the success of these goals.
-\citep{beckerSustainabilityScienceManaging2024}.
-Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment.
+In agriculture, the consideration of environment is critical to the success of the industry.
+The question of environmental sustainability has continued to grow in importance as further pressures such as climate change impact the industry TODO:reference.
+The question of sustainability entails the consideration of a multitude of factors, not only due to physical differences between locations/habitats but also due to priorities driven by a myriad of perspectives such as consumers, ecosystems, government and industry.
+It is important to consider each factor with respect to its relevant perspectives, and to be explicit about accompanying definitions of factors and perspectives.
 
-In agriculture, the consideration of environment is critical to the success of the industry.
-The question of environmental sustainability has continued to grow in importance as further pressures such as climate change impact the industry.
-TODO:reference
-When sustainability is considered with reference to the environment perspectives can vary, not only due to physical differences but also due to priorities driven by a myriad of perspectives such as consumers, government and industry.
-It is important to consider many perspectives or be explicit about the perspectives consulted.
-It is shown that in Switz that the use of collaborative appraoches in which people can come to agreeance on particular significances and their effects it is helpful to \autocite{dichiaraCollaborativeApproachAchieving2024}
-In Australia, views of both industry and consumer are united in their tendency towards the priority to improve/regulate resource inputs such as chemical use and be mindful of \autocite{dumbrellComparingAustralianPublic2024}
+To address the significant consideration of different perspectives, collaborative efforts are a useful tool to come to agreeance upon the significance of different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
+In Australia, views of both industry and consumer are united in their priority to improve and regulate resources inputs such as chemical use and be mindful of \citep{dumbrellComparingAustralianPublic2024}
 
-To include perspectives from industry experts and to maintain a causal structure we used Bayesian Networks.
-This allows the illustration of the model in a graphical sense as well as the ability to incorporate data and abstractions from experts together.
-
+Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being common \citep{gehringerMappingSustainabilityMeasurement2024}.
+Other approaches utilise the identification of key factors, and utilise their measurements as a proxy to indicate the impact to, or the health of, the environment #TODO:Ref.
+The measuring of sustainability through the use of these tools can help to manage risk and promote resilience for industries through identifying sustainable goals and the key factors of interest that contribute to the success of these goals \citep{klemesAssessingMeasuringEnvironmental2015} \citep{beckerSustainabilityScienceManaging2024}.
+Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method to achieve this in this study is through a Bayesian Network.
+#TODO: The definition of a Bayesian network needs to be way more polished
 A Bayesian Network is a graphical model, being comprised of nodes and edges.
@@
 
+The use of a Bayesian Network allowed the ability to include perspectives from industry experts and create a causal structure.
+The graphical nature of the Bayesian Network also helped in the illustration of the model and conveying the complexity and relationship of different factors to one another as well as to vineyards' impact of the environment.
+Furthermore, data collected across Australia could also be used to help inform both scenarios and the model alongside expert opinion.
+
 \subsection{Elicitation}
 
-The Bayesian Network was constructed using a mixture of data and expert elliciation.
+The Bayesian Network was constructed using a mixture of data and expert elicitation.
+Elicitation was conducted through a series of workshops.
+Each workshop had a primary focus such as: scope, structure and parameterisation; however, prior concepts were built upon iteratively.
+The first important establishment was the scope of the network, and how well it could or couldn't be adapted to the wide variety of circumstances within the Australian winegrowing industry.
+Following this was the discussion around the structure of the network, entailing the detailing of relationships and stricter definitions of each factor to one another.
+Finally, variables were paramatised using conditional probabilities.
 
-The structure of the
+% \citep{mayfieldDesigningExpertledBayesian2023} -> this reference also uses a similar method which we can cite alongside everything else.
+% % These are transcribed notes from Korb & Nicholson:
 
-\citep{mayfieldDesigningExpertledBayesian2023} -> this reference also uses a similar method which we can cite alongside everything else.
-% These are transcribed notes from Korb & Nicholson:
+% \citep{korbBayesianArtificialIntelligence2011} Korb & Nicholson describe three major issues in the creation of Bayesian Networks though knowledge Engineering:
+% - Generating Arc Structure
+% - Parametarisation
+% - dealing with utilities
 
-\citep{korbBayesianArtificialIntelligence2011} Korb & Nicholson describe three major issues in the creation of Bayesian Networks though knowledge Engineering:
-- Generating Arc Structure
-- Parametarisation
-- dealing with utilities
+Each element within the elicitation process was iteratively 
+Elicitation was conduct ach  Although workshops focussed on a single issue, it was important to continually address each issue in an iterative fashion.
+The approach to ensuring a sound and sane network, was to directly address common issues that occur during the construction of Bayesian Networks using ellicitation as outlined by #TODO: Korb and Nicholson.
+These issues are similarly highlighted by #:TODO: Pitchforth.
 
-Korb and Nicholson also describe 16 common problems that occur during the construction of Bayesian. Korb and Nicholson suggest methods for overcoming this similarly to Pitchforth:
-\subsubsection{The process}
-\subsubsection{Parameterizing before evaluating the structure}
+Transparency with the expert panel was a key ingredient with this approach, highlighting explicitly what these problems were and how we would overcome them.
+This included agreeing upon definitions of each node before connecting edges between them.
+
+Although originally multiclass nodes existed, the bayesian network was altered to only include binary class nodes. Each edge between a node had to answer the following questions:
 \begin{enumerate}
         \item Are the nodes in the BN the right ones?
-        \item Are the state spaces (values) for each node correct?
+        % \item Are the state spaces (values) for each node correct?
         \item Are the arcs right?
 \end{enumerate}
-If the answer to any of the above questions is no; then the structure will not be sufficiently defined for the parametarisation of the CPT.
-In this paper we explicitly defined the structure of the BN prior to CPT parametarisation.
-This involved:
+If the answer to any of the above questions was no; then the structure was not considered sufficiently defined.
+Although we explicitly defined the structure of the BN prior to CPT parametarisation.
+This process continued when adding conditionaly probability values.
+The entire process of construction iinvolved the steps:
 \begin{enumerate}
-        \item exposing the panel to a strawman model in an intial workshop
-        \item Describing the model and the process invovled in defining the structure of a BN
-        \item The expert panel reviewing possible nodes and arcs, defining their own structures prior to a second workshop (with correspondence between expert panel members prior to the next workshop)
-        \item A second workshop to agree upon the final structure of the model
+        \item exposing the panel to a strawman argument/model/definition
+        \item Outlining the model and the process involved in defining the structure of a BN
+        \item The expert panel reviewing possible nodes and arcs and definitions
+        \item Defining their own structure, node or term.
+        \item Agreeing upon the final definition, structure or model.
 \end{enumerate}
 \subsubsection{Trying to build the full model all at once}
+
 Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:

### 2024-03-07 article.tex
elicitation

@@
 The Bayesian Network was constructed using a mixture of data and expert elicitation.
-Elicitation was conducted through a series of workshops.
-Each workshop had a primary focus such as: scope, structure and parameterisation; however, prior concepts were built upon iteratively.
+The format followed recommendations from \cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}.
+Where, we progressed from problem definition, structure, parametarisation to validation.
+Experts were initially informed regarding the process to establish an understanding of what each step would be comprise of, as well as highlighting common pitfalls and how we would address them.
+With common problems being listed by authors such as:
+\begin{enumerate}
+        \item Not understanding the problem context, complexity without value.
+        \item Getting arc directions wrong
+        \item too many parent nodes
+        \item Bias expert estimates
+        \item Inconsistent probabilities
+        \item Being absolutely certain
+\end{enumerate}
+To address these issues, experts were kept well-informed of them as well as variable definitions and problem scope.
+Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency.
+Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel industry experts
+
+Each workshop had a primary focus such as: scope, structure or parameterisation; with, prior concepts being built upon iteratively.
 The first important establishment was the scope of the network, and how well it could or couldn't be adapted to the wide variety of circumstances within the Australian winegrowing industry.
@@
 Finally, variables were paramatised using conditional probabilities.
+
+To introduce new concepts and how they interacted, preliminary simplified versions (strawman examples) were provided to experts; with the intention of these examples to be examined, critiqued, and improved upon.
+The use of these strawman examples enabled a more engaged and effective review process, in which experts were initially able to interact with how these concepts would fit together with other elements of the model they had developed up to that point.
+The strawman examples were crafted from a foundation of literature and data to offer a basic, layman's understanding of key factors and concepts, serving as a starting point for further development and discussion.
 
@@
 
-Each element within the elicitation process was iteratively 
-Elicitation was conduct ach  Although workshops focussed on a single issue, it was important to continually address each issue in an iterative fashion.
+% Each element within the elicitation process was iteratively 
+% Elicitation was conduct ach  Although workshops focussed on a single issue, it was important to continually address each issue in an iterative fashion.
 The approach to ensuring a sound and sane network, was to directly address common issues that occur during the construction of Bayesian Networks using ellicitation as outlined by #TODO: Korb and Nicholson.
@@
 \subsubsection{Complexity without value}
-A very common impulse, when something isk nown about thep roblem, is to want to put it in the model.
+A very common impulse, when something is known about the problem, is to want to put it in the model.
 But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value).

### 2024-03-11 article.tex
methods - needs a final pass

@@
 In agriculture, the consideration of environment is critical to the success of the industry.
-The question of environmental sustainability has continued to grow in importance as further pressures such as climate change impact the industry TODO:reference.
-The question of sustainability entails the consideration of a multitude of factors, not only due to physical differences between locations/habitats but also due to priorities driven by a myriad of perspectives such as consumers, ecosystems, government and industry.
-It is important to consider each factor with respect to its relevant perspectives, and to be explicit about accompanying definitions of factors and perspectives.
+The question of environmental sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
+The question of sustainability entails the consideration of a multitude of factors, not only due to physical differences between locations/habitats but also due to priorities driven by a myriad of perspectives such as consumers, ecosystems, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
+It is important to consider each factor with respect to its relevant perspectives, and to be explicit how each of these factors and perspectives are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.
 
-To address the significant consideration of different perspectives, collaborative efforts are a useful tool to come to agreeance upon the significance of different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
-In Australia, views of both industry and consumer are united in their priority to improve and regulate resources inputs such as chemical use and be mindful of \citep{dumbrellComparingAustralianPublic2024}
+Collaboration between experts from different perspectives is a useful method to come to agreeance upon the significance of different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
+In Australia, views of both industry and consumer are united in their priority to improve greenhouse gas emissions and resources inputs through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
+Although there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
 
 Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being common \citep{gehringerMappingSustainabilityMeasurement2024}.
-Other approaches utilise the identification of key factors, and utilise their measurements as a proxy to indicate the impact to, or the health of, the environment #TODO:Ref.
-The measuring of sustainability through the use of these tools can help to manage risk and promote resilience for industries through identifying sustainable goals and the key factors of interest that contribute to the success of these goals \citep{klemesAssessingMeasuringEnvironmental2015} \citep{beckerSustainabilityScienceManaging2024}.
-Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method to achieve this in this study is through a Bayesian Network.
-#TODO: The definition of a Bayesian network needs to be way more polished
+Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or health of, the environment \citep{floresWhatSustainabilityWine2018}.
+The measuring of sustainability through the use of these tools can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}.
+Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
+
+\subsection{Bayesian Networks}
+
 A Bayesian Network is a graphical model, being comprised of nodes and edges.
-Uniquely, Bayesian Networks contain the operation within the nodes themselves instead of across the edges.
-This is done in the form probability tables, which are informed by the edges.
-There is simplicity within the calculations done within a node, as it is fundamentally achieved through sum and division operations; however great complexity is introduced when a node is informed by many parents, of which may also have many parents.
-The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes.
+Uniquely, Bayesian Networks contain the network's operations within the nodes themselves instead of across the edges.
+This is done in the form probability tables, with connections being informed by the edges.
+There is simplicity within the calculations done within a node, as it is fundamentally achieved through sum and division operations.
+However, great complexity is introduced when a node is informed by many parents, which can also have many parents themselves.
+The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes \citep{korbBayesianArtificialIntelligence2011}.
 The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.
 
-The use of a Bayesian Network allowed the ability to include perspectives from industry experts and create a causal structure.
-The graphical nature of the Bayesian Network also helped in the illustration of the model and conveying the complexity and relationship of different factors to one another as well as to vineyards' impact of the environment.
+The use of a Bayesian Network allows the ability to include perspectives from industry experts and create a causal structure.
+The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact \citep{pourretBayesianNetworksPractical2008}.
 Furthermore, data collected across Australia could also be used to help inform both scenarios and the model alongside expert opinion.
+
+The calculations of a Bayesian Network are based on Bayes' theorem, shown as follows
+\begin{equation}\label{bayesformula}
+P(A|B)= {P(B|A)P(A)}\over{P(B)}
+\end{equation}.
+Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
+Within a Bayesian Network, an event can be considered any given node.
+Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes.
+This is an iterative application of \ref{bayesformula}, which can be achieved through
+
+\begin{equation}
+        \mathbb(P) (X_{1}=x_{1},...X_{n}=x_{n})=\prod_{n}^{i=1}p(x_{i}|x_{Parents(i)})
+\end{equation},
+
+for a selected node $i$ given the parents and their local conditional distributions.
+
+The iterative nature, or the ability to show the difference in probable outcomes of different sets of events and their uncertainty allows for the ability to conduct inference.
+This type of Bayesian inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present.
+The sets of different outcomes is the stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods.
+
+One of the greatest abilities within this style of inference is Marginalization.
+In which, the outcome of a particular event can be determined irrespective of other outcomes.
+This type of marginalisation is intuitively represented as nodes conditional independence is illustrated inherently through the structure of the graph by its edges.
+TODO:
+Bayesian Networks created in this study were formalised using BayesFusion \citep{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities.
+The use of Bayes fuse software was used both through the GUI interface and the SMILE API \citep{bayesfusionGeNIeModelerUSER2022} system using C++ \citep{ISO:2012:III}.
 
@@
 The format followed recommendations from \cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}.
-Where, we progressed from problem definition, structure, parametarisation to validation.
-Experts were initially informed regarding the process to establish an understanding of what each step would be comprise of, as well as highlighting common pitfalls and how we would address them.
-With common problems being listed by authors such as:
+Where, we progressed iteratively through from problem definition, to structure, to parametarisation, and then to validation.
+Experts were initially informed regarding the process to establish an understanding of what each step would be comprised of, as well as highlighting common pitfalls and how we would address them.
+With common problems being listed by both authors being:
 \begin{enumerate}
-        \item Not understanding the problem context, complexity without value.
+        \item Not understanding the problem context
+        \item complexity without value
         \item Getting arc directions wrong
@@
 \end{enumerate}
-To address these issues, experts were kept well-informed of them as well as variable definitions and problem scope.
+To address these issues, experts were kept well-informed of them, as well as variable definitions and problem scope.
 Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency.
-Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel industry experts
+Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts
 
 Each workshop had a primary focus such as: scope, structure or parameterisation; with, prior concepts being built upon iteratively.
-The first important establishment was the scope of the network, and how well it could or couldn't be adapted to the wide variety of circumstances within the Australian winegrowing industry.
-Following this was the discussion around the structure of the network, entailing the detailing of relationships and stricter definitions of each factor to one another.
+The first important establishment was the scope of the network, and how well it could or couldn't be adapted to a wide variety of circumstances within the Australian winegrowing industry.
+Following this was the discussion around the structure of the network, which entailed the description of relationships and stricter definitions of each factor to one another.
 Finally, variables were paramatised using conditional probabilities.
@@
 To introduce new concepts and how they interacted, preliminary simplified versions (strawman examples) were provided to experts; with the intention of these examples to be examined, critiqued, and improved upon.
-The use of these strawman examples enabled a more engaged and effective review process, in which experts were initially able to interact with how these concepts would fit together with other elements of the model they had developed up to that point.
+The use of these strawman examples enabled a more engaged and effective review process.
+Experts were initially able to interact with elements of the model and see how they worked together.
 The strawman examples were crafted from a foundation of literature and data to offer a basic, layman's understanding of key factors and concepts, serving as a starting point for further development and discussion.
+
+\subsection{CPT Interpolating}
+
+As is often the case, the most arduous endeavour is to attribute probabilities to events defined within the Bayesian Network \citep{korbBayesianArtificialIntelligence2011}.
+Due to the growing complexity of the network throughout the study each event was described by binary classes.
+With the classes depicting a positive or negative environmental outcome.
+Furthermore, the complexity of the variables, particularly water, were overwhelmingly interrelated to operations across the vineyard.
+To attempt to capture this complexity but not dilute the ability to work with various scenarios the conditional probabilities were interpolated.
+
+This method utilised interpolation between two anchored points.
+One point represented the case of all factors being true/positive and the other represented all factors being false/negative.
+The interpolation was achieved by designating each factor an attributed weight.
+Where weights were indicative of a factors overall influence to its child node.
+During workshop discussion participants were the most comfortable using scores out of 10 to describe a factors influence its child node.
+
+Using this method, we calculate any given probability, by
+\begin{equation}
+        p=x\sum_{i}^{n} + y\sum_{m}^{i} 
+\end{equation},
+for n number of true or contributing factors and m false or not contributing factors. We know the solutions for when all contributing factors are true ($p_t$) or all were false ($p_f$). Where,
+\begin{equation}
+        p_t=x\sum_{i}^{n} 
+        \text{ and }
+        p_f=y\sum_{m}^{i}
+\end{equation}.
+From here values for $x$ and $y$ are able to be derived using the sum of the provided weights.
+
+\subsection{Validation}
+
+The method for validation sought to address concerns presented by \citep{pitchforthProposedValidationFramework2013}; this focussed on the nomological, face, content, concurrent, convergent, descriminant and predictive validity.
+This partly incorporated validations steps during the process of constructing the Bayesian network itself.
+Specifically when considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario.
+In part, the selection process for experts, aspired to be diverse within their regional knowledge and expertise in an attempt to broaden the ability to critique choices.
+Although it was agreed that multiple scenarios were well captured by the trees structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions.
+This requirement aligned with literature, which highlights how  regional variation is considered a driving factor for many vineyard outcomes and priorities \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
+
+The Face and content validity of the network was questioned directly by the expert panel through the structure and conditional probability phases.
+The choice of binary discretisation was due to two reasons; that it captured the relevant contribution to the node in question and limited the model from becoming to overly complex and circumstantial.
+This helped to avoid some overtly specific scenarios in favour for broader vineyard decisions; whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
+This approach went hand in hand with the content validation.
+Where, it was found that the limitation of the model was primarily regional, which aligned again with other researchers finds \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
+Specifically, the question of water resources, which was central to the model and highly interrelated \citep{carmonaUseParticipatoryObjectOriented2011}.
+
+Similarly, the convergent validity of the model was accomplished through the broader discretisation of nodes into binary form of positive or negatively affecting the environmental impact of the vineyard.
+Allowing a clear delineation in localised subnetworks within the model.
+The alignment of the model to other research helped in answering its concurrent validation.
+It was found that other studies emphasised the same variables, especially in the consideration of yield and regional factors that influence vineyard outcomes \cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}.
+Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}.
+
+The descriminant validation of the model was the most difficult.
+In that the definitions of each node changed over the course of the models inception.
+This brought the difficulty that nodes connected by edges would have to be reconsidered each time a definition changed.
+This issue was simply overcome through explicit definitions accessible to all participants and directly addressing issues caused by definitions before further developing the model.
+Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes from \citep{korbBayesianArtificialIntelligence2011}.
+
+The structure of the model itself was similar to other models in the presence of variables but differed in some of their relation due to the terminal node being environmental impact.
+The paramitisation of the nodes did differ to other studies as every node was thought of in regard to the terminal node and how they subsequently affected the environmental outcomes of a vineyard and not other priorities such as yield.
+The descriminant validity of the model was highlighted through the acknowledgement of the models requirement to be tuned to any specific wine region before being able to be properly employed.
+Furthermore the predictive validity was able to be well established through two methods, the use of a case study and the consideration of extreme outcomes.
+
+\subsection{Case study: Coonawarra}
+
+Due to the regional limitations of the model experts proposed a case study of a specific and well understood region: Coonawarra in South Australia.
+The choice of the region was due to the prevalence of data within the region, and around the region as well as expert understanding of the region's unique challenges and benefits to winegrowing.
+The Coonawarra model was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.
 

### 2024-03-11 article.tex
methods

@@
 The question of environmental sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
-The question of sustainability entails the consideration of a multitude of factors, not only due to physical differences between locations/habitats but also due to priorities driven by a myriad of perspectives such as consumers, ecosystems, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
-It is important to consider each factor with respect to its relevant perspectives, and to be explicit how each of these factors and perspectives are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.
+The question of sustainability requires the consideration of a multitude of factors, not only due to physical differences between locations/habitats but also due to priorities driven by a myriad of perspectives from as consumers, ecosystems, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
+It is important to consider each factor with respect to its relevant perspectives, and to be explicit in how each of these factors and perspectives are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.
 
-Collaboration between experts from different perspectives is a useful method to come to agreeance upon the significance of different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
-In Australia, views of both industry and consumer are united in their priority to improve greenhouse gas emissions and resources inputs through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
-Although there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
+Collaboration between experts from different perspectives is a useful method to reconcile opinions of the significance of different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
+In Australia, the views of both industry and consumer are united in their priority to improve greenhouse gas emissions and resource inputs through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
+While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
 
 Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being common \citep{gehringerMappingSustainabilityMeasurement2024}.
-Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or health of, the environment \citep{floresWhatSustainabilityWine2018}.
+Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citep{floresWhatSustainabilityWine2018}.
 The measuring of sustainability through the use of these tools can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}.
@@
 Uniquely, Bayesian Networks contain the network's operations within the nodes themselves instead of across the edges.
-This is done in the form probability tables, with connections being informed by the edges.
+This is done in the form of probability tables, with connections being informed by the edges.
 There is simplicity within the calculations done within a node, as it is fundamentally achieved through sum and division operations.
@@
 
-The use of a Bayesian Network allows the ability to include perspectives from industry experts and create a causal structure.
+The use of a Bayesian Network allows for the ability to include perspectives from industry experts and create a causal structure.
 The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact \citep{pourretBayesianNetworksPractical2008}.
@@
 Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
-Within a Bayesian Network, an event can be considered any given node.
+Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes.
 Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes.
@@
 \end{equation},
-
 for a selected node $i$ given the parents and their local conditional distributions.
@@
 This type of Bayesian inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present.
-The sets of different outcomes is the stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods.
+The sets of different outcomes then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods.
 
@@
 This type of marginalisation is intuitively represented as nodes conditional independence is illustrated inherently through the structure of the graph by its edges.
-TODO:
-Bayesian Networks created in this study were formalised using BayesFusion \citep{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities.
+
+Bayesian Networks created in this study were created using BayesFusion \citep{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities.
 The use of Bayes fuse software was used both through the GUI interface and the SMILE API \citep{bayesfusionGeNIeModelerUSER2022} system using C++ \citep{ISO:2012:III}.
@@
 Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency.
-Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts
+Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.
 
@@
 Due to the growing complexity of the network throughout the study each event was described by binary classes.
-With the classes depicting a positive or negative environmental outcome.
-Furthermore, the complexity of the variables, particularly water, were overwhelmingly interrelated to operations across the vineyard.
+With the classes depicting a positive or negative contribution to a vineyard's environmental outcome.
+Furthermore, the complexity of the variables, particularly water use, were overwhelmingly interrelated to operations across the vineyard.
 To attempt to capture this complexity but not dilute the ability to work with various scenarios the conditional probabilities were interpolated.
@@
 One point represented the case of all factors being true/positive and the other represented all factors being false/negative.
-The interpolation was achieved by designating each factor an attributed weight.
-Where weights were indicative of a factors overall influence to its child node.
-During workshop discussion participants were the most comfortable using scores out of 10 to describe a factors influence its child node.
+The interpolation was achieved by designating each factor an attributed weight; where, weights were indicative of a factor's overall influence to its child node.
+During workshop discussion participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.
 
-Using this method, we calculate any given probability, by
+Using this method, any given probability can be calculated using
 \begin{equation}
@@
 
-The method for validation sought to address concerns presented by \citep{pitchforthProposedValidationFramework2013}; this focussed on the nomological, face, content, concurrent, convergent, descriminant and predictive validity.
-This partly incorporated validations steps during the process of constructing the Bayesian network itself.
-Specifically when considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario.
+The method for validation sought to address concerns presented by \citep{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
+Validation steps were partly incorporated during the process of constructing the Bayesian network itself.
+Specifically when considering the nomological validity of the network; the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario.
 In part, the selection process for experts, aspired to be diverse within their regional knowledge and expertise in an attempt to broaden the ability to critique choices.
 Although it was agreed that multiple scenarios were well captured by the trees structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions.
-This requirement aligned with literature, which highlights how  regional variation is considered a driving factor for many vineyard outcomes and priorities \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
+This requirement aligned with literature, which highlighted how regional variation is considered a driving factor for many vineyard outcomes and priorities \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
 
@@
 The choice of binary discretisation was due to two reasons; that it captured the relevant contribution to the node in question and limited the model from becoming to overly complex and circumstantial.
-This helped to avoid some overtly specific scenarios in favour for broader vineyard decisions; whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
+This helped to avoid some overtly specific scenarios in favour for broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
 This approach went hand in hand with the content validation.
-Where, it was found that the limitation of the model was primarily regional, which aligned again with other researchers finds \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
+Where, it was found that the limitation of the model was primarily regional, which aligned again with the findings of other researchers \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
 Specifically, the question of water resources, which was central to the model and highly interrelated \citep{carmonaUseParticipatoryObjectOriented2011}.
 
-Similarly, the convergent validity of the model was accomplished through the broader discretisation of nodes into binary form of positive or negatively affecting the environmental impact of the vineyard.
-Allowing a clear delineation in localised subnetworks within the model.
-The alignment of the model to other research helped in answering its concurrent validation.
-It was found that other studies emphasised the same variables, especially in the consideration of yield and regional factors that influence vineyard outcomes \cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}.
+Similarly, the convergent validity of the model was accomplished through the broader discretisation of nodes into the binary forms of positive and negative affects on the environmental impact of the vineyard.
+This manner of discretisation allowed a clear delineation in localised subnetworks within the model.
+The alignment of the model to other research helped to further answer questions of concurrent validation.
+In that, it was found that other studies emphasised the same variables selected by our experts.
+This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes \cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}.
 Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}.
 
-The descriminant validation of the model was the most difficult.
-In that the definitions of each node changed over the course of the models inception.
+The discriminant validation of the model was the most difficult, as the definitions of each node changed over the course of the model's inception.
 This brought the difficulty that nodes connected by edges would have to be reconsidered each time a definition changed.
-This issue was simply overcome through explicit definitions accessible to all participants and directly addressing issues caused by definitions before further developing the model.
-Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes from \citep{korbBayesianArtificialIntelligence2011}.
+This issue was simply overcome through explicit definitions accessible to all participants, and by directly addressing issues caused by definitions before further development of the model.
+Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes \citep{korbBayesianArtificialIntelligence2011}.
 
 The structure of the model itself was similar to other models in the presence of variables but differed in some of their relation due to the terminal node being environmental impact.
-The paramitisation of the nodes did differ to other studies as every node was thought of in regard to the terminal node and how they subsequently affected the environmental outcomes of a vineyard and not other priorities such as yield.
-The descriminant validity of the model was highlighted through the acknowledgement of the models requirement to be tuned to any specific wine region before being able to be properly employed.
-Furthermore the predictive validity was able to be well established through two methods, the use of a case study and the consideration of extreme outcomes.
+The paramitisation of the nodes did differ to other studies, as every node was related and thought of with regard, to the terminal node and how they subsequently affected the environmental outcomes of a vineyard and not other more prevalent outcomes such as yield \citep{laurentReviewIssuesMethods2021}.
+The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being able to be properly employed.
+Furthermore, the predictive validity was able to be well established through two methods, the use of a case study and the consideration of extreme outcomes.
 
@@
 Due to the regional limitations of the model experts proposed a case study of a specific and well understood region: Coonawarra in South Australia.
-The choice of the region was due to the prevalence of data within the region, and around the region as well as expert understanding of the region's unique challenges and benefits to winegrowing.
+The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing.
 The Coonawarra model was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.

### 2024-03-11 draft.tex
draft emailed to kerrie, also using overleaf

--- 2024-03-11 article.tex
@@
-%%%%%%%%%%%%%%%
-% Paper setup %
-%%%%%%%%%%%%%%%
-
-% What is your topic?
-The topic of this paper is the environmental sustainability of vineyards within Australia.
-% What is the context for your reserach?
-The context of this research is that the Australian wine sector in general has gone through many tribulations due to economic, environmental and social pressures.
-Previously we attempted to highlight areas of concern through the use of statistical models, which were able to show strong correlations between various environmental and economic factors.
-However, discussions with industry and experts helped to identify that these relationships were not entirely causal, with some management and process of winegrowers obfuscating effects by directly contracting them.
-A key example of this was the lack of water use change during drought periods due to various methods that were used to obtain either more water or to circumvent the detrimental effects of lacking water resources.
-% What do you want to achieve?
-The identification of key factors; and their relation and contribution, direct or indirect, to the environmental sustainability of Australian winegrowing.
-% Are there any relationships you want to explore?
-This is key to this study. The relationships are in many ways more important to the research than the effects.
-
-%%%%%%%%%%%%%%%%
-% Working title
-%
 \title{Measuring environmental sustainability with Australian vine growers using Bayesian Networks}
-
-% Description
-% NB Avoid titles along the lines of: “Effects of ...”, “The role of ...”, etc.  Be specific about the effect and its significance so that your reader knows what is on offer.
-
-% For example, rather than write a title like “The effect of factor X on astrophysical properties of green cheese.”,
-
-% be specific about the effect and write something more like ...
-
-% “Factor X halves the lunar thermal diffusivity of  green cheese”.
-
-% You will usually find it easier to write an effective title if you make your title a sentence.
-
-% Notes
-% N/a
-
-%%%%%%%%%%%%%%%%%%%%
-% Intended readers
-%
-% David Klassen (wine maker Taylors)
-% Dpt Agriculture - EL worker
-        % They would like to know for policy
-% Lawson - asked about OOBNs
-% Winegrower - Someone from the limestones coast. The guy from Robe was interested.
-
-% Description:
-% Name 4 or 5 potential readers - give their names and why they would be interested  (e.g.
-“Ichabod Crane, paleo-fudgologist interested in polygalactic fudginomiality”, not “assorted paleo-fudgologists”).
-
-% Your readers should be outside your institution.
-
-% Notes
-% Many viticulturalists I know of are on the panel. It makes it hard to get one in particular.
-
-%%%%%%%%%%%%%%%%%%%%%
-% Anticipated Journal
-%
-% OIV Congress 2024
-
-% Descrption
-% Ensure that all readers are likely to read the nominated journal  (e.g.  few non-researchers read refereed academic journals; politicians simply don’t read).
-
-% Notes
-% Strangely this is less likely to be other researchers. Unless they are interested in Wine.
-
-%%%%%%%%%%%%
-% Question %
-%%%%%%%%%%%%
-
-% TODO: review the following questions:
-What are the key factors/indicators of environmental  sustainability in the australian winegrowing industry?
-How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
-What are the key factors that relate directly to environmental sustainability, and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?
-
-% Things to consider
-%
-% Why is the knowledge important?
-This was identified as a gap within our own prior research and is helpful in creating a basis for scenario assessment and comparison.
-This will allow a greater understanding of how these factors change within different scenarios; whether that be climate, region, business goal.
-% What is the significance?
-The significance is to bridge the gap between correlations and data to causal relationships.
-To inform growers using factors that are within their control, or how factors within their control are indfuenced by natural phenomenon.
-% How will the findings be utilised?
-These findings will be used to help inform the wider winegrowing community of what factors are most significant to environmental outcomes, and how they interact with one another.
-In practice this study aids a grower through informing them of how decisions impact environmental outcomes and how changing circumstance contribute to these factors and outcomes.
-% What improvements may be derived from this result?
-A wider more informed understanding of contributing factors to environmental impact and how different factors relate to one another to contribute to these findings.
-% Are the terms well defined?
-The terms are well defined. This was a key outcome of this project.
-% Do experts think your question is important/relevant/doable?
-Experts helped to guide this decision, and changed the trajectory of this project in response to data presented and how well they believed they could inform the study.
-
-% What is the nature of your question?
-%         who, what, where, when, why, how?
-What are the key factors that contribute to environmental impact within the Australian winegrowing industry?
-How do these key factors relate to each other and what are the factors that influence them?
-What are the decision that can be made by growers that can change the environmental outcomes of their vineyards?
-How do these factors chagne across well understood scenarios?
-% You can have more than one question.
-
-% What is the most important question your paper will pose?
-What are the key factors to environmental impact within the Australian winegrowing industry, and how are these factors related?
-% NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.
-
-% Why is the question/issue/problem worth examining?
-By examining the key and relevant factors to vineyards' environmental impacts we can better prepare for future changes in climate pressure, economic restrictions; that is we can better use this model to assess the potential environmental outcomes of the wine industry, as informed by experts, given potential upcoming challenges or changes.
-% Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.
-“Nothing much is known” is not sufficient justification by itself.
-You have to show why the gap in knowledge is important.
-Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
-The collection of data and subsequent statistical analytics can only go so far as to fill the gap between cause and effects within wiengrowing.
-This research helps to fully understand the relevant decisions being made, how they are informed and what the known outcomes are.
-This helps to align these results to data collected to show stronger causal relationships than pure correlative, or hypothetical postulations of statistical analysis.
-%%%%%%%%%%
-% Answer %
-%%%%%%%%%%
-
-% What is the answer to question
-%
-% 
-% NB  You must give a direct answer to the question posed.
-% Notes
-
-% Will the findings be considered significant?
-
-% How did you gather the evidence? 
-%
-% Briefly outline the methods you used to gather your evidence.
-
-% What is the main evidence?
-%
-% Briefly outline the key results.  Focus on outcomes.
-
-% What can you add to theory?
-%  
-% A research paper has to add to broader understanding. What will yours contribute?  Think about how your results and conclusions will change how people see the world.
-%
-% Many people have trouble with this section.
-Do not recycle the results.
-Focus on the conceptual models that explain why your results are as they are, or why they are different from what might have been expected.
-Your contribution may be something new or it may be confirmation of something already known but in a slightly different context.
-%
-% Sometimes the contribution to theory is not a simple answer but a better understanding of the questions that ought to be asked in future.
-%
-% Again, expect to draw heavily on the literature in framing your answer, but cite the literature only sparingly here (you can go into full detail when you prepare your discussion).
-
-% What can you add to practice?
-%
-% Superior research also has practical consequences.
-What are the consequences of your work?
-Think about how your results and conclusions might change what people do.
-Do not merely restate your results.
-
-%%%%%%%%%%%%%%%
-% Future work %
-%%%%%%%%%%%%%%%
-
-% What remains unresolved?
-% 
-% You may or may not have a lot to say here.  Some of it may be useful in your discussion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%       Workshop ideas      %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Ice breaker
-% - who are you what are you involved in.
-% Who knows who?
-%
-
-% Ask the expert team to nominate scenarios of interest then enter evidence into the BN to represent these scenarios.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Notes for this article! %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% The creation of the model was done in the following stages (this is on page xxiv):
-
-%  + The conceptual model
-%  + key sustainability indicators
-%  + Connection of key indicators to available measurable variables
-
-% The identified measurable variables were:
-
-% Econoomy (Farm to gate was used):
-%  + Economics
-        % + Debt
-        % + Assets
-        % + Investment
-%  + profitability
-        % + Interest
-        % + Income
-        % + Competitiveness
-% %  + Work force
-%         + Employment
-%         + Productivity
-%         + Management
-%  + market
-        % + Commodity prices
-        % + Supply
-        % + Risks
-%  + physicals
-        % + Efficiency
-        % + Resource
-        % + Inputs
-%  + commodity prices
-%  + Supply and risks
-
-% Social (across farm, factory and market)
-%  + employment
-        % + Labour
-        % + Training
-        % + Management
-%  + legal and ethics
-        % + Discrimination
-        % + Compliance (regulatory)
-%  + community
-        % + Culture
-        % + Value
-        % + Cohesion (participation/social responsibility)
-%  + health and safety
-        % + Animal welfare
-        % + occupational
-        % + Consumer
-%  + product
-        % + Nutrition
-        % + marketing
-
-% Environment
-%  + Reource Efficiency
-%         + Water
-%         + Energy & emissions
-%         + land and soil
-%  + Waste
-%         + Water Waste
-%         + Solid Waste
-
-% A high | low | medium score was used
-
-%%%%%%%%%%%%%%
-
-% The research for this project has identified that there is no uniform
-% way to measure sustainability, no uniform agreement on indicators
-% that could be used for measurement and even less agreement on
-% which metrics should be used to quantify these indicators. This is
-% best demonstrated that of the 72 triple bottom line frameworks, the
-% indicator water occurred in 64 of these frameworks, although there
-% appeared to be no standard metric identified to measure how water
-% was measured. This is an endemic problem with sustainability
-% measurement.
-
-% The forces which drive the social, economic and environmental sectors, the decision-makers who have the power or influence to accept or reject change, cannot be ignored, if change is to be achieved (van Kerkhoff and Lebel, 2006).It may be that part of the problem with the progress of sustainable development in the past has been the traditional divide between those undertaking the systematic research and those on the ground required to take up and act on the results of such.
-The dissemination of research results has usually only occurred on completion, in a unidirectional, linear communication (van Kerkhoff and Lebel, 2006), whereas, as grounded researchers explain, the ownership of ideas and a willingness to implement these relies on a more collaborative approach from the outset, before research has even commenced.
-It requires acknowledging that experts exist in all spheres and need to be able to share information and debate, in order to come to agreement on issues, assessment tools, priorities for remediation and an optimal approach to solving problems (Corbin and Strauss, 2008; Johnson and Mengersen, 2009), e.g.
-improving sustainability.
-
-% The sustainability Bayesian network model was constructed using
-% open source software and has been delivered as a software package.
-% A future project could focus on making it easier for a wider range of
-% relevant stakeholders to engage with the model. For example a
-% graphical user interface to the model could be developed and
-% then web-enabled so that stakeholders can readily interact with the
-% model and run scenarios.
-
-% The concept of sustainability has been described as the most
-% challenging policy concept ever developed (Spangenberg, 2004).
-% There are more than 100 definitions of sustainability and sustainable
-% development (Labuschagne et al., 2005). The most frequently cited
-% definition comes from the pivotal 1987 World Commission on
-% Environment and Development ‘Brundtland Report’, ‘development
-% that meets the needs of the present without compromising the ability
-% of future generations to meet their own needs’ (WCED, 1987).
-
-% It is necessary to understand the impacts of each system on one another, for example, the impact of industries on climate change, diminishing resources, economic shifts and social change.
-In turn, it is necessary to understand the impact of variables such as these on an industry, its future viability, its surrounding communities and the economies they feed or depend on (Brundtland, 2007).
-Thus, a tool is required that can measure complexity within and between systems and model how changes in one element, positive or negative, might flow on to others.
-Only then can strategies for sustainability be developed with reduced risk of unintended negative consequences (Johnson and Mengersen, 2012).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% references to check:
-
-% https://www.sciencedirect.com/science/article/pii/S1462901122003872
-
-%%%%
-% A triple bottom line planning tool for measuring sustainability; A systems approach to sustinability using the Australian dairy industry as a case study.
-
-% Capra, 1996; 
-% Johnson and Mengersen, 2012)
-
-% Murphy (2002)
-%  A diagram of graphical models!
-
-% The below references are from the previous OIV conference
-%       Interestingly the theme was sustainability.
-
-% 2023-3134: A DIGITAL TWIN APPLICATION FOR VINEYARDS SUSTAINABLE MANAGEMENT
-% Vittorio Faluomi: Tecnovine srl, Italy, vittorio.faluomi@tecnovine.com
-
-% 2023-3299: SUSTAINABLE PRODUCTION OF GRAPEVINE AND WINE IN TEXAS
-% Amit Dhingra: Department of Horticultural Sciences, USA, amit.dhingra@ag.tamu.edu
-
-% 2023-2958: DO SUSTAINABILITY CREDENTIALS NO LONGER SERVE AS A COMPETITIVE ADVANTAGE? - THE
-% QUEST FOR COMPETITIVE PARITY WITH REGARD TO SUSTAINABILITY IN THE WINE INDUSTRY
-% Barbara Richter: Hochschule Geisenheim University, Germany, barbara.richter@hs-gm.de
-
-% 2023-3028: THE BLOCKCHAIN FOR THE SUSTAINABILITY OF DESIGNATIONS OF ORIGIN AND QUALITY AGRI-
-% FOOD DISTRICTS: THE CASE OF VERMENTINO DI GALLURA D.O.C.G.
-% Graziella Benedetto, Forleo Marina: University of Sassari, Italy, gbenedet@uniss.it
-
-%  **************** This one looks super relavent
-% 2023-3044: SUSTAINABILITY ASSESSMENT: TESTING AND VALIDATING A HIERARCHICAL FRAMEWORK IN THE
-% PORTUGUESE WINE SECTOR CONTEXT.
-% Ana Trigo, Ana Marta-Costa, Rui Fragoso: Centre for Transdisciplinary Development Studies (CETRAD), University of Trás-
-% os-Montes e Alto Douro (UTAD)., Portugal, anatrigo@utad.pt
-
-% 2023-3146: USER-GENERATED CONTENT AND RELEVANCE OF SUSTAINABILITY ATTRIBUTES FOR WINE
-% CONSUMERS
-% Miguel-Ángel Gómez-Borja, Inmaculada Carrasco, Juan-Sebastián Castillo: Universidad de Castilla-La Mancha, Spain,
-% miguelangel.gborja@uclm.es
-
-% 2023-2844: THE JOURNEY TO FARMLAND SOIL RESTORATION: UNDERSTANDING AND MEASURING
-% PROGRESS TOWARDS SUSTAINABILITY
-% Alberto Acedo: Biome Makers, Spain, acedo@biomemakers.com
-
-% 2023-3239: ECOLOGICAL CRITERIA FOR A SUSTAINABILITY ASSESSMENT USING THE EXAMPLE OF THE ONLINE
-% CERTIFICATION "NACHHALTIG AUSTRIA" (SUSTAINABLE AUSTRIA)
-% Franz Rosner, Barbara Richter: Federal College and Research Institute for Viticulture and Pomology Klosterneuburg,
-% Austria, franz.rosner@weinobst.at
-
-% 2023-3084: THE IMPORTANCE OF RURAL EXTENSION AND ADVISORY SERVICES TO ACHIEVE A SUSTAINABLE
-% VITICULTURE IN A CLIMATE CHANGE SCENARIO
-% Ana Chambel: AVIPE, Portugal, ana.chambel@avipe.pt
-
-% 2023-3220: EXPLORING BAYESIAN BELIEF NETWORK TO SUPPORT SUSTAINABLE VINEYARD IRRIGATION IN
-% BRAZILIAN SEMI-ARID
-% Luiz Gustavo Lovato: UNICAMP, Brazil, luizglovato@gmail.com
-
-% PO-302
-% 2023-2856: DATA DRIVEN APPROACH TO ENERGY EFFICIENCY IN WINERIES
-% Gellio Ciotti, Marco Bietresato, Alessandro Zironi, Roberto Zironi, Rino Gubiani: Università degli Studi di Udine, Italy,
-% gellio.ciotti@uniud.it
-
-%%%%%%%%%%%%
-% Definitions:
-
-%%
-% Iterative Bayesian network developement cycle
-%
-% \autocite{johnsonIntegratedBayesianNetwork2009}
-% This article  illustrates a proposed integrated Bayesiannetwork  modeling  approach  using OOBNs within theiterative Bayesian network development cycle (IBNDC
-% ^ This is a really comprehensive and well written definition of object orientated bayesian networks!
-% 
-%
-%
-
-%%
-% integrated Bayesian networks
-%
-% The complex nature of environmental issues makes themideal case studies for the use of Bayesian networks as anintegration tool (Varis and Kuikka 1999; Uusitalo 2007;Barton et al. 2008), 
-%
-% Integrated models incorporate other types of tools like regression etc - it is literally what we are doing here.
-I would ask for a better definition from kerrie though.
-The term is used a lot but I cannot find an explicit definition.
-%
-
-%%
-% Self-organising systems.
-%
-% Sustainability is one such complex system.
-It comprises complex interacting factors and processes (e.g.
-in the context of the dairy study: farm, factory and market processes; and environmental, social and economic factors).
-It is self-organising; it does not require external intervention to thrive or deteriorate (e.g.
-an ecosystem can be sustainable through self-organisation).
-It can also exhibit emergent behaviour, since intervening in one part of the sustainability system can have unintended and quite extreme effects in seemingly unrelated parts of the system (Johnson and Mengersen, 2012).
-%
-% These systems are exactly what you think they are. It is described in physics, chemistry, social sciences and philosophy.
-% 
-% The wiki is quite informative.
-%https://en.wikipedia.org/wiki/Self-organization
-
-% Initiatives to improve the environmental impacts of the Australian Wine industry have been ongoing since the 1990s; with recommendations to implement strategies for national programs that would help educate industry members in sustainable practices (Keith Jones, 2002).
-The first legislative initiative to support national programs was the Environmental Management Guidelines for Vineyards in Western Australia during 2002 (Nind, 2002).
-The first national program was the Australian Wine Industry Stewardship, beginning shortly after, during 2004 (WFA, 2009).
-This program was replaced multiple times during the 2000s, first by the Australian Wine Environmental Stewardship, and then by EnviroWine, finally becoming EntWine in 2009.
-The period in the 2000s was further influenced by several key researchers and program leaders, where concurrently multiple regions developed approaches to sustainable management tied to sustainability programs (SWA, 2023).
-EntWine was eventually acquired by the Australian Wine Research Institute and Australian Grape & Wine during 2015; which would lead to its redevelopment into Sustainable Winegrowing Australia (SWA) during 2019/2020 (SWA, 2023).
-%             2.1.2. Previous Research and Motivation
-% During the period of 2010 to 2023 data was collected voluntarily from wine industry members through the national sustainability programs, ultimately being in SWA possession as of 2023.
-The data set was used in 2020 to analyse sustainable practices, resulting in the development of a Resource Intensity Score (RIS); where the RIS was a summary indicator value of a vineyard’s energy use, emissions and water use (Nayak et al., 2020).
-The analysis then fit vineyards’ RIS values to 55 variables sourced from 23 separate wine regions during the period of 2015 to 2018 through the use of Stepwise Regression modelling.
-It was found that the top 10% gross margin vineyards had a lower operating cost and a lower RIS score than vineyards in the bottom 10% gross margin.
-% The motivation for this thesis is to investigate the differences between the top 10% gross margin vineyards and those of the bottom 10%, hoping to uncover what the key differences were and to relate them to sustainable practices; as there is a known gap in the literature due to the difficulty to evaluate relationships using empirical evidence of both the environmental and economic impacts of sustainable practices in viticulture.
-This difficulty stems from data scarcity, industry complexity and transparency.
-While there have been attempts to fill these gaps, methodologies and indicators have lacked in ability to compare different regions and scales (Baiano, 2021).
-%             2.1.3. Economic Pressures
-% Historically strong demands for Australian wine have helped to create a thriving industry, however recently sharp reductions in exports to mainland China due to significant deposit tariffs have caused  a decline of 19% in Australian export value during the 2021-2022 financial year (see Figure 1) (Wine Australia, 2022).
-The pressure brought on by the drop in export value has been exacerbated by loss of tourism and labour due to the COVID-19 pandemic, global freight crisis, war in Europe and rising inflation (Wine Australia, 2021a, 2020).
-These pressures within the wine industry have trickled down to vineyards, where winemakers retain unwanted wine, creating an oversupply of grapes.
-Currently the proposed strategy to soften pressures proposed by Wine Australia includes initiatives focused on market diversification, and sustainability to build resilience in the coming years.
-% Figure 1:  The exports of Australian wine over time in Australian Dollars Free On Board, comparing exports between China and the rest of the world.
-This graphic is taken from the Wine Australia Annual Report of 2020-21(Wine Australia, 2022).
-%             2.1.4. Environmental Pressures
-% There are several environmental concerns that affect viticulture, including loss of soil quality, lack of rain, hail, disease, fire, and frost; with climate change exacerbating these issues.
-In 2020, 40,000 tonnes of grapes were lost across 18 different wine regions due to bush fires and smoke taint; the predicted incidence of wildfires is expected to increase (Canadell et al., 2021).
-In comparison to countrywide pressures such as drought, this damage made up only 3% of the total amount of grapes for that year; although acknowledged as a considerable loss on an individual basis, it was deemed to be only a minor national concern by Wine Australia when compared to other environmental pressures such as drought (Wine Australia, 2020).
-
-%
-%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
-% What the hell is a regional strategy
-% And how do you define, or know what trategy each region is using?
-%
-% Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.
-
-% This does not really address what the methods are - aside from classisifcation trees in the most vague sense.
-% What are the results briefly? why should someone read this article?
-% What is interesting - what will be discussed in the article with regard to these results? What makes me want to read the article?
-% And what is the take away point of the article? If I cant be bothered to read this article, what piece of knowledge can you leave mewiwth that I could recommend the article to someone else with?
 
@@
 
-% \citep{mayfieldDesigningExpertledBayesian2023} -> this reference also uses a similar method which we can cite alongside everything else.
-% % These are transcribed notes from Korb & Nicholson:
+\section{References}
 
-% \citep{korbBayesianArtificialIntelligence2011} Korb & Nicholson describe three major issues in the creation of Bayesian Networks though knowledge Engineering:
-% - Generating Arc Structure
-% - Parametarisation
-% - dealing with utilities
+\bibliography{references} % This points to the references.bib file - the file extention is automatically added.
 
-% Each element within the elicitation process was iteratively 
-% Elicitation was conduct ach  Although workshops focussed on a single issue, it was important to continually address each issue in an iterative fashion.
-The approach to ensuring a sound and sane network, was to directly address common issues that occur during the construction of Bayesian Networks using ellicitation as outlined by #TODO: Korb and Nicholson.
-These issues are similarly highlighted by #:TODO: Pitchforth.
+\end{linenumbers}
+\end{document}
 
-Transparency with the expert panel was a key ingredient with this approach, highlighting explicitly what these problems were and how we would overcome them.
-This included agreeing upon definitions of each node before connecting edges between them.
-
-Although originally multiclass nodes existed, the bayesian network was altered to only include binary class nodes. Each edge between a node had to answer the following questions:
-\begin{enumerate}
-        \item Are the nodes in the BN the right ones?
-        % \item Are the state spaces (values) for each node correct?
-        \item Are the arcs right?
-\end{enumerate}
-If the answer to any of the above questions was no; then the structure was not considered sufficiently defined.
-Although we explicitly defined the structure of the BN prior to CPT parametarisation.
-This process continued when adding conditionaly probability values.
-The entire process of construction iinvolved the steps:
-\begin{enumerate}
-        \item exposing the panel to a strawman argument/model/definition
-        \item Outlining the model and the process involved in defining the structure of a BN
-        \item The expert panel reviewing possible nodes and arcs and definitions
-        \item Defining their own structure, node or term.
-        \item Agreeing upon the final definition, structure or model.
-\end{enumerate}
-\subsubsection{Trying to build the full model all at once}
-
-Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
-\begin{enumerate}
-        \item dividing models into subcomponents
-        \item breaking down the problem into a single target variable
-        \item reducing the scope of the problem
-        \item Setting a single time frame for the problem
-\end{enumerate}
-The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
-Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards.
-This also reduced the BN to a single terminal node.
-It was further decided to create the BN as a single season to limit its complexity.
-
-\subsection{The problem}
-\subsubsection{Not understanding the problem context, complexity without value.}
-It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
-\begin{enumerate}
-        \item what do you want to reason about?
-        \item What dont you know?
-        \item What information do you have?
-        \item What do you know?
-These questions are well addressed in prior research.
-The creation of baseline models showed strong linear relationships between many variables.
-The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability.
-here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
-\subsubsection{Complexity without value}
-A very common impulse, when something is known about the problem, is to want to put it in the model.
-But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value).
-Instead, the knowledge engineer must focus on the problem:
-"Which of the known variables are most relevant to the problem?"
-- This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential probelsm that will come with a cumbersome model.
-\end{enumerate}
-\subsection{Structure - Nodes}
-The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
-\begin{enumerate}
-        \item Getting the node values wrong
-        \item Node values aren't exhaustive
-        \item Node values aren't mutually exclusive
-        \item Incorrect modelling of mutually exclusive outcomes
-        \item Trying to model fuzzy categories
-        \item Confusing state and Probability
-        \item Confusion about what the node represents
-\end{enumerate}
-Two major strategies were employed to overcome these problems.
-Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node.
-For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
-\subsection{Structure Arcs}
-\subsubsection{Getting the arc directions wrong}
-Arc directions are commonly wrong for the following reasons:
-\begin{enumerate}
-        \item Modelling reasoning rather than causation
-        \item Inverting cause and effect
-        \item Missing variables
-\end{enumerate}
-To note: Korb and Nicholson do not actually suggest a method for overcoming these problems.
-There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation.
-It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
-\subsubsection{Too many parents}
-Sometimes it is unavoidable that a node is affected by many factors, or other nodes.
-There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child.
-This technique was employed in the creation of the structure of the BN with the expert panel.
-\subsection{Parameters}
-\subsubsection{Experts estimates of probabilities are biased}
-\begin{enumerate}
-        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
-        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
-        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison.
-"Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
-        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.
-
-\end{enumerate}
-We have attempted to overcome this with two methods.
-A diverse and varried expert panel.
-Those participanting have experience in multiple vineyards as managers and other duties as well as the panel itself having varied manager/owners from different regions and scale.
-With some experts being more specialised in specific areas such as agro-chemicals.
-\subsubsection{Inconsistent probabilities}
-The collection of probabilities for when the CPT is large can result in inconsistent probabilities.
-The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
-The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}.
-In this study we overcame this through the use of worded response such as high and low.
-We then assigned probabilities to those broader cases.
-We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
-% \item Inconsistent "filling in" of large CPTs:
--       -       - Being dead certain.
-\subsubsection{Incoherent probabilities (not summing to 1)}
-We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
-\subsubsection{Being dead certain}
-It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
-Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.
-
-\citep{morganUncertaintyGuideDealing1990}
-Two attributes of good elicitation process are:
-\begin{enumerate}
-        \item The expert should be apprised of what is known about the process, especially the nearly universal tendency to overcomefidence and other forms of bias.
-In order to avoid some problems, values should be elicited in random order and the expert not given feedback on how the different values fit together until a complet set has been elicited.
-        \item The elicitation process is not simply one of requesting and recording numbers but also one of the refining the definitions of variables and terms to be used in the model.
-What values are elicited depends directly upon the interpretation of terms and these should be made as explicit as possible and recorded during the elicitation.
-This is part of the process management described earlier.
-\end{enumerate}
--
-
-\citep{Boneh2021} Boneh, T.
-(2010).
-Ontology and Bayesian decision networks for supporting the meterological forecasting process.
-Ph.
-D thesis, Clayton School of infomration technology, Monash university
-Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:
-- Bayesian Network Structure
-- Probability Parameters
-- Decision Structure
-- Utilities Preference
-
-Pitchforth \citep{pitchforthProposedValidationFramework2013} agrees with this style of structure naming these steps as:
-- Structure
-- Discretisation
-- Parametarisation
-- Model behaviour
-- Validation
-
-Korb & Nicholson have a similar view to Pitchforth. utilising a waterfall style developemental approach which include 5 stages:
-- Building the BN
--       - Structure
--       - Parameters
--       - Preferences
-- Validation
--       - Sensitivity Analysis
--       - Accuracy testing
-- Field testing
--       - Alpha/Beta testing
--       - Acceptance testing
-- Industrial use
--       - Collection of Statistics
-- Refinement
--       - Updating procedures
--       - Regression testing
-
-Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)
-
-With validation incorporating the expert scrutiny of the models begaviour for scenarios, as well as comparing this to both data and other literature.
-
-\subsection{Structure and Conditional Probabilities}
-
-\subsection{Validation}
-
-\citep{korbBayesianArtificialIntelligence2011}
-
-% Abstract
-
-1. Introduction to Methodology
-
-    Brief overview of the research approach and the rationale behind using a Bayesian Network (BN) model for sustainability assessment in viticulture.
-    Mention of the collaborative expert elicitation process and the sequential workshops that shaped the model development.
-
-2. Identification of Sustainability Indicators
-
-    Description of the process for selecting sustainability indicators, including the use of data from Sustainable Wine Australia.
-    Criteria for indicator selection, focusing on relevance to environmental, economic, and social dimensions of sustainability in winegrowing.
-
-3. Expert Elicitation Process
-
-    Overview of the expert panel composition and the expertise represented.
-    Objectives and structure of the expert elicitation process, highlighting the series of workshops conducted.
-
-Workshop 1: Variable Review and Straw Man Model Introduction
-
-    Objectives: To agree on the sustainability indicators and introduce the initial straw man model.
-    Activities: Discussion on indicator relevance and definitions; presentation of the straw man model.
-    Outcomes: Agreement on initial set of variables and conceptual understanding of the model's direction.
-
-Workshop 2: Model Structure Refinement and Interpolation Method Introduction
-
-    Objectives: To refine the model's structure and address the complexity of CPTs through an interpolation method.
-    Activities: Examination of variable relationships; identification of complex CPTs; proposal of the linear interpolation method.
-    Outcomes: Revised model structure; decision to develop and implement the interpolation method for complex CPTs.
-
-Workshop 3: Finalization of CPTs and Case Study Selection
-
-    Objectives: To finalize CPT values using the interpolation method and select a case study for model application.
-    Activities: Presentation and application of the interpolation method; finalization of CPT values; selection of the Coonawarra wine region for the case study.
-    Outcomes: Completion of model parameterization; selection of case study region emphasizing the model's practical application.
-
-4. Development and Implementation of the Interpolation Method
-
-    Detailed explanation of the linear interpolation method developed to manage the complexity of CPTs for variables with extensive connections.
-    Justification for choosing this method and its anticipated impact on the model's usability and accuracy.
-
-5. Case Study Application: Coonawarra Wine Region
-
-    Rationale for selecting the Coonawarra wine region as a case study to apply and test the BN model.
-    Brief description of how the model was applied to this specific context, including any regional data used and adjustments made for the case study.
-
-6. Model Validation
-
-    Overview of the validation process employed to ensure the accuracy and reliability of the BN model.
-    Description of internal and external validation measures, including expert review and comparison with independent datasets.
-
-7. Conclusion
-
-    Summary of the methodological approach, emphasizing the collaborative expert elicitation process and the innovative solutions developed for model construction and parameterization.
-    Brief mention of the significance of the methodology for sustainability assessment in viticulture and potential implications for future research and practice.
-
-\section{Title}
-A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.
-
-\section{Abstract}
-
-The assessment of environmental sustainability in the Australian winegrowing industry remains a complex issue involving changing and compounding factors.
-To address this, we developed a Bayesian Network (BN) using data and expert elicitation to summarise the key factors, their relationships, and how they come together to influence vineyards' environmental outcomes.
-The study leveraged diverse expert perspectives to mitigate biases in probability estimations and promote discourse.
-
-The development of the BN involved an iterative process, including variable selection and definition, the defining of model structure and variable relationships, and finally the determining of relationship significance through probabilities.
-Expert input was pivotal in structuring the BN model, ensuring relevance to industry, and how a variables influence changed across regions and scenarios.
-
-Due to the possible variation in any given vineyard scenario the BN model was expanded to review a case study of the Coonawarra wine region in South Australia.
-This highlighted regional differences between growers whilst also maintaining the significance of industry-wide concerns such as the use of agrochemicals.
-To promote accessibility and scrutiny the BN was further developed into an application, allowing the possibility of further industry and stakeholder feedback; enabling a systematic re-evaluation of significant factors to the wine growing industry and how they change over time.
+\endinput

### 2024-05-21 article.tex
minor edits - included introduction start!

@@
 Previously we attempted to highlight areas of concern through the use of statistical models, which were able to show strong correlations between various environmental and economic factors.
-However, discussions with industry and experts helped to identify that these relationships were not entirely causal, with some management and process of winegrowers obfuscating effects by directly contracting them.
+However, discussions with industry and experts helped to identify that these relationships were not entirely causal, with some management and process of winegrowers obfuscating effects by directly addressing them.
 A key example of this was the lack of water use change during drought periods due to various methods that were used to obtain either more water or to circumvent the detrimental effects of lacking water resources.
@@
 %
-\title{Measuring environmental sustainability with Australian vine growers using Bayesian Networks}
+\title{Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards}
 
@@
 
-% Descrption
-% Ensure that all readers are likely to read the nominated journal  (e.g.  few non-researchers read refereed academic journals; politicians simply don’t read).
-
-% Notes
-% Strangely this is less likely to be other researchers. Unless they are interested in Wine.
+% TODO: The original conference has fallen through we will need somewhere else.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Significance and Impact %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Highlight the importance of this
+
+% Stress the practical implications and potential benefits for winegrowers.
+
+%  Explain how your research could influence policy and practice?
+% TODO: How is this done in academia? The result should be measurable? yet many papers do not have impact or it would be considered "industry"? what is the noemclature of this?
+
 %%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% TODO: I believe this is the diary industry paper.
 
@@
 %%%%%%%%%%%%%%
+
+% Introduction?
+
+% This research provides valuable insights and data that can inform and guide decisions made by policymakers and industry leaders in the Australian winegrowing sector.
+By identifying key sustainability factors and their interactions, this study offers evidence-based recommendations that can support the development of more effective and sustainable agricultural practices and policies.
 

### 2024-06-03 article.tex
Polished Questions in the results section

@@
 How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
-What are the key factors that relate directly to environmental sustainability, and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?
+What are the key factors that relate directly to environmental sustainability?
+- and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?
 
@@
 
+\section{Results}
+
+    What are the factors of environmental sustainability in the Australian winegrowing industry?
+        Purpose: Explore and understand the both the literature and industry perspectives on this.
+        Results Literature review. Industry list of factors.
+
+    How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
+        Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
+        Results: Use the agreed upon definitions to fully realise factors and their impact.
+
+    What are the relationships between these factors in the Australian winegrowing industry?
+        Purpose: Explore and understand the causal and correlated relationships among the factors.
+        Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
+
+    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
+        Purpose: Examine regional differences and tailor sustainability strategies.
+        Results: Compare the generic model to the Coonawarra model.
+Acknowledge there is more work to be done here due to the amount of regions across Australia and the world.
+Prevous work also helps to illustrate these differences.
+
+    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
+        Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
+        Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.
+
+    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are percieveed to directly impact environmental sustainability.
+        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
+
+Structuring the Results Section Based on These Questions:
+Introduction to Results
+
+    Content: Briefly restate the refined research questions.
+    Explanation: Explain the approach to answering these questions using the BN model and CPT values.
+
+Primary Factors Identification
+
+Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+
+    Content: Present the primary factors identified through your analysis.
+    Data: Use the rigorous definitions and the generic BN to highlight these factors.
+    Figures/Tables: Include a table or figure showing the key factors and their relative importance.
+
+Quantitative Measurement and Analysis
+
+Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?
+
+    Content: Describe the methods used to measure and analyze the key factors.
+    Data: Show measurements and analytical results from the CPT values in the specific BN models.
+    Figures/Tables: Include charts or tables showing the measurements and analyses.
+
+Relationships Between Factors
+
+Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
+
+    Content: Discuss the direct and indirect relationships identified.
+    Data: Present interaction diagrams or tables.
+    Figures/Tables: Include a BN tree diagram illustrating these relationships.
+
+Regional Variations
+
+Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
+
+    Content: Compare the key factors and their impacts across different regions.
+    Data: Present comparisons between the two specific BN models from different growers.
+    Figures/Tables: Include figures comparing regional differences.
+
+Scenario Analysis
+
+Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
+
+    Content: Analyze the impact of different scenarios on environmental sustainability.
+    Data: Use scenario-based BN queries to show changes in key factors and their impacts.
+    Figures/Tables: Include charts or tables summarizing the scenario analysis results.
+
+Example Framework for Presenting Results:
+Introduction to Results
+
+"The results of this study are structured to address five primary research questions aimed at understanding the key factors and their interactions affecting the environmental impact of vineyards in the Australian winegrowing industry.
+The analysis leverages Bayesian Network models to provide a comprehensive view of these factors and their contributions."
+Primary Factors Identification
+
+Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+Results:
+
+    Identified Factors: Water usage, pesticide application, soil management, etc.
+    Data Source: Defined terms provided by industry experts and the generic BN model.
+    Figures: Table 1 shows the key factors and their relative importance derived from the BN analysis.
+
+Quantitative Measurement and Analysis
+
+Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?
+Results:
+
+    Measurements: Quantitative analysis of key factors using CPT values from two specific BN models.
+    Data Source: CPT values from BN models of two growers.
+    Figures: Table 2 presents the measurements and analysis results.
+
+Relationships Between Factors
+
+Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
+Results:
+
+    Interactions: Direct and indirect relationships as illustrated by the BN model.
+    Data Source: Generic BN model and specific models.
+    Figures: Figure 1 illustrates the BN tree diagram showing these relationships.
+
+Regional Variations
+
+Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
+Results:
+
+    Regional Variability: Comparison of factors and impacts across regions using specific BN models.
+    Data Source: BN models from two growers in different regions.
+    Figures: Figure 2 compares the BN models for different regions.
+
+Scenario Analysis
+
+Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
+Results:
+
+    Scenarios: Impact analysis under different scenarios using BN models.
+    Data Source: Scenario-based BN queries.
+    Figures: Table 3 summarizes the scenario analysis results.
+
+This refined approach ensures that your Results section directly addresses your research questions and clearly presents your findings.
+Let me know if there are specific details or sections you’d like further refined!
+
 \section{Title}

### 2024-06-04 article.tex
addeed results sub headings

@@
 
-    What are the factors of environmental sustainability in the Australian winegrowing industry?
-        Purpose: Explore and understand the both the literature and industry perspectives on this.
-        Results Literature review. Industry list of factors.
-
+\subsection{Industry definitions}
 How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
@@
 Results: Use the agreed upon definitions to fully realise factors and their impact.
+
+\subsection{Comparative Analysis of Literature and Industry Perspectives}
+    What are the factors of environmental sustainability in the Australian winegrowing industry?
+        Purpose: Explore and understand the both the literature and industry perspectives on this.
+        Results Literature review. Industry list of factors. Mind Map? Leximancer network.
+        - Use the same words as the definitions in the search to show the parralels and differences.
 
@@
 
+        \subsection{Sustainability in Coonawarra Winegrowing: Key Factors and Influences}
+        Sustainability in Coonawarra Winegrowing: Key Factors and Influences
     How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
@@
 
+\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
     What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?

### 2024-06-04 article.tex
updated results order/flow

@@
     What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
-        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are percieveed to directly impact environmental sustainability.
+        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
         Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.

### 2024-06-11 article.tex
searches and .bibs

@@
 
+Table of definitions
+
 \subsection{Comparative Analysis of Literature and Industry Perspectives}
@@
 
+Leximancer figure
+
+\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
+    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
+        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
+
     What are the relationships between these factors in the Australian winegrowing industry?
@@
 
-\subsection{Sustainability in Coonawarra Winegrowing: Key Factors and Influences}
+Figure of General model
+
+\subsection{Sustainability specifics: Coonawarra Winegrowing}
         Sustainability in Coonawarra Winegrowing: Key Factors and Influences
+    #TODO: what are the regional specifics of coonawarra
     How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
@@
 
-    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
+    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
         Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
@@
 
-\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
-    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
-        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
-        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
+Figure Marcel + robyn BNs
 
+% =================================
 Structuring the Results Section Based on These Questions:

### 2024-06-11 article.tex
searches and .bib
editted results

@@
 Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
-
+\subsection{Literature Review}
+#TODO:
 \subsection{Bayesian Networks}
@@
 Furthermore, the predictive validity was able to be well established through two methods, the use of a case study and the consideration of extreme outcomes.
+
+\subsection{Sensitivity analysis}
+
+The sensitivity analysis conducted in this study utilised the Bayesian Network software GeNie, implementing the algorithm developed by \cite{article}; an optimisation of \autocite{Castillo1996ANM} and \cite{Gaag1998PracticableSA}.
+The method allows for efficient computation of the influence of parameter variations on the output probabilities of a Bayesian network, making it particularly suitable for complex models.
+Sensitivity was calculated on the terminal node 'Environmental Impact' to reflect its sensitivity to changes in other nodes.
+
+The process utilises two outward and an inward propagation across a junction tree, a data structure representing the Bayesian network.
+These propagations are essential for establishing the necessary cliques that allow for the calculation of the sensitivity function using the coefficients $\gamma$ and $\delta$.
+
+These coefficients are used in determining evidence through
+
+$$ y = {{p(a, e)(x)}\over{p(e)(x)}}={{\alpha x + \beta}\over{\gamma x + \delta}} $$.
+
+Where $y$ is the posterior marginal of interest, given evidence $e$, with respect to the parameter $x$.
+
+% y - a posterior marginal of interest
+% e - evidence
+% x - all possible probability parameters
+% a - node of interest
+% $$ y = p(a|e)$$
+
+% $$ y = \alpha x + \beta $$
+
+% marginal distribution of any given parent node of a - any given node parent of a
+% b - the ith given parent node of a
+% pi - the parent nodes of the b ith node
+% $$ x = p(b_{i}|\pi) $$
+
+% $$ p(e)(x) = \gamma x + \delta $$
+
+% For each parameter under investigation, the sensitivity function 
+% $$ y=\alpha x + \beta x $$
+
+% y=αx+βγx+δy=γx+δαx+β​ is determined, where yy represents the posterior marginal probability, and xx is the parameter in question.
+The coefficients (αα, ββ, γγ, δδ) in this function are computed using the results from the propagations, ensuring computational efficiency.
+
+The methodology is extendable to n-way sensitivity analysis, allowing for the examination of the joint effects of multiple parameters.
+This involves identifying the relevant parameters and their influence on the posterior marginals using the same propagation strategy multiple times.
+
+By employing this method, the sensitivity analysis avoids the extensive computational demands of traditional brute-force approaches, which require numerous network evaluations.
+Instead, this approach ensures that all potential parameters are considered with minimal computational overhead; allowing the use of multiple scenarios based off different evidence.
 
@@
 
-Table of definitions
+\ref{table:definitions}
+
+The key factors identified were defined as shown in Table 1.
+By utilising these definitions, each factor's contribution to environmental sustainability was assessed.
+The definitions provided a clear framework for measurement, ensuring that the factors could be consistently evaluated.
+
+The quantification of each factor allowed for a systematic analysis of their impacts.
+For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact.
+Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).
+
+By applying these definitions, the study effectively translated the qualitative aspects of environmental sustainability into usable metrics.
+This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships.
+
+The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving environmental sustainability; allowing each factor's contribution to be clearly understood and relationships  explicitly defined.
 
@@
 
-Leximancer figure
+        TODO: write a summary description of the leximancer outputs.
 
 \subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
-    What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
-        Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
-        Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
-
-    What are the relationships between these factors in the Australian winegrowing industry?
-        Purpose: Explore and understand the causal and correlated relationships among the factors.
-        Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
-
-Figure of General model
+    % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+    %     Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
+    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
+
+    % What are the relationships between these factors in the Australian winegrowing industry?
+    %     Purpose: Explore and understand the causal and correlated relationships among the factors.
+    %     Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
+
+\label{figure:generalBN}
+
+The relationships between the nodes defined by the industry panel are depicted in~\ref{figure:generalBN}.
+The figure highlights which factors are influenced by others.
+For instance the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
+It also illustrates the complex nature of variables such as water and their interrelatedness.
+
+The BN provided a comprehensive overview of how these factors interact, showing not only direct relationships but also how changes in one factor can propagate through the network to affect others.
+This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry.
+
+By using the generic BN, the study was able to illustrate the complexity of interactions that define environmental sustainability in Australian winegrowing.
+
+% Comparing this with the data from Sustainable Winegrowing Australia (SWA), it was evident that the factors identified in the BN align with the critical areas SWA focuses on, such as water use, greenhouse gas emissions, and agrochemical use.
+This alignment reinforces the importance of these factors and supports the findings of the BN analysis.
+% What are the relationships between these factors in the Australian winegrowing industry?
+
+% Purpose: Explore and understand the causal and correlated relationships among the factors.
+
+TODO: compare these relationships to that of leximancer
 

### 2024-06-11 article.tex
results template to get started on descriptions

@@
 
-\label{figure:generalBN}
+\begin{figure}[h!]
+    \centering
+    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
+    \caption{The resultant Bayesian network after initial discussions of how factors that contribute to environmental impact are related.
+Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}
+    \label{fig:generalBN}
+\end{figure}
 
@@
 
-TODO: compare these relationships to that of leximancer
+% TODO: compare these relationships to that of leximancer
 
 \subsection{Sustainability specifics: Coonawarra Winegrowing}
-        Sustainability in Coonawarra Winegrowing: Key Factors and Influences
-    #TODO: what are the regional specifics of coonawarra
-    How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
-        Purpose: Examine regional differences and tailor sustainability strategies.
-        Results: Compare the generic model to the Coonawarra model.
+    %     Sustainability in Coonawarra Winegrowing: Key Factors and Influences
+    % #TODO: what are the regional specifics of coonawarra
+    % How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
+    %     Purpose: Examine regional differences and tailor sustainability strategies.
+    %     Results: Compare the generic model to the Coonawarra model.
 Acknowledge there is more work to be done here due to the amount of regions across Australia and the world.
@@
 
-    How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
-        Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
-        Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.
-
-Figure Marcel + robyn BNs
+    % How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
+    %     Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
+    %     Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.
+
+\begin{figure}[h!]
+    \centering
+    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
+    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}
+    \label{fig:coonawarra_bn}
+  \end{figure}
+
+% TODO: the exclusion of renewable fuels due to none being used in coonawarra
+% the difference in vineyard floor management and its relationship to tractors
+% The influence of compost, soil depth and clay content.
+although not specifically significant due to not listing the CPTs - it was highlighted as significant with different influence values depending on the direct field in question and not just which vineyard.
+% variation occurs all the way to the vine level!
+
+  This subsection examines how the identified key factors impacting environmental sustainability vary across different wine regions in Australia, with a focus on Coonawarra.
+By comparing the generic Bayesian Network (BN) model to the Coonawarra-specific model (Figure \ref{fig
+  } and Figure \ref{fig
+  }), we identify regional characteristics that influence these variations.
+
+  The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors like soil management practices show regional variation.
+The Coonawarra model highlights the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
+It is important to acknowledge that this analysis is preliminary and further work is required to cover the numerous wine regions across Australia and globally.
+Previous studies have also illustrated similar regional differences, underscoring the complexity and necessity of localised sustainability assessments.
+
+  By using Conditional Probability Tables (CPTs) within the BN, the significant contributions of different variables to environmental sustainability in Coonawarra were assessed. Figures \ref{fig
+  } and \ref{fig
+  } illustrate these networks with nodes coloured according to their sensitivity values relative to environmental impact.
+
+  The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact.
+For instance, the Coonawarra-specific model demonstrates that changes in water management practices have a higher sensitivity to environmental impact compared to the generic model.
+This highlights the critical areas where regulatory and environmental interventions could have the most substantial effect.
+
+  By assessing the BN, it becomes evident which factors are the most influential in driving environmental sustainability in Coonawarra.
+This detailed evaluation helps prioritize actions and policies that could lead to significant improvements in the region's sustainability practices.
 

### 2024-06-11 article.tex
eod back up

@@
 
-  The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors like soil management practices show regional variation.
+The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors such as soil show variation not only at a regional level but sometimes at the paddock level as described by the expert panel.
 The Coonawarra model highlights the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
-It is important to acknowledge that this analysis is preliminary and further work is required to cover the numerous wine regions across Australia and globally.
-Previous studies have also illustrated similar regional differences, underscoring the complexity and necessity of localised sustainability assessments.
+It is important to acknowledge that this analysis also illustrates that further work would be required to describe other regions or specific vineyards.
+
+The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact.
+For instance, the Coonawarra-specific model demonstrates that the significance that pest/disease, and agrochemicals have a higher sensitivity to environmental impact compared factors such as green house gas emissions.
+Importantly that these sensitive factors also link greatly to one another, highlighting how critical areas for regulatory and environmental interventions can be to multiple factors beyond their specific target.
 
@@
 
-  The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact.
-For instance, the Coonawarra-specific model demonstrates that changes in water management practices have a higher sensitivity to environmental impact compared to the generic model.
-This highlights the critical areas where regulatory and environmental interventions could have the most substantial effect.
-
 By assessing the BN, it becomes evident which factors are the most influential in driving environmental sustainability in Coonawarra.

### 2024-06-18 article.tex
added definitions table

@@
 Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
+
 \subsection{Literature Review}
 #TODO:
+
 \subsection{Bayesian Networks}
@@
 
-\subsection{CPT Interpolating}
+\subsection{CPT interpolating}
 
@@
 Where $y$ is the posterior marginal of interest, given evidence $e$, with respect to the parameter $x$.
+
+% FIXME: should I extrapolate on this method?
 
@@
 \end{enumerate}
+
 \subsection{Structure - Nodes}
@@
 For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
+
 \subsection{Structure Arcs}
@@
 This technique was employed in the creation of the structure of the BN with the expert panel.
+
 \subsection{Parameters}
@@
 \subsection{Industry definitions}
+
 How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
@@
 
-\ref{table:definitions}
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}[h]\ref{table:definitions}
+    \begin{tabular}{@{}llll@{}}
+    \toprule
+    \textbf{Variable name} & Definition & \textbf{Ideal Class} & Not Ideal Class \\ \midrule
+    \textbf{Water use} & Total amount of water used by a vineyard in a financial year (ML/Ha) & \textbf{Low} & High \\
+    \textbf{Agrochemical type} & When selecting agrochemicals, those which are less hazardous to beneficial organisms and/or have a lower environmental impact are considered & \textbf{Yes} & No \\
+    \textbf{Spray application number} & Number of foliar spray applications used to control pests and diseases (spray applications/Ha/FY) & \textbf{Low} & High \\
+    \textbf{Agrochemical legislation} & The legislated regulations regarding agrochemical use as specified by the APVMA.
+Dog book recommendations are further restrictions for export wine production and to protect the reputation of Australian wine.
+& \textbf{Yes} & No \\
+    \textbf{Vineyard floor management} & Proportion of vineyard floor covered with a cover crop. & High & \textbf{Low} \\
+    \textbf{Pest and disease management methods} & All available methods of management are considered before a management program is chosen (i.e.
+biological, chemical, cultural, mechanical, and technological) & \textbf{Yes} & No \\
+    \textbf{Electricity use} & Total amount of electricity used by a vineyard in a financial year (kWh/Ha) & \textbf{Low} & High \\
+    \textbf{Electricity Price} & The unit cost of electricity purchased by a vineyard & \textbf{Low} & High \\
+    \textbf{Renewable energy} & Percentage of energy that is renewable & High & \textbf{Low} \\
+    \textbf{GHG emissions} & Total amount of GHG emission produced by a vineyard in a financial year (Kg CO2e/Ha) as calculated  by NGA legislation & \textbf{Low} & High \\
+    \textbf{Environmental Impact} & The positive/negative impact a vineyard has on its immediate environment (to gate). & \textbf{Ideal} & Not Ideal \\
+    \textbf{Fertiliser use} & Total amount of nitrogen (synthetic and organic) used by a vineyard in a financial year (Kg/Ha) & \textbf{Low} & High \\
+    \textbf{Fuel use} & Total amount of fuel (diesel, petrol, lpg and biodiesel) used by a vineyard in a financial year (L/Ha) & \textbf{Low} & High \\
+    \textbf{Renewable Fuel} & Percentage of fuel used that is renewable. & High & \textbf{Low} \\
+    \textbf{Grape Price} & Grape price per tonne & High & \textbf{Low} \\
+    \textbf{Nutrient leaching management} & The depletion of nutrients in the grapevine root zone is minimised through best practice irrigation scheduling and soil moisture monitoring.
+& \textbf{Yes} & No \\
+    \textbf{Market supply and demand} & The relationship between the quantity of winegrapes produced and the quantity that consumers wish to buy & High & \textbf{Low} \\
+    \textbf{Pest and Disease Management} & The management of pests and diseases such as through the employ of fungicide and pesticides & \textbf{Yes} & No \\
+    \textbf{Soil degradation management} & Areas at risk of degradation via compaction or erosion are identified and actions to remediate and minimise degradation are taken (i.e.
+don’t traffic waterlogged soils, minimise cultivation, maintain vineyard floor cover with cover crops, etc.) & No & \textbf{Yes} \\
+    \textbf{Soil organic carbon management} & Areas with low or declining soil organic carbon levels are identified and actions to improve soil carbon levels are taken (i.e.
+minimise cultivation, maintain vineyard floor cover with cover crops, apply mulch or compost, etc.) & \textbf{Yes} & No \\
+    \textbf{Tractor passes} & The number of times a tractor passes over the whole vine row area & \textbf{Low} & High \\
+    \textbf{Water use efficiency} & The amount of water used per tonne of grapes produced & High & \textbf{Low} \\
+    \textbf{Water licences} & Current water licences and permits are adhered to & \textbf{Yes} & No \\
+    \textbf{Water Price} & The cost per unit of water paid for by a vineyard & \textbf{Low} & High \\
+    \textbf{Water quality} & Water used for irrigation is assessed annually for quality (pH, chloride, sodium absorption ratio, electrical conductivity, soluble solids, hardness, microbial contamination).
+Water that may case soil degradation or irrigation inefficiency is treated before use.
+& \textbf{Yes} & No \\
+    \textbf{Water Scarcity} & Whether the country is suffering drought or not (s defined by BOM) & No & \textbf{Yes} \\
+    \textbf{Weather Conditions} & A vineyard’s regional climatic conditions. & \textbf{Ideal} & Not Ideal \\
+    \textbf{Grape quality and yield targets} & The yield and quality targets of a vineyard block as outlines in the grape supply contract. & \textbf{Ideal} & Not Ideal \\
+    \textbf{Agrochemical score} & Agrochemicals with high human and environmental hazard scores are avoided. & \textbf{Yes} & No \\ \bottomrule
+    \end{tabular}
+\end{table}
 

### 2024-06-18 article.tex
lexi table and fig

@@
+% Packages:
+
+\usepackage{graphicx}
+
 %%%%%%%%%%%%%%%
@@
 % Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}[h]\ref{table:definitions}
+% \usepackage{booktabs} TODO: check the BN definitions align properly.
+\begin{table}[h]\label{tab:definitions} 
     \begin{tabular}{@{}llll@{}}
@@
 
-The key factors identified were defined as shown in Table 1.
+The key factors identified were defined as shown in Table \ref{tab:definitions}.
 By utilising these definitions, each factor's contribution to environmental sustainability was assessed.
@@
         - Use the same words as the definitions in the search to show the parralels and differences.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+\begin{table}[h]\label{tab:lexi}
+    \begin{tabular}{@{}llrr@{}}
+    \toprule
+    \textbf{Concept} & \textbf{Kind} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
+    water & WORD & 1321 & 100 \\
+    change & WORD & 817 & 62 \\
+    climate & WORD & 789 & 60 \\
+    disease & WORD & 646 & 49 \\
+    change & WORD & 569 & 43 \\
+    grapevine & WORD & 565 & 43 \\
+    viticulture & WORD & 565 & 43 \\
+    soil & WORD & 450 & 34 \\
+    plant & WORD & 425 & 32 \\
+    different & WORD & 300 & 23 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+    \begin{figure}[h]
+        \centering
+        \includegraphics[width=\linewidth]{Winegrowing-concept-map}
+        \caption{Your caption here}
+        \label{fig:lexi}
+    \end{figure}
 

### 2024-06-18 article.tex
Coonawarra case study more fleshed out

@@
 
-% TODO: compare these relationships to that of leximancer
+The bibliometric analysis using Leximancer, revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry.
+The most prominent concept was water.
+The critical importance of other variables being measured by their comparative appearance in articles relative to water (making water 100\%).
+
+Other significant concepts included "change", "climate", and "disease".
+These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see \ref{tab:lexi}).
+Furthermore, change and climate were kept separate to illustrate the variety of different chagings such as in practice, legislation and resource abundance.
+Additionally, although not in the top 10; "soil", "region", "practices", and "legislation" also appear to be dominant features within the literature.
+These factors are critical as they shape the environmental strategies employed by vineyards.
+
+The major concepts of these features was change, grapevine, water and land (see Figure \ref{fig:lexi}).
+these concepts illustrate the overarching theme between how the different concepts are connected, which showed very similar themes to that of the industry panel.
+A key difference was the rarity in how secondary and tertairy drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease.
+With these conceps being related to the operations in fields as a result of changing practices or implementing different pest controls.
+
+Together these outputs provide a comprehensive overview of the key factors affecting environmental sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement.
+This analysis underscores the multifaceted nature of sustainability, highlighting both the primary concerns and the interconnected secondary factors that must be managed on the ground.
 
 \subsection{Sustainability specifics: Coonawarra Winegrowing}
+
+Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture.
+The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}.
+Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around environmental sustainability practices to specific regional factors.
+
+In this case study, we apply BN to model and analyze the complex interactions between various environmental factors affecting wine production in Coonawarra.
+By incorporating industry-specific data and expert knowledge, the BN framework allows us to quantify the impacts of key variables such as water use, agrochemical application, soil health, and climate conditions to each other.
+This approach not only aids in understanding the current sustainability status of the region but also helps in identifying potential areas for improvement and implementing effective management strategies.
+
+The insights gained from this case study can serve as a valuable reference for other winegrowing regions aiming to enhance their environmental sustainability practices through the use of advanced probabilistic models like Bayesian Networks.
+
     %     Sustainability in Coonawarra Winegrowing: Key Factors and Influences
@@
 
-By assessing the BN, it becomes evident which factors are the most influential in driving environmental sustainability in Coonawarra.
-This detailed evaluation helps prioritize actions and policies that could lead to significant improvements in the region's sustainability practices.
+In the Coonawarra-specific BN, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions.
+These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.
+
+The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management and tractor passes.
+In one, more tractor passes were used purposefully to manage the vineyard floor; the other managed vineyard floor as a consequence of tractor passes, leveraging opportunities when the tractor was used.
+This distinction highlights how operational decisions can vary based on regional practices and priorities.
+A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land.
+However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.
+
+As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture.
+The edges between different factors reveals that water is the most connected.
+Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
+
+The Coonawarra-specific BN supports the findings from the literature, with a more structured map of how factors interact compared to the automatically generated figures from tools like Leximancer.
+The BN provides a detailed view of the relationships between factors, highlighting the central role of water and the interconnectedness of pest management, market pressures, and climate conditions.
+Additionally, the BNs emphasise economic factors, such as market pressures and grape prices, and includes how they interact within a scope of secondary factors like fuel and electricity use.
+
+% The other case study BN aligns with the literature by visually representing connections and highlighting significant factors through bibliometric analysis.
+However, the BN derived from the industry panel offers explicit connections and sensitivity analyses based on expert knowledge, providing a more nuanced understanding of the factors and their impacts compared to the broader mind maps generated from literature reviews.
+
+The two case study BNs are almost identical in their significant factors and interactions.
+Both emphasize the importance of water quality, pest and disease management, and climate conditions.
+The primary difference is the sensitivity to tractor passes, water quality, water scarcity, and soil degradation management, with one model showing higher sensitivity to these factors.
+Aside from the role of tractor passes, there are no major differences between the two BNs.
+The similarity in significant factors and their interactions underscores the robustness of the BN approach in capturing the critical elements of environmental sustainability in winegrowing.
+
+The findings from the case study align closely with the literature, illustrating more directly how factors that contribute to environmental sustaianbility are connected.
+The BNs provide a detailed and structured view of primary factors and their relationships to secondary and tertiary concerns within the industry.
+This detailed evaluation helps prioritise actions and policies that could lead to significant improvements in the sustainability practices of winegrowing regions.
 

### 2024-06-18 article.tex
fixed lexi table (removed column of "word"

@@
 \begin{table}[h]\label{tab:lexi}
-    \begin{tabular}{@{}llrr@{}}
+\begin{tabular}{@{}lrr@{}}
 \toprule
-    \textbf{Concept} & \textbf{Kind} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
-    water & WORD & 1321 & 100 \\
-    change & WORD & 817 & 62 \\
-    climate & WORD & 789 & 60 \\
-    disease & WORD & 646 & 49 \\
-    change & WORD & 569 & 43 \\
-    grapevine & WORD & 565 & 43 \\
-    viticulture & WORD & 565 & 43 \\
-    soil & WORD & 450 & 34 \\
-    plant & WORD & 425 & 32 \\
-    different & WORD & 300 & 23 \\ \bottomrule
+\textbf{Concept} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
+water & 1321 & 100 \\
+change & 817 & 62 \\
+climate & 789 & 60 \\
+disease & 646 & 49 \\
+change & 569 & 43 \\
+grapevine & 565 & 43 \\
+viticulture & 565 & 43 \\
+soil & 450 & 34 \\
+plant & 425 & 32 \\
+different & 300 & 23 \\ \bottomrule
 \end{tabular}

### 2024-06-20 article.tex
reshuffling of results!

@@
 
-How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
-Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
-Results: Use the agreed upon definitions to fully realise factors and their impact.
+% How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
+% Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
+% Results: Use the agreed upon definitions to fully realise factors and their impact.
 
@@
 The key factors identified were defined as shown in Table \ref{tab:definitions}.
-By utilising these definitions, each factor's contribution to environmental sustainability was assessed.
-The definitions provided a clear framework for measurement, ensuring that the factors could be consistently evaluated.
-
-The quantification of each factor allowed for a systematic analysis of their impacts.
+By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed.
+The quantification of each factor allowed for a systematic assessment of their impacts.
 For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact.
@@
 This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships.
-
 The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving environmental sustainability; allowing each factor's contribution to be clearly understood and relationships explicitly defined.
+This was key within the construction of the BN, were the industry panel could easily refer to the specifics of each definition and thus how it might relate to other factors.
+
+\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
+
+    % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+    %     Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
+    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
+
+    % What are the relationships between these factors in the Australian winegrowing industry?
+    %     Purpose: Explore and understand the causal and correlated relationships among the factors.
+    %     Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
+
+\begin{figure}[h!]
+    \centering
+    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
+    \caption{The resultant Bayesian network after initial discussions of how factors that contribute to environmental impact are related.
+Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}
+    \label{fig:generalBN}
+\end{figure}
+
+The relationships between the nodes defined by the industry panel are depicted in~\ref{figure:generalBN}.
+The figure highlights which factors are influenced by others.
+For instance the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
+It also illustrates the complex nature of variables such as water and their interrelatedness.
+
+The BN provided a comprehensive overview of how these factors interact, showing not only direct relationships but also how changes in one factor can propagate through the network to affect others.
+This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry.
+
+By using the generic BN, the study was able to illustrate the complexity of interactions that define environmental sustainability in Australian winegrowing.
 
 \subsection{Comparative Analysis of Literature and Industry Perspectives}
-    What are the factors of environmental sustainability in the Australian winegrowing industry?
-        Purpose: Explore and understand the both the literature and industry perspectives on this.
-        Results Literature review. Industry list of factors. Mind Map? Leximancer network.
-        - Use the same words as the definitions in the search to show the parralels and differences.
+    % What are the factors of environmental sustainability in the Australian winegrowing industry?
+    %     Purpose: Explore and understand the both the literature and industry perspectives on this.
+    %     Results Literature review. Industry list of factors. Mind Map? Leximancer network.
+    %     - Use the same words as the definitions in the search to show the parralels and differences.
 
@@
 
-        TODO: write a summary description of the leximancer outputs.
-
-\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
-    % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
-    %     Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
-    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
-
-    % What are the relationships between these factors in the Australian winegrowing industry?
-    %     Purpose: Explore and understand the causal and correlated relationships among the factors.
-    %     Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
-
-\begin{figure}[h!]
-    \centering
-    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
-    \caption{The resultant Bayesian network after initial discussions of how factors that contribute to environmental impact are related.
-Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}
-    \label{fig:generalBN}
-\end{figure}
-
-The relationships between the nodes defined by the industry panel are depicted in~\ref{figure:generalBN}.
-The figure highlights which factors are influenced by others.
-For instance the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
-It also illustrates the complex nature of variables such as water and their interrelatedness.
-
-The BN provided a comprehensive overview of how these factors interact, showing not only direct relationships but also how changes in one factor can propagate through the network to affect others.
-This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry.
-
-By using the generic BN, the study was able to illustrate the complexity of interactions that define environmental sustainability in Australian winegrowing.
-
 % Comparing this with the data from Sustainable Winegrowing Australia (SWA), it was evident that the factors identified in the BN align with the critical areas SWA focuses on, such as water use, greenhouse gas emissions, and agrochemical use.
@@
 
-In this case study, we apply BN to model and analyze the complex interactions between various environmental factors affecting wine production in Coonawarra.
-By incorporating industry-specific data and expert knowledge, the BN framework allows us to quantify the impacts of key variables such as water use, agrochemical application, soil health, and climate conditions to each other.
+Identified key factors impacting environmental sustainability were examined with regard to Coonawarra.
+By comparing the generic Bayesian Network (Figure \ref{fig:b}) model to the Coonawarra-specific model (Figure \ref{fig:robyn} and Figure \ref{fig:marcel}), we identified regional characteristics that influence these variations.
+In this case study, we altered the general Australian BN to model and analyse the complex interactions between various environmental factors affecting wine production in Coonawarra.
+By incorporating industry-specific data and expert knowledge, the BN framework allowed us to quantify the impacts of key variables such as water use, agrochemical application, soil health, and climate conditions to each other.
 This approach not only aids in understanding the current sustainability status of the region but also helps in identifying potential areas for improvement and implementing effective management strategies.
-
-The insights gained from this case study can serve as a valuable reference for other winegrowing regions aiming to enhance their environmental sustainability practices through the use of advanced probabilistic models like Bayesian Networks.
+The resultant two models represent the final consensus, reflecting the diverse perspectives and occasionally differing viewpoints among the experts, necessitating the development of two distinct but complementary models.
 
@@
     \centering
-    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
-    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}
-    \label{fig:coonawarra_bn}
+    \includegraphics[width=\linewidth]{robyn}
+    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:robyn}
+\end{figure}
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=\linewidth]{marcel}
+    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:marcel}
 \end{figure}
@@
 
-  This subsection examines how the identified key factors impacting environmental sustainability vary across different wine regions in Australia, with a focus on Coonawarra.
-By comparing the generic Bayesian Network (BN) model to the Coonawarra-specific model (Figure \ref{fig
-  } and Figure \ref{fig
-  }), we identify regional characteristics that influence these variations.
-
 The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors such as soil show variation not only at a regional level but sometimes at the paddock level as described by the expert panel.
-The Coonawarra model highlights the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
+Figure \ref{fig:robyn} and \ref{fig:marcel} highlight the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
 It is important to acknowledge that this analysis also illustrates that further work would be required to describe other regions or specific vineyards.
 
-The CPT values allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact.
-For instance, the Coonawarra-specific model demonstrates that the significance that pest/disease, and agrochemicals have a higher sensitivity to environmental impact compared factors such as green house gas emissions.
-Importantly that these sensitive factors also link greatly to one another, highlighting how critical areas for regulatory and environmental interventions can be to multiple factors beyond their specific target.
-
-By using Conditional Probability Tables (CPTs) within the BN, the significant contributions of different variables to environmental sustainability in Coonawarra were assessed. Figures \ref{fig
-  } and \ref{fig
-  } illustrate these networks with nodes coloured according to their sensitivity values relative to environmental impact.
-
-In the Coonawarra-specific BN, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions.
-These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.
-
 The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management and tractor passes.
-In one, more tractor passes were used purposefully to manage the vineyard floor; the other managed vineyard floor as a consequence of tractor passes, leveraging opportunities when the tractor was used.
+In one, greater tractor passes were used purposefully to manage the vineyard floor; the other managed vineyard floor as a consequence of tractor passes, leveraging opportunities when the tractor was used.
 This distinction highlights how operational decisions can vary based on regional practices and priorities.
@@
 The edges between different factors reveals that water is the most connected.
-Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
+Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.Within both of the models, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions.
+These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.
+
+The influence of factors on each other are described through the CPT values (see appendix) and allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact.
+For instance, the significant sensitivity that environmental impact had with regard to pests/disease, climate and agrochemicals compared to factors such as green house gas emissions.
+Importantly that these sensitive factors also link greatly to one another, highlighting how critical areas for regulatory and environmental interventions can be to multiple factors beyond their specific target.
+Furthermore, the relationships help to illustrate the further complexity of how these significant factors relate to these further considerations such as greenhouse gas emissions and the extended connection to fuel or electricity use.
+Where addressing issues such as disease can require the increased use of tractors and thus fuel.
 
@@
 
+\section{}
+
 % =================================

### 2024-06-23 article.tex
backup from Friday, uploading monday

@@
 %%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%
+% Working title
+%
+\title{Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards}
+
+\section{Abstract}
 
@@
 
-%%%%%%%%%%%%%%%%
-% Working title
-%
-\title{Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards}
+\section{Introduction}
 
@@
 
+The key factors identified were defined as shown in Table \ref{tab:definitions}.
+By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed by the industry panel.
+The quantification of each factor allowed for a systematic assessment of their impacts.
+For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact.
+Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).
+
 % How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
@@
 % Results: Use the agreed upon definitions to fully realise factors and their impact.
-
+% 
 % Please add the following required packages to your document preamble:
 % \usepackage{booktabs} TODO: check the BN definitions align properly.
+% 
 \begin{table}[h]\label{tab:definitions} 
@@
 
-The key factors identified were defined as shown in Table \ref{tab:definitions}.
-By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed.
-The quantification of each factor allowed for a systematic assessment of their impacts.
-For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact.
-Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).
-
 By applying these definitions, the study effectively translated the qualitative aspects of environmental sustainability into usable metrics.
@@
 
+The relationships between the concepts defined by the industry panel are depicted in~\ref{figure:generalBN} as nodes in the Bayesian Network.
+The network highlights which factors are influenced by others in the form of an acyclic directed graph.
+Notably, the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
+It also illustrates the complex nature of variables such as water and their interrelatedness.
+
     % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
@@
     %     Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
-
+% 
 \begin{figure}[h!]
@@
     \caption{The resultant Bayesian network after initial discussions of how factors that contribute to environmental impact are related.
-Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}
-    \label{fig:generalBN}
+Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}\label{fig:generalBN}
 \end{figure}
 
-The relationships between the nodes defined by the industry panel are depicted in~\ref{figure:generalBN}.
-The figure highlights which factors are influenced by others.
-For instance the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
-It also illustrates the complex nature of variables such as water and their interrelatedness.
-
-The BN provided a comprehensive overview of how these factors interact, showing not only direct relationships but also how changes in one factor can propagate through the network to affect others.
+The BN provided a comprehensive overview of how factors defined by the industry panel, would interact.
+Showing not only direct relationships but also how changes in one factor can propagate through the network to affect others.
 This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry.
-
-By using the generic BN, the study was able to illustrate the complexity of interactions that define environmental sustainability in Australian winegrowing.
+This network illustrates the complexity of interactions that define environmental sustainability in Australian winegrowing.
+Furthermore, the extent of relationships helps to intrinsically show the importance of variables such as water; which is prolific in how it is interconnected with other vineyard aspects.
+
+Figure~\ref{fig:generalBN}, illustrates the importance of water, disease/pests and climate through their prominent connections and numerous child nodes.
+Variables such as fuel use and soil management are resultant children nodes that connect these external pressures to decisions that offer potential solutions or interventions to aid in pursuing more sustainable outcomes.
 
 \subsection{Comparative Analysis of Literature and Industry Perspectives}
+
+The bibliometric analysis using Leximancer, revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry.
+The most prominent concept was water (see Table \ref{tab:lexi}).
+The critical importance of other variables being measured by their comparative appearance in articles relative to water (making water 100\%).
+
     % What are the factors of environmental sustainability in the Australian winegrowing industry?
@@
 
+% Comparing this with the data from Sustainable Winegrowing Australia (SWA), it was evident that the factors identified in the BN align with the critical areas SWA focuses on, such as water use, greenhouse gas emissions, and agrochemical use.
+This alignment reinforces the importance of these factors and supports the findings of the BN analysis.
+% What are the relationships between these factors in the Australian winegrowing industry?
+
+% Purpose: Explore and understand the causal and correlated relationships among the factors.
+
+The most significant concepts along with "water", included "change", "climate", and "disease".
+These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see \ref{tab:lexi}).
+Furthermore, change and climate were kept separate to illustrate the variety of different changes, such as in practice, legislation and resource abundance.
+Additionally, although not in the top 10; "soil", "region", "practices", and "legislation" also appear to be dominant features within the literature.
+These factors are critical as they shape the environmental strategies employed by vineyards.
+
+The prominence of different factors is visually described in Figure \ref{fig:lexi}, with the network depicting the frequency of these concepts appearing together.
+With the major concepts of these features being change, grapevine, water and land.
+These concepts illustrated the overarching theme between how the different concepts are connected, which showed very similar themes to that of the industry panel.
+
 \begin{figure}[h]
@@
 
-% Comparing this with the data from Sustainable Winegrowing Australia (SWA), it was evident that the factors identified in the BN align with the critical areas SWA focuses on, such as water use, greenhouse gas emissions, and agrochemical use.
-This alignment reinforces the importance of these factors and supports the findings of the BN analysis.
-% What are the relationships between these factors in the Australian winegrowing industry?
-
-% Purpose: Explore and understand the causal and correlated relationships among the factors.
-
-The bibliometric analysis using Leximancer, revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry.
-The most prominent concept was water.
-The critical importance of other variables being measured by their comparative appearance in articles relative to water (making water 100\%).
-
-Other significant concepts included "change", "climate", and "disease".
-These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see \ref{tab:lexi}).
-Furthermore, change and climate were kept separate to illustrate the variety of different chagings such as in practice, legislation and resource abundance.
-Additionally, although not in the top 10; "soil", "region", "practices", and "legislation" also appear to be dominant features within the literature.
-These factors are critical as they shape the environmental strategies employed by vineyards.
-
-The major concepts of these features was change, grapevine, water and land (see Figure \ref{fig:lexi}).
-these concepts illustrate the overarching theme between how the different concepts are connected, which showed very similar themes to that of the industry panel.
-A key difference was the rarity in how secondary and tertairy drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease.
-With these conceps being related to the operations in fields as a result of changing practices or implementing different pest controls.
-
+A key difference between the concepts from Leximancer and the Bayesian Network was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease.
+With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls.
 Together these outputs provide a comprehensive overview of the key factors affecting environmental sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement.
@@
 
-\section{}
+\section{Discussion}
 

### 2024-06-24 article.tex
cleaned up notes etc

@@
 \usepackage{graphicx}
+\usepackage{listings}
+\usepackage{xcolor}
+
+\lstset{
+  basicstyle=\ttfamily,
+  frame=single,
+  backgroundcolor=\color{lightgray!20},
+  keywordstyle=\color{blue},
+  commentstyle=\color{gray},
+  stringstyle=\color{green},
+  showstringspaces=false
+}
 
@@
 %
-\title{Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards}
-
-\section{Abstract}
+
+% \section{Preamble notes}
 
@@
 
-\section{Introduction}
-
 % Description
@@
 
-% TODO: review the following questions:
-What are the key factors/indicators of environmental sustainability in the australian winegrowing industry?
-How can we measure and relate the factors that contribute to sustainability in the australian winegrowing industry?
-What are the key factors that relate directly to environmental sustainability?
-- and what in turn are the factors that contribute to these (and thus indirectly to environmental sustainability)?
-
 % Things to consider
@@
 % Why is the knowledge important?
-This was identified as a gap within our own prior research and is helpful in creating a basis for scenario assessment and comparison.
+% This was identified as a gap within our own prior research and is helpful in creating a basis for scenario assessment and comparison.
 This will allow a greater understanding of how these factors change within different scenarios; whether that be climate, region, business goal.
-% What is the significance?
-The significance is to bridge the gap between correlations and data to causal relationships.
+% % What is the significance?
+% The significance is to bridge the gap between correlations and data to causal relationships.
 To inform growers using factors that are within their control, or how factors within their control are indfuenced by natural phenomenon.
-% How will the findings be utilised?
-These findings will be used to help inform the wider winegrowing community of what factors are most significant to environmental outcomes, and how they interact with one another.
+% % How will the findings be utilised?
+% These findings will be used to help inform the wider winegrowing community of what factors are most significant to environmental outcomes, and how they interact with one another.
 In practice this study aids a grower through informing them of how decisions impact environmental outcomes and how changing circumstance contribute to these factors and outcomes.
-% What improvements may be derived from this result?
-A wider more informed understanding of contributing factors to environmental impact and how different factors relate to one another to contribute to these findings.
-% Are the terms well defined?
-The terms are well defined. This was a key outcome of this project.
-% Do experts think your question is important/relevant/doable?
-Experts helped to guide this decision, and changed the trajectory of this project in response to data presented and how well they believed they could inform the study.
-
-% What is the nature of your question?
-%         who, what, where, when, why, how?
-What are the key factors that contribute to environmental impact within the Australian winegrowing industry?
-How do these key factors relate to each other and what are the factors that influence them?
-What are the decision that can be made by growers that can change the environmental outcomes of their vineyards?
-How do these factors chagne across well understood scenarios?
-% You can have more than one question.
-
-% What is the most important question your paper will pose?
-What are the key factors to environmental impact within the Australian winegrowing industry, and how are these factors related?
-% NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.
-
-% Why is the question/issue/problem worth examining?
-By examining the key and relevant factors to vineyards' environmental impacts we can better prepare for future changes in climate pressure, economic restrictions; that is we can better use this model to assess the potential environmental outcomes of the wine industry, as informed by experts, given potential upcoming challenges or changes.
-% Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.
+% % What improvements may be derived from this result?
+% A wider more informed understanding of contributing factors to environmental impact and how different factors relate to one another to contribute to these findings.
+% % Are the terms well defined?
+% The terms are well defined. This was a key outcome of this project.
+% % Do experts think your question is important/relevant/doable?
+% Experts helped to guide this decision, and changed the trajectory of this project in response to data presented and how well they believed they could inform the study.
+
+% % What is the nature of your question?
+% %         who, what, where, when, why, how?
+% What are the key factors that contribute to environmental impact within the Australian winegrowing industry?
+% How do these key factors relate to each other and what are the factors that influence them?
+% What are the decision that can be made by growers that can change the environmental outcomes of their vineyards?
+% How do these factors chagne across well understood scenarios?
+% % You can have more than one question.
+
+% % What is the most important question your paper will pose?
+% What are the key factors to environmental impact within the Australian winegrowing industry, and how are these factors related?
+% % NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.
+
+% % Why is the question/issue/problem worth examining?
+% By examining the key and relevant factors to vineyards' environmental impacts we can better prepare for future changes in climate pressure, economic restrictions; that is we can better use this model to assess the potential environmental outcomes of the wine industry, as informed by experts, given potential upcoming challenges or changes.
+% % Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.
 “Nothing much is known” is not sufficient justification by itself.
@@
 Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
-The collection of data and subsequent statistical analytics can only go so far as to fill the gap between cause and effects within wiengrowing.
+% The collection of data and subsequent statistical analytics can only go so far as to fill the gap between cause and effects within wiengrowing.
 This research helps to fully understand the relevant decisions being made, how they are informed and what the known outcomes are.
@@
 
+\section{Title}
+A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.
+
+\section{Abstract}
+
+The assessment of environmental sustainability in the Australian winegrowing industry remains a complex issue involving changing and compounding factors.
+To address this, we developed a Bayesian Network (BN) using data and expert elicitation to summarise the key factors, their relationships, and how they come together to influence vineyards' environmental outcomes.
+The study leveraged diverse expert perspectives to mitigate biases in probability estimations and promote discourse.
+
+The development of the BN involved an iterative process, including variable selection and definition, the defining of model structure and variable relationships, and finally the determining of relationship significance through probabilities.
+Expert input was pivotal in structuring the BN model, ensuring relevance to industry, and how a variables influence changed across regions and scenarios.
+
+Due to the possible variation in any given vineyard scenario the BN model was expanded to review a case study of the Coonawarra wine region in South Australia.
+This highlighted regional differences between growers whilst also maintaining the significance of industry-wide concerns such as the use of agrochemicals.
+To promote accessibility and scrutiny the BN was further developed into an application, allowing the possibility of further industry and stakeholder feedback; enabling a systematic re-evaluation of significant factors to the wine growing industry and how they change over time.
+
+\section{Introduction}
+TODO: refs
+The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation.
+This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries.
+This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs).
+A broader model of Australian winegrowing was created, with a more specific case study looking at the Coonawarra winegrowing region being conducted to create a rigorous and quantitative approach to understanding sustainable practices and the relationships between these factors.
+
+Bayesian Networks are probabilistic models that effectively capture and analyse the interactions between multiple factors in complex systems.
+By integrating expert knowledge and region-specific data, BNs were able to provide a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing.
+This methodology not only shed light on current sustainability practices but also identified critical areas for intervention through illustrating the interconnectedness of each of the factors and how they directly or indirectly influence one another.
+
+This research is guided by several fundamental inquiries aimed at enhancing our understanding of environmental sustainability in viticulture.
+a primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified.
+Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how factors influence might change regionally.
+Additionally, the study investigates how these factors interact within a Bayesian Network model, providing a framework for understanding their complex interdependencies.
+The final question, looks at how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.
+
+The industry panel was used as a catalyst in the early stages of this research to help explore these multifaceted questions.
+A comprehensive literature review was compiled through both structured searches.
+This extensive review established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing.
+To ensure a robust and comprehensive approach, a combination of qualitative and quantitative methods were employed within the creation of the BN; this included expert consultations and data analysis, which were instrumental in the BNs construction and validation.
+The consultations were done through the use of An industry panel comprising experts in viticulture and environmental sustainability, which provided insights and guidance throughout the research process.
+Their expertise was crucial in defining and quantifying the key factors, and further understanding the specific regional characteristics to Coonawarra.
+Through the integration of industry knowledge and academic research this study aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.
+
+% The results section presents an in-depth analysis of The Coonawarra case study, highlighted significant factors identified by the BN and their interactions.
+Key factors such as water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions were found to be the most influential on environmental sustainability in the region.
+Comparative analysis with another case study BN and existing literature underscores the robustness and relevance of our findings.
+
+This study provides critical insight into enhancing environmental sustainability through informed decision-making and targeted interventions by highlighting the sensitivity of different factors to the environmental sustainability of vineyards.
+The findings have significant implications for the local viticulture industry and offer a replicable framework for other agricultural sectors aiming to achieve sustainability.
+
 \section{Methods}
@@
 \subsection{Literature Review}
-#TODO:
+
+The literature review was a crucial component of this study, designed to establish a comprehensive understanding of existing knowledge on environmental sustainability in viticulture.
+The review aimed to identify key factors influencing sustainability, understanding their interactions, and to compare findings with the results obtained from the Bayesian Network and expert definitions.
+
+A systematic search strategy was employed to ensure a thorough review of the literature.
+The search included multiple academic journals; with search terms being broadly based on key factors given from the industry panel.
+This approach was used capture a wide range of relevant literature, incorporating keywords associated with viticulture, sustainability, and other agricultural operations related to the definitions provided by the expert panel.
+The general query (adapted to different formats for various journals and bibliographic databases) used for the literature search was:
+
+% This is the query in a code-like format.
+\begin{lstlisting}[language=]
+    (Water OR Agrochemical OR Chemical OR Ground management OR Pest OR Disease OR Management OR Electricity OR Energy OR GHG OR Emissions OR Greenhouse gas emissions OR Environmental OR Environment OR Ecological OR Fertiliser OR Fertilizer OR Fuel OR Biofuel OR Price OR Nutrient OR Runoff OR Leeching OR Market OR Supply and demand OR Soil OR Organic carbon OR SOC OR Tractor OR Field OR Operations OR Weather OR Climate OR Yield OR Production)
+    AND
+    (Sustainability OR Sustainable OR Eco-friendly OR Environmentally friendly OR Green practices)
+    AND
+    (Viticulture OR Winegrowing OR Vineyard)
+    \end{lstlisting}
+Inclusion and Exclusion Criteria
+
+To ensure the relevance and quality of the literature reviewed, specific inclusion and exclusion criteria were applied.
+Articles were only excluded if they were not available in full text or were not written in English.
+Journals beyond those included were also examined especially where they offered in-depth reviews of sustainability within agriculture or winegrowing; methodological reviews within this context were also included.
+
+Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies used in previous studies.
+The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.
+
+An expert panel comprising specialists in viticulture and environmental sustainability was engaged throughout the literature review process.
+The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.
+By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture.
+This approach ensured that the study's results were not only robust and scientifically sound but also practically relevant and actionable for industry stakeholders.
 
@@
 \end{equation}.
+
 Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
@@
 
-$$ y = {{p(a, e)(x)}\over{p(e)(x)}}={{\alpha x + \beta}\over{\gamma x + \delta}} $$.
+\begin{equation}
+y = {{p(a, e)(x)}\over{p(e)(x)}}={{\alpha x + \beta}\over{\gamma x + \delta}}
+\end{equation}.
 
@@
 
-% FIXME: should I extrapolate on this method?
+% should I extrapolate on this method?
 
@@
 
-Due to the regional limitations of the model experts proposed a case study of a specific and well understood region: Coonawarra in South Australia.
+Due to the regional limitations of the model, experts proposed a case study of a specific and well understood region: Coonawarra in South Australia.
 The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing.
-The Coonawarra model was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.
+The Coonawarra BN was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.
+Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for undervine operations and more purposeful undervine management, as well as the inclusion of further soil based factors that could be significant for particular sites.
+
+% \subsection{Methods notes}
 
@@
 
-Transparency with the expert panel was a key ingredient with this approach, highlighting explicitly what these problems were and how we would overcome them.
+% Transparency with the expert panel was a key ingredient with this approach, highlighting explicitly what these problems were and how we would overcome them.
 This included agreeing upon definitions of each node before connecting edges between them.
 
-Although originally multiclass nodes existed, the bayesian network was altered to only include binary class nodes. Each edge between a node had to answer the following questions:
-\begin{enumerate}
-        \item Are the nodes in the BN the right ones?
-        % \item Are the state spaces (values) for each node correct?
-        \item Are the arcs right?
-\end{enumerate}
-If the answer to any of the above questions was no; then the structure was not considered sufficiently defined.
+% Although originally multiclass nodes existed, the bayesian network was altered to only include binary class nodes. Each edge between a node had to answer the following questions:
+% \begin{enumerate}
+%         \item Are the nodes in the BN the right ones?
+%         % \item Are the state spaces (values) for each node correct?
+%         \item Are the arcs right?
+% \end{enumerate}
+% If the answer to any of the above questions was no; then the structure was not considered sufficiently defined.
 Although we explicitly defined the structure of the BN prior to CPT parametarisation.
@@
 The entire process of construction iinvolved the steps:
-\begin{enumerate}
-        \item exposing the panel to a strawman argument/model/definition
-        \item Outlining the model and the process involved in defining the structure of a BN
-        \item The expert panel reviewing possible nodes and arcs and definitions
-        \item Defining their own structure, node or term.
-        \item Agreeing upon the final definition, structure or model.
-\end{enumerate}
-\subsubsection{Trying to build the full model all at once}
-
-Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
-\begin{enumerate}
-        \item dividing models into subcomponents
-        \item breaking down the problem into a single target variable
-        \item reducing the scope of the problem
-        \item Setting a single time frame for the problem
-\end{enumerate}
-The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
-Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards.
+% \begin{enumerate}
+%         \item exposing the panel to a strawman argument/model/definition
+%         \item Outlining the model and the process involved in defining the structure of a BN
+%         \item The expert panel reviewing possible nodes and arcs and definitions
+%         \item Defining their own structure, node or term.
+%         \item Agreeing upon the final definition, structure or model.
+% \end{enumerate}
+% \subsubsection{Trying to build the full model all at once}
+
+% Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
+% \begin{enumerate}
+%         \item dividing models into subcomponents
+%         \item breaking down the problem into a single target variable
+%         \item reducing the scope of the problem
+%         \item Setting a single time frame for the problem
+% \end{enumerate}
+% The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
+% Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards.
 This also reduced the BN to a single terminal node.
@@
 
-\subsection{The problem}
-\subsubsection{Not understanding the problem context, complexity without value.}
-It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
-\begin{enumerate}
-        \item what do you want to reason about?
-        \item What dont you know?
-        \item What information do you have?
-        \item What do you know?
-These questions are well addressed in prior research.
+% \subsubsection{The problem}
+% \subsubsection{Not understanding the problem context, complexity without value.}
+% It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
+% \begin{enumerate}
+%         \item what do you want to reason about?
+%         \item What dont you know?
+%         \item What information do you have?
+%         \item What do you know?
+% These questions are well addressed in prior research.
 The creation of baseline models showed strong linear relationships between many variables.
@@
 here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
-\subsubsection{Complexity without value}
-A very common impulse, when something is known about the problem, is to want to put it in the model.
+% \subsubsection{Complexity without value}
+% A very common impulse, when something is known about the problem, is to want to put it in the model.
 But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value).
 Instead, the knowledge engineer must focus on the problem:
-"Which of the known variables are most relevant to the problem?"
-- This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential probelsm that will come with a cumbersome model.
-\end{enumerate}
-
-\subsection{Structure - Nodes}
-The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
-\begin{enumerate}
-        \item Getting the node values wrong
-        \item Node values aren't exhaustive
-        \item Node values aren't mutually exclusive
-        \item Incorrect modelling of mutually exclusive outcomes
-        \item Trying to model fuzzy categories
-        \item Confusing state and Probability
-        \item Confusion about what the node represents
-\end{enumerate}
-Two major strategies were employed to overcome these problems.
+% "Which of the known variables are most relevant to the problem?"
+% - This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential problem that will come with a cumbersome model.
+% \end{enumerate}
+
+% \subsubsection{Structure - Nodes}
+% The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
+% \begin{enumerate}
+%         \item Getting the node values wrong
+%         \item Node values aren't exhaustive
+%         \item Node values aren't mutually exclusive
+%         \item Incorrect modelling of mutually exclusive outcomes
+%         \item Trying to model fuzzy categories
+%         \item Confusing state and Probability
+%         \item Confusion about what the node represents
+% \end{enumerate}
+% Two major strategies were employed to overcome these problems.
 Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node.
@@
 
-\subsection{Structure Arcs}
-\subsubsection{Getting the arc directions wrong}
-Arc directions are commonly wrong for the following reasons:
-\begin{enumerate}
-        \item Modelling reasoning rather than causation
-        \item Inverting cause and effect
-        \item Missing variables
-\end{enumerate}
-To note: Korb and Nicholson do not actually suggest a method for overcoming these problems.
+% \subsubsection{Structure Arcs}
+% \subsubsection{Getting the arc directions wrong}
+% Arc directions are commonly wrong for the following reasons:
+% \begin{enumerate}
+%         \item Modelling reasoning rather than causation
+%         \item Inverting cause and effect
+%         \item Missing variables
+% \end{enumerate}
+% To note: Korb and Nicholson do not actually suggest a method for overcoming these problems.
 There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation.
 It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
-\subsubsection{Too many parents}
-Sometimes it is unavoidable that a node is affected by many factors, or other nodes.
+% \subsubsection{Too many parents}
+% Sometimes it is unavoidable that a node is affected by many factors, or other nodes.
 There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child.
@@
 
-\subsection{Parameters}
-\subsubsection{Experts estimates of probabilities are biased}
-\begin{enumerate}
-        \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
-        \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
-        \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison.
+% \subsubsection{Parameters}
+% \subsubsection{Experts estimates of probabilities are biased}
+% \begin{enumerate}
+%         \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
+%         \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
+%         \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison.
 "Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
-        \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.
-
-\end{enumerate}
-We have attempted to overcome this with two methods.
+%         \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.
+
+% \end{enumerate}
+% We have attempted to overcome this with two methods.
 A diverse and varried expert panel.
@@
 With some experts being more specialised in specific areas such as agro-chemicals.
-\subsubsection{Inconsistent probabilities}
-The collection of probabilities for when the CPT is large can result in inconsistent probabilities.
+% \subsubsection{Inconsistent probabilities}
+% The collection of probabilities for when the CPT is large can result in inconsistent probabilities.
 The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
-The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}.
+% The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}.
 In this study we overcame this through the use of worded response such as high and low.
@@
 We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
-% \item Inconsistent "filling in" of large CPTs:
--       -       - Being dead certain.
-\subsubsection{Incoherent probabilities (not summing to 1)}
-We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
-\subsubsection{Being dead certain}
-It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
-Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.
-
-\citep{morganUncertaintyGuideDealing1990}
-Two attributes of good elicitation process are:
-\begin{enumerate}
-        \item The expert should be apprised of what is known about the process, especially the nearly universal tendency to overcomefidence and other forms of bias.
+% % \item Inconsistent "filling in" of large CPTs:
+% -       -       - Being dead certain.
+% \subsubsection{Incoherent probabilities (not summing to 1)}
+% We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
+% \subsubsection{Being dead certain}
+% It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
+% Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.
+
+% \citep{morganUncertaintyGuideDealing1990}
+% Two attributes of good elicitation process are:
+% \begin{enumerate}
+%         \item The expert should be apprised of what is known about the process, especially the nearly universal tendency to overcomefidence and other forms of bias.
 In order to avoid some problems, values should be elicited in random order and the expert not given feedback on how the different values fit together until a complet set has been elicited.
-        \item The elicitation process is not simply one of requesting and recording numbers but also one of the refining the definitions of variables and terms to be used in the model.
+%         \item The elicitation process is not simply one of requesting and recording numbers but also one of the refining the definitions of variables and terms to be used in the model.
 What values are elicited depends directly upon the interpretation of terms and these should be made as explicit as possible and recorded during the elicitation.
 This is part of the process management described earlier.
-\end{enumerate}
--
-
-\citep{Boneh2021} Boneh, T.
+% \end{enumerate}
+% -
+
+% \citep{Boneh2021} Boneh, T.
 (2010).
@@
 D thesis, Clayton School of infomration technology, Monash university
-Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:
-- Bayesian Network Structure
-- Probability Parameters
-- Decision Structure
-- Utilities Preference
-
-Pitchforth \citep{pitchforthProposedValidationFramework2013} agrees with this style of structure naming these steps as:
-- Structure
-- Discretisation
-- Parametarisation
-- Model behaviour
-- Validation
-
-Korb & Nicholson have a similar view to Pitchforth. utilising a waterfall style developemental approach which include 5 stages:
-- Building the BN
--       - Structure
--       - Parameters
--       - Preferences
-- Validation
--       - Sensitivity Analysis
--       - Accuracy testing
-- Field testing
--       - Alpha/Beta testing
--       - Acceptance testing
-- Industrial use
--       - Collection of Statistics
-- Refinement
--       - Updating procedures
--       - Regression testing
-
-Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)
-
-With validation incorporating the expert scrutiny of the models begaviour for scenarios, as well as comparing this to both data and other literature.
-
-\subsection{Structure and Conditional Probabilities}
-
-\subsection{Validation}
-
-\citep{korbBayesianArtificialIntelligence2011}
-
-% Abstract
-
-1. Introduction to Methodology
-
-    Brief overview of the research approach and the rationale behind using a Bayesian Network (BN) model for sustainability assessment in viticulture.
-    Mention of the collaborative expert elicitation process and the sequential workshops that shaped the model development.
-
-2. Identification of Sustainability Indicators
-
-    Description of the process for selecting sustainability indicators, including the use of data from Sustainable Wine Australia.
-    Criteria for indicator selection, focusing on relevance to environmental, economic, and social dimensions of sustainability in winegrowing.
-
-3. Expert Elicitation Process
-
-    Overview of the expert panel composition and the expertise represented.
-    Objectives and structure of the expert elicitation process, highlighting the series of workshops conducted.
-
-Workshop 1: Variable Review and Straw Man Model Introduction
-
-    Objectives: To agree on the sustainability indicators and introduce the initial straw man model.
-    Activities: Discussion on indicator relevance and definitions; presentation of the straw man model.
-    Outcomes: Agreement on initial set of variables and conceptual understanding of the model's direction.
-
-Workshop 2: Model Structure Refinement and Interpolation Method Introduction
-
-    Objectives: To refine the model's structure and address the complexity of CPTs through an interpolation method.
-    Activities: Examination of variable relationships; identification of complex CPTs; proposal of the linear interpolation method.
-    Outcomes: Revised model structure; decision to develop and implement the interpolation method for complex CPTs.
-
-Workshop 3: Finalization of CPTs and Case Study Selection
-
-    Objectives: To finalize CPT values using the interpolation method and select a case study for model application.
-    Activities: Presentation and application of the interpolation method; finalization of CPT values; selection of the Coonawarra wine region for the case study.
-    Outcomes: Completion of model parameterization; selection of case study region emphasizing the model's practical application.
-
-4. Development and Implementation of the Interpolation Method
-
-    Detailed explanation of the linear interpolation method developed to manage the complexity of CPTs for variables with extensive connections.
-    Justification for choosing this method and its anticipated impact on the model's usability and accuracy.
-
-5. Case Study Application: Coonawarra Wine Region
-
-    Rationale for selecting the Coonawarra wine region as a case study to apply and test the BN model.
-    Brief description of how the model was applied to this specific context, including any regional data used and adjustments made for the case study.
-
-6. Model Validation
-
-    Overview of the validation process employed to ensure the accuracy and reliability of the BN model.
-    Description of internal and external validation measures, including expert review and comparison with independent datasets.
-
-7. Conclusion
-
-    Summary of the methodological approach, emphasizing the collaborative expert elicitation process and the innovative solutions developed for model construction and parameterization.
-    Brief mention of the significance of the methodology for sustainability assessment in viticulture and potential implications for future research and practice.
+% Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:
+% - Bayesian Network Structure
+% - Probability Parameters
+% - Decision Structure
+% - Utilities Preference
+
+% Pitchforth \citep{pitchforthProposedValidationFramework2013} agrees with this style of structure naming these steps as:
+% - Structure
+% - Discretisation
+% - Parametarisation
+% - Model behaviour
+% - Validation
+
+% Korb & Nicholson have a similar view to Pitchforth. utilising a waterfall style developemental approach which include 5 stages:
+% - Building the BN
+% -       - Structure
+% -       - Parameters
+% -       - Preferences
+% - Validation
+% -       - Sensitivity Analysis
+% -       - Accuracy testing
+% - Field testing
+% -       - Alpha/Beta testing
+% -       - Acceptance testing
+% - Industrial use
+% -       - Collection of Statistics
+% - Refinement
+% -       - Updating procedures
+% -       - Regression testing
+
+% Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)
+
+% With validation incorporating the expert scrutiny of the models begaviour for scenarios, as well as comparing this to both data and other literature.
+
+% \subsubsection{Structure and Conditional Probabilities}
+
+% \subsubsection{Validation}
+
+% \citep{korbBayesianArtificialIntelligence2011}
+
+% % Abstract
+
+% 1. Introduction to Methodology
+
+%     Brief overview of the research approach and the rationale behind using a Bayesian Network (BN) model for sustainability assessment in viticulture.
+%     Mention of the collaborative expert elicitation process and the sequential workshops that shaped the model development.
+
+% 2. Identification of Sustainability Indicators
+
+%     Description of the process for selecting sustainability indicators, including the use of data from Sustainable Wine Australia.
+%     Criteria for indicator selection, focusing on relevance to environmental, economic, and social dimensions of sustainability in winegrowing.
+
+% 3. Expert Elicitation Process
+
+%     Overview of the expert panel composition and the expertise represented.
+%     Objectives and structure of the expert elicitation process, highlighting the series of workshops conducted.
+
+% Workshop 1: Variable Review and Straw Man Model Introduction
+
+%     Objectives: To agree on the sustainability indicators and introduce the initial straw man model.
+%     Activities: Discussion on indicator relevance and definitions; presentation of the straw man model.
+%     Outcomes: Agreement on initial set of variables and conceptual understanding of the model's direction.
+
+% Workshop 2: Model Structure Refinement and Interpolation Method Introduction
+
+%     Objectives: To refine the model's structure and address the complexity of CPTs through an interpolation method.
+%     Activities: Examination of variable relationships; identification of complex CPTs; proposal of the linear interpolation method.
+%     Outcomes: Revised model structure; decision to develop and implement the interpolation method for complex CPTs.
+
+% Workshop 3: Finalization of CPTs and Case Study Selection
+
+%     Objectives: To finalize CPT values using the interpolation method and select a case study for model application.
+%     Activities: Presentation and application of the interpolation method; finalization of CPT values; selection of the Coonawarra wine region for the case study.
+%     Outcomes: Completion of model parameterization; selection of case study region emphasizing the model's practical application.
+
+% 4. Development and Implementation of the Interpolation Method
+
+%     Detailed explanation of the linear interpolation method developed to manage the complexity of CPTs for variables with extensive connections.
+%     Justification for choosing this method and its anticipated impact on the model's usability and accuracy.
+
+% 5. Case Study Application: Coonawarra Wine Region
+
+%     Rationale for selecting the Coonawarra wine region as a case study to apply and test the BN model.
+%     Brief description of how the model was applied to this specific context, including any regional data used and adjustments made for the case study.
+
+% 6. Model Validation
+
+%     Overview of the validation process employed to ensure the accuracy and reliability of the BN model.
+%     Description of internal and external validation measures, including expert review and comparison with independent datasets.
+
+% 7. Conclusion
+
+%     Summary of the methodological approach, emphasizing the collaborative expert elicitation process and the innovative solutions developed for model construction and parameterization.
+%     Brief mention of the significance of the methodology for sustainability assessment in viticulture and potential implications for future research and practice.
 
@@
 
+% \subsection{Results notes}
+
+% % =================================
+% Structuring the Results Section Based on These Questions:
+% Introduction to Results
+
+%     Content: Briefly restate the refined research questions.
+%     Explanation: Explain the approach to answering these questions using the BN model and CPT values.
+
+% Primary Factors Identification
+
+% Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+
+%     Content: Present the primary factors identified through your analysis.
+%     Data: Use the rigorous definitions and the generic BN to highlight these factors.
+%     Figures/Tables: Include a table or figure showing the key factors and their relative importance.
+
+% Quantitative Measurement and Analysis
+
+% Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?
+
+%     Content: Describe the methods used to measure and analyze the key factors.
+%     Data: Show measurements and analytical results from the CPT values in the specific BN models.
+%     Figures/Tables: Include charts or tables showing the measurements and analyses.
+
+% Relationships Between Factors
+
+% Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
+
+%     Content: Discuss the direct and indirect relationships identified.
+%     Data: Present interaction diagrams or tables.
+%     Figures/Tables: Include a BN tree diagram illustrating these relationships.
+
+% Regional Variations
+
+% Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
+
+%     Content: Compare the key factors and their impacts across different regions.
+%     Data: Present comparisons between the two specific BN models from different growers.
+%     Figures/Tables: Include figures comparing regional differences.
+
+% Scenario Analysis
+
+% Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
+
+%     Content: Analyze the impact of different scenarios on environmental sustainability.
+%     Data: Use scenario-based BN queries to show changes in key factors and their impacts.
+%     Figures/Tables: Include charts or tables summarizing the scenario analysis results.
+
+% Example Framework for Presenting Results:
+% Introduction to Results
+
+% "The results of this study are structured to address five primary research questions aimed at understanding the key factors and their interactions affecting the environmental impact of vineyards in the Australian winegrowing industry.
+The analysis leverages Bayesian Network models to provide a comprehensive view of these factors and their contributions."
+% Primary Factors Identification
+
+% Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+% Results:
+
+%     Identified Factors: Water usage, pesticide application, soil management, etc.
+%     Data Source: Defined terms provided by industry experts and the generic BN model.
+%     Figures: Table 1 shows the key factors and their relative importance derived from the BN analysis.
+
+% Quantitative Measurement and Analysis
+
+% Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?
+% Results:
+
+%     Measurements: Quantitative analysis of key factors using CPT values from two specific BN models.
+%     Data Source: CPT values from BN models of two growers.
+%     Figures: Table 2 presents the measurements and analysis results.
+
+% Relationships Between Factors
+
+% Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
+% Results:
+
+%     Interactions: Direct and indirect relationships as illustrated by the BN model.
+%     Data Source: Generic BN model and specific models.
+%     Figures: Figure 1 illustrates the BN tree diagram showing these relationships.
+
+% Regional Variations
+
+% Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
+% Results:
+
+%     Regional Variability: Comparison of factors and impacts across regions using specific BN models.
+%     Data Source: BN models from two growers in different regions.
+%     Figures: Figure 2 compares the BN models for different regions.
+
+% Scenario Analysis
+
+% Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
+% Results:
+
+%     Scenarios: Impact analysis under different scenarios using BN models.
+%     Data Source: Scenario-based BN queries.
+%     Figures: Table 3 summarizes the scenario analysis results.
+
+% This refined approach ensures that your Results section directly addresses your research questions and clearly presents your findings.
+Let me know if there are specific details or sections you’d like further refined!
+
 \section{Discussion}
-
-% =================================
-Structuring the Results Section Based on These Questions:
-Introduction to Results
-
-    Content: Briefly restate the refined research questions.
-    Explanation: Explain the approach to answering these questions using the BN model and CPT values.
-
-Primary Factors Identification
-
-Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
-
-    Content: Present the primary factors identified through your analysis.
-    Data: Use the rigorous definitions and the generic BN to highlight these factors.
-    Figures/Tables: Include a table or figure showing the key factors and their relative importance.
-
-Quantitative Measurement and Analysis
-
-Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?
-
-    Content: Describe the methods used to measure and analyze the key factors.
-    Data: Show measurements and analytical results from the CPT values in the specific BN models.
-    Figures/Tables: Include charts or tables showing the measurements and analyses.
-
-Relationships Between Factors
-
-Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
-
-    Content: Discuss the direct and indirect relationships identified.
-    Data: Present interaction diagrams or tables.
-    Figures/Tables: Include a BN tree diagram illustrating these relationships.
-
-Regional Variations
-
-Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
-
-    Content: Compare the key factors and their impacts across different regions.
-    Data: Present comparisons between the two specific BN models from different growers.
-    Figures/Tables: Include figures comparing regional differences.
-
-Scenario Analysis
-
-Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
-
-    Content: Analyze the impact of different scenarios on environmental sustainability.
-    Data: Use scenario-based BN queries to show changes in key factors and their impacts.
-    Figures/Tables: Include charts or tables summarizing the scenario analysis results.
-
-Example Framework for Presenting Results:
-Introduction to Results
-
-"The results of this study are structured to address five primary research questions aimed at understanding the key factors and their interactions affecting the environmental impact of vineyards in the Australian winegrowing industry.
-The analysis leverages Bayesian Network models to provide a comprehensive view of these factors and their contributions."
-Primary Factors Identification
-
-Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
-Results:
-
-    Identified Factors: Water usage, pesticide application, soil management, etc.
-    Data Source: Defined terms provided by industry experts and the generic BN model.
-    Figures: Table 1 shows the key factors and their relative importance derived from the BN analysis.
-
-Quantitative Measurement and Analysis
-
-Question: How can these key factors be quantitatively measured and analyzed to assess their contributions to sustainability in the Australian winegrowing industry?
-Results:
-
-    Measurements: Quantitative analysis of key factors using CPT values from two specific BN models.
-    Data Source: CPT values from BN models of two growers.
-    Figures: Table 2 presents the measurements and analysis results.
-
-Relationships Between Factors
-
-Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
-Results:
-
-    Interactions: Direct and indirect relationships as illustrated by the BN model.
-    Data Source: Generic BN model and specific models.
-    Figures: Figure 1 illustrates the BN tree diagram showing these relationships.
-
-Regional Variations
-
-Question: How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
-Results:
-
-    Regional Variability: Comparison of factors and impacts across regions using specific BN models.
-    Data Source: BN models from two growers in different regions.
-    Figures: Figure 2 compares the BN models for different regions.
-
-Scenario Analysis
-
-Question: How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in the Australian winegrowing industry?
-Results:
-
-    Scenarios: Impact analysis under different scenarios using BN models.
-    Data Source: Scenario-based BN queries.
-    Figures: Table 3 summarizes the scenario analysis results.
-
-This refined approach ensures that your Results section directly addresses your research questions and clearly presents your findings.
-Let me know if there are specific details or sections you’d like further refined!
-
-\section{Title}
-A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.
-
-\section{Abstract}
-
-The assessment of environmental sustainability in the Australian winegrowing industry remains a complex issue involving changing and compounding factors.
-To address this, we developed a Bayesian Network (BN) using data and expert elicitation to summarise the key factors, their relationships, and how they come together to influence vineyards' environmental outcomes.
-The study leveraged diverse expert perspectives to mitigate biases in probability estimations and promote discourse.
-
-The development of the BN involved an iterative process, including variable selection and definition, the defining of model structure and variable relationships, and finally the determining of relationship significance through probabilities.
-Expert input was pivotal in structuring the BN model, ensuring relevance to industry, and how a variables influence changed across regions and scenarios.
-
-Due to the possible variation in any given vineyard scenario the BN model was expanded to review a case study of the Coonawarra wine region in South Australia.
-This highlighted regional differences between growers whilst also maintaining the significance of industry-wide concerns such as the use of agrochemicals.
-To promote accessibility and scrutiny the BN was further developed into an application, allowing the possibility of further industry and stakeholder feedback; enabling a systematic re-evaluation of significant factors to the wine growing industry and how they change over time.

### 2024-06-24 article.tex
discussion start

@@
 \section{Discussion}
+
+This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of graphical models.
+These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing; where a keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated.
+
+Of these factors, the BN was able to show the critical nature that water played as one of the most interconnected variables.
+Furthermore, how the influence of water use reached multiple variables that reflected different operational decisions within a vineyard such as tractor use, disease and pest prevention, as well as management strategies for soil.
+This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.
+
+Of further significance was the management of pests and diseases, market pressures and climate.
+With these external influencing being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
+Particularly, climate was an interface between water and pest/disease, due to it being a determining factor in temperature and water availability.
+
+Climate and weather conditions are shown to be significant determinants of environmental sustainability in viticulture.
+The BN models capture the complexity of these factors, demonstrating how they influence water availability, pest and disease pressures, and overall vineyard health.
+Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change.
+Comparative Analysis with Existing Literature
+
+Such elements being used in some operational responses to things such as disease through the use of agrochemicals.
+Where, environmental sustainability was highly sensitive to as a factor; the case study highlighting its direct influnce on environmental sustainability.
+A major concern from the industry panel was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts.
+The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately.
+
+The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest and disease control, economic pressures, and climate conditions as key factors.
+However, the BN models provide a more structured and detailed map of how these factors interact, offering a clearer understanding of their interdependencies and relative importance.
+
+The study's results align well with previous research, reinforcing the significance of the identified factors.
+For instance, the critical role of water management is well-documented in the literature, and this study further elucidates its central position within the network of sustainability factors.
+
+While the existing literature provides a broad understanding of sustainability in viticulture, this study offers novel insights through the use of BN models.
+These models reveal specific pathways and interactions that are less apparent in traditional analyses, highlighting areas where targeted interventions could have the most significant impact.
+
+The comparison with previous research highlights how the BN approach can expand our understanding of sustainability by integrating expert knowledge and empirical data into a coherent framework.
+This method not only confirms known relationships but also uncovers new connections and sensitivities that are critical for informed decision-making.
+
+% The models indicated that effective pest and disease management can mitigate the need for extensive agrochemical use, thereby reducing the environmental footprint of viticulture.
+This interaction is crucial for developing integrated pest management strategies that are both effective and sustainable.
+
+Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have a substantial impact on sustainability practices.
+The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers.
+The BN models helped to illustrate how economic incentives can be drivers of sustainable practices.
+The definitive influence and relationships between what are more tertiary considerations of environmental sustainability being more directly connected to further considerations such as operational costs; is a potential further avenue of research that would compliment this work greatly.
+
+In summary, the interpretation of results from the Bayesian Network models enhances our understanding of environmental sustainability in viticulture by providing a detailed and structured analysis of key factors and their interactions.
+The findings underscore the importance of integrated management practices that consider the interconnected nature of water quality, pest and disease management, market pressures, agrochemical use, and climate conditions.
+By aligning with and expanding upon existing literature, this study offers valuable insights for both researchers and practitioners aiming to promote sustainability in viticulture.
+
+Comparison with Previous Research:
+
+    How do the results of this study compare with existing literature on sustainability in viticulture?
+    What consistencies and discrepancies are observed between our findings and those reported in previous studies?
+    What might explain any differences between our results and those of other studies?
+
+Explanation of Unexpected Findings:
+
+    Were there any unexpected or anomalous findings in the study?
+    What potential explanations can be proposed for these unexpected results?
+    How do these findings impact the overall conclusions of the study?
+
+Implications of the Study:
+
+    What are the broader implications of the study's findings for the field of viticulture and environmental sustainability?
+    How might these results inform practical applications in vineyard management and policy-making?
+    What theoretical contributions does this study make to the understanding of sustainability in agriculture?
+
+Limitations:
+
+    What are the main limitations of this study?
+    How do these limitations affect the interpretation and generalizability of the results?
+    What methodological or contextual factors should be considered when applying these findings to other regions or contexts?
+
+Suggestions for Future Research:
+
+    What gaps in the current knowledge were identified through this study?
+    What specific areas or questions should future research focus on to build upon these findings?
+    What methodological improvements or alternative approaches could enhance future studies on this topic?
+
+Conclusions:
+
+    What are the primary conclusions drawn from this study?
+    How do these conclusions integrate with the broader body of knowledge on environmental sustainability in viticulture?
+    What are the key takeaways for stakeholders in the viticulture industry and for future research directions?
+
+\section{Conclusion}

### 2024-06-24 article.tex
discussion progress

@@
 
+% Needed references are currently highlighted as TODO:
+
 This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of graphical models.
-These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing; where a keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated.
-
-Of these factors, the BN was able to show the critical nature that water played as one of the most interconnected variables.
-Furthermore, how the influence of water use reached multiple variables that reflected different operational decisions within a vineyard such as tractor use, disease and pest prevention, as well as management strategies for soil.
+These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing.
+A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting the critical nature that water use plays.
+As one of the most interconnected variables, the influence of water use reaches almost every variable, with its connection to operational decisions being reflected within its connection to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
 This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.
@@
 Of further significance was the management of pests and diseases, market pressures and climate.
-With these external influencing being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
-Particularly, climate was an interface between water and pest/disease, due to it being a determining factor in temperature and water availability.
-
-Climate and weather conditions are shown to be significant determinants of environmental sustainability in viticulture.
-The BN models capture the complexity of these factors, demonstrating how they influence water availability, pest and disease pressures, and overall vineyard health.
-Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change.
-Comparative Analysis with Existing Literature
-
-Such elements being used in some operational responses to things such as disease through the use of agrochemicals.
-Where, environmental sustainability was highly sensitive to as a factor; the case study highlighting its direct influnce on environmental sustainability.
-A major concern from the industry panel was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts.
+With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
+Particularly, climate acted as an interface between water and pest/disease, due to it being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:.
+Of the greatest concern to climate is how it influences water availability, pest and disease pressures, and overall vineyard health.
+Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:.
+In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:.
+The BN models capture the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.
+
+the case study highlighted the direct influence on environmental sustainability, where it was found to be the most sensitive to elements used in operational responses to factors such as disease through the use of agrochemicals.
+A major concern from the industry panel was, that while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts.
 The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately.
-
-The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest and disease control, economic pressures, and climate conditions as key factors.
-However, the BN models provide a more structured and detailed map of how these factors interact, offering a clearer understanding of their interdependencies and relative importance.
-
-The study's results align well with previous research, reinforcing the significance of the identified factors.
-For instance, the critical role of water management is well-documented in the literature, and this study further elucidates its central position within the network of sustainability factors.
-
-While the existing literature provides a broad understanding of sustainability in viticulture, this study offers novel insights through the use of BN models.
-These models reveal specific pathways and interactions that are less apparent in traditional analyses, highlighting areas where targeted interventions could have the most significant impact.
-
-The comparison with previous research highlights how the BN approach can expand our understanding of sustainability by integrating expert knowledge and empirical data into a coherent framework.
-This method not only confirms known relationships but also uncovers new connections and sensitivities that are critical for informed decision-making.
+TODO: A literature review regarding this does here TODO:
 
@@
 This interaction is crucial for developing integrated pest management strategies that are both effective and sustainable.
+
+The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest and disease control, economic pressures, and climate conditions as key factors.
+However, the BN models provides structure to the broader way of how these factors interact, offering a clearer understanding of their interdependencies and relative importance.
+Many of these singular relationships are well defined within literature studies such as TODO:.
+
+While the existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study.
+The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered.
+A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the Bn to be used as a framework that can further integrate other studies results into these relationships.
 

### 2024-06-24 article.tex
first pass discussion without reference sand elaboration

@@
 
-This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of graphical models.
+This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input.
 These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing.
-A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting the critical nature that water use plays.
-As one of the most interconnected variables, the influence of water use reaches almost every variable, with its connection to operational decisions being reflected within its connection to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
+A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical nature as one of the most interconnected variables.
+The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
 This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.
@@
 With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
-Particularly, climate acted as an interface between water and pest/disease, due to it being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:.
-Of the greatest concern to climate is how it influences water availability, pest and disease pressures, and overall vineyard health.
+In particular, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:.
+Of great concern to climate was how it influenced water availability, pest/disease pressures, and its overall contribution to vineyard health.
 Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:.
@@
 
-the case study highlighted the direct influence on environmental sustainability, where it was found to be the most sensitive to elements used in operational responses to factors such as disease through the use of agrochemicals.
-A major concern from the industry panel was, that while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts.
+The case study highlighted the direct influences on environmental sustainability, where environmental sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors.
+A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts.
 The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately.
-TODO: A literature review regarding this does here TODO:
-
-% The models indicated that effective pest and disease management can mitigate the need for extensive agrochemical use, thereby reducing the environmental footprint of viticulture.
-This interaction is crucial for developing integrated pest management strategies that are both effective and sustainable.
-
-The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest and disease control, economic pressures, and climate conditions as key factors.
-However, the BN models provides structure to the broader way of how these factors interact, offering a clearer understanding of their interdependencies and relative importance.
-Many of these singular relationships are well defined within literature studies such as TODO:.
-
-While the existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study.
+TODO: A literature review regarding this does here TODO:.
+
+The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest/disease control, economic pressures, and climate conditions as key factors.
+Many of these singular relationships are well-defined within literature studies such as TODO:.
+
+The BN models provide structure to the broader way of how how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to environmental sustainability as an outcome.
+The existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study.
 The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered.
-A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the Bn to be used as a framework that can further integrate other studies results into these relationships.
-
-Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have a substantial impact on sustainability practices.
-The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers.
+A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships TODO:.
+
 The BN models helped to illustrate how economic incentives can be drivers of sustainable practices.
-The definitive influence and relationships between what are more tertiary considerations of environmental sustainability being more directly connected to further considerations such as operational costs; is a potential further avenue of research that would compliment this work greatly.
-
-In summary, the interpretation of results from the Bayesian Network models enhances our understanding of environmental sustainability in viticulture by providing a detailed and structured analysis of key factors and their interactions.
-The findings underscore the importance of integrated management practices that consider the interconnected nature of water quality, pest and disease management, market pressures, agrochemical use, and climate conditions.
-By aligning with and expanding upon existing literature, this study offers valuable insights for both researchers and practitioners aiming to promote sustainability in viticulture.
+The definitive influence and relationships between what are more tertiary considerations of environmental sustainability being directly connected to further considerations such as operational costs.
+Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have an impact on sustainability practices but were limited in this study through only reviewing them within the lens of environmental sustainability.
+The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers as well as what may be much more specific circumstance; of which is a potential further avenue of research that would compliment this work significantly.
 
@@
 \section{Conclusion}
+
+The interpretation of results from the Bayesian Network models enhances our understanding of environmental sustainability in viticulture by providing a detailed and structured analysis of key factors and their interactions.
+The findings underscore the importance of integrated management practices that consider the interconnected nature of water quality, pest and disease management, market pressures, agrochemical use, and climate conditions.
+By aligning with and expanding upon existing literature, this study offers valuable insights for both researchers and practitioners aiming to promote sustainability in viticulture.

### 2024-06-24 article.tex
discussion pre reference insertion and extrapolation

@@
 
-This investigation highlighted the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input.
+This investigation highlights the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input.
 These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing.
-A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical nature as one of the most interconnected variables.
+A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables.
 The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
-This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate.
+This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate TODO:.
 
@@
 In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:.
-The BN models capture the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.
+The BN models captured the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.
 
@@
 A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts.
-The model emphasised the need for balanced and regulated agrochemical practices; and especially for those to be followed appropriately.
+The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices to be followed appropriately.
 TODO: A literature review regarding this does here TODO:.
@@
 
-The BN models provide structure to the broader way of how how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to environmental sustainability as an outcome.
+The BN models provide structure to the broader way of how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to environmental sustainability as an outcome.
 The existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study.
@@
 A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships TODO:.
+
+By linking fuel and electricity use with well-studied factors like water and climate, the BN model broadens the scope of sustainability research in viticulture, emphasising the interconnected nature of these challenges.
+Integrating elements which play critical roles in vineyard operational decisions such as tractor, fuel and electricity use, which were more peripheral within the bibliometric analysis, to central themes like water, pests/disease and climate offered a holistic view of sustainability in winegrowing.
+The model demonstrated how fuel, tractor, and electricity use are intertwined with factors such as water and climate through propagation.
+Even though environmental sustainability was not highly sensitive to such factors, they directly relate to operational decisions that can be influenced by growers over a season.
+For example, electricity and fuel use are crucial for irrigation systems, as well as fuel use and tractors required for operations linked to soil preparation, management, and pest/disease control actions.
+Notably these operational decisions can be preventative or reactionary within a season TODO:.
+With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (water, climate and disease TODO: check these connections) particularly all of which are affected by climate TODO:.
+Additionally, the need to adapt to changing climate conditions can drive increased use of fuel and electricity, potentially exacerbating greenhouse gas emissions.
+The findings align with TODO:, suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practices TODO:.
+This integrated perspective is crucial for developing effective strategies to enhance the sustainability of the winegrowing industry.
+
+The integration of expert knowledge was an essential part of constructing these BNs, particularly in defining the structure of the network and the CPTs.
+However, even within this analysis, disagreements were present amongst the panel especially as the models became more granular.
+The model is limited by the knowledge of the expert panel and by its specificity to the Australian, and further the Coonawarra context.
+The model created is also limited, in that, it solely represents the outcomes of a single season in isolation.
+No further accounting for past or future factors that may affect vineyard outcomes or decisions were considered.
+A dynamic Bayesian network could potentially address this issue but would require further investigations regarding the temporal factors that occur between seasons.
+Although this is a limitting factor, the model created within this study could still operate as the central static consideration between these temporal factors if future research was conducted.
+Similarly, spatial influences are also difficult to generalise to.
+Factors influencing sustainability in one winegrowing region may differ significantly from those in another region due to variations in climate, soil types, management practices, and economic conditions.
+Therefore, the applicability of the BN developed for the Coonawarra region does not extend seamlessly to other wine regions.
+The more general model for Australia would also need to be altered to generalise to other countries due to the wide and varying circumstances that exist from country to country.
 
@@
 
-Comparison with Previous Research:
-
-    How do the results of this study compare with existing literature on sustainability in viticulture?
-    What consistencies and discrepancies are observed between our findings and those reported in previous studies?
-    What might explain any differences between our results and those of other studies?
-
-Explanation of Unexpected Findings:
-
-    Were there any unexpected or anomalous findings in the study?
-    What potential explanations can be proposed for these unexpected results?
-    How do these findings impact the overall conclusions of the study?
-
-Implications of the Study:
-
-    What are the broader implications of the study's findings for the field of viticulture and environmental sustainability?
-    How might these results inform practical applications in vineyard management and policy-making?
-    What theoretical contributions does this study make to the understanding of sustainability in agriculture?
-
-Limitations:
-
-    What are the main limitations of this study?
-    How do these limitations affect the interpretation and generalizability of the results?
-    What methodological or contextual factors should be considered when applying these findings to other regions or contexts?
-
-Suggestions for Future Research:
-
-    What gaps in the current knowledge were identified through this study?
-    What specific areas or questions should future research focus on to build upon these findings?
-    What methodological improvements or alternative approaches could enhance future studies on this topic?
-
-Conclusions:
-
-    What are the primary conclusions drawn from this study?
-    How do these conclusions integrate with the broader body of knowledge on environmental sustainability in viticulture?
-    What are the key takeaways for stakeholders in the viticulture industry and for future research directions?
-
 \section{Conclusion}

### 2024-06-25 article.tex
discussion refs

@@
 % What are the relationships between these factors in the Australian winegrowing industry?
-
+% 
 % Purpose: Explore and understand the causal and correlated relationships among the factors.
@@
 The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
-This finding aligns with water being the lifeblood of agriculture, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate TODO:.
+This finding aligns with water being the lifeblood of agriculture~\cite{chawlaWaterProductivityAgriculture2023}, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~\cite{australianbureauofstatisticsWaterUseAustralian2021}.
 
@@
 With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
-In particular, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease TODO:.
+In particular, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease~\cite{boisClimateVsGrapevine2017}.
 Of great concern to climate was how it influenced water availability, pest/disease pressures, and its overall contribution to vineyard health.
-Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change TODO:.
-In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield, erosion, and are further determinants of chosen grape varieties TODO:.
+Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change~\cite{agostaRegionalClimateVariability2012,alsafadiFutureScenariosBioclimatic2023,barriguinhaVineyardYieldEstimation2021,sharmaChapterImpactClimate2014}.
+In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield~\cite{barriguinhaVineyardYieldEstimation2021,antonComparativeStudyRisk2012}, erosion~\cite{biddoccuEvaluationSoilErosion2020,doi:10.1177/0309133319861833}, and are further determinants of chosen grape varieties~\cite{topferGrapeVarietiesAre2022, petriashviliImpactClimateChange2023}.
 The BN models captured the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.
 
-The case study highlighted the direct influences on environmental sustainability, where environmental sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors.
-A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts.
-The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices to be followed appropriately.
+The case study highlighted the direct influences on environmental sustainability, where environmental sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}).
+A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\cite{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}.
+The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~\cite{baianoOverviewSustainabilityWine2021}.
+
 TODO: A literature review regarding this does here TODO:.
@@
 The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered.
-A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships TODO:.
+A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships~\cite{kimphuctranMachineLearningProbabilistic2022,kollerObjectOrientedBayesianNetworks1997,korbBayesianArtificialIntelligence2011}.
 
@@
 For example, electricity and fuel use are crucial for irrigation systems, as well as fuel use and tractors required for operations linked to soil preparation, management, and pest/disease control actions.
-Notably these operational decisions can be preventative or reactionary within a season TODO:.
-With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (water, climate and disease TODO: check these connections) particularly all of which are affected by climate TODO:.
+Notably these operational decisions can be preventative or reactionary within a season.
+With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (soil, water and disease) particularly all of which are connected to climate~\cite{fragaClimateChangeNew2020,tofaloClimateChangeWine2023,naigeonDATADecisionmakingViticulture2023}.
 Additionally, the need to adapt to changing climate conditions can drive increased use of fuel and electricity, potentially exacerbating greenhouse gas emissions.
-The findings align with TODO:, suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practices TODO:.
+The findings align with literature, with researchers highlighting how different operations contribute to climate change through greenhouse gas emmissions \cite{pilafidisAssessingEnergyUse2023,cechPesticideUseAssociated2022,zhangEstimatingEconomicEnvironmental2019} and conversely how climate change increases pressure on farmers~\cite{barnaEditorialImprovingSustainability2023,costaRoleSoilTemperature2023,atakClimateChangeAdaptive2024}, suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practice~\cite{pereiraViticultureClimateChange2023}.
 This integrated perspective is crucial for developing effective strategies to enhance the sustainability of the winegrowing industry.
@@
 A dynamic Bayesian network could potentially address this issue but would require further investigations regarding the temporal factors that occur between seasons.
-Although this is a limitting factor, the model created within this study could still operate as the central static consideration between these temporal factors if future research was conducted.
+Although this is a limiting factor, the model created within this study could still operate as the central static consideration between these temporal factors if future research was conducted.
 Similarly, spatial influences are also difficult to generalise to.

### 2024-06-25 article.tex
discussion finished

@@
 
-% Needed references are currently highlighted as TODO:
-
 This investigation highlights the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input.
@@
 
-TODO: A literature review regarding this does here TODO:.
-
 The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest/disease control, economic pressures, and climate conditions as key factors.
-Many of these singular relationships are well-defined within literature studies such as TODO:.
+Many of these singular relationships are well-defined within literature studies such as those between climate and pest/disease \cite{olatinwoChapterWeatherbasedPest2014}.
+Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combatting external pressures such climate, water scarciy and disease \cite{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}.
+Tools such as Bayesian networks are becoming more applied to assist with the creation of decision support tools such as with water management \cite{carmonaUseParticipatoryObjectOriented2011} or vineyard placement \cite{abbalDecisionSupportSystem2016}.
+However, the combination of holistic approaches to reviewing sustainable practices in the adoption of techniques through measurable and holistic approaches is a growing need in policy creation and uptake of new novel sustainable practices \autocite{mayfieldDesigningExpertledBayesian2023,baianoOverviewSustainabilityWine2021,dichiaraCollaborativeApproachAchieving2024}.
+Although more holistic approaches are required to review the total accumulated benefits of sustainable practices, it is well aligned between researchers, the public and policy-makers that this endeavour is of great importance to the Australian agricultural industry as a whole \cite{dumbrellComparingAustralianPublic2024}.
 
@@
 \section{Conclusion}
-
-The interpretation of results from the Bayesian Network models enhances our understanding of environmental sustainability in viticulture by providing a detailed and structured analysis of key factors and their interactions.
-The findings underscore the importance of integrated management practices that consider the interconnected nature of water quality, pest and disease management, market pressures, agrochemical use, and climate conditions.
-By aligning with and expanding upon existing literature, this study offers valuable insights for both researchers and practitioners aiming to promote sustainability in viticulture.

### 2024-06-25 article.tex
Conclusion

@@
 \section{Conclusion}
+
+This study provides an in-depth examination of environmental sustainability in Australia and the Coonawarra winegrowing region using BNs.
+Through integrating industry expertise and empirical data, the BN models developed in this research offered a structured and quantitative framework for understanding the complex interactions amongst key factors influencing environmental sustainability.
+The findings highlight the critical role of water quality and availability, emphasising its critical influence on all operational decisions either directly or propagating through other factors.
+With this critical nature being due to water being the most interconnected factor.
+With this high interrelatedness emphasising the importance efficient water management practices enhancing sustainability in viticulture.
+
+Pest and disease management emerged as another significant factor, with effective control strategies having the potential to mitigate excessive agrochemical use and its associated environmental impacts.
+The study also identified the substantial impact of market pressures and economic factors on sustainability practices, illustrating how economic incentives can drive or hinder sustainable vineyard management.
+Of significant relation both in the literature and the BN was climate's influence on all of these factors as well as overall vineyard health.
+The BN models captured the intricate ways these factors interact, highlighting the need for adaptive management strategies to cope with climate variability and change.
+With these factors all being connected in someway within the model through propagation across the BN.
+
+The comparative analysis with existing literature affirmed the relationships explored by the expert panel adding robustness of the study's findings.
+With the BN itself, aligning well with previously identified key factors while providing a more detailed map of their interdependencies.
+The BN approach not only confirmed known relationships but also illustrated how these relationships looked holistically across sustainability within the winegrowing industry.
+
+Overall a comprehensive analysis of key factors and their interactions within the Australian winegrowing industry was gained.
+The use of BN models for further regions could help to inform more specific targeted interventions and policy-making, aiding in the promoting of sustainable practices in the winegrowing industry.
+The integration of expert knowledge and empirical data in this research demonstrates the potential of BNs as powerful decision support tools for sustainability analysis and decision-making in agriculture.
+With the potential to enhance this research being the further incorporation of time, other regional specific considerations and economic outcomes related to these environmental concerns.

### 2024-06-25 article.tex
abstract

@@
 
-The assessment of environmental sustainability in the Australian winegrowing industry remains a complex issue involving changing and compounding factors.
-To address this, we developed a Bayesian Network (BN) using data and expert elicitation to summarise the key factors, their relationships, and how they come together to influence vineyards' environmental outcomes.
-The study leveraged diverse expert perspectives to mitigate biases in probability estimations and promote discourse.
-
-The development of the BN involved an iterative process, including variable selection and definition, the defining of model structure and variable relationships, and finally the determining of relationship significance through probabilities.
-Expert input was pivotal in structuring the BN model, ensuring relevance to industry, and how a variables influence changed across regions and scenarios.
-
-Due to the possible variation in any given vineyard scenario the BN model was expanded to review a case study of the Coonawarra wine region in South Australia.
-This highlighted regional differences between growers whilst also maintaining the significance of industry-wide concerns such as the use of agrochemicals.
-To promote accessibility and scrutiny the BN was further developed into an application, allowing the possibility of further industry and stakeholder feedback; enabling a systematic re-evaluation of significant factors to the wine growing industry and how they change over time.
+Environmental sustainability in the Australian winegrowing industry involves complex, interacting factors.
+To address this, we developed a Bayesian Network (BN) model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes.
+The BN model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability.
+A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use.
+The BN model, accessible via an application, allows for continuous industry feedback and adaptation.
+Future research should explore dynamic BNs to address temporal variations and extend applicability to other regions.
+This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
 
@@
 With the potential to enhance this research being the further incorporation of time, other regional specific considerations and economic outcomes related to these environmental concerns.
+
+% end

### 2024-07-18 article.tex
reviewing article for edits

@@
 % Packages:
-
+\begin{document}
+
+\documentclass[12pt]{article}
 \usepackage{graphicx}
+\usepackage{booktabs}
 \usepackage{listings}
@@
 \section{Introduction}
-TODO: refs
-The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation.
-This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries.
+
+The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}.
+This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
 This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs).
@@
 
-Bayesian Networks are probabilistic models that effectively capture and analyse the interactions between multiple factors in complex systems.
+Bayesian Networks are probabilistic models that effectively capture and analyse the interactions between multiple factors in complex systems~\cite{korbBayesianArtificialIntelligence2011}.
 By integrating expert knowledge and region-specific data, BNs were able to provide a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing.
@@
 This research is guided by several fundamental inquiries aimed at enhancing our understanding of environmental sustainability in viticulture.
-a primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified.
+A primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified.
 Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how factors influence might change regionally.
@@
 
-This study provides critical insight into enhancing environmental sustainability through informed decision-making and targeted interventions by highlighting the sensitivity of different factors to the environmental sustainability of vineyards.
+% This study provides critical insight into enhancing environmental sustainability through informed decision-making and targeted interventions by highlighting the sensitivity of different factors to the environmental sustainability of vineyards.
 The findings have significant implications for the local viticulture industry and offer a replicable framework for other agricultural sectors aiming to achieve sustainability.
@@
 
-% end
+\section{References}
+% Your references text goes here.
+\bibliographystyle{plain}
+\bibliography{references}
+
+\end{document}

### 2024-08-06 article.tex
edits up to methods

@@
 
-%%%%%%%%%%%%%%%
-% Paper setup %
-%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%
-% Working title
-%
-
-% \section{Preamble notes}
-
-% What is your topic?
-The topic of this paper is the environmental sustainability of vineyards within Australia.
-% What is the context for your reserach?
-The context of this research is that the Australian wine sector in general has gone through many tribulations due to economic, environmental and social pressures.
-Previously we attempted to highlight areas of concern through the use of statistical models, which were able to show strong correlations between various environmental and economic factors.
-However, discussions with industry and experts helped to identify that these relationships were not entirely causal, with some management and process of winegrowers obfuscating effects by directly addressing them.
-A key example of this was the lack of water use change during drought periods due to various methods that were used to obtain either more water or to circumvent the detrimental effects of lacking water resources.
-% What do you want to achieve?
-The identification of key factors; and their relation and contribution, direct or indirect, to the environmental sustainability of Australian winegrowing.
-% Are there any relationships you want to explore?
-This is key to this study. The relationships are in many ways more important to the research than the effects.
-
-% Description
-% NB Avoid titles along the lines of: “Effects of ...”, “The role of ...”, etc.  Be specific about the effect and its significance so that your reader knows what is on offer.
-
-% For example, rather than write a title like “The effect of factor X on astrophysical properties of green cheese.”,
-
-% be specific about the effect and write something more like ...
-
-% “Factor X halves the lunar thermal diffusivity of  green cheese”.
-
-% You will usually find it easier to write an effective title if you make your title a sentence.
-
-% Notes
-% N/a
-
-%%%%%%%%%%%%%%%%%%%%
-% Intended readers
-%
-% David Klassen (wine maker Taylors)
-% Dpt Agriculture - EL worker
-        % They would like to know for policy
-% Lawson - asked about OOBNs
-% Winegrower - Someone from the limestones coast. The guy from Robe was interested.
-
-% Description:
-% Name 4 or 5 potential readers - give their names and why they would be interested  (e.g.
-“Ichabod Crane, paleo-fudgologist interested in polygalactic fudginomiality”, not “assorted paleo-fudgologists”).
-
-% Your readers should be outside your institution.
-
-% Notes
-% Many viticulturalists I know of are on the panel. It makes it hard to get one in particular.
-
-%%%%%%%%%%%%%%%%%%%%%
-% Anticipated Journal
-%
-% OIV Congress 2024
-
-% TODO: The original conference has fallen through we will need somewhere else.
-
-%%%%%%%%%%%%
-% Question %
-%%%%%%%%%%%%
-
-% Things to consider
-%
-% Why is the knowledge important?
-% This was identified as a gap within our own prior research and is helpful in creating a basis for scenario assessment and comparison.
-This will allow a greater understanding of how these factors change within different scenarios; whether that be climate, region, business goal.
-% % What is the significance?
-% The significance is to bridge the gap between correlations and data to causal relationships.
-To inform growers using factors that are within their control, or how factors within their control are indfuenced by natural phenomenon.
-% % How will the findings be utilised?
-% These findings will be used to help inform the wider winegrowing community of what factors are most significant to environmental outcomes, and how they interact with one another.
-In practice this study aids a grower through informing them of how decisions impact environmental outcomes and how changing circumstance contribute to these factors and outcomes.
-% % What improvements may be derived from this result?
-% A wider more informed understanding of contributing factors to environmental impact and how different factors relate to one another to contribute to these findings.
-% % Are the terms well defined?
-% The terms are well defined. This was a key outcome of this project.
-% % Do experts think your question is important/relevant/doable?
-% Experts helped to guide this decision, and changed the trajectory of this project in response to data presented and how well they believed they could inform the study.
-
-% % What is the nature of your question?
-% %         who, what, where, when, why, how?
-% What are the key factors that contribute to environmental impact within the Australian winegrowing industry?
-% How do these key factors relate to each other and what are the factors that influence them?
-% What are the decision that can be made by growers that can change the environmental outcomes of their vineyards?
-% How do these factors chagne across well understood scenarios?
-% % You can have more than one question.
-
-% % What is the most important question your paper will pose?
-% What are the key factors to environmental impact within the Australian winegrowing industry, and how are these factors related?
-% % NB It is essential that your answer is framed as a direct question.  Your response must end with a question mark.
-
-% % Why is the question/issue/problem worth examining?
-% By examining the key and relevant factors to vineyards' environmental impacts we can better prepare for future changes in climate pressure, economic restrictions; that is we can better use this model to assess the potential environmental outcomes of the wine industry, as informed by experts, given potential upcoming challenges or changes.
-% % Briefly outline the problem you are tackling and explain why the problem is important to knowledge in general.
-“Nothing much is known” is not sufficient justification by itself.
-You have to show why the gap in knowledge is important.
-Expect to draw heavily on your reading of the literature in framing your answer but do not get into detail of  author and year.
-% The collection of data and subsequent statistical analytics can only go so far as to fill the gap between cause and effects within wiengrowing.
-This research helps to fully understand the relevant decisions being made, how they are informed and what the known outcomes are.
-This helps to align these results to data collected to show stronger causal relationships than pure correlative, or hypothetical postulations of statistical analysis.
-%%%%%%%%%%
-% Answer %
-%%%%%%%%%%
-
-% What is the answer to question
-%
-% 
-% NB  You must give a direct answer to the question posed.
-% Notes
-
-% Will the findings be considered significant?
-
-% How did you gather the evidence? 
-%
-% Briefly outline the methods you used to gather your evidence.
-
-% What is the main evidence?
-%
-% Briefly outline the key results.  Focus on outcomes.
-
-% What can you add to theory?
-%  
-% A research paper has to add to broader understanding. What will yours contribute?  Think about how your results and conclusions will change how people see the world.
-%
-% Many people have trouble with this section.
-Do not recycle the results.
-Focus on the conceptual models that explain why your results are as they are, or why they are different from what might have been expected.
-Your contribution may be something new or it may be confirmation of something already known but in a slightly different context.
-%
-% Sometimes the contribution to theory is not a simple answer but a better understanding of the questions that ought to be asked in future.
-%
-% Again, expect to draw heavily on the literature in framing your answer, but cite the literature only sparingly here (you can go into full detail when you prepare your discussion).
-
-% What can you add to practice?
-%
-% Superior research also has practical consequences.
-What are the consequences of your work?
-Think about how your results and conclusions might change what people do.
-Do not merely restate your results.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Significance and Impact %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Highlight the importance of this
-
-% Stress the practical implications and potential benefits for winegrowers.
-
-%  Explain how your research could influence policy and practice?
-% TODO: How is this done in academia? The result should be measurable? yet many papers do not have impact or it would be considered "industry"? what is the noemclature of this?
-
-%%%%%%%%%%%%%%%
-% Future work %
-%%%%%%%%%%%%%%%
-
-% What remains unresolved?
-% 
-% You may or may not have a lot to say here.  Some of it may be useful in your discussion.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%       Workshop ideas      %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Ice breaker
-% - who are you what are you involved in.
-% Who knows who?
-%
-
-% Ask the expert team to nominate scenarios of interest then enter evidence into the BN to represent these scenarios.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Notes for this article! %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% TODO: I believe this is the diary industry paper.
-
-% The creation of the model was done in the following stages (this is on page xxiv):
-
-%  + The conceptual model
-%  + key sustainability indicators
-%  + Connection of key indicators to available measurable variables
-
-% The identified measurable variables were:
-
-% Econoomy (Farm to gate was used):
-%  + Economics
-        % + Debt
-        % + Assets
-        % + Investment
-%  + profitability
-        % + Interest
-        % + Income
-        % + Competitiveness
-% %  + Work force
-%         + Employment
-%         + Productivity
-%         + Management
-%  + market
-        % + Commodity prices
-        % + Supply
-        % + Risks
-%  + physicals
-        % + Efficiency
-        % + Resource
-        % + Inputs
-%  + commodity prices
-%  + Supply and risks
-
-% Social (across farm, factory and market)
-%  + employment
-        % + Labour
-        % + Training
-        % + Management
-%  + legal and ethics
-        % + Discrimination
-        % + Compliance (regulatory)
-%  + community
-        % + Culture
-        % + Value
-        % + Cohesion (participation/social responsibility)
-%  + health and safety
-        % + Animal welfare
-        % + occupational
-        % + Consumer
-%  + product
-        % + Nutrition
-        % + marketing
-
-% Environment
-%  + Reource Efficiency
-%         + Water
-%         + Energy & emissions
-%         + land and soil
-%  + Waste
-%         + Water Waste
-%         + Solid Waste
-
-% A high | low | medium score was used
-
-%%%%%%%%%%%%%%
-
-% Introduction?
-
-% This research provides valuable insights and data that can inform and guide decisions made by policymakers and industry leaders in the Australian winegrowing sector.
-By identifying key sustainability factors and their interactions, this study offers evidence-based recommendations that can support the development of more effective and sustainable agricultural practices and policies.
-
-% The research for this project has identified that there is no uniform
-% way to measure sustainability, no uniform agreement on indicators
-% that could be used for measurement and even less agreement on
-% which metrics should be used to quantify these indicators. This is
-% best demonstrated that of the 72 triple bottom line frameworks, the
-% indicator water occurred in 64 of these frameworks, although there
-% appeared to be no standard metric identified to measure how water
-% was measured. This is an endemic problem with sustainability
-% measurement.
-
-% The forces which drive the social, economic and environmental sectors, the decision-makers who have the power or influence to accept or reject change, cannot be ignored, if change is to be achieved (van Kerkhoff and Lebel, 2006).It may be that part of the problem with the progress of sustainable development in the past has been the traditional divide between those undertaking the systematic research and those on the ground required to take up and act on the results of such.
-The dissemination of research results has usually only occurred on completion, in a unidirectional, linear communication (van Kerkhoff and Lebel, 2006), whereas, as grounded researchers explain, the ownership of ideas and a willingness to implement these relies on a more collaborative approach from the outset, before research has even commenced.
-It requires acknowledging that experts exist in all spheres and need to be able to share information and debate, in order to come to agreement on issues, assessment tools, priorities for remediation and an optimal approach to solving problems (Corbin and Strauss, 2008; Johnson and Mengersen, 2009), e.g.
-improving sustainability.
-
-% The sustainability Bayesian network model was constructed using
-% open source software and has been delivered as a software package.
-% A future project could focus on making it easier for a wider range of
-% relevant stakeholders to engage with the model. For example a
-% graphical user interface to the model could be developed and
-% then web-enabled so that stakeholders can readily interact with the
-% model and run scenarios.
-
-% The concept of sustainability has been described as the most
-% challenging policy concept ever developed (Spangenberg, 2004).
-% There are more than 100 definitions of sustainability and sustainable
-% development (Labuschagne et al., 2005). The most frequently cited
-% definition comes from the pivotal 1987 World Commission on
-% Environment and Development ‘Brundtland Report’, ‘development
-% that meets the needs of the present without compromising the ability
-% of future generations to meet their own needs’ (WCED, 1987).
-
-% It is necessary to understand the impacts of each system on one another, for example, the impact of industries on climate change, diminishing resources, economic shifts and social change.
-In turn, it is necessary to understand the impact of variables such as these on an industry, its future viability, its surrounding communities and the economies they feed or depend on (Brundtland, 2007).
-Thus, a tool is required that can measure complexity within and between systems and model how changes in one element, positive or negative, might flow on to others.
-Only then can strategies for sustainability be developed with reduced risk of unintended negative consequences (Johnson and Mengersen, 2012).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% references to check:
-
-% https://www.sciencedirect.com/science/article/pii/S1462901122003872
-
-%%%%
-% A triple bottom line planning tool for measuring sustainability; A systems approach to sustinability using the Australian dairy industry as a case study.
-
-% Capra, 1996; 
-% Johnson and Mengersen, 2012)
-
-% Murphy (2002)
-%  A diagram of graphical models!
-
-% The below references are from the previous OIV conference
-%       Interestingly the theme was sustainability.
-
-% 2023-3134: A DIGITAL TWIN APPLICATION FOR VINEYARDS SUSTAINABLE MANAGEMENT
-% Vittorio Faluomi: Tecnovine srl, Italy, vittorio.faluomi@tecnovine.com
-
-% 2023-3299: SUSTAINABLE PRODUCTION OF GRAPEVINE AND WINE IN TEXAS
-% Amit Dhingra: Department of Horticultural Sciences, USA, amit.dhingra@ag.tamu.edu
-
-% 2023-2958: DO SUSTAINABILITY CREDENTIALS NO LONGER SERVE AS A COMPETITIVE ADVANTAGE? - THE
-% QUEST FOR COMPETITIVE PARITY WITH REGARD TO SUSTAINABILITY IN THE WINE INDUSTRY
-% Barbara Richter: Hochschule Geisenheim University, Germany, barbara.richter@hs-gm.de
-
-% 2023-3028: THE BLOCKCHAIN FOR THE SUSTAINABILITY OF DESIGNATIONS OF ORIGIN AND QUALITY AGRI-
-% FOOD DISTRICTS: THE CASE OF VERMENTINO DI GALLURA D.O.C.G.
-% Graziella Benedetto, Forleo Marina: University of Sassari, Italy, gbenedet@uniss.it
-
-%  **************** This one looks super relavent
-% 2023-3044: SUSTAINABILITY ASSESSMENT: TESTING AND VALIDATING A HIERARCHICAL FRAMEWORK IN THE
-% PORTUGUESE WINE SECTOR CONTEXT.
-% Ana Trigo, Ana Marta-Costa, Rui Fragoso: Centre for Transdisciplinary Development Studies (CETRAD), University of Trás-
-% os-Montes e Alto Douro (UTAD)., Portugal, anatrigo@utad.pt
-
-% 2023-3146: USER-GENERATED CONTENT AND RELEVANCE OF SUSTAINABILITY ATTRIBUTES FOR WINE
-% CONSUMERS
-% Miguel-Ángel Gómez-Borja, Inmaculada Carrasco, Juan-Sebastián Castillo: Universidad de Castilla-La Mancha, Spain,
-% miguelangel.gborja@uclm.es
-
-% 2023-2844: THE JOURNEY TO FARMLAND SOIL RESTORATION: UNDERSTANDING AND MEASURING
-% PROGRESS TOWARDS SUSTAINABILITY
-% Alberto Acedo: Biome Makers, Spain, acedo@biomemakers.com
-
-% 2023-3239: ECOLOGICAL CRITERIA FOR A SUSTAINABILITY ASSESSMENT USING THE EXAMPLE OF THE ONLINE
-% CERTIFICATION "NACHHALTIG AUSTRIA" (SUSTAINABLE AUSTRIA)
-% Franz Rosner, Barbara Richter: Federal College and Research Institute for Viticulture and Pomology Klosterneuburg,
-% Austria, franz.rosner@weinobst.at
-
-% 2023-3084: THE IMPORTANCE OF RURAL EXTENSION AND ADVISORY SERVICES TO ACHIEVE A SUSTAINABLE
-% VITICULTURE IN A CLIMATE CHANGE SCENARIO
-% Ana Chambel: AVIPE, Portugal, ana.chambel@avipe.pt
-
-% 2023-3220: EXPLORING BAYESIAN BELIEF NETWORK TO SUPPORT SUSTAINABLE VINEYARD IRRIGATION IN
-% BRAZILIAN SEMI-ARID
-% Luiz Gustavo Lovato: UNICAMP, Brazil, luizglovato@gmail.com
-
-% PO-302
-% 2023-2856: DATA DRIVEN APPROACH TO ENERGY EFFICIENCY IN WINERIES
-% Gellio Ciotti, Marco Bietresato, Alessandro Zironi, Roberto Zironi, Rino Gubiani: Università degli Studi di Udine, Italy,
-% gellio.ciotti@uniud.it
-
-%%%%%%%%%%%%
-% Definitions:
-
-%%
-% Iterative Bayesian network developement cycle
-%
-% \autocite{johnsonIntegratedBayesianNetwork2009}
-% This article  illustrates a proposed integrated Bayesiannetwork  modeling  approach  using OOBNs within theiterative Bayesian network development cycle (IBNDC
-% ^ This is a really comprehensive and well written definition of object orientated bayesian networks!
-% 
-%
-%
-
-%%
-% integrated Bayesian networks
-%
-% The complex nature of environmental issues makes themideal case studies for the use of Bayesian networks as anintegration tool (Varis and Kuikka 1999; Uusitalo 2007;Barton et al. 2008), 
-%
-% Integrated models incorporate other types of tools like regression etc - it is literally what we are doing here.
-I would ask for a better definition from kerrie though.
-The term is used a lot but I cannot find an explicit definition.
-%
-
-%%
-% Self-organising systems.
-%
-% Sustainability is one such complex system.
-It comprises complex interacting factors and processes (e.g.
-in the context of the dairy study: farm, factory and market processes; and environmental, social and economic factors).
-It is self-organising; it does not require external intervention to thrive or deteriorate (e.g.
-an ecosystem can be sustainable through self-organisation).
-It can also exhibit emergent behaviour, since intervening in one part of the sustainability system can have unintended and quite extreme effects in seemingly unrelated parts of the system (Johnson and Mengersen, 2012).
-%
-% These systems are exactly what you think they are. It is described in physics, chemistry, social sciences and philosophy.
-% 
-% The wiki is quite informative.
-%https://en.wikipedia.org/wiki/Self-organization
-
-% Initiatives to improve the environmental impacts of the Australian Wine industry have been ongoing since the 1990s; with recommendations to implement strategies for national programs that would help educate industry members in sustainable practices (Keith Jones, 2002).
-The first legislative initiative to support national programs was the Environmental Management Guidelines for Vineyards in Western Australia during 2002 (Nind, 2002).
-The first national program was the Australian Wine Industry Stewardship, beginning shortly after, during 2004 (WFA, 2009).
-This program was replaced multiple times during the 2000s, first by the Australian Wine Environmental Stewardship, and then by EnviroWine, finally becoming EntWine in 2009.
-The period in the 2000s was further influenced by several key researchers and program leaders, where concurrently multiple regions developed approaches to sustainable management tied to sustainability programs (SWA, 2023).
-EntWine was eventually acquired by the Australian Wine Research Institute and Australian Grape & Wine during 2015; which would lead to its redevelopment into Sustainable Winegrowing Australia (SWA) during 2019/2020 (SWA, 2023).
-%             2.1.2. Previous Research and Motivation
-% During the period of 2010 to 2023 data was collected voluntarily from wine industry members through the national sustainability programs, ultimately being in SWA possession as of 2023.
-The data set was used in 2020 to analyse sustainable practices, resulting in the development of a Resource Intensity Score (RIS); where the RIS was a summary indicator value of a vineyard’s energy use, emissions and water use (Nayak et al., 2020).
-The analysis then fit vineyards’ RIS values to 55 variables sourced from 23 separate wine regions during the period of 2015 to 2018 through the use of Stepwise Regression modelling.
-It was found that the top 10% gross margin vineyards had a lower operating cost and a lower RIS score than vineyards in the bottom 10% gross margin.
-% The motivation for this thesis is to investigate the differences between the top 10% gross margin vineyards and those of the bottom 10%, hoping to uncover what the key differences were and to relate them to sustainable practices; as there is a known gap in the literature due to the difficulty to evaluate relationships using empirical evidence of both the environmental and economic impacts of sustainable practices in viticulture.
-This difficulty stems from data scarcity, industry complexity and transparency.
-While there have been attempts to fill these gaps, methodologies and indicators have lacked in ability to compare different regions and scales (Baiano, 2021).
-%             2.1.3. Economic Pressures
-% Historically strong demands for Australian wine have helped to create a thriving industry, however recently sharp reductions in exports to mainland China due to significant deposit tariffs have caused  a decline of 19% in Australian export value during the 2021-2022 financial year (see Figure 1) (Wine Australia, 2022).
-The pressure brought on by the drop in export value has been exacerbated by loss of tourism and labour due to the COVID-19 pandemic, global freight crisis, war in Europe and rising inflation (Wine Australia, 2021a, 2020).
-These pressures within the wine industry have trickled down to vineyards, where winemakers retain unwanted wine, creating an oversupply of grapes.
-Currently the proposed strategy to soften pressures proposed by Wine Australia includes initiatives focused on market diversification, and sustainability to build resilience in the coming years.
-% Figure 1:  The exports of Australian wine over time in Australian Dollars Free On Board, comparing exports between China and the rest of the world.
-This graphic is taken from the Wine Australia Annual Report of 2020-21(Wine Australia, 2022).
-%             2.1.4. Environmental Pressures
-% There are several environmental concerns that affect viticulture, including loss of soil quality, lack of rain, hail, disease, fire, and frost; with climate change exacerbating these issues.
-In 2020, 40,000 tonnes of grapes were lost across 18 different wine regions due to bush fires and smoke taint; the predicted incidence of wildfires is expected to increase (Canadell et al., 2021).
-In comparison to countrywide pressures such as drought, this damage made up only 3% of the total amount of grapes for that year; although acknowledged as a considerable loss on an individual basis, it was deemed to be only a minor national concern by Wine Australia when compared to other environmental pressures such as drought (Wine Australia, 2020).
-
-%
-%This analysis addresses the knowledge gap regarding the effectiveness of regional level strategies employed in the wine industry and their relation to grape quality.
-% What the hell is a regional strategy
-% And how do you define, or know what trategy each region is using?
-%
-% Through the use of classification trees this study aims to highlight the key differences in sustainable practices at a regional level and how these practices relate to the different grades of grape quality.
-
-% This does not really address what the methods are - aside from classisifcation trees in the most vague sense.
-% What are the results briefly? why should someone read this article?
-% What is interesting - what will be discussed in the article with regard to these results? What makes me want to read the article?
-% And what is the take away point of the article? If I cant be bothered to read this article, what piece of knowledge can you leave mewiwth that I could recommend the article to someone else with?
-
 \section{Title}
@@
 The BN model, accessible via an application, allows for continuous industry feedback and adaptation.
-Future research should explore dynamic BNs to address temporal variations and extend applicability to other regions.
 This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
@@
 This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs).
-A broader model of Australian winegrowing was created, with a more specific case study looking at the Coonawarra winegrowing region being conducted to create a rigorous and quantitative approach to understanding sustainable practices and the relationships between these factors.
+To create a rigorous and quantitative approach to understanding sustainable practices and the relationships between factors associated with these practices, a broad model of Australian winegrowing was created.
+This model was followed by a more specific case study looking at the Coonawarra winegrowing region.
 
-Bayesian Networks are probabilistic models that effectively capture and analyse the interactions between multiple factors in complex systems~\cite{korbBayesianArtificialIntelligence2011}.
-By integrating expert knowledge and region-specific data, BNs were able to provide a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing.
-This methodology not only shed light on current sustainability practices but also identified critical areas for intervention through illustrating the interconnectedness of each of the factors and how they directly or indirectly influence one another.
+BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~\cite{korbBayesianArtificialIntelligence2011}.
+BNs also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiements, outcomes from published literature, and so on.
+In this study, the BNs integrated expert knowledge and region-specific data within a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing.
+This methodology shed light on current sustainability practices, identified critical areas for intervention and facilitated evolution of the potential impact of various management action or climate scenarios.
 
@@
 A primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified.
-Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how factors influence might change regionally.
-Additionally, the study investigates how these factors interact within a Bayesian Network model, providing a framework for understanding their complex interdependencies.
-The final question, looks at how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.
+Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how the relative influence of factors might change regionally.
+Additionally, the study investigates how these factors interact with each other.
+The final question is, how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.
 
-The industry panel was used as a catalyst in the early stages of this research to help explore these multifaceted questions.
-A comprehensive literature review was compiled through both structured searches.
-This extensive review established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing.
-To ensure a robust and comprehensive approach, a combination of qualitative and quantitative methods were employed within the creation of the BN; this included expert consultations and data analysis, which were instrumental in the BNs construction and validation.
-The consultations were done through the use of An industry panel comprising experts in viticulture and environmental sustainability, which provided insights and guidance throughout the research process.
-Their expertise was crucial in defining and quantifying the key factors, and further understanding the specific regional characteristics to Coonawarra.
-Through the integration of industry knowledge and academic research this study aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.
-
-% The results section presents an in-depth analysis of The Coonawarra case study, highlighted significant factors identified by the BN and their interactions.
-Key factors such as water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions were found to be the most influential on environmental sustainability in the region.
-Comparative analysis with another case study BN and existing literature underscores the robustness and relevance of our findings.
-
-% This study provides critical insight into enhancing environmental sustainability through informed decision-making and targeted interventions by highlighting the sensitivity of different factors to the environmental sustainability of vineyards.
-The findings have significant implications for the local viticulture industry and offer a replicable framework for other agricultural sectors aiming to achieve sustainability.
+An industry panel comprising experts in viticulture and environmental sustainability, was convened to guide the project.
+The panel acted as a catalyst in the early stages of the research to help explore the above questions.
+The panel input was supported by a comprehensive literature review, which established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing.
+To ensure a robust and comprehensive BN, a combination of qualitative and quantitative methods were employed in its creation via expert consultations and data analysis.
+The study thus aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.
 
@@
 Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for undervine operations and more purposeful undervine management, as well as the inclusion of further soil based factors that could be significant for particular sites.
-
-% \subsection{Methods notes}
-
-% \citep{mayfieldDesigningExpertledBayesian2023} -> this reference also uses a similar method which we can cite alongside everything else.
-% % These are transcribed notes from Korb & Nicholson:
-
-% \citep{korbBayesianArtificialIntelligence2011} Korb & Nicholson describe three major issues in the creation of Bayesian Networks though knowledge Engineering:
-% - Generating Arc Structure
-% - Parametarisation
-% - dealing with utilities
-
-% Each element within the elicitation process was iteratively 
-% Elicitation was conduct ach  Although workshops focussed on a single issue, it was important to continually address each issue in an iterative fashion.
-The approach to ensuring a sound and sane network, was to directly address common issues that occur during the construction of Bayesian Networks using ellicitation as outlined by #TODO: Korb and Nicholson.
-These issues are similarly highlighted by #:TODO: Pitchforth.
-
-% Transparency with the expert panel was a key ingredient with this approach, highlighting explicitly what these problems were and how we would overcome them.
-This included agreeing upon definitions of each node before connecting edges between them.
-
-% Although originally multiclass nodes existed, the bayesian network was altered to only include binary class nodes. Each edge between a node had to answer the following questions:
-% \begin{enumerate}
-%         \item Are the nodes in the BN the right ones?
-%         % \item Are the state spaces (values) for each node correct?
-%         \item Are the arcs right?
-% \end{enumerate}
-% If the answer to any of the above questions was no; then the structure was not considered sufficiently defined.
-Although we explicitly defined the structure of the BN prior to CPT parametarisation.
-This process continued when adding conditionaly probability values.
-The entire process of construction iinvolved the steps:
-% \begin{enumerate}
-%         \item exposing the panel to a strawman argument/model/definition
-%         \item Outlining the model and the process involved in defining the structure of a BN
-%         \item The expert panel reviewing possible nodes and arcs and definitions
-%         \item Defining their own structure, node or term.
-%         \item Agreeing upon the final definition, structure or model.
-% \end{enumerate}
-% \subsubsection{Trying to build the full model all at once}
-
-% Korb & Nicholson say that it is nearly impossible to build a complex BN all in one go. They recommend:
-% \begin{enumerate}
-%         \item dividing models into subcomponents
-%         \item breaking down the problem into a single target variable
-%         \item reducing the scope of the problem
-%         \item Setting a single time frame for the problem
-% \end{enumerate}
-% The strawman was presented as three subcomponents that pertained to the triple bottom line's environment, economy and social aspects.
-% Within the first workshop it was agreed on by the expert panel to reduce the scope from a triple bottom line to only reviewing the environmental impacts of vineyards.
-This also reduced the BN to a single terminal node.
-It was further decided to create the BN as a single season to limit its complexity.
-
-% \subsubsection{The problem}
-% \subsubsection{Not understanding the problem context, complexity without value.}
-% It is crucial to gain a clear understanding of the problem and its context. This can be seen as answering the following questions:
-% \begin{enumerate}
-%         \item what do you want to reason about?
-%         \item What dont you know?
-%         \item What information do you have?
-%         \item What do you know?
-% These questions are well addressed in prior research.
-The creation of baseline models showed strong linear relationships between many variables.
-The creation of XGBoosted trees uncovered the ability to well inform any particular variable but with no real causal structure or understandability.
-here we seek to pursue causality and link these variables together in a way that is more aligned with a decision support structure than purely as a predictive exercise.
-% \subsubsection{Complexity without value}
-% A very common impulse, when something is known about the problem, is to want to put it in the model.
-But including everything known, just because it is known, simply adds complexity to the model without adding any value (and in fact often reduces value).
-Instead, the knowledge engineer must focus on the problem:
-% "Which of the known variables are most relevant to the problem?"
-% - This issue in its the simplest form has attempted to be overcome through trying to mediate the workshop and inform experts of the potential problem that will come with a cumbersome model.
-% \end{enumerate}
-
-% \subsubsection{Structure - Nodes}
-% The list below is each of the problems, which can be addressed together in some fashion as the approaches of solving them overlap.
-% \begin{enumerate}
-%         \item Getting the node values wrong
-%         \item Node values aren't exhaustive
-%         \item Node values aren't mutually exclusive
-%         \item Incorrect modelling of mutually exclusive outcomes
-%         \item Trying to model fuzzy categories
-%         \item Confusing state and Probability
-%         \item Confusion about what the node represents
-% \end{enumerate}
-% Two major strategies were employed to overcome these problems.
-Tying nodes explicitly to a data source that corroborated the definition and state in some manner as the node.
-For node s that did not have data set they were sought to be defined with an explicit explanation that experts agreed upon or had some external explanation such as legislation.
-
-% \subsubsection{Structure Arcs}
-% \subsubsection{Getting the arc directions wrong}
-% Arc directions are commonly wrong for the following reasons:
-% \begin{enumerate}
-%         \item Modelling reasoning rather than causation
-%         \item Inverting cause and effect
-%         \item Missing variables
-% \end{enumerate}
-% To note: Korb and Nicholson do not actually suggest a method for overcoming these problems.
-There is an inherint risk in creating a model and not having knowledge of a missing variable or of a causation.
-It is important to acknowledge that there is always a possibility that causation is mixed up with reasoning, and that not all variables are always known.
-% \subsubsection{Too many parents}
-% Sometimes it is unavoidable that a node is affected by many factors, or other nodes.
-There are some methods to help overcome this such as divorcing, in which a node is created to capture the cumulative affects of several parents on a child.
-This technique was employed in the creation of the structure of the BN with the expert panel.
-
-% \subsubsection{Parameters}
-% \subsubsection{Experts estimates of probabilities are biased}
-% \begin{enumerate}
-%         \item Overconfidence: The attribution of higher than justifiable probabilities to nodes/events.
-%         \indent The tendency to attribute higher than justifiable probabilities (\citep{lichtensteinCalibrationProbabilitiesState1982} 
-%         \item Anchoring: The tendency towards higher/lower based off of an arbitrary point of comparison.
-"Anchoring" people at a higher or lower than normal prediction because of some assumption or example  \citep{kahnemanPsychologyPrediction1973}.
-%         \item Availability: The assessing of an event as more probable than is justifiable becaues it is more memorable or noticeable \citep{tverskyJudgmentUncertaintyHeuristics1974}.
-
-% \end{enumerate}
-% We have attempted to overcome this with two methods.
-A diverse and varried expert panel.
-Those participanting have experience in multiple vineyards as managers and other duties as well as the panel itself having varied manager/owners from different regions and scale.
-With some experts being more specialised in specific areas such as agro-chemicals.
-% \subsubsection{Inconsistent probabilities}
-% The collection of probabilities for when the CPT is large can result in inconsistent probabilities.
-The collection of probabilities at different times or if probabilities are supplied by different experts can result in inconsistent probabilities as well.
-% The use of desciptors such as very high or low can be of assistance \cite{vandergaag2013elicit}.
-In this study we overcame this through the use of worded response such as high and low.
-We then assigned probabilities to those broader cases.
-We had every expert agree upon each of the probabilities so that they could argue for or against any particular bias and so that the probabilities would even out to a more broader applicability, across all of the experts experiences.
-% % \item Inconsistent "filling in" of large CPTs:
-% -       -       - Being dead certain.
-% \subsubsection{Incoherent probabilities (not summing to 1)}
-% We used software that automatically detected incoherent probabilities when filling in the CPT values to overocme this problem.
-% \subsubsection{Being dead certain}
-% It is important that we limit over confidence (A quote form mark twain was used in the korb and Nicholson). 
-% Our best defence against this was to use multiple experts with different experiences and to challenge them when something was certain. To ask why and to check in about their thoughts.
-
-% \citep{morganUncertaintyGuideDealing1990}
-% Two attributes of good elicitation process are:
-% \begin{enumerate}
-%         \item The expert should be apprised of what is known about the process, especially the nearly universal tendency to overcomefidence and other forms of bias.
-In order to avoid some problems, values should be elicited in random order and the expert not given feedback on how the different values fit together until a complet set has been elicited.
-%         \item The elicitation process is not simply one of requesting and recording numbers but also one of the refining the definitions of variables and terms to be used in the model.
-What values are elicited depends directly upon the interpretation of terms and these should be made as explicit as possible and recorded during the elicitation.
-This is part of the process management described earlier.
-% \end{enumerate}
-% -
-
-% \citep{Boneh2021} Boneh, T.
-(2010).
-Ontology and Bayesian decision networks for supporting the meterological forecasting process.
-Ph.
-D thesis, Clayton School of infomration technology, Monash university
-% Boneh 2010 describe Knowledge Engineering with Bayesian Networks (KEBN) as occurring in a 4 stage life cycle:
-% - Bayesian Network Structure
-% - Probability Parameters
-% - Decision Structure
-% - Utilities Preference
-
-% Pitchforth \citep{pitchforthProposedValidationFramework2013} agrees with this style of structure naming these steps as:
-% - Structure
-% - Discretisation
-% - Parametarisation
-% - Model behaviour
-% - Validation
-
-% Korb & Nicholson have a similar view to Pitchforth. utilising a waterfall style developemental approach which include 5 stages:
-% - Building the BN
-% -       - Structure
-% -       - Parameters
-% -       - Preferences
-% - Validation
-% -       - Sensitivity Analysis
-% -       - Accuracy testing
-% - Field testing
-% -       - Alpha/Beta testing
-% -       - Acceptance testing
-% - Industrial use
-% -       - Collection of Statistics
-% - Refinement
-% -       - Updating procedures
-% -       - Regression testing
-
-% Where discretisation and validation are additional steps to assign intervals to continuous factors (discretisation) and to ensure the models appropriateness (validation)
-
-% With validation incorporating the expert scrutiny of the models begaviour for scenarios, as well as comparing this to both data and other literature.
-
-% \subsubsection{Structure and Conditional Probabilities}
-
-% \subsubsection{Validation}
-
-% \citep{korbBayesianArtificialIntelligence2011}
-
-% % Abstract
-
-% 1. Introduction to Methodology
-
-%     Brief overview of the research approach and the rationale behind using a Bayesian Network (BN) model for sustainability assessment in viticulture.
-%     Mention of the collaborative expert elicitation process and the sequential workshops that shaped the model development.
-
-% 2. Identification of Sustainability Indicators
-
-%     Description of the process for selecting sustainability indicators, including the use of data from Sustainable Wine Australia.
-%     Criteria for indicator selection, focusing on relevance to environmental, economic, and social dimensions of sustainability in winegrowing.
-
-% 3. Expert Elicitation Process
-
-%     Overview of the expert panel composition and the expertise represented.
-%     Objectives and structure of the expert elicitation process, highlighting the series of workshops conducted.
-
-% Workshop 1: Variable Review and Straw Man Model Introduction
-
-%     Objectives: To agree on the sustainability indicators and introduce the initial straw man model.
-%     Activities: Discussion on indicator relevance and definitions; presentation of the straw man model.
-%     Outcomes: Agreement on initial set of variables and conceptual understanding of the model's direction.
-
-% Workshop 2: Model Structure Refinement and Interpolation Method Introduction
-
-%     Objectives: To refine the model's structure and address the complexity of CPTs through an interpolation method.
-%     Activities: Examination of variable relationships; identification of complex CPTs; proposal of the linear interpolation method.
-%     Outcomes: Revised model structure; decision to develop and implement the interpolation method for complex CPTs.
-
-% Workshop 3: Finalization of CPTs and Case Study Selection
-
-%     Objectives: To finalize CPT values using the interpolation method and select a case study for model application.
-%     Activities: Presentation and application of the interpolation method; finalization of CPT values; selection of the Coonawarra wine region for the case study.
-%     Outcomes: Completion of model parameterization; selection of case study region emphasizing the model's practical application.
-
-% 4. Development and Implementation of the Interpolation Method
-
-%     Detailed explanation of the linear interpolation method developed to manage the complexity of CPTs for variables with extensive connections.
-%     Justification for choosing this method and its anticipated impact on the model's usability and accuracy.
-
-% 5. Case Study Application: Coonawarra Wine Region
-
-%     Rationale for selecting the Coonawarra wine region as a case study to apply and test the BN model.
-%     Brief description of how the model was applied to this specific context, including any regional data used and adjustments made for the case study.
-
-% 6. Model Validation
-
-%     Overview of the validation process employed to ensure the accuracy and reliability of the BN model.
-%     Description of internal and external validation measures, including expert review and comparison with independent datasets.
-
-% 7. Conclusion
-
-%     Summary of the methodological approach, emphasizing the collaborative expert elicitation process and the innovative solutions developed for model construction and parameterization.
-%     Brief mention of the significance of the methodology for sustainability assessment in viticulture and potential implications for future research and practice.
 

### 2024-08-06 article.tex
saving edits

@@
 The question of environmental sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
-The question of sustainability requires the consideration of a multitude of factors, not only due to physical differences between locations/habitats but also due to priorities driven by a myriad of perspectives from as consumers, ecosystems, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
-It is important to consider each factor with respect to its relevant perspectives, and to be explicit in how each of these factors and perspectives are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.
+The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
+It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.
 
-Collaboration between experts from different perspectives is a useful method to reconcile opinions of the significance of different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
-In Australia, the views of both industry and consumer are united in their priority to improve greenhouse gas emissions and resource inputs through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
+Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
+In Australia, all of the above groups mentioned are  united in the priority to improve greenhouse gas emissions and resource inputs through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
 While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
-
+% TODO:
+% KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this para out and absorb refs into the lit review.
+G, K and F seem quite relevant but this paragraph doesnt do them justice so expand or move.
+% 
+% Review further comments about this paragraph - its not a good piece of work but it is important to consider how impact and sustainability is or could be measured and interpretted.
+Perhaps go deeper like you did in your confirmation.
 Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being common \citep{gehringerMappingSustainabilityMeasurement2024}.
@@
 Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% End suggestion.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Literature Review}
 
-The literature review was a crucial component of this study, designed to establish a comprehensive understanding of existing knowledge on environmental sustainability in viticulture.
-The review aimed to identify key factors influencing sustainability, understanding their interactions, and to compare findings with the results obtained from the Bayesian Network and expert definitions.
+The literature review was designed to access existing knowledge on environmental sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.
 
-A systematic search strategy was employed to ensure a thorough review of the literature.
-The search included multiple academic journals; with search terms being broadly based on key factors given from the industry panel.
-This approach was used capture a wide range of relevant literature, incorporating keywords associated with viticulture, sustainability, and other agricultural operations related to the definitions provided by the expert panel.
+These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification. 
+% Clarify that the review helped inform the strawman model and was only used as a comparison point afterwards.
+
+A systematic search of terms, broadly based on key factors given from the industry panel, was conducted.
 The general query (adapted to different formats for various journals and bibliographic databases) used for the literature search was:
@@
     \end{lstlisting}
-Inclusion and Exclusion Criteria
 
-To ensure the relevance and quality of the literature reviewed, specific inclusion and exclusion criteria were applied.
+Specific inclusion and exclusion criteria were applied in the literature search.
 Articles were only excluded if they were not available in full text or were not written in English.
-Journals beyond those included were also examined especially where they offered in-depth reviews of sustainability within agriculture or winegrowing; methodological reviews within this context were also included.
+In-depth reviews of sustainability within agriculture or winegrowing and methodological reviews within this context were also included.
 
-Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies used in previous studies.
-The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.
+Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies
+% TODO: Methodologies of what - in this case sustainability, needs to be clarified.
+used in previous studies. The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.
 
-An expert panel comprising specialists in viticulture and environmental sustainability was engaged throughout the literature review process.
+The expert panel comprising specialists in viticulture and environmental sustainability was engaged throughout the literature review process.
 The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.

### 2024-08-08 article.tex
saving edits progress

@@
 The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.
-By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture.
+% By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture.
 This approach ensured that the study's results were not only robust and scientifically sound but also practically relevant and actionable for industry stakeholders.
@@
 
-A Bayesian Network is a graphical model, being comprised of nodes and edges.
+A BN is a graphical model, comprising of nodes and edges.
 Uniquely, Bayesian Networks contain the network's operations within the nodes themselves instead of across the edges.
-This is done in the form of probability tables, with connections being informed by the edges.
-There is simplicity within the calculations done within a node, as it is fundamentally achieved through sum and division operations.
+In the BN structure adopted in the study, these operations were encapsulated through a conditional probability table for each node, with connections between the nodes being defined by edges.
+This results in computational simplicity, since each node is dependent only on its parent and simplicity within the calculations are achieved through sum, multiplication and division operations
+% .
 However, great complexity is introduced when a node is informed by many parents, which can also have many parents themselves.
-The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes \citep{korbBayesianArtificialIntelligence2011}.
-The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.
+The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes
+\citep{korbBayesianArtificialIntelligence2011}.
+% The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.
 
-The use of a Bayesian Network allows for the ability to include perspectives from industry experts and create a causal structure.
-The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact \citep{pourretBayesianNetworksPractical2008}.
-Furthermore, data collected across Australia could also be used to help inform both scenarios and the model alongside expert opinion.
+The use of a BN allowed for collaboration between experts to create a causal structure, identifying important factors and agreeing on the relationships between factors
+%.
+The ability to include perspectives from industry experts and create a causal structure.
+The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact
+\citep{pourretBayesianNetworksPractical2008}.
+Furthermore, data collected across Australia could also be used to help inform the model structure as well as quantify the associated conditional probabilities alongside expert opinion.
 
-The calculations of a Bayesian Network are based on Bayes' theorem, shown as follows
-\begin{equation}\label{bayesformula}
-P(A|B)= {P(B|A)P(A)}\over{P(B)}
-\end{equation}.
+% The calculations of a Bayesian Network are based on Bayes' theorem, shown as follows
+% \begin{equation}\label{bayesformula}
+% P(A|B)= {P(B|A)P(A)}\over{P(B)}
+% \end{equation}.
 
-Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
+% Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
 Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes.
@@
 
+Given the directed acyclic graph (DAC) structure of the BN, each quantification of a node only depends on the parent of that node, and is conditionally independent of the other nodes in the network collectively, then,
+
 \begin{equation}
-        \mathbb(P) (X_{1}=x_{1},...X_{n}=x_{n})=\prod_{n}^{i=1}p(x_{i}|x_{Parents(i)})
+        p(x_{0}=x_{0}) (X_{1}=x_{1},...X_{n}=x_{n})=p(n|x_{parents})\prod_{n}^{i=1}p(x_{i}|x_{Parents(i)})
 \end{equation},
-for a selected node $i$ given the parents and their local conditional distributions.
+
+% for a selected node $i$ given the parents and their local conditional distributions.
+Where $x_0$ is the target variable and $x_i$ denotes the quantified information in the i$^th$ node, and $p$ denotes its probability distribution.
 

### 2024-08-13 article.tex
Update article.tex

@@
 
-The iterative nature, or the ability to show the difference in probable outcomes of different sets of events and their uncertainty allows for the ability to conduct inference.
-This type of Bayesian inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present.
+The ability to present different probable outcomes for various sets of events and their associated uncertainties enables the conduction of inference.
+This inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present.
 The sets of different outcomes then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods.
-
-One of the greatest abilities within this style of inference is Marginalization.
+One of the greatest abilities of this type of inference is Marginalization.
 In which, the outcome of a particular event can be determined irrespective of other outcomes.
-This type of marginalisation is intuitively represented as nodes conditional independence is illustrated inherently through the structure of the graph by its edges.
+This type of marginalisation is intuitively represented as nodes conditional independence and illustrated inherently through the structure of the graph by its edges.
 
 Bayesian Networks created in this study were created using BayesFusion \citep{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities.
-The use of Bayes fuse software was used both through the GUI interface and the SMILE API \citep{bayesfusionGeNIeModelerUSER2022} system using C++ \citep{ISO:2012:III}.
+The Bayes fuse software was used both through the GUI interface and the SMILE API \citep{bayesfusionGeNIeModelerUSER2022} system using C++ \citep{ISO:2012:III}.
 
-\subsection{Elicitation}
+\subsection{BN Construction and Quantification}
 
-The Bayesian Network was constructed using a mixture of data and expert elicitation.
-The format followed recommendations from \cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}.
-Where, we progressed iteratively through from problem definition, to structure, to parametarisation, and then to validation.
-Experts were initially informed regarding the process to establish an understanding of what each step would be comprised of, as well as highlighting common pitfalls and how we would address them.
-With common problems being listed by both authors being:
-\begin{enumerate}
-        \item Not understanding the problem context
-        \item complexity without value
-        \item Getting arc directions wrong
-        \item too many parent nodes
-        \item Bias expert estimates
-        \item Inconsistent probabilities
-        \item Being absolutely certain
-\end{enumerate}
+The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by \textcite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}.
+The process progressed iteratively through problem definition, structure, parameterization, and validation.
+Initially, experts were informed about the process to ensure a clear understanding of each step and to highlight common pitfalls, as well as how these would be addressed.
+Some of the common problems identified by both authors include a lack of understanding of the problem context, the introduction of complexity without value, incorrect arc directions, an excessive number of parent nodes, biased expert estimates, inconsistent probabilities, and an unwarranted certainty in estimates.
 To address these issues, experts were kept well-informed of them, as well as variable definitions and problem scope.
@@
 
-\subsection{CPT interpolating}
+\subsection{CPT interpolation}
 
-As is often the case, the most arduous endeavour is to attribute probabilities to events defined within the Bayesian Network \citep{korbBayesianArtificialIntelligence2011}.
-Due to the growing complexity of the network throughout the study each event was described by binary classes.
-With the classes depicting a positive or negative contribution to a vineyard's environmental outcome.
-Furthermore, the complexity of the variables, particularly water use, were overwhelmingly interrelated to operations across the vineyard.
-To attempt to capture this complexity but not dilute the ability to work with various scenarios the conditional probabilities were interpolated.
+As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network \citep{korbBayesianArtificialIntelligence2011}.
+For reasons of comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes.
+The classes represented a positive or negative contribution to a vineyard's environmental outcome helping to reduce this complexity.
+Furthermore, the intricacy of variables, particularly water use, were overwhelmingly interrelated to operations across the vineyard.
+To attempt to capture this complexity but not dilute the ability to work with various scenarios experts were asked to provide key input into complex CPT cells and the CPT cells were interpolated.
+The experts then reviewed and amended or approved the derived CPTs.
 
-This method utilised interpolation between two anchored points.
+This interpolation method utilised filling in cells between two anchored points.
 One point represented the case of all factors being true/positive and the other represented all factors being false/negative.
-The interpolation was achieved by designating each factor an attributed weight; where, weights were indicative of a factor's overall influence to its child node.
+The interpolation was achieved by designating each factor an attributed weight, where weights were indicative of a factor's overall influence to its child node.
 During workshop discussion participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.
 
-Using this method, any given probability can be calculated using
+Using this method, a given probability was calculated using
 \begin{equation}
-        p=x\sum_{i}^{n} + y\sum_{m}^{i} 
+        p=x\sum_{i}^{n}\alpha_{i} + y\sum_{i}^{m}\beta_{i} 
 \end{equation},
-for n number of true or contributing factors and m false or not contributing factors. We know the solutions for when all contributing factors are true ($p_t$) or all were false ($p_f$). Where,
+n count of true (or ideal states) and m false (or not ideal states) factors. The solutions for when all contributing factors are true ($p_t$) or all are false ($p_f$) is,
 \begin{equation}
-        p_t=x\sum_{i}^{n} 
+        p_t=x\sum_{i}^{n}\alpha_{i} 
         \text{ and }
-        p_f=y\sum_{m}^{i}
+        p_f=y\sum_{i}^{m}\beta_{i}
 \end{equation}.
-From here values for $x$ and $y$ are able to be derived using the sum of the provided weights.
+The values for $x$ and $y$ can be derived using the sum of the provided BN weights.
+An assumption of 'smoothness' is taken between worst and best case scenarios when utilising this method.
+All possible combinations between all states being true (or ideal) and all being false (not ideal) are also mirrored such, with the only consideration being given, is that of how heavily weighted a variables state is compared to the others.
 
-\subsection{Validation}
+\subsection{BN Validation}
 
-The method for validation sought to address concerns presented by \citep{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
-Validation steps were partly incorporated during the process of constructing the Bayesian network itself.
-Specifically when considering the nomological validity of the network; the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario.
-In part, the selection process for experts, aspired to be diverse within their regional knowledge and expertise in an attempt to broaden the ability to critique choices.
-Although it was agreed that multiple scenarios were well captured by the trees structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions.
-This requirement aligned with literature, which highlighted how regional variation is considered a driving factor for many vineyard outcomes and priorities \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
+The method for validation sought to address criteria presented by \textcite{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
+Nomological validity refers to ensuring that the BN fits within a broader theoretical context, aligning with established literature.
+Face validity involves evaluating whether the model appears to be a valid representation based on expert judgment.
+Content validity checks that the model includes all relevant factors and relationships from both literature and expert knowledge, ensuring nothing critical is omitted.
+Concurrent validity is concerned with whether the BN or its components behave consistently when compared with other similar networks.
+Convergent validity assesses how closely the BN aligns with models that describe similar systems, while discriminant validity ensures that the BN is distinct from models representing different systems.
+Finally, predictive validity examines the BN's ability to accurately predict system behavior.Validation steps were partly incorporated during the process of constructing the Bayesian network itself.
+When considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario.
+The selection process for experts, encouraged diversity in their regional knowledge and expertise in order to broaden the ability to critique choices.
+Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
 
-The Face and content validity of the network was questioned directly by the expert panel through the structure and conditional probability phases.
-The choice of binary discretisation was due to two reasons; that it captured the relevant contribution to the node in question and limited the model from becoming to overly complex and circumstantial.
-This helped to avoid some overtly specific scenarios in favour for broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
-This approach went hand in hand with the content validation.
-Where, it was found that the limitation of the model was primarily regional, which aligned again with the findings of other researchers \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
-Specifically, the question of water resources, which was central to the model and highly interrelated \citep{carmonaUseParticipatoryObjectOriented2011}.
+The face and content validity of the network was questioned directly by the expert panel through the structure and conditional probability phases.
+This helped to avoid some overtly specific scenarios in favour of broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
+This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
+% Specifically, the question of water resources, which was central to the model and highly interrelated \citep{carmonaUseParticipatoryObjectOriented2011}.
 
-Similarly, the convergent validity of the model was accomplished through the broader discretisation of nodes into the binary forms of positive and negative affects on the environmental impact of the vineyard.
-This manner of discretisation allowed a clear delineation in localised subnetworks within the model.
-The alignment of the model to other research helped to further answer questions of concurrent validation.
-In that, it was found that other studies emphasised the same variables selected by our experts.
+Similarly, the convergent validity of the model was accomplished through the checking the alignment of the model to other research, which helped to further answer questions of concurrent validation.
+This process was undertaken after the regional models were developed in unison with the literature review and creation of leximancer concept map.
+It was found that other studies emphasised the same variables selected by our experts.
 This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes \cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}.
@@
 
-The structure of the model itself was similar to other models in the presence of variables but differed in some of their relation due to the terminal node being environmental impact.
-The paramitisation of the nodes did differ to other studies, as every node was related and thought of with regard, to the terminal node and how they subsequently affected the environmental outcomes of a vineyard and not other more prevalent outcomes such as yield \citep{laurentReviewIssuesMethods2021}.
+The factors within the BN had similar parent nodes to factors that appeared in other models from the literature (i.e yield generally utilised area, water, fuel as predictors), although there were key differences.
+The differences were primarily due to the consideration of nodes as factors that related and were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the environmental outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation \citep{laurentReviewIssuesMethods2021}.
 The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being able to be properly employed.
@@
 \subsection{Sensitivity analysis}
+% TODO: add a paragraph about what you mean by sensitivity analysis and why a BN facilitates this, its important! KM
+The sensitivity analysis conducted in this study utilised the Bayesian Network software GeNie, implementing the algorithm developed by \textcite{article}; an optimisation of \textcite{Castillo1996ANM} and \textcite{Gaag1998PracticableSA}.
+The method allowed for efficient computation of the influence of parameter variations on the output probabilities of the BNs terminal node 'Environmental Impact'.
 
-The sensitivity analysis conducted in this study utilised the Bayesian Network software GeNie, implementing the algorithm developed by \cite{article}; an optimisation of \autocite{Castillo1996ANM} and \cite{Gaag1998PracticableSA}.
-The method allows for efficient computation of the influence of parameter variations on the output probabilities of a Bayesian network, making it particularly suitable for complex models.
-Sensitivity was calculated on the terminal node 'Environmental Impact' to reflect its sensitivity to changes in other nodes.
-
-The process utilises two outward and an inward propagation across a junction tree, a data structure representing the Bayesian network.
+The process utilises two outward and one inward propagation across a junction tree, a data structure that represents the Bayesian network by organizing its nodes into a tree of cliques, where each clique is a subset of nodes that are fully connected within the network.
+Propagation refers to the method of passing messages (or updating beliefs) through this junction tree to ensure consistency across the network, allowing for the efficient calculation of probabilities.
 These propagations are essential for establishing the necessary cliques that allow for the calculation of the sensitivity function using the coefficients $\gamma$ and $\delta$.
@@
 
-Where $y$ is the posterior marginal of interest, given evidence $e$, with respect to the parameter $x$.
+where $\alpha$, $\beta$, $\gamma$ and $\delta$ are constants with respect to $x$.
+$y$ is the posterior marginal of interest, which refers to the probability distribution of a subset of variables (in this case, $y$) after taking into account the given evidence $e$, with respect to the parameter $x$ (a factor or state of a node within the BN).
 
@@
 
-Due to the regional limitations of the model, experts proposed a case study of a specific and well understood region: Coonawarra in South Australia.
+% #TODO: make sure this fits in ~ moved paragraph
+Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture.
+The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}.
+Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around environmental sustainability practices to specific regional factors.
+
+As discussed above the expert advisory panel proposed the development of a reigonal model to augment and focus the primary general model.
+For specificity the panel proposed a case study of a specific and well understood region: Coonawarra in South Australia.
 The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing.
-The Coonawarra BN was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.
+The Coonawarra BN was based on the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.
 Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for undervine operations and more purposeful undervine management, as well as the inclusion of further soil based factors that could be significant for particular sites.
@@
 
-The key factors identified were defined as shown in Table \ref{tab:definitions}.
+The key factors identified by the industry panel and their agreed definitions are shown in Table \ref{tab:definitions}.
 By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed by the industry panel.
@@
 %
+
+% TODO: table caption!@!
 \begin{table}[h]\label{tab:definitions} 
@@
     \toprule
-    \textbf{Variable name} & Definition & \textbf{Ideal Class} & Not Ideal Class \\ \midrule
+    \textbf{Factor name} & Definition & \textbf{Ideal Class} & Not Ideal Class \\ \midrule
     \textbf{Water use} & Total amount of water used by a vineyard in a financial year (ML/Ha) & \textbf{Low} & High \\
@@
 
+% TODO: you need a new heading as its the BN strucutre not key factors
 \subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
 
-The relationships between the concepts defined by the industry panel are depicted in~\ref{figure:generalBN} as nodes in the Bayesian Network.
-The network highlights which factors are influenced by others in the form of an acyclic directed graph.
+The relationships between the facets in Table \ref{tab:definitions}  as agreed by the industry panel, are depicted in the BN model in Fig ~\ref{figure:generalBN}.
+The BN highlights which factors are influenced by others in the form of an acyclic directed graph.
 Notably, the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
@@
     % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
-    \caption{The resultant Bayesian network after initial discussions of how factors that contribute to environmental impact are related.
-Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}\label{fig:generalBN}
+    \caption{The resultant BN illustrating the relationships between vineyard factors and environmental impact in Australian winegrowing.}\label{fig:generalBN}
 \end{figure}
+% TODO: expand the description of the figure to indflude the blue, green ghold and pink definitions.
 
-The BN provided a comprehensive overview of how factors defined by the industry panel, would interact.
+% The BN provided a comprehensive overview of how factors defined by the industry panel, would interact.
 Showing not only direct relationships but also how changes in one factor can propagate through the network to affect others.
@@
 
+% TODO: expand, you have built the reader up to this point so do justice to the BN!
 Figure~\ref{fig:generalBN}, illustrates the importance of water, disease/pests and climate through their prominent connections and numerous child nodes.
@@
 
-The bibliometric analysis using Leximancer, revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry.
+% TODO: Reults of lit review: no. articles, etc Here
+
+The bibliometric analysis using Leximancer revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry.
 The most prominent concept was water (see Table \ref{tab:lexi}).
-The critical importance of other variables being measured by their comparative appearance in articles relative to water (making water 100\%).
+The critical importance of other variables is indicated by their comparative appearance in articles relative to water (making water 100\%).
 
@@
 \begin{table}[h]\label{tab:lexi}
+    \caption{Table \ref{tab:lexi} Table \ref{tab}: Key Concepts Identified in the Bibliometric Analysis of Environmental Sustainability in the Australian Winegrowing Industry.}
     \begin{tabular}{@{}lrr@{}}
@@
 
-The most significant concepts along with "water", included "change", "climate", and "disease".
-These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see \ref{tab:lexi}).
+The most significant concepts along with water, included change, climate, and disease.
+These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see Table \ref{tab:lexi}).
 Furthermore, change and climate were kept separate to illustrate the variety of different changes, such as in practice, legislation and resource abundance.
@@
 
-The prominence of different factors is visually described in Figure \ref{fig:lexi}, with the network depicting the frequency of these concepts appearing together.
-With the major concepts of these features being change, grapevine, water and land.
-These concepts illustrated the overarching theme between how the different concepts are connected, which showed very similar themes to that of the industry panel.
+The prominence of different factors is visually described in Figure \ref{fig:lexi}, with the size of nodes in the diagram depicting the frequency of these concepts appearing in literature.
+Figure \ref{fig:lexi} also illustrates the connection between concepts through edges, and overlaying the most related concepts, change, grapevine, water and land as coloured areas on the diagram.
+With the most related concepts being of similar themes to that of the industry panel's Bayesian Network.
 
@@
 
-A key difference between the concepts from Leximancer and the Bayesian Network was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease.
-With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls.
+A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease (even though disease was quite prominent in both).
+% With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls.
 Together these outputs provide a comprehensive overview of the key factors affecting environmental sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement.
@@
 
-\subsection{Sustainability specifics: Coonawarra Winegrowing}
-
-Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture.
-The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}.
-Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around environmental sustainability practices to specific regional factors.
+\subsection{Region-specific BN: Coonawarra}
 

### 2024-08-13 article.tex
Update article.tex

@@
 \subsection{Region-specific BN: Coonawarra}
+% TODO: add CPTs to appendix
+
+Two distinct BNs were constructed for the Coonawarra region, each reflecting alternative points of view taken by experts.
+The models diverged in their structural representations with a differing emphasis on specific causal relationships.
+One BN  (see Figure \ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between weather conditions and agrochemical scores.
+The other BN, while structurally similar, did not include these connections.
+The use of two separately scored BNs with differing structure ensured that the BNs captured the diversity of expert views regarding the primary drivers of environmental outcomes in the region.
 
@@
 The resultant two models represent the final consensus, reflecting the diverse perspectives and occasionally differing viewpoints among the experts, necessitating the development of two distinct but complementary models.
+
+Key factors impacting environmental sustainability in Coonawarra were examined by developing region-specific BNs, Figure \ref{fig:robyn} and Figure \ref{fig:marcel} were based on the generic structural model illustrated in Figure \ref{fig}.
+The general model was adapted to reflect the unique regional characteristics of Coonawarra, resulting in some structural differences between the region specific models as well as the original generic model.
+These adaptations allowed us to review the interactions between key environmental factors such as water use, agrochemical application, soil health, and climate conditions.
+The importance of these variables is highlighted through their relative weightings, as determined by expert input, offering a nuanced understanding of sustainability in the Coonawarra wineregion.The two case study BNs are almost identical in their significant factors and interactions.
+Both emphasize the importance of water quality, pest and disease management, and climate conditions.
+The primary difference is the sensitivity to tractor passes, water quality, water scarcity, and soil degradation management, with Figure \ref{fig:robyn} showing higher sensitivity to these factors.
 
@@
 The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors such as soil show variation not only at a regional level but sometimes at the paddock level as described by the expert panel.
-Figure \ref{fig:robyn} and \ref{fig:marcel} highlight the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
-It is important to acknowledge that this analysis also illustrates that further work would be required to describe other regions or specific vineyards.
+Figures \ref{fig:robyn} and \ref{fig:marcel} highlight the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
 
-The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management and tractor passes.
-In one, greater tractor passes were used purposefully to manage the vineyard floor; the other managed vineyard floor as a consequence of tractor passes, leveraging opportunities when the tractor was used.
-This distinction highlights how operational decisions can vary based on regional practices and priorities.
+The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes.
+In Figure \ref{fig:marcel}, greater tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used.
+This distinction highlighted how operational decisions can vary based on regional practices and priorities.
 A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land.
@@
 As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture.
-The edges between different factors reveals that water is the most connected.
-Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.Within both of the models, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions.
+Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
+Within both of the models, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions.
 These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.
 
-The influence of factors on each other are described through the CPT values (see appendix) and allow for an in-depth analysis of how changes in key factors, under various environmental and regulatory scenarios, influence the overall environmental impact.
-For instance, the significant sensitivity that environmental impact had with regard to pests/disease, climate and agrochemicals compared to factors such as green house gas emissions.
-Importantly that these sensitive factors also link greatly to one another, highlighting how critical areas for regulatory and environmental interventions can be to multiple factors beyond their specific target.
-Furthermore, the relationships help to illustrate the further complexity of how these significant factors relate to these further considerations such as greenhouse gas emissions and the extended connection to fuel or electricity use.
-Where addressing issues such as disease can require the increased use of tractors and thus fuel.
+The CPT values (see appendix) describe how factors influence each other, allowing for a detailed analysis of environmental impact under various scenarios.
+Environmental impact was particularly sensitive to management strategies (pest, disease, soil carbon and spray applications) in both BNs.
+These sensitive factors are closely linked to resource use variables (water, fuel and electricity), showing how targeted regulatory and operational interventions can influence multiple sustainability aspects beyond their immediate focus.
 
-The Coonawarra-specific BN supports the findings from the literature, with a more structured map of how factors interact compared to the automatically generated figures from tools like Leximancer.
+The Coonawarra-specific BNs both support the findings from the literature, with a more structured map of how factors interact compared to the Leximancer summary in Figure \ref{fig:lexi}.
 The BN provides a detailed view of the relationships between factors, highlighting the central role of water and the interconnectedness of pest management, market pressures, and climate conditions.
@@
 
-The two case study BNs are almost identical in their significant factors and interactions.
-Both emphasize the importance of water quality, pest and disease management, and climate conditions.
-The primary difference is the sensitivity to tractor passes, water quality, water scarcity, and soil degradation management, with one model showing higher sensitivity to these factors.
-Aside from the role of tractor passes, there are no major differences between the two BNs.
+%  Aside from the role of tractor passes, there are no major differences between the two BNs.
 The similarity in significant factors and their interactions underscores the robustness of the BN approach in capturing the critical elements of environmental sustainability in winegrowing.
-
-The findings from the case study align closely with the literature, illustrating more directly how factors that contribute to environmental sustaianbility are connected.
-The BNs provide a detailed and structured view of primary factors and their relationships to secondary and tertiary concerns within the industry.
-This detailed evaluation helps prioritise actions and policies that could lead to significant improvements in the sustainability practices of winegrowing regions.
 
@@
 These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing.
-A keener understanding of how these factors both interact and effect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables.
+A keener understanding of how these factors both interact and affect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables.
 The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
@@
 
-Of further significance was the management of pests and diseases, market pressures and climate.
-With these external influences being prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
-In particular, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease~\cite{boisClimateVsGrapevine2017}.
-Of great concern to climate was how it influenced water availability, pest/disease pressures, and its overall contribution to vineyard health.
+Further significant factors were the management of pests and diseases, market pressures and climate.
+Factors that were caused by external events such as seasonal changes were prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
+Importantly, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease~\cite{boisClimateVsGrapevine2017}.
 Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change~\cite{agostaRegionalClimateVariability2012,alsafadiFutureScenariosBioclimatic2023,barriguinhaVineyardYieldEstimation2021,sharmaChapterImpactClimate2014}.
@@
 The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~\cite{baianoOverviewSustainabilityWine2021}.
+
+% The findings from the case study align closely with the literature, illustrating more directly how factors that contribute to environmental sustaianbility are connected.
+The BNs provide a detailed and structured view of primary factors and their relationships to secondary and tertiary concerns within the industry.
+This detailed evaluation helps prioritise actions and policies that could lead to significant improvements in the sustainability practices of winegrowing regions.
 

### 2024-08-14 article.tex
Final KM edits
Ready for Mardi

@@
 While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
-% TODO:
+% old comment
 % KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this para out and absorb refs into the lit review.
@@
 Perhaps go deeper like you did in your confirmation.
-Methods for measuring sustainability comprise a wide variety of approaches with the use of index systems being common \citep{gehringerMappingSustainabilityMeasurement2024}.
+Methods for measuring sustainability comprise a wide variety that of approaches with the use of index systems being common.
+The use of index systems is beneficial in comparing sustainability performance across different industries or geographic regions.
+As \textcite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
 Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citep{floresWhatSustainabilityWine2018}.
-The measuring of sustainability through the use of these tools can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}.
+The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}.
+For instance, frameworks like MESMIS categorize sustainability measures into "descriptors" (guidelines), "indicators" (metrics for measuring changes), and "parameters" (limits for indicators) \citep{candido_sustainability_2015}.
+This structure allows for a more granular assessment of sustainability by linking broad guidelines to specific, measurable outcomes.
+By focusing on key indicators such as soil health, water usage, and biodiversity, the sustainability of wine production practices can be gauged with greater precision.
+These proxy measurements are crucial for understanding how specific actions or practices affect broader environmental outcomes, thereby enabling more targeted and effective sustainability efforts.
 Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
@@
 % This is the query in a code-like format.
-\begin{lstlisting}[language=]
+\begin{lstlisting}[language=]\label{query}
     (Water OR Agrochemical OR Chemical OR Ground management OR Pest OR Disease OR Management OR Electricity OR Energy OR GHG OR Emissions OR Greenhouse gas emissions OR Environmental OR Environment OR Ecological OR Fertiliser OR Fertilizer OR Fuel OR Biofuel OR Price OR Nutrient OR Runoff OR Leeching OR Market OR Supply and demand OR Soil OR Organic carbon OR SOC OR Tractor OR Field OR Operations OR Weather OR Climate OR Yield OR Production)
@@
 
-Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies
-% TODO: Methodologies of what - in this case sustainability, needs to be clarified.
-used in previous studies. The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.
+Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies used in studies that analysed any of the concepts listed by experts.
+The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.
 
@@
 \subsection{Sensitivity analysis}
-% TODO: add a paragraph about what you mean by sensitivity analysis and why a BN facilitates this, its important! KM
-The sensitivity analysis conducted in this study utilised the Bayesian Network software GeNie, implementing the algorithm developed by \textcite{article}; an optimisation of \textcite{Castillo1996ANM} and \textcite{Gaag1998PracticableSA}.
+
+Sensitivity analysis is a crucial step in evaluating the robustness and reliability of a BN model.
+It involves assessing how variations in input parameters influences a selected variables resultant probability distribution (or posterior in this case).
+In this study, sensitivity analysis was used to visualise the impact of factors on the environmental impact node.
+This was used to provide insight into which factors had the most influence on environmental impact, the BNs terminal node.
+BNs facilitates sensitivity analyses by allowing for the systematic examination of how small changes in one or more input variables affect the probability distribution of a selected node.
+This is particularly important when reviewing the sensitivity analysis in the context of environmental impact as it adds to the understanding of how relationships between variables and their potential impacts can guide decision-making or improve model accuracy.
+
+In this study, the sensitivity analysis conducted utilised the Bayesian Network software GeNie, implementing the algorithm developed by \textcite{article}; an optimisation of \textcite{Castillo1996ANM} and \textcite{Gaag1998PracticableSA}.
 The method allowed for efficient computation of the influence of parameter variations on the output probabilities of the BNs terminal node 'Environmental Impact'.
@@
 
-% #TODO: make sure this fits in ~ moved paragraph
+Due to Coonawarra's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying BNs.
 Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture.
@@
 
-% TODO: table caption!@!
 \begin{table}[h]\label{tab:definitions} 
     \begin{tabular}{@{}llll@{}}
+        \caption{\textbf{Table 1:} This table provides the definitions of key terms and concepts utilised throughout the study.
+Each term is explained in the context of its relevance to the terminal node environmental impact.
+The table was used by experts throughout the study to maintain clarity and meaning behind concepts and how they related.}
     \toprule
@@
 
-% TODO: you need a new heading as its the BN strucutre not key factors
-\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}
+\subsection{Bayesian Network Structure for Environmental Sustainability in Australian Winegrowing}
 
@@
     % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
-    \caption{The resultant BN illustrating the relationships between vineyard factors and environmental impact in Australian winegrowing.}\label{fig:generalBN}
+    \caption{The resultant Bayesian Network (BN) illustrating the relationships between vineyard factors and environmental impact in Australian winegrowing.
+The network's nodes are color-coded to indicate the source and nature of the data: Blue nodes represent expert-led ideas that are not directly supported by data, Green nodes are supported by data contained in Sustainable Winegrowing Australia's database, and Gold nodes correspond to variables with readily accessible public data.
+The terminal node is highlighted in pink.}\label{fig:generalBN}
 \end{figure}
-% TODO: expand the description of the figure to indflude the blue, green ghold and pink definitions.
 
@@
 
-% TODO: expand, you have built the reader up to this point so do justice to the BN!
-Figure~\ref{fig:generalBN}, illustrates the importance of water, disease/pests and climate through their prominent connections and numerous child nodes.
-Variables such as fuel use and soil management are resultant children nodes that connect these external pressures to decisions that offer potential solutions or interventions to aid in pursuing more sustainable outcomes.
+Figure~\ref{fig:generalBN}, illustrates the intricate relationships between various vineyard factors and their impact on environmental sustainability in the Australian winegrowing industry.
+The BN structure highlights the critical role of water, disease/pest management, and climate, which are depicted as central nodes with numerous connections to other variables.
+These connections underscore the importance of these factors as key drivers of environmental impact, influencing a wide number of other nodes within the network.
+
+The network shows how external pressures, such as water availability and climate variability, have cascading effects on vineyard operations.
+For instance, variables like fuel use and soil management emerge as child nodes within the network, representing operational decisions that respond to these external pressures.
+The BN effectively captures the complexity of these interactions, illustrating how decisions made at the operational level, such as the optimisation of fuel use or improving soil management practices, can serve as potential interventions to lessen environmental impact.
+These interventions are critical in pursuing more sustainable outcomes, mitigating the adverse effects of environmental stressors, and enhancing the resilience of the winegrowing system.
+
+By mapping these relationships, the BN provides a visual and analytical framework that aids in identifying the most influential factors and understanding their interdependencies.
+This, in turn, helps inform decisions toward more environmentally sustainable practices.
 
@@
 
-% TODO: Reults of lit review: no. articles, etc Here
+As part of this study, a comprehensive literature review was conducted to assess the current state of research on environmental sustainability in the winegrowing industry and as part of the BNs validation.
+The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see \ref{query}).
+The articles span a range of topics, including sustainability metrics, operational practices, and the influence of regulatory frameworks on environmental outcomes.
 
+The number of articles that contained key terms is outlined in Table \ref{tab:lexi}.
 The bibliometric analysis using Leximancer revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry.
 The most prominent concept was water (see Table \ref{tab:lexi}).
-The critical importance of other variables is indicated by their comparative appearance in articles relative to water (making water 100\%).
+The critical importance of other variables is indicated by their comparative appearance in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
 
@@
 \subsection{Region-specific BN: Coonawarra}
-% TODO: add CPTs to appendix
+% TODO: add CPTs to appendix - do this as a final step!
 

### 2024-08-26 article.tex
initial mardi edits - pg 14

@@
 \section{Title}
-A Bayesian Network Model based decision support tool for Environmental Sustainability in the Australian Winegrowing Industry.
+A Bayesian Network Model based decision support tool for sustainability in the Australian Winegrowing Industry.
 
@@
 
-Environmental sustainability in the Australian winegrowing industry involves complex, interacting factors.
+Sustainability in the Australian winegrowing industry involves complex, interacting factors.
 To address this, we developed a Bayesian Network (BN) model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes.
@@
 \section{Introduction}
-
-The imperative for environmental sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}.
-This is especially true for Viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
-This study investigates environmental sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs).
+% TODO: introduce the concept of sustainability and define it! Especially within the context of this study!! 
+The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}.
+This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
+This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs).
 To create a rigorous and quantitative approach to understanding sustainable practices and the relationships between factors associated with these practices, a broad model of Australian winegrowing was created.
@@
 
-This research is guided by several fundamental inquiries aimed at enhancing our understanding of environmental sustainability in viticulture.
-A primary question is how key factors impacting environmental sustainability can be rigorously defined and quantified.
+This research is guided by several fundamental inquiries aimed at enhancing our understanding of sustainability in viticulture.
+A primary question is how key factors impacting sustainability can be rigorously defined and quantified.
 Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how the relative influence of factors might change regionally.
@@
 
-An industry panel comprising experts in viticulture and environmental sustainability, was convened to guide the project.
+An industry panel comprising experts in viticulture and sustainability, was convened to guide the project.
 The panel acted as a catalyst in the early stages of the research to help explore the above questions.
@@
 In agriculture, the consideration of environment is critical to the success of the industry.
-The question of environmental sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
+The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
 The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
@@
 Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
-In Australia, all of the above groups mentioned are united in the priority to improve greenhouse gas emissions and resource inputs through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
+In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
 While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
@@
 
-The literature review was designed to access existing knowledge on environmental sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.
+The literature review was designed to access existing knowledge on sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.
 
 These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification. 
-% Clarify that the review helped inform the strawman model and was only used as a comparison point afterwards.
+% TODO: Clarify that the review helped inform the strawman model and was only used as a comparison point afterwards.
 
@@
 
-Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing environmental sustainability in viticulture, their interactions, and the methodologies used in studies that analysed any of the concepts listed by experts.
+Once relevant articles were identified, data extraction was conducted to gather information on the key factors influencing sustainability in viticulture, their interactions, and the methodologies used in studies that analysed any of the concepts listed by experts.
 The extracted data was then processed using Leximancer to identify common themes and concepts in the existing literature.
 
-The expert panel comprising specialists in viticulture and environmental sustainability was engaged throughout the literature review process.
+The expert panel comprising specialists in viticulture and sustainability was engaged throughout the literature review process.
 The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.
@@
 Due to Coonawarra's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying BNs.
-Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture.
+Located in South Australia's Limestone Coast zone, Coonawarra is distinguished by its cooler climate and the unique soils shaped by the region's distinctive geology.
+This combination provides an exceptional foundation for viticulture, making Coonawarra a renowned wine-producing area.
 The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}.
-Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around environmental sustainability practices to specific regional factors.
+Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around sustainability practices to specific regional factors.
 
@@
 The key factors identified by the industry panel and their agreed definitions are shown in Table \ref{tab:definitions}.
-By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed by the industry panel.
+By utilising these definitions, each factor's contribution to sustainability were quantified and assessed by the industry panel.
 The quantification of each factor allowed for a systematic assessment of their impacts.
@@
 
-% How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
-% Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
+% How can these key factors be rigorously defined so that they are quantifiable contributions to sustainability?
+% Purpose: Develop the factors into well-defined and measurable impacts on sustainability.
 % Results: Use the agreed upon definitions to fully realise factors and their impact.
@@
     \textbf{Water Scarcity} & Whether the country is suffering drought or not (s defined by BOM) & No & \textbf{Yes} \\
-    \textbf{Weather Conditions} & A vineyard’s regional climatic conditions. & \textbf{Ideal} & Not Ideal \\
+    \textbf{Climate Conditions} & A vineyard’s regional climatic conditions. & \textbf{Ideal} & Not Ideal \\
     \textbf{Grape quality and yield targets} & The yield and quality targets of a vineyard block as outlines in the grape supply contract. & \textbf{Ideal} & Not Ideal \\
@@
 
-By applying these definitions, the study effectively translated the qualitative aspects of environmental sustainability into usable metrics.
+By applying these definitions, the study effectively translated the qualitative aspects of sustainability into usable metrics.
 This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships.
-The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving environmental sustainability; allowing each factor's contribution to be clearly understood and relationships explicitly defined.
+The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving sustainability; allowing each factor's contribution to be clearly understood and relationships explicitly defined.
 This was key within the construction of the BN, were the industry panel could easily refer to the specifics of each definition and thus how it might relate to other factors.
 
-\subsection{Bayesian Network Structure for Environmental Sustainability in Australian Winegrowing}
+\subsection{Bayesian Network Structure for sustainability in Australian Winegrowing}
 
@@
 
-    % What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
-    %     Purpose: Identify the most influential variables directly affecting environmental sustainability and those that are perceived to directly impact environmental sustainability.
+    % What are the primary factors that significantly impact sustainability in the Australian winegrowing industry?
+    %     Purpose: Identify the most influential variables directly affecting sustainability and those that are perceived to directly impact sustainability.
     %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
@@
 This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry.
-This network illustrates the complexity of interactions that define environmental sustainability in Australian winegrowing.
+This network illustrates the complexity of interactions that determine sustainability in Australian winegrowing.
 Furthermore, the extent of relationships helps to intrinsically show the importance of variables such as water; which is prolific in how it is interconnected with other vineyard aspects.
 
-Figure~\ref{fig:generalBN}, illustrates the intricate relationships between various vineyard factors and their impact on environmental sustainability in the Australian winegrowing industry.
+Figure~\ref{fig:generalBN}, illustrates the intricate relationships between various vineyard factors and their impact on sustainability in the Australian winegrowing industry.
 The BN structure highlights the critical role of water, disease/pest management, and climate, which are depicted as central nodes with numerous connections to other variables.
@@
 
-As part of this study, a comprehensive literature review was conducted to assess the current state of research on environmental sustainability in the winegrowing industry and as part of the BNs validation.
+As part of this study, a comprehensive literature review was conducted to assess the current state of research on sustainability in the winegrowing industry and as part of the BNs validation.
 The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see \ref{query}).
@@
 The number of articles that contained key terms is outlined in Table \ref{tab:lexi}.
-The bibliometric analysis using Leximancer revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry.
+The bibliometric analysis using Leximancer revealed key concepts and their relevance to sustainability in the Australian winegrowing industry.
 The most prominent concept was water (see Table \ref{tab:lexi}).
-The critical importance of other variables is indicated by their comparative appearance in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
+The critical importance of other variables is indicated by their comparative frequncy in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
 
-    % What are the factors of environmental sustainability in the Australian winegrowing industry?
+    % What are the factors of sustainability in the Australian winegrowing industry?
     %     Purpose: Explore and understand the both the literature and industry perspectives on this.
@@
 \begin{table}[h]\label{tab:lexi}
-    \caption{Table \ref{tab:lexi} Table \ref{tab}: Key Concepts Identified in the Bibliometric Analysis of Environmental Sustainability in the Australian Winegrowing Industry.}
+    \caption{Table \ref{tab:lexi} Table \ref{tab}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}
     \begin{tabular}{@{}lrr@{}}
@@
     disease & 646 & 49 \\
-    change & 569 & 43 \\
+    change & 569 & 43 \\ %TODO: One of these should be something other than change!!! THey both cant be!!
     grapevine & 565 & 43 \\
@@
 
-A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease (even though disease was quite prominent in both).
+A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainability concerns such as disease (even though disease was quite prominent in both).\
+% TODO: THis is a key point can you explore this a bit more by telling us the practical impact and implications?
+DOes it mean the prev research has focussed on the wrong areas and what does it mean we need to do?
+More in a particular area?
+% TODO: Note the discussion with Mardi surrounding causality.
+And discuss further the differences later on about how the models both result in the same significant concerns for sustainability even though they are different models and even though some of the causality is shifted.
+%  What does it mean? That some operational decisions are paramount to sustainability in an environmental context.
+% That different approaches can have different causal relationships - i.e spraying for prevention and spraying in response to disease.
+% That management strategies might change the emphasis of certain affects, or change the ability to control different minor outcomes but some concerns are more important and require direct attention such as disease pressures.
+% It is incredibly important that we can acknowledge that some of these relationships can exist as dual casualities or bi-directionally, which brings into question models that cannot take this into account.
+Or take into account the difference in management strategies and how that does or does not change environmental concerns.
+
 % With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls.
-Together these outputs provide a comprehensive overview of the key factors affecting environmental sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement.
+Together these outputs provide a comprehensive overview of the key factors affecting sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement.
 This analysis underscores the multifaceted nature of sustainability, highlighting both the primary concerns and the interconnected secondary factors that must be managed on the ground.
+% TODO: ML: I don't understand how these words were selected.
+Are they concepts or just frequently used words.
+Are they al relevant?
+May need some explanation.
+- in reference to the Leximancer diagram.
 
@@
 The models diverged in their structural representations with a differing emphasis on specific causal relationships.
-One BN  (see Figure \ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between weather conditions and agrochemical scores.
+One BN  (see Figure \ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between climate conditions and agrochemical scores.
 The other BN, while structurally similar, did not include these connections.
@@
 
-Identified key factors impacting environmental sustainability were examined with regard to Coonawarra.
+Identified key factors impacting sustainability were examined with regard to Coonawarra.
 By comparing the generic Bayesian Network (Figure \ref{fig:b}) model to the Coonawarra-specific model (Figure \ref{fig:robyn} and Figure \ref{fig:marcel}), we identified regional characteristics that influence these variations.
@@
 
-Key factors impacting environmental sustainability in Coonawarra were examined by developing region-specific BNs, Figure \ref{fig:robyn} and Figure \ref{fig:marcel} were based on the generic structural model illustrated in Figure \ref{fig}.
+Key factors impacting sustainability in Coonawarra were examined by developing region-specific BNs, Figure \ref{fig:robyn} and Figure \ref{fig:marcel} were based on the generic structural model illustrated in Figure \ref{fig}.
 The general model was adapted to reflect the unique regional characteristics of Coonawarra, resulting in some structural differences between the region specific models as well as the original generic model.
@@
     % How do changes in key factors under various environmental and regulatory scenarios influence the overall environmental impact in Coonawarra?
-    %     Purpose: Assess different factors overall influence to environmental sustainability given the definitions used.
-    %     Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects environmental sustainability.
+    %     Purpose: Assess different factors overall influence to sustainability given the definitions used.
+    %     Results: Use the CPT values to assess the significant contribution of different variables on the BN and how that effects sustainability.
 
@@
     \includegraphics[width=\linewidth]{robyn}
-    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:robyn}
+    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:robyn}
 \end{figure}
@@
     \includegraphics[width=\linewidth]{marcel}
-    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting environmental sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:marcel}
+    \caption{Coonawarra-specific Bayesian Network illustrating key factors impacting sustainability, with nodes coloured by sensitivity to environmental impact.}\label{fig:marcel}
 \end{figure}
@@
 The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes.
-In Figure \ref{fig:marcel}, greater tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used.
+In Figure \ref{fig:marcel}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used.
+% TODO: the prior sentance is not likely to be understood by a more general audience. also why?
 This distinction highlighted how operational decisions can vary based on regional practices and priorities.
@@
 As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture.
-Weather conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
-Within both of the models, the most significant factors impacting environmental sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate/weather conditions.
+Climate conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
+Within both of the models, the most significant factors impacting sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate conditions.
 These factors were identified as having the highest sensitivity to environmental impact, indicating their crucial roles in the sustainability of the region.
@@
 %  Aside from the role of tractor passes, there are no major differences between the two BNs.
-The similarity in significant factors and their interactions underscores the robustness of the BN approach in capturing the critical elements of environmental sustainability in winegrowing.
+The similarity in significant factors and their interactions underscores the robustness of the BN approach in capturing the critical elements of sustainability in winegrowing.
 
@@
 
-% Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+% Question: What are the primary factors that significantly impact sustainability in the Australian winegrowing industry?
 
@@
 
-% Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
+% Question: What are the direct and indirect relationships between these key factors and sustainability in the Australian winegrowing industry?
 
@@
 
-%     Content: Analyze the impact of different scenarios on environmental sustainability.
+%     Content: Analyze the impact of different scenarios on sustainability.
 %     Data: Use scenario-based BN queries to show changes in key factors and their impacts.
@@
 
-% Question: What are the primary factors that significantly impact environmental sustainability in the Australian winegrowing industry?
+% Question: What are the primary factors that significantly impact sustainability in the Australian winegrowing industry?
 % Results:
@@
 
-% Question: What are the direct and indirect relationships between these key factors and environmental sustainability in the Australian winegrowing industry?
+% Question: What are the direct and indirect relationships between these key factors and sustainability in the Australian winegrowing industry?
 % Results:
@@
 
-This investigation highlights the key factors of Australian winegrowing that contribute to  environmental sustainability through the lens of BNs created with assistance from industry input.
-These models have established the intricate, and interconnected nature of various influences on environmental sustainability in Australian winegrowing.
+This investigation highlights the key factors of Australian winegrowing that contribute to  sustainability through the lens of BNs created with assistance from industry input.
+These models have established the intricate, and interconnected nature of various influences on sustainability in Australian winegrowing.
 A keener understanding of how these factors both interact and affect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables.
@@
 Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change~\cite{agostaRegionalClimateVariability2012,alsafadiFutureScenariosBioclimatic2023,barriguinhaVineyardYieldEstimation2021,sharmaChapterImpactClimate2014}.
-In a more general sense climate and weather conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield~\cite{barriguinhaVineyardYieldEstimation2021,antonComparativeStudyRisk2012}, erosion~\cite{biddoccuEvaluationSoilErosion2020,doi:10.1177/0309133319861833}, and are further determinants of chosen grape varieties~\cite{topferGrapeVarietiesAre2022, petriashviliImpactClimateChange2023}.
+In a more general sense climate conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield~\cite{barriguinhaVineyardYieldEstimation2021,antonComparativeStudyRisk2012}, erosion~\cite{biddoccuEvaluationSoilErosion2020,doi:10.1177/0309133319861833}, and are further determinants of chosen grape varieties~\cite{topferGrapeVarietiesAre2022, petriashviliImpactClimateChange2023}.
 The BN models captured the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.
 
-The case study highlighted the direct influences on environmental sustainability, where environmental sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}).
+The case study highlighted the direct influences on sustainability, where sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}).
 A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\cite{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}.
@@
 
-The BN models provide structure to the broader way of how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to environmental sustainability as an outcome.
+The BN models provide structure to the broader way of how the major factors within literature interact, offering a clearer understanding of their interdependencies and relative sensitivity with regard to sustainability as an outcome.
 The existing literature provides exceptional detailed understanding of many mechanisms behind the relationships explored within this study.
@@
 The model demonstrated how fuel, tractor, and electricity use are intertwined with factors such as water and climate through propagation.
-Even though environmental sustainability was not highly sensitive to such factors, they directly relate to operational decisions that can be influenced by growers over a season.
+Even though sustainability was not highly sensitive to such factors, they directly relate to operational decisions that can be influenced by growers over a season.
 For example, electricity and fuel use are crucial for irrigation systems, as well as fuel use and tractors required for operations linked to soil preparation, management, and pest/disease control actions.
@@
 The BN models helped to illustrate how economic incentives can be drivers of sustainable practices.
-The definitive influence and relationships between what are more tertiary considerations of environmental sustainability being directly connected to further considerations such as operational costs.
-Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have an impact on sustainability practices but were limited in this study through only reviewing them within the lens of environmental sustainability.
+The definitive influence and relationships between what are more tertiary considerations of sustainability being directly connected to further considerations such as operational costs.
+Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have an impact on sustainability practices but were limited in this study through only reviewing them within the lens of sustainability.
 The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers as well as what may be much more specific circumstance; of which is a potential further avenue of research that would compliment this work significantly.
@@
 
-This study provides an in-depth examination of environmental sustainability in Australia and the Coonawarra winegrowing region using BNs.
-Through integrating industry expertise and empirical data, the BN models developed in this research offered a structured and quantitative framework for understanding the complex interactions amongst key factors influencing environmental sustainability.
+This study provides an in-depth examination of sustainability in Australia and the Coonawarra winegrowing region using BNs.
+Through integrating industry expertise and empirical data, the BN models developed in this research offered a structured and quantitative framework for understanding the complex interactions amongst key factors influencing sustainability.
 The findings highlight the critical role of water quality and availability, emphasising its critical influence on all operational decisions either directly or propagating through other factors.

### 2024-08-28 article.tex
ML: edits - up to final todo's

@@
 This distinction highlighted how operational decisions can vary based on regional practices and priorities.
-A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense on larger plots of land.
+A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense.
+% TODO: This requires further explanation.
 However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.
+% TODO: The other had fewer tractor passes because they performed 2 operations in a single pass. 
+% ML: As I read this, I wander whether there was some bias because the group were very attuuned to the data and had a strong preference to efficient management techniques.
+Im not convinced that this is representative of coonawarra per se.
 
@@
 Climate conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
+% TODO: This is significant...
 Within both of the models, the most significant factors impacting sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate conditions.
@@
 Additionally, the BNs emphasise economic factors, such as market pressures and grape prices, and includes how they interact within a scope of secondary factors like fuel and electricity use.
+% TODO: Highlight, in the above paragraph, how the BN differs from other BNs
 
@@
 \section{Discussion}
-
+% weather or climate?
 This investigation highlights the key factors of Australian winegrowing that contribute to  sustainability through the lens of BNs created with assistance from industry input.
@@
 A keener understanding of how these factors both interact and affect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables.
+%TODO: And therefore what to sustainability?
 The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
@@
 
-The case study highlighted the direct influences on sustainability, where sustainability was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}).
+The case study highlighted the direct influences on environmental impact, where it was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}).
 A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\cite{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}.
@@
 The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers as well as what may be much more specific circumstance; of which is a potential further avenue of research that would compliment this work significantly.
+% TODO: What do you mean here?
 
@@
 
-This study provides an in-depth examination of sustainability in Australia and the Coonawarra winegrowing region using BNs.
+This study provides an in-depth examination of sustainable winegrowing in Australia and the Coonawarra winegrowing region using BNs.
 Through integrating industry expertise and empirical data, the BN models developed in this research offered a structured and quantitative framework for understanding the complex interactions amongst key factors influencing sustainability.
 The findings highlight the critical role of water quality and availability, emphasising its critical influence on all operational decisions either directly or propagating through other factors.
-With this critical nature being due to water being the most interconnected factor.
-With this high interrelatedness emphasising the importance efficient water management practices enhancing sustainability in viticulture.
+With this critical nature being due to water being the most interconnected factor, emphasising the importance efficient water management practices enhancing sustainability in viticulture.
 

### 2024-08-28 article.tex
fucking work

@@
 A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use.
-The BN model, accessible via an application, allows for continuous industry feedback and adaptation.
 This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
@@
 \section{Introduction}
-% TODO: introduce the concept of sustainability and define it! Especially within the context of this study!!
+
 The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}.
 This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
-This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs).
-To create a rigorous and quantitative approach to understanding sustainable practices and the relationships between factors associated with these practices, a broad model of Australian winegrowing was created.
+This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs) to create a broad model of Australian winegrowing.
 This model was followed by a more specific case study looking at the Coonawarra winegrowing region.
-
+Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~\citep{beaumelle_biodiversity_2023} criterion for assessing sustainability has become multifaceted and led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics (Baiano, 2021; Montalvo-Falcón et al., 2023; Waye, 2008).
+In this study we focus on the environmental aspect of sustainability through the use of 'environmental impact' as the terminal node within the network, linking relevant factors through structures described by an expert panel.
+% TODO: insert reference above
 BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~\cite{korbBayesianArtificialIntelligence2011}.
@@
 This research is guided by several fundamental inquiries aimed at enhancing our understanding of sustainability in viticulture.
-A primary question is how key factors impacting sustainability can be rigorously defined and quantified.
-Another focus delves into identifying the unique regional characteristics of different regions, using the Coonawarra winegrowing region to illustrate how the relative influence of factors might change regionally.
+A primary question is how key factors impact the environment, and how these factors can be rigorously defined and quantified.
+Furthremore, the study delves into how factors change due to the unique characteristics of different winegrowing regions, using the Coonawarra region to illustrate how the relative influence of factors change.
 Additionally, the study investigates how these factors interact with each other.

### 2024-08-29 article.tex
Mardi edits done - a couple lookups left

@@
 This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
-This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs) to create a broad model of Australian winegrowing.
-This model was followed by a more specific case study looking at the Coonawarra winegrowing region.
-Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~\citep{beaumelle_biodiversity_2023} criterion for assessing sustainability has become multifaceted and led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics (Baiano, 2021; Montalvo-Falcón et al., 2023; Waye, 2008).
+This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs) to create a broad model for Australian.
+This broad model was followed by a more specific case study looking at the Coonawarra winegrowing region.
+Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~\citep{beaumelle_biodiversity_2023} criterion for assessing sustainability has become multifaceted and has led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics \citep{baiano_overview_2021,montalvo-falconSustainabilityResearchWine2023, waye_carbon_2008}.
 In this study we focus on the environmental aspect of sustainability through the use of 'environmental impact' as the terminal node within the network, linking relevant factors through structures described by an expert panel.
-% TODO: insert reference above
-BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~\cite{korbBayesianArtificialIntelligence2011}.
+
+BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~\citep{korbBayesianArtificialIntelligence2011}.
 BNs also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiements, outcomes from published literature, and so on.
@@
 
-The literature review was designed to access existing knowledge on sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.
-
+The literature review was designed to assess existing knowledge on sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.
 These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification.
-% TODO: Clarify that the review helped inform the strawman model and was only used as a comparison point afterwards.
-
-A systematic search of terms, broadly based on key factors given from the industry panel, was conducted.
+The most prominent way of informing the model was the construction of an initial strawman model to describe different relationships explored in the literature, which helped as a beginning point for the experts to discuss the specific applicability of relationships for different Australian contexts.
+The literature review was done using systematic search of terms, broadly based on key factors given from the industry panel, was conducted.
 The general query (adapted to different formats for various journals and bibliographic databases) used for the literature search was:
@@
 % Please add the following required packages to your document preamble:
-% \usepackage{booktabs} TODO: check the BN definitions align properly.
+% \usepackage{booktabs}
 %
@@
     \textbf{Water Scarcity} & Whether the country is suffering drought or not (s defined by BOM) & No & \textbf{Yes} \\
-    \textbf{Climate Conditions} & A vineyard’s regional climatic conditions. & \textbf{Ideal} & Not Ideal \\
+    \textbf{Climate Conditions} & A vineyard's regional climatic conditions. & \textbf{Ideal} & Not Ideal \\
     \textbf{Grape quality and yield targets} & The yield and quality targets of a vineyard block as outlines in the grape supply contract. & \textbf{Ideal} & Not Ideal \\
@@
     \includegraphics[width=\linewidth]{Winegrowing-concept-map}
-    \caption{Your caption here}
+    \caption{TODO: add a caption the explains what the connection between concepts in lexi is and how words are selected and culled - what is a concept. Reference the Lexi proceedures followed too}
     \label{fig:lexi}
@@
 
-A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainability concerns such as disease (even though disease was quite prominent in both).\
-% TODO: THis is a key point can you explore this a bit more by telling us the practical impact and implications?
-DOes it mean the prev research has focussed on the wrong areas and what does it mean we need to do?
-More in a particular area?
-% TODO: Note the discussion with Mardi surrounding causality.
-And discuss further the differences later on about how the models both result in the same significant concerns for sustainability even though they are different models and even though some of the causality is shifted.
-%  What does it mean? That some operational decisions are paramount to sustainability in an environmental context.
-% That different approaches can have different causal relationships - i.e spraying for prevention and spraying in response to disease.
-% That management strategies might change the emphasis of certain affects, or change the ability to control different minor outcomes but some concerns are more important and require direct attention such as disease pressures.
-% It is incredibly important that we can acknowledge that some of these relationships can exist as dual casualities or bi-directionally, which brings into question models that cannot take this into account.
-Or take into account the difference in management strategies and how that does or does not change environmental concerns.
+A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainability concerns such as disease (even though disease was quite prominent in both).
+Notably the sensitivity of the Coonawarra models align with the focus of literature and analyses, focusing on  aspects such as disease, water, soil health and climate.
+The combination of agreeing with these primary concerns whilst highlighting their connection to operational variables such as tractor, and fuel use; is an important step to realising the benefits of combined efforts of prevention through scenario assessments.
+Considering variables that are related to an operational standpoint as well as environmental Furthers the ability to show the consideration of environmental impact within vineyard operational decisions and how it may lower the costly use of agrochemicals and fuel.
 
@@
 This analysis underscores the multifaceted nature of sustainability, highlighting both the primary concerns and the interconnected secondary factors that must be managed on the ground.
-% TODO: ML: I don't understand how these words were selected.
-Are they concepts or just frequently used words.
-Are they al relevant?
-May need some explanation.
-- in reference to the Leximancer diagram.
 
@@
 The models diverged in their structural representations with a differing emphasis on specific causal relationships.
-One BN  (see Figure \ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between climate conditions and agrochemical scores.
-The other BN, while structurally similar, did not include these connections.
-The use of two separately scored BNs with differing structure ensured that the BNs captured the diversity of expert views regarding the primary drivers of environmental outcomes in the region.
+One BN (see Figure~\ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between climate conditions and agrochemical scores.
+The other BN (see \ref{fig:robyn}), while structurally similar, did not include these connections.
+The node for renewable fuels was also removed in Figure~\ref{fig:robyn} to more accurately reflect the lack of use of them in the Coonawarra region, whereas Figure~\ref{fig:marcel} included the node to illustrate the potential benefits if it were used.
+The differences in structure reflect difference in management approaches and the way problems can be approached.
+This difference in management style was most apparent in the causal relationship between tractor passes and undervine management, where the edge between the nodes is reversed between the two models.
+The difference highlights how operational decisions can alter the causal relationship of nodes to one another, with an example discussed regarding the use of agrochemical spray as preventative vs as a response to disease.
+The first decision would have the act of spraying cause a lower probability of disease to occur, and the second being that the presence of disease would be more likely to initiate the use of agrochemicals.
+The two arguments for the relationship between tractor passes and under vine management reflect this type of causal reversal, where they differed in the use of tractors to actively manage the undervine area or to leverage the tractor when it was already being used for other tasks to then manage the undervine as a consequence.
+These types of differences in management perspectives can greatly effect the root decision that impacts the environmental even if they do not directly change the most sensitive or contributing factors, as in this case both models maintained similar sensitivities to agrochemical use, water, and climate.
 
@@
     %     Sustainability in Coonawarra Winegrowing: Key Factors and Influences
-    % #TODO: what are the regional specifics of coonawarra
     % How do the identified key factors vary across different wine regions in Australia, and what regional characteristics influence these variations?
@@
 
-% TODO: the exclusion of renewable fuels due to none being used in coonawarra
 % the difference in vineyard floor management and its relationship to tractors
@@
 The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes.
-In Figure \ref{fig:marcel}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:robyn} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used.
-% TODO: the prior sentance is not likely to be understood by a more general audience. also why?
-This distinction highlighted how operational decisions can vary based on regional practices and priorities.
-A point was also raised that scale can cause a further driving factor, where tractor passes may be greatly increased as an expense.
-% TODO: This requires further explanation.
-However, this issue as well as directly attributing measurable cause to granular specifics such as composting, soil depth and clay content cannot be fully addressed without site or paddock specific knowledge.
-% TODO: The other had fewer tractor passes because they performed 2 operations in a single pass. 
+In Figure \ref{fig:robyn}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:marcel} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used.
+A distinction which highlighted how operational decisions and priorities can vary and influence the cause of environmental impacts without changing the involved factors, simply through changing the 'why' of nodes' connections.
+A point was also raised that scale can cause a further driving factor.
+The data helped to inform the level of influence scale can have with many vineyards being anywhere from a few to hundreds of hectares in size.
+The difference between the cost of a tractor pass in smaller vineyards covering only a few kilometres of rows compared with the possibility of thousands of kilometres of rows, can influence the reality of deciding to do multiple tasks in one pass and the level of consequence in the form of labour and fuel costs for larger vineyards to choose to utilise another tractor pass.
+However, many of these considerations can also be caused by more granular variables that are not within these models, such as composting, soil depth and clay content.
+The inability to consider different activitiies at multiple scales without hte use of multiple models becomes a limiting factor.
+
 % ML: As I read this, I wander whether there was some bias because the group were very attuuned to the data and had a strong preference to efficient management techniques.
@@
 
+% This is significant... (refering to below)
 As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture.
 Climate conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
-% TODO: This is significant...
 Within both of the models, the most significant factors impacting sustainability are water quality, pest and disease management, market pressures, agrochemical use, and climate conditions.
@@
 Additionally, the BNs emphasise economic factors, such as market pressures and grape prices, and includes how they interact within a scope of secondary factors like fuel and electricity use.
-% TODO: Highlight, in the above paragraph, how the BN differs from other BNs
 
@@
 A keener understanding of how these factors both interact and affect one another from the perspective of research and industry is illustrated within these models, with a major outcome being the highlighting of water use's critical importance as one of the most interconnected variables.
-%TODO: And therefore what to sustainability?
 The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
 This finding aligns with water being the lifeblood of agriculture~\cite{chawlaWaterProductivityAgriculture2023}, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~\cite{australianbureauofstatisticsWaterUseAustralian2021}.
+The connection of variables that were linked to operational decisions such as tractor passes, fuel and electricity use illustrated both a way in which the reduction of water use, affects from changes in water quality, climate and disease can influence them.
+And, how different causal relationships between nodes can be a result of different management perspectives.
+These differences and relations help to broaden the consideration of factors when making decision in vineyards with regards to how the impact the environment.
 
@@
 
-The BN models helped to illustrate how economic incentives can be drivers of sustainable practices.
-The definitive influence and relationships between what are more tertiary considerations of sustainability being directly connected to further considerations such as operational costs.
-Market pressures, including the demand for high-quality grapes through factors such as grape prices, were found to have an impact on sustainability practices but were limited in this study through only reviewing them within the lens of sustainability.
-The ability to effectively gauge whether operations could afford to engage further with management programs for factors such as soil, pests, disease etc was in part driven by the economic climate provided to growers as well as what may be much more specific circumstance; of which is a potential further avenue of research that would compliment this work significantly.
-% TODO: What do you mean here?
+The relationships of nodes associated with operational and management  decisions illustrated how different drivers from nodes several edges away from environmetnal impact could still be driving forces through their causal influence of the primary contributing factors.
+Furthermore, extenral considerations such as market pressures, the demand for high-quality grapes through factors such as grape prices, were found to have an impact on the environment through how they influenced internal responses, such as the use of more water to increase yields as a response to price increases.
+The economic drivers of some of the decisions would be a great compliment in determinig how the priority of these decision might be made alongside their environmental concerns, and poses a potential avenue for further research.
 

### 2024-09-02 article.tex
attempt to compile to send to Kate

@@
-% Packages:
-\begin{document}
-
-\documentclass[12pt]{article}
-\usepackage{graphicx}
-\usepackage{booktabs}
-\usepackage{listings}
-\usepackage{xcolor}
+\documentclass[fleqn,10pt]{wlscirep}
 
@@
 
-\section{Title}
-A Bayesian Network Model based decision support tool for sustainability in the Australian Winegrowing Industry.
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{graphicx}
+\usepackage{booktabs}
+\usepackage{listings}
+\usepackage{xcolor}
 
-\section{Abstract}
+\title{A Bayesian Network Model based decision support tool for sustainability in the Australian Winegrowing Industry.}
 
+\author[1,2,3,*]{Bryce Boyd}
+\author[1]{Kate Helmsteadt}
+\author[2]{Mardi Longbottom}
+\author[1]{Kerrie Mengersen}
+
+\affil[1]{QUT, Mathematical Sciences, Brisbane, Australia}
+\affil[2]{AWRI, Adelaide, Australia}
+\affil[3]{Food Agility CRC}
+
+\affil[*]{bryce.polley@awri.com.au}
+
+%\keywords{Keyword1, Keyword2, Keyword3}
+
+\begin{abstract}
 Sustainability in the Australian winegrowing industry involves complex, interacting factors.
@@
 This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
+\end{abstract}
+
+\begin{document}
 
@@
 
-The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}.
-This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
+The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\citation{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}.
+This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\citation{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
 This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs) to create a broad model for Australian.
 This broad model was followed by a more specific case study looking at the Coonawarra winegrowing region.
-Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~\citep{beaumelle_biodiversity_2023} criterion for assessing sustainability has become multifaceted and has led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics \citep{baiano_overview_2021,montalvo-falconSustainabilityResearchWine2023, waye_carbon_2008}.
-In this study we focus on the environmental aspect of sustainability through the use of 'environmental impact' as the terminal node within the network, linking relevant factors through structures described by an expert panel.
+Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~\citation{beaumelle_biodiversity_2023} criterion for assessing sustainability has become multifaceted and has led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics \citation{baiano_overview_2021,montalvo-falconSustainabilityResearchWine2023, waye_carbon_2008}.
+In this study we focus on the environmental aspect of sustainability through the use of `environmental impact' as the terminal node within the network, linking relevant factors through structures described by an expert panel.
 
-BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~\citep{korbBayesianArtificialIntelligence2011}.
+BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~\citation{korbBayesianArtificialIntelligence2011}.
 BNs also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiements, outcomes from published literature, and so on.
@@
 In agriculture, the consideration of environment is critical to the success of the industry.
-The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citep{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
-The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry \citep{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
-It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined \citep{santiago-brownSustainabilityAssessmentWineGrape2015}.
+The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citation{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
+The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry \citation{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
+It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined \citation{santiago-brownSustainabilityAssessmentWineGrape2015}.
 
-Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes \citep{dichiaraCollaborativeApproachAchieving2024}.
-In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers \citep{dumbrellComparingAustralianPublic2024}.
-While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
+Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes \citation{dichiaraCollaborativeApproachAchieving2024}.
+In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers \citation{dumbrellComparingAustralianPublic2024}.
+While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citation{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
 % old comment
@@
 The use of index systems is beneficial in comparing sustainability performance across different industries or geographic regions.
-As \textcite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
-Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citep{floresWhatSustainabilityWine2018}.
-The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citep{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}.
-For instance, frameworks like MESMIS categorize sustainability measures into "descriptors" (guidelines), "indicators" (metrics for measuring changes), and "parameters" (limits for indicators) \citep{candido_sustainability_2015}.
+As \textcitation{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
+Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citation{floresWhatSustainabilityWine2018}.
+The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citation{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}.
+For instance, frameworks like MESMIS categorize sustainability measures into `descriptors' (guidelines), `indicators' (metrics for measuring changes), and `parameters' (limits for indicators) \citation{candido_sustainability_2015}.
 This structure allows for a more granular assessment of sustainability by linking broad guidelines to specific, measurable outcomes.
@@
 The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes
-\citep{korbBayesianArtificialIntelligence2011}.
+\citation{korbBayesianArtificialIntelligence2011}.
 % The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.
@@
 The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact
-\citep{pourretBayesianNetworksPractical2008}.
+\citation{pourretBayesianNetworksPractical2008}.
 Furthermore, data collected across Australia could also be used to help inform the model structure as well as quantify the associated conditional probabilities alongside expert opinion.
@@
 
-% Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
+% Where we calculate the probability of an event A given an event B, as demonstrated by \citation{bayesLIIEssaySolving1763}.
 Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes.
 Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes.
-This is an iterative application of \ref{bayesformula}, which can be achieved through
+This is an iterative application of~\ref{bayesformula}, which can be achieved through
 
@@
 \begin{equation}
-        p(x_{0}=x_{0}) (X_{1}=x_{1},...X_{n}=x_{n})=p(n|x_{parents})\prod_{n}^{i=1}p(x_{i}|x_{Parents(i)})
+        p(x_{0}=x_{0}) (X_{1}=x_{1},\ldots X_{n}=x_{n})=p(n|x_{parents})\prod_{n}^{i=1}p(x_{i}|x_{Parents(i)})
 \end{equation},
@@
 % for a selected node $i$ given the parents and their local conditional distributions.
-Where $x_0$ is the target variable and $x_i$ denotes the quantified information in the i$^th$ node, and $p$ denotes its probability distribution.
+Where $x_0$ is the target variable and $x_i$ denotes the quantified information in the i$^{th}$ node, and $p$ denotes its probability distribution.
 
@@
 
-Bayesian Networks created in this study were created using BayesFusion \citep{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities.
-The Bayes fuse software was used both through the GUI interface and the SMILE API \citep{bayesfusionGeNIeModelerUSER2022} system using C++ \citep{ISO:2012:III}.
+Bayesian Networks created in this study were created using BayesFusion \citation{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities.
+The Bayes fuse software was used both through the GUI interface and the SMILE API \citation{bayesfusionGeNIeModelerUSER2022} system using C++ \citation{ISO:2012:III}.
 
@@
 
-The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by \textcite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}.
+The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by \textcitation{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}.
 The process progressed iteratively through problem definition, structure, parameterization, and validation.
@@
 
-As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network \citep{korbBayesianArtificialIntelligence2011}.
+As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network \citation{korbBayesianArtificialIntelligence2011}.
 For reasons of comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes.
@@
 The values for $x$ and $y$ can be derived using the sum of the provided BN weights.
-An assumption of 'smoothness' is taken between worst and best case scenarios when utilising this method.
+An assumption of `smoothness' is taken between worst and best case scenarios when utilising this method.
 All possible combinations between all states being true (or ideal) and all being false (not ideal) are also mirrored such, with the only consideration being given, is that of how heavily weighted a variables state is compared to the others.
@@
 
-The method for validation sought to address criteria presented by \textcite{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
+The method for validation sought to address criteria presented by \textcitation{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
 Nomological validity refers to ensuring that the BN fits within a broader theoretical context, aligning with established literature.
@@
 The selection process for experts, encouraged diversity in their regional knowledge and expertise in order to broaden the ability to critique choices.
-Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
+Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions \citation{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
 
@@
 This helped to avoid some overtly specific scenarios in favour of broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
-This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
-% Specifically, the question of water resources, which was central to the model and highly interrelated \citep{carmonaUseParticipatoryObjectOriented2011}.
+This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors \citation{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
+% Specifically, the question of water resources, which was central to the model and highly interrelated \citation{carmonaUseParticipatoryObjectOriented2011}.
 
@@
 It was found that other studies emphasised the same variables selected by our experts.
-This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes \cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}.
-Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}.
+This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes \citation{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}.
+Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively \citation{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}.
 
@@
 This issue was simply overcome through explicit definitions accessible to all participants, and by directly addressing issues caused by definitions before further development of the model.
-Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes \citep{korbBayesianArtificialIntelligence2011}.
+Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes \citation{korbBayesianArtificialIntelligence2011}.
 
 The factors within the BN had similar parent nodes to factors that appeared in other models from the literature (i.e yield generally utilised area, water, fuel as predictors), although there were key differences.
-The differences were primarily due to the consideration of nodes as factors that related and were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the environmental outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation \citep{laurentReviewIssuesMethods2021}.
+The differences were primarily due to the consideration of nodes as factors that related and were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the environmental outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation \citation{laurentReviewIssuesMethods2021}.
 The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being able to be properly employed.
@@
 
-In this study, the sensitivity analysis conducted utilised the Bayesian Network software GeNie, implementing the algorithm developed by \textcite{article}; an optimisation of \textcite{Castillo1996ANM} and \textcite{Gaag1998PracticableSA}.
-The method allowed for efficient computation of the influence of parameter variations on the output probabilities of the BNs terminal node 'Environmental Impact'.
+In this study, the sensitivity analysis conducted utilised the Bayesian Network software GeNie, implementing the algorithm developed by \textcitation{article}; an optimisation of \textcitation{Castillo1996ANM} and \textcitation{Gaag1998PracticableSA}.
+The method allowed for efficient computation of the influence of parameter variations on the output probabilities of the BNs terminal node `Environmental Impact'.
 
@@
 This combination provides an exceptional foundation for viticulture, making Coonawarra a renowned wine-producing area.
-The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}.
+The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \citation{hallidayAustralianWineEncyclopedia2009}.
 Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around sustainability practices to specific regional factors.
@@
 
-The key factors identified by the industry panel and their agreed definitions are shown in Table \ref{tab:definitions}.
+The key factors identified by the industry panel and their agreed definitions are shown in Table~\ref{tab:definitions}.
 By utilising these definitions, each factor's contribution to sustainability were quantified and assessed by the industry panel.
 The quantification of each factor allowed for a systematic assessment of their impacts.
-For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact.
+For example, `Water Use' was quantified as `High' or `Low', enabling a straightforward assessment of its environmental impact.
 Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).
@@
     \textbf{Spray application number} & Number of foliar spray applications used to control pests and diseases (spray applications/Ha/FY) & \textbf{Low} & High \\
-    \textbf{Agrochemical legislation} & The legislated regulations regarding agrochemical use as specified by the APVMA.
-Dog book recommendations are further restrictions for export wine production and to protect the reputation of Australian wine.
+    \textbf{Agrochemical legislation} & The legislated regulations regarding agrochemical use as specified by the APVMA.~Dog book recommendations are further restrictions for export wine production and to protect the reputation of Australian wine.
 & \textbf{Yes} & No \\
     \textbf{Vineyard floor management} & Proportion of vineyard floor covered with a cover crop. & High & \textbf{Low} \\
-    \textbf{Pest and disease management methods} & All available methods of management are considered before a management program is chosen (i.e.
-biological, chemical, cultural, mechanical, and technological) & \textbf{Yes} & No \\
+    \textbf{Pest and disease management methods} & All available methods of management are considered before a management program is chosen (i.e.~biological, chemical, cultural, mechanical, and technological) & \textbf{Yes} & No \\
     \textbf{Electricity use} & Total amount of electricity used by a vineyard in a financial year (kWh/Ha) & \textbf{Low} & High \\
@@
     \textbf{Pest and Disease Management} & The management of pests and diseases such as through the employ of fungicide and pesticides & \textbf{Yes} & No \\
-    \textbf{Soil degradation management} & Areas at risk of degradation via compaction or erosion are identified and actions to remediate and minimise degradation are taken (i.e.
-don’t traffic waterlogged soils, minimise cultivation, maintain vineyard floor cover with cover crops, etc.) & No & \textbf{Yes} \\
-    \textbf{Soil organic carbon management} & Areas with low or declining soil organic carbon levels are identified and actions to improve soil carbon levels are taken (i.e.
-minimise cultivation, maintain vineyard floor cover with cover crops, apply mulch or compost, etc.) & \textbf{Yes} & No \\
+    \textbf{Soil degradation management} & Areas at risk of degradation via compaction or erosion are identified and actions to remediate and minimise degradation are taken (i.e.~don't traffic waterlogged soils, minimise cultivation, maintain vineyard floor cover with cover crops, etc.) & No & \textbf{Yes} \\
+    \textbf{Soil organic carbon management} & Areas with low or declining soil organic carbon levels are identified and actions to improve soil carbon levels are taken (i.e.~minimise cultivation, maintain vineyard floor cover with cover crops, apply mulch or compost, etc.) & \textbf{Yes} & No \\
     \textbf{Tractor passes} & The number of times a tractor passes over the whole vine row area & \textbf{Low} & High \\
@@
 
-The relationships between the facets in Table \ref{tab:definitions}  as agreed by the industry panel, are depicted in the BN model in Fig ~\ref{figure:generalBN}.
+The relationships between the facets in Table~\ref{tab:definitions}  as agreed by the industry panel, are depicted in the BN model in Fig~\ref{figure:generalBN}.
 The BN highlights which factors are influenced by others in the form of an acyclic directed graph.
@@
 As part of this study, a comprehensive literature review was conducted to assess the current state of research on sustainability in the winegrowing industry and as part of the BNs validation.
-The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see \ref{query}).
+The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see~\ref{query}).
 The articles span a range of topics, including sustainability metrics, operational practices, and the influence of regulatory frameworks on environmental outcomes.
 
-The number of articles that contained key terms is outlined in Table \ref{tab:lexi}.
+The number of articles that contained key terms is outlined in Table~\ref{tab:lexi}.
 The bibliometric analysis using Leximancer revealed key concepts and their relevance to sustainability in the Australian winegrowing industry.
-The most prominent concept was water (see Table \ref{tab:lexi}).
+The most prominent concept was water (see Table~\ref{tab:lexi}).
 The critical importance of other variables is indicated by their comparative frequncy in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
@@
 \begin{table}[h]\label{tab:lexi}
-    \caption{Table \ref{tab:lexi} Table \ref{tab}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}
+    \caption{Table~\ref{tab:lexi} Table~\ref{tab}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}
     \begin{tabular}{@{}lrr@{}}
@@
     disease & 646 & 49 \\
-    change & 569 & 43 \\ %TODO: One of these should be something other than change!!! THey both cant be!!
+    change & 569 & 43 \\
+    %TODO: One of these should be something other than change!!! THey both cant be!!
     grapevine & 565 & 43 \\
@@
 The most significant concepts along with water, included change, climate, and disease.
-These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see Table \ref{tab:lexi}).
+These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see Table~\ref{tab:lexi}).
 Furthermore, change and climate were kept separate to illustrate the variety of different changes, such as in practice, legislation and resource abundance.
-Additionally, although not in the top 10; "soil", "region", "practices", and "legislation" also appear to be dominant features within the literature.
+Additionally, although not in the top 10; `soil', `region', `practices', and `legislation' also appear to be dominant features within the literature.
 These factors are critical as they shape the environmental strategies employed by vineyards.
 
-The prominence of different factors is visually described in Figure \ref{fig:lexi}, with the size of nodes in the diagram depicting the frequency of these concepts appearing in literature.
-Figure \ref{fig:lexi} also illustrates the connection between concepts through edges, and overlaying the most related concepts, change, grapevine, water and land as coloured areas on the diagram.
+The prominence of different factors is visually described in Figure~\ref{fig:lexi}, with the size of nodes in the diagram depicting the frequency of these concepts appearing in literature.
+Figure~\ref{fig:lexi} also illustrates the connection between concepts through edges, and overlaying the most related concepts, change, grapevine, water and land as coloured areas on the diagram.
 With the most related concepts being of similar themes to that of the industry panel's Bayesian Network.
@@
     \includegraphics[width=\linewidth]{Winegrowing-concept-map}
-    \caption{TODO: add a caption the explains what the connection between concepts in lexi is and how words are selected and culled - what is a concept. Reference the Lexi proceedures followed too}
-    \label{fig:lexi}
+    \caption{hello}\label{fig:lexi}
+        % TODO: add a caption the explains what the connection between concepts in lexi is and how words are selected and culled - what is a concept. Reference the Lexi proceedures followed too}
 \end{figure}
@@
 
-\subsection{Region-specific BN: Coonawarra}
+\subsection{Region-specific BN:~Coonawarra}
 % TODO: add CPTs to appendix - do this as a final step!
@@
 The models diverged in their structural representations with a differing emphasis on specific causal relationships.
-One BN (see Figure~\ref{fig:marcel} explicitly incorporated connections between soil degradation and tractor passes, as well as between climate conditions and agrochemical scores.
-The other BN (see \ref{fig:robyn}), while structurally similar, did not include these connections.
+One BN (see Figure~\ref{fig:marcel}) explicitly incorporated connections between soil degradation and tractor passes, as well as between climate conditions and agrochemical scores.
+The other BN (see~\ref{fig:robyn}), while structurally similar, did not include these connections.
 The node for renewable fuels was also removed in Figure~\ref{fig:robyn} to more accurately reflect the lack of use of them in the Coonawarra region, whereas Figure~\ref{fig:marcel} included the node to illustrate the potential benefits if it were used.
@@
 Identified key factors impacting sustainability were examined with regard to Coonawarra.
-By comparing the generic Bayesian Network (Figure \ref{fig:b}) model to the Coonawarra-specific model (Figure \ref{fig:robyn} and Figure \ref{fig:marcel}), we identified regional characteristics that influence these variations.
+By comparing the generic Bayesian Network (Figure~\ref{fig:b}) model to the Coonawarra-specific model (Figure~\ref{fig:robyn} and Figure~\ref{fig:marcel}), we identified regional characteristics that influence these variations.
 In this case study, we altered the general Australian BN to model and analyse the complex interactions between various environmental factors affecting wine production in Coonawarra.
@@
 
-Key factors impacting sustainability in Coonawarra were examined by developing region-specific BNs, Figure \ref{fig:robyn} and Figure \ref{fig:marcel} were based on the generic structural model illustrated in Figure \ref{fig}.
+Key factors impacting sustainability in Coonawarra were examined by developing region-specific BNs, Figure~\ref{fig:robyn} and Figure~\ref{fig:marcel} were based on the generic structural model illustrated in Figure~\ref{fig}.
 The general model was adapted to reflect the unique regional characteristics of Coonawarra, resulting in some structural differences between the region specific models as well as the original generic model.
@@
 Both emphasize the importance of water quality, pest and disease management, and climate conditions.
-The primary difference is the sensitivity to tractor passes, water quality, water scarcity, and soil degradation management, with Figure \ref{fig:robyn} showing higher sensitivity to these factors.
+The primary difference is the sensitivity to tractor passes, water quality, water scarcity, and soil degradation management, with Figure~\ref{fig:robyn} showing higher sensitivity to these factors.
 
@@
 The comparison reveals that while some factors, such as water use and agrochemical legislation, remain consistently significant, other factors such as soil show variation not only at a regional level but sometimes at the paddock level as described by the expert panel.
-Figures \ref{fig:robyn} and \ref{fig:marcel} highlight the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
+Figures~\ref{fig:robyn} and~\ref{fig:marcel} highlight the unique environmental and regulatory conditions specific to this region, indicating a need for tailored sustainability strategies.
 
 The primary difference in interactions between the two BNs (see Figure~\ref{fig:robyn} and~\ref{fig:marcel}) lies in vineyard floor management, seasonal conditions and tractor passes.
-In Figure \ref{fig:robyn}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure \ref{fig:marcel} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used.
-A distinction which highlighted how operational decisions and priorities can vary and influence the cause of environmental impacts without changing the involved factors, simply through changing the 'why' of nodes' connections.
+In Figure~\ref{fig:robyn}, a higher number of tractor passes were used purposefully to manage the vineyard floor; as opposed to Figure~\ref{fig:marcel} where vineyard floor was managed as a consequence of tractor passes, leveraging opportunities when the tractor was used.
+A distinction which highlighted how operational decisions and priorities can vary and influence the cause of environmental impacts without changing the involved factors, simply through changing the `why' of nodes' connections.
 A point was also raised that scale can cause a further driving factor.
@@
 
-The Coonawarra-specific BNs both support the findings from the literature, with a more structured map of how factors interact compared to the Leximancer summary in Figure \ref{fig:lexi}.
+The Coonawarra-specific BNs both support the findings from the literature, with a more structured map of how factors interact compared to the Leximancer summary in Figure~\ref{fig:lexi}.
 The BN provides a detailed view of the relationships between factors, highlighting the central role of water and the interconnectedness of pest management, market pressures, and climate conditions.
@@
 The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
-This finding aligns with water being the lifeblood of agriculture~\cite{chawlaWaterProductivityAgriculture2023}, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~\cite{australianbureauofstatisticsWaterUseAustralian2021}.
+This finding aligns with water being the lifeblood of agriculture~\citation{chawlaWaterProductivityAgriculture2023}, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~\citation{australianbureauofstatisticsWaterUseAustralian2021}.
 The connection of variables that were linked to operational decisions such as tractor passes, fuel and electricity use illustrated both a way in which the reduction of water use, affects from changes in water quality, climate and disease can influence them.
@@
 Factors that were caused by external events such as seasonal changes were prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
-Importantly, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease~\cite{boisClimateVsGrapevine2017}.
-Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change~\cite{agostaRegionalClimateVariability2012,alsafadiFutureScenariosBioclimatic2023,barriguinhaVineyardYieldEstimation2021,sharmaChapterImpactClimate2014}.
-In a more general sense climate conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield~\cite{barriguinhaVineyardYieldEstimation2021,antonComparativeStudyRisk2012}, erosion~\cite{biddoccuEvaluationSoilErosion2020,doi:10.1177/0309133319861833}, and are further determinants of chosen grape varieties~\cite{topferGrapeVarietiesAre2022, petriashviliImpactClimateChange2023}.
+Importantly, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease~\citation{boisClimateVsGrapevine2017}.
+Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change~\citation{agostaRegionalClimateVariability2012,alsafadiFutureScenariosBioclimatic2023,barriguinhaVineyardYieldEstimation2021,sharmaChapterImpactClimate2014}.
+In a more general sense climate conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield~\citation{barriguinhaVineyardYieldEstimation2021,antonComparativeStudyRisk2012}, erosion~\citation{biddoccuEvaluationSoilErosion2020,doi:10.1177/0309133319861833}, and are further determinants of chosen grape varieties~\citation{topferGrapeVarietiesAre2022, petriashviliImpactClimateChange2023}.
 The BN models captured the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.
@@
 The case study highlighted the direct influences on environmental impact, where it was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}).
-A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\cite{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}.
-The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~\cite{baianoOverviewSustainabilityWine2021}.
+A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\citation{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}.
+The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~\citation{baianoOverviewSustainabilityWine2021}.
 
@@
 The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest/disease control, economic pressures, and climate conditions as key factors.
-Many of these singular relationships are well-defined within literature studies such as those between climate and pest/disease \cite{olatinwoChapterWeatherbasedPest2014}.
-Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combatting external pressures such climate, water scarciy and disease \cite{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}.
-Tools such as Bayesian networks are becoming more applied to assist with the creation of decision support tools such as with water management \cite{carmonaUseParticipatoryObjectOriented2011} or vineyard placement \cite{abbalDecisionSupportSystem2016}.
-However, the combination of holistic approaches to reviewing sustainable practices in the adoption of techniques through measurable and holistic approaches is a growing need in policy creation and uptake of new novel sustainable practices \autocite{mayfieldDesigningExpertledBayesian2023,baianoOverviewSustainabilityWine2021,dichiaraCollaborativeApproachAchieving2024}.
-Although more holistic approaches are required to review the total accumulated benefits of sustainable practices, it is well aligned between researchers, the public and policy-makers that this endeavour is of great importance to the Australian agricultural industry as a whole \cite{dumbrellComparingAustralianPublic2024}.
+Many of these singular relationships are well-defined within literature studies such as those between climate and pest/disease \citation{olatinwoChapterWeatherbasedPest2014}.
+Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combatting external pressures such climate, water scarciy and disease \citation{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}.
+Tools such as Bayesian networks are becoming more applied to assist with the creation of decision support tools such as with water management \citation{carmonaUseParticipatoryObjectOriented2011} or vineyard placement \citation{abbalDecisionSupportSystem2016}.
+However, the combination of holistic approaches to reviewing sustainable practices in the adoption of techniques through measurable and holistic approaches is a growing need in policy creation and uptake of new novel sustainable practices \autocitation{mayfieldDesigningExpertledBayesian2023,baianoOverviewSustainabilityWine2021,dichiaraCollaborativeApproachAchieving2024}.
+Although more holistic approaches are required to review the total accumulated benefits of sustainable practices, it is well aligned between researchers, the public and policy-makers that this endeavour is of great importance to the Australian agricultural industry as a whole \citation{dumbrellComparingAustralianPublic2024}.
 
@@
 The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered.
-A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships~\cite{kimphuctranMachineLearningProbabilistic2022,kollerObjectOrientedBayesianNetworks1997,korbBayesianArtificialIntelligence2011}.
+A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships~\citation{kimphuctranMachineLearningProbabilistic2022,kollerObjectOrientedBayesianNetworks1997,korbBayesianArtificialIntelligence2011}.
 
@@
 Notably these operational decisions can be preventative or reactionary within a season.
-With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (soil, water and disease) particularly all of which are connected to climate~\cite{fragaClimateChangeNew2020,tofaloClimateChangeWine2023,naigeonDATADecisionmakingViticulture2023}.
+With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (soil, water and disease) particularly all of which are connected to climate~\citation{fragaClimateChangeNew2020,tofaloClimateChangeWine2023,naigeonDATADecisionmakingViticulture2023}.
 Additionally, the need to adapt to changing climate conditions can drive increased use of fuel and electricity, potentially exacerbating greenhouse gas emissions.
-The findings align with literature, with researchers highlighting how different operations contribute to climate change through greenhouse gas emmissions \cite{pilafidisAssessingEnergyUse2023,cechPesticideUseAssociated2022,zhangEstimatingEconomicEnvironmental2019} and conversely how climate change increases pressure on farmers~\cite{barnaEditorialImprovingSustainability2023,costaRoleSoilTemperature2023,atakClimateChangeAdaptive2024}, suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practice~\cite{pereiraViticultureClimateChange2023}.
+The findings align with literature, with researchers highlighting how different operations contribute to climate change through greenhouse gas emmissions \citation{pilafidisAssessingEnergyUse2023,cechPesticideUseAssociated2022,zhangEstimatingEconomicEnvironmental2019} and conversely how climate change increases pressure on farmers~\citation{barnaEditorialImprovingSustainability2023,costaRoleSoilTemperature2023,atakClimateChangeAdaptive2024}, suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practice~\citation{pereiraViticultureClimateChange2023}.
 This integrated perspective is crucial for developing effective strategies to enhance the sustainability of the winegrowing industry.
@@
 The BN models captured the intricate ways these factors interact, highlighting the need for adaptive management strategies to cope with climate variability and change.
-With these factors all being connected in someway within the model through propagation across the BN.
+With these factors all being connected in someway within the model through propagation across the BN.\@
 

### 2024-09-02 article.tex
idk whats wrong with it

@@
 \documentclass[fleqn,10pt]{wlscirep}
-
-\lstset{
-  basicstyle=\ttfamily,
-  frame=single,
-  backgroundcolor=\color{lightgray!20},
-  keywordstyle=\color{blue},
-  commentstyle=\color{gray},
-  stringstyle=\color{green},
-  showstringspaces=false
-}
 
@@
 \usepackage[T1]{fontenc}
+
+\usepackage{booktabs}
 \usepackage{graphicx}
-\usepackage{booktabs}
+\usepackage{siunitx}
+
+% \usepackage{tabular}
+
 \usepackage{listings}
 \usepackage{xcolor}
+\usepackage{amsmath}
+
+% \usepackage{biblatex}
+% \addbibresource{\_references.bib}
+% \bibliography{refs} % Entries are in the refs.bib file
 
@@
 
-\section{Introduction}
+\lstset{
+  basicstyle=\ttfamily,
+  frame=single,
+  backgroundcolor=\color{lightgray!20},
+  keywordstyle=\color{blue},
+  commentstyle=\color{gray},
+  stringstyle=\color{green},
+  showstringspaces=false
+}
 
-The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~\citation{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}.
-This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~\citation{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}.
+\section*{Introduction}
+
+The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~(\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}).
+This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~(\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}).
 This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs) to create a broad model for Australian.
 This broad model was followed by a more specific case study looking at the Coonawarra winegrowing region.
-Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~\citation{beaumelle_biodiversity_2023} criterion for assessing sustainability has become multifaceted and has led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics \citation{baiano_overview_2021,montalvo-falconSustainabilityResearchWine2023, waye_carbon_2008}.
+Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~(\cite{beaumelleBiodiversityConservationEcosystem2023}) criterion for assessing sustainability has become multifaceted and has led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics~(\cite{baianoOverviewSustainabilityWine2021,montalvo-falconSustainabilityResearchWine2023, wayeCarbonFootprintsFood2008}).
 In this study we focus on the environmental aspect of sustainability through the use of `environmental impact' as the terminal node within the network, linking relevant factors through structures described by an expert panel.
 
-BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~\citation{korbBayesianArtificialIntelligence2011}.
+BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~(\cite{korbBayesianArtificialIntelligence2011}).
 BNs also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiements, outcomes from published literature, and so on.
@@
 
-\section{Methods}
+\section*{Methods}
 
 In agriculture, the consideration of environment is critical to the success of the industry.
-The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change \citation{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}.
-The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry \citation{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}.
-It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined \citation{santiago-brownSustainabilityAssessmentWineGrape2015}.
+The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change~(\cite{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}).
+The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry~(\cite{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}).
+It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined~(\cite{santiago-brownSustainabilityAssessmentWineGrape2015}).
 
-Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes \citation{dichiaraCollaborativeApproachAchieving2024}.
-In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers \citation{dumbrellComparingAustralianPublic2024}.
-While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources \citation{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}.
+Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes~(\cite{dichiaraCollaborativeApproachAchieving2024}).
+In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers~(\cite{dumbrellComparingAustralianPublic2024}).
+While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}).
 % old comment
@@
 The use of index systems is beneficial in comparing sustainability performance across different industries or geographic regions.
-As \textcitation{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
-Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment \citation{floresWhatSustainabilityWine2018}.
-The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes \citation{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}.
-For instance, frameworks like MESMIS categorize sustainability measures into `descriptors' (guidelines), `indicators' (metrics for measuring changes), and `parameters' (limits for indicators) \citation{candido_sustainability_2015}.
+As~\cite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
+Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment~(\cite{floresWhatSustainabilityWine2018}).
+The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes~(\cite{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}).
+For instance, frameworks like MESMIS categorize sustainability measures into `descriptors' (guidelines), `indicators' (metrics for measuring changes), and `parameters' (limits for indicators)~(\cite{klemes_assessing_2015}).
 This structure allows for a more granular assessment of sustainability by linking broad guidelines to specific, measurable outcomes.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Literature Review}
+\subsection*{Literature Review}
 
@@
 
-% This is the query in a code-like format.
-\begin{lstlisting}[language=]\label{query}
-    (Water OR Agrochemical OR Chemical OR Ground management OR Pest OR Disease OR Management OR Electricity OR Energy OR GHG OR Emissions OR Greenhouse gas emissions OR Environmental OR Environment OR Ecological OR Fertiliser OR Fertilizer OR Fuel OR Biofuel OR Price OR Nutrient OR Runoff OR Leeching OR Market OR Supply and demand OR Soil OR Organic carbon OR SOC OR Tractor OR Field OR Operations OR Weather OR Climate OR Yield OR Production)
-    AND
-    (Sustainability OR Sustainable OR Eco-friendly OR Environmentally friendly OR Green practices)
-    AND
-    (Viticulture OR Winegrowing OR Vineyard)
-    \end{lstlisting}
+% % This is the query in a code-like format.
+% \begin{lstlisting}[language=]
+%     (Water OR Agrochemical OR Chemical OR Ground management OR Pest OR Disease OR Management OR Electricity OR Energy OR GHG OR Emissions OR Greenhouse gas emissions OR Environmental OR Environment OR Ecological OR Fertiliser OR Fertilizer OR Fuel OR Biofuel OR Price OR Nutrient OR Runoff OR Leeching OR Market OR Supply and demand OR Soil OR Organic carbon OR SOC OR Tractor OR Field OR Operations OR Weather OR Climate OR Yield OR Production)
+%     AND
+%     (Sustainability OR Sustainable OR Eco-friendly OR Environmentally friendly OR Green practices)
+%     AND
+%     (Viticulture OR Winegrowing OR Vineyard)
+% \end{lstlisting}\label{query}
 
@@
 
-\subsection{Bayesian Networks}
+\subsection*{Bayesian Networks}
 
@@
 The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes
-\citation{korbBayesianArtificialIntelligence2011}.
+(\cite{korbBayesianArtificialIntelligence2011}).
 % The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.
@@
 The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact
-\citation{pourretBayesianNetworksPractical2008}.
+(\cite{pourretBayesianNetworksPractical2008}).
 Furthermore, data collected across Australia could also be used to help inform the model structure as well as quantify the associated conditional probabilities alongside expert opinion.
@@
 
-% Where we calculate the probability of an event A given an event B, as demonstrated by \citation{bayesLIIEssaySolving1763}.
+% Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
 Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes.
@@
 This type of marginalisation is intuitively represented as nodes conditional independence and illustrated inherently through the structure of the graph by its edges.
+Bayesian Networks created in this study were created using BayesFusion~(\cite{bayesfusionGeNIeModelerUSER2022}) to calculate the networks and their probabilities.
+% The Bayes fuse software was used both through the GUI interface and the SMILE API \cite{bayesfusionGeNIeModelerUSER2022} system using C++ (\cite{ISO:2012:III}).
 
-Bayesian Networks created in this study were created using BayesFusion \citation{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities.
-The Bayes fuse software was used both through the GUI interface and the SMILE API \citation{bayesfusionGeNIeModelerUSER2022} system using C++ \citation{ISO:2012:III}.
+\subsection*{BN Construction and Quantification}
 
-\subsection{BN Construction and Quantification}
-
-The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by \textcitation{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}.
+The Bayesian Network was constructed using a mixture of data and expert elicite, following the format recommended by~(\cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}).
 The process progressed iteratively through problem definition, structure, parameterization, and validation.
@@
 Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency.
-Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.
+Communication included in-person and electronic one-on-ones and group sessions; with elicite of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.
 
@@
 
-\subsection{CPT interpolation}
+\subsection*{CPT interpolation}
 
-As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network \citation{korbBayesianArtificialIntelligence2011}.
+As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network (\cite{korbBayesianArtificialIntelligence2011}).
 For reasons of comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes.
@@
 
-\subsection{BN Validation}
+\subsection*{BN Validation}
 
-The method for validation sought to address criteria presented by \textcitation{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
+The method for validation sought to address criteria presented by~\cite{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
 Nomological validity refers to ensuring that the BN fits within a broader theoretical context, aligning with established literature.
@@
 The selection process for experts, encouraged diversity in their regional knowledge and expertise in order to broaden the ability to critique choices.
-Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions \citation{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.
+Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}).
 
@@
 This helped to avoid some overtly specific scenarios in favour of broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
-This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors \citation{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}.
-% Specifically, the question of water resources, which was central to the model and highly interrelated \citation{carmonaUseParticipatoryObjectOriented2011}.
+This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors~(\cite{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}).
+% Specifically, the question of water resources, which was central to the model and highly interrelated \cite{carmonaUseParticipatoryObjectOriented2011}.
 
@@
 It was found that other studies emphasised the same variables selected by our experts.
-This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes \citation{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}.
-Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively \citation{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}.
+This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes~(\cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}).
+Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively~(\cite{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}).
 
@@
 This issue was simply overcome through explicit definitions accessible to all participants, and by directly addressing issues caused by definitions before further development of the model.
-Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes \citation{korbBayesianArtificialIntelligence2011}.
+Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes~(\cite{korbBayesianArtificialIntelligence2011}).
 
 The factors within the BN had similar parent nodes to factors that appeared in other models from the literature (i.e yield generally utilised area, water, fuel as predictors), although there were key differences.
-The differences were primarily due to the consideration of nodes as factors that related and were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the environmental outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation \citation{laurentReviewIssuesMethods2021}.
+The differences were primarily due to the consideration of nodes as factors that related and were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the environmental outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation~(\cite{laurentReviewIssuesMethods2021}).
 The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being able to be properly employed.
@@
 
-\subsection{Sensitivity analysis}
+\subsection*{Sensitivity analysis}
 
@@
 
-In this study, the sensitivity analysis conducted utilised the Bayesian Network software GeNie, implementing the algorithm developed by \textcitation{article}; an optimisation of \textcitation{Castillo1996ANM} and \textcitation{Gaag1998PracticableSA}.
+In this study, the sensitivity analysis conducted utilised the Bayesian Network software GeNie, implementing the algorithm developed by~\cite{article}; an optimisation of~\cite{Castillo1996ANM} and~\cite{Gaag1998PracticableSA}.
 The method allowed for efficient computation of the influence of parameter variations on the output probabilities of the BNs terminal node `Environmental Impact'.
@@
 \begin{equation}
-y = {{p(a, e)(x)}\over{p(e)(x)}}={{\alpha x + \beta}\over{\gamma x + \delta}}
+y = \frac{p(a, e)(x)}{p(e)(x)}=\frac{\alpha x + \beta}{\gamma x + \delta}
 \end{equation}.
@@
 
-\subsection{Case study: Coonawarra}
+\subsection*{Case study: Coonawarra}
 
@@
 This combination provides an exceptional foundation for viticulture, making Coonawarra a renowned wine-producing area.
-The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \citation{hallidayAustralianWineEncyclopedia2009}.
+The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon~(\cite{hallidayAustralianWineEncyclopedia2009}).
 Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around sustainability practices to specific regional factors.
@@
 
-\section{Results}
+\section*{Results}
 
-\subsection{Industry definitions}
+\subsection*{Industry definitions}
 
@@
 
-\begin{table}[h]\label{tab:definitions} 
+\begin{table}[h]
     \begin{tabular}{@{}llll@{}}
-        \caption{\textbf{Table 1:} This table provides the definitions of key terms and concepts utilised throughout the study.
-Each term is explained in the context of its relevance to the terminal node environmental impact.
-The table was used by experts throughout the study to maintain clarity and meaning behind concepts and how they related.}
     \toprule
@@
 & \textbf{Yes} & No \\
-    \textbf{Water Scarcity} & Whether the country is suffering drought or not (s defined by BOM) & No & \textbf{Yes} \\
+    \textbf{Water Scarcity} & Whether the country is suffering drought or not (defined by BOM) & No & \textbf{Yes} \\
     \textbf{Climate Conditions} & A vineyard's regional climatic conditions. & \textbf{Ideal} & Not Ideal \\
@@
     \end{tabular}
+    \caption{\textbf{Table 1:} This table provides the definitions of key terms and concepts utilised throughout the study.
+Each term is explained in the context of its relevance to the terminal node environmental impact.
+The table was used by experts throughout the study to maintain clarity and meaning behind concepts and how they related.}\label{tab:definitions}
 \end{table}
@@
 
-\subsection{Bayesian Network Structure for sustainability in Australian Winegrowing}
+\subsection*{Bayesian Network Structure for sustainability in Australian Winegrowing}
 
@@
 
-\subsection{Comparative Analysis of Literature and Industry Perspectives}
+\subsection*{Comparative Analysis of Literature and Industry Perspectives}
 
@@
 The critical importance of other variables is indicated by their comparative frequncy in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
-
 % What are the factors of sustainability in the Australian winegrowing industry?
@@
 %     - Use the same words as the definitions in the search to show the parralels and differences.
-
 % Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-\begin{table}[h]\label{tab:lexi}
-    \caption{Table~\ref{tab:lexi} Table~\ref{tab}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}
+\begin{table}[h]
     \begin{tabular}{@{}lrr@{}}
@@
     \end{tabular}
+    \caption{Table~\ref{tab:lexi} Table~\ref{tab}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}\label{tab:lexi}
 \end{table}
-
 % Comparing this with the data from Sustainable Winegrowing Australia (SWA), it was evident that the factors identified in the BN align with the critical areas SWA focuses on, such as water use, greenhouse gas emissions, and agrochemical use.
@@
     \caption{hello}\label{fig:lexi}
-        % TODO: add a caption the explains what the connection between concepts in lexi is and how words are selected and culled - what is a concept. Reference the Lexi proceedures followed too}
+        % TODO: add a caption the explains what the connection between concepts in lexi is and how words are selected and culled - what is a concept. Reference the Lexi proceedures followed too
 \end{figure}
@@
 
-\subsection{Region-specific BN:~Coonawarra}
+\subsection*{Region-specific BN:~Coonawarra}
 % TODO: add CPTs to appendix - do this as a final step!
@@
 
-% \subsection{Results notes}
+% \subsection*{Results notes}
 
@@
 
-\section{Discussion}
+\section*{Discussion}
 % weather or climate?
@@
 The influence of water use reached almost every variable, with its connection to operational decisions being reflected within its propagation to other factors such as tractor use, disease and pest prevention, as well as management strategies for soil.
-This finding aligns with water being the lifeblood of agriculture~\citation{chawlaWaterProductivityAgriculture2023}, essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~\citation{australianbureauofstatisticsWaterUseAustralian2021}.
+This finding aligns with water being the lifeblood of agriculture~(\cite{chawlaWaterProductivityAgriculture2023}), essential for both the health of the vines and the broader ecosystem, especially within Australia's dry climate~(\cite{australianbureauofstatisticsWaterUseAustralian2021}).
 The connection of variables that were linked to operational decisions such as tractor passes, fuel and electricity use illustrated both a way in which the reduction of water use, affects from changes in water quality, climate and disease can influence them.
@@
 Factors that were caused by external events such as seasonal changes were prominently connected to vineyard operations through their connection to factors such as fuel, tractor, water and electricity use.
-Importantly, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease~\citation{boisClimateVsGrapevine2017}.
-Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change~\citation{agostaRegionalClimateVariability2012,alsafadiFutureScenariosBioclimatic2023,barriguinhaVineyardYieldEstimation2021,sharmaChapterImpactClimate2014}.
-In a more general sense climate conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield~\citation{barriguinhaVineyardYieldEstimation2021,antonComparativeStudyRisk2012}, erosion~\citation{biddoccuEvaluationSoilErosion2020,doi:10.1177/0309133319861833}, and are further determinants of chosen grape varieties~\citation{topferGrapeVarietiesAre2022, petriashviliImpactClimateChange2023}.
+Importantly, climate acted as an interface between water and pest/disease, due to climate being a determining factor in temperature and water availability which are highly influential to pests and disease~(\cite{boisClimateVsGrapevine2017}).
+Understanding these interactions is vital for developing adaptive management strategies that can cope with climate variability and change~(\cite{agostaRegionalClimateVariability2012,alsafadiFutureScenariosBioclimatic2023,barriguinhaVineyardYieldEstimation2021,sharmaChapterImpactClimate2014}).
+In a more general sense climate conditions are shown within the literature to be significant determinants of a variety of factors within vineyards such as yield~\cite{barriguinhaVineyardYieldEstimation2021,antonComparativeStudyRisk2012}, erosion~(\cite{biddoccuEvaluationSoilErosion2020,doi:10.1177/0309133319861833}), and are further determinants of chosen grape varieties~(\cite{topferGrapeVarietiesAre2022, petriashviliImpactClimateChange2023}).
 The BN models captured the complexity of how climate can propagate to these considerations through other factors; as well as how these other factors are connected.
@@
 The case study highlighted the direct influences on environmental impact, where it was found to be most sensitive to factors such as pests/disease, water use, economic pressures and climate which were found to be highly related through their connection to elements used in operational responses such as the use of agrochemicals and tractors (see Figures~\ref{fig:robyn} and~\ref{fig:marcel}).
-A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~\citation{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}.
-The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~\citation{baianoOverviewSustainabilityWine2021}.
+A major concern from the industry panel within these relationships was that, while necessary for maintaining vine health and productivity, excessive or inappropriate agrochemical use can lead to major negative environmental impacts~(\cite{alonsogonzalezUnveilingTerroirEvaluating2024,manjarres-lopezAssessmentPesticideResidues2021}).
+The model emphasised the need for balanced and regulated agrochemical practices; and especially for such practices being followed appropriately~(\cite{baianoOverviewSustainabilityWine2021}).
 
@@
 The findings from this study are consistent with the existing literature on sustainability in viticulture, which also identifies water management, pest/disease control, economic pressures, and climate conditions as key factors.
-Many of these singular relationships are well-defined within literature studies such as those between climate and pest/disease \citation{olatinwoChapterWeatherbasedPest2014}.
-Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combatting external pressures such climate, water scarciy and disease \citation{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}.
-Tools such as Bayesian networks are becoming more applied to assist with the creation of decision support tools such as with water management \citation{carmonaUseParticipatoryObjectOriented2011} or vineyard placement \citation{abbalDecisionSupportSystem2016}.
-However, the combination of holistic approaches to reviewing sustainable practices in the adoption of techniques through measurable and holistic approaches is a growing need in policy creation and uptake of new novel sustainable practices \autocitation{mayfieldDesigningExpertledBayesian2023,baianoOverviewSustainabilityWine2021,dichiaraCollaborativeApproachAchieving2024}.
-Although more holistic approaches are required to review the total accumulated benefits of sustainable practices, it is well aligned between researchers, the public and policy-makers that this endeavour is of great importance to the Australian agricultural industry as a whole \citation{dumbrellComparingAustralianPublic2024}.
+Many of these singular relationships are well-defined within literature studies such as those between climate and pest/disease~(\cite{olatinwoChapterWeatherbasedPest2014}).
+Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combatting external pressures such climate, water scarciy and disease~(\cite{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}).
+Tools such as Bayesian networks are becoming more applied to assist with the creation of decision support tools such as with water management~(\cite{carmonaUseParticipatoryObjectOriented2011}) or vineyard placement~(\cite{abbalDecisionSupportSystem2016}).
+However, the combination of holistic approaches to reviewing sustainable practices in the adoption of techniques through measurable and holistic approaches is a growing need in policy creation and uptake of new novel sustainable practices~(\cite{mayfieldDesigningExpertledBayesian2023,baianoOverviewSustainabilityWine2021,dichiaraCollaborativeApproachAchieving2024}).
+Although more holistic approaches are required to review the total accumulated benefits of sustainable practices, it is well aligned between researchers, the public and policy-makers that this endeavour is of great importance to the Australian agricultural industry as a whole~(\cite{dumbrellComparingAustralianPublic2024}).
 
@@
 The BN allows the further exploration of the peripheral connections beyond these relationships to be further considered.
-A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships~\citation{kimphuctranMachineLearningProbabilistic2022,kollerObjectOrientedBayesianNetworks1997,korbBayesianArtificialIntelligence2011}.
+A strength behind the use of Bayesian Network is the ability to replace edges between nodes with any analysis that allows for the derivation of a posterior from some input prior; allowing for the BN to be used as a framework that can further integrate other studies results into these relationships~(\cite{kimphuctranMachineLearningProbabilistic2022,kollerObjectOrientedBayesianNetworks1997,korbBayesianArtificialIntelligence2011}).
 
@@
 Notably these operational decisions can be preventative or reactionary within a season.
-With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (soil, water and disease) particularly all of which are connected to climate~\citation{fragaClimateChangeNew2020,tofaloClimateChangeWine2023,naigeonDATADecisionmakingViticulture2023}.
+With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (soil, water and disease) particularly all of which are connected to climate~(\cite{fragaClimateChangeNew2020,tofaloClimateChangeWine2023,naigeonDATADecisionmakingViticulture2023}).
 Additionally, the need to adapt to changing climate conditions can drive increased use of fuel and electricity, potentially exacerbating greenhouse gas emissions.
-The findings align with literature, with researchers highlighting how different operations contribute to climate change through greenhouse gas emmissions \citation{pilafidisAssessingEnergyUse2023,cechPesticideUseAssociated2022,zhangEstimatingEconomicEnvironmental2019} and conversely how climate change increases pressure on farmers~\citation{barnaEditorialImprovingSustainability2023,costaRoleSoilTemperature2023,atakClimateChangeAdaptive2024}, suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practice~\citation{pereiraViticultureClimateChange2023}.
+The findings align with literature, with researchers highlighting how different operations contribute to climate change through greenhouse gas emmissions~(\cite{pilafidisAssessingEnergyUse2023,cechPesticideUseAssociated2022,zhangEstimatingEconomicEnvironmental2019}) and conversely how climate change increases pressure on farmers~(\cite{barnaEditorialImprovingSustainability2023,costaRoleSoilTemperature2023,atakClimateChangeAdaptive2024}), suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practice~(\cite{pereiraViticultureClimateChange2023}).
 This integrated perspective is crucial for developing effective strategies to enhance the sustainability of the winegrowing industry.
@@
 
-\section{Conclusion}
+\section*{Conclusion}
 
@@
 
-\section{References}
+\section*{References}
 % Your references text goes here.
-\bibliographystyle{plain}
-\bibliography{references}
+% \bibliographystyle{plain}
+% \printbibliography
+% \bibliographystyle{plain} % We choose the "plain" reference style
+\bibliography{references} % Entries are in the refs.bib file
 

### 2024-09-03 article.tex
Pre-Kate update incorporating scientific reports template

@@
 \documentclass[fleqn,10pt]{wlscirep}
-
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-
-\usepackage{booktabs}
-\usepackage{graphicx}
-\usepackage{siunitx}
-
-% \usepackage{tabular}
-
 \usepackage{listings}
-\usepackage{xcolor}
-\usepackage{amsmath}
-
-% \usepackage{biblatex}
-% \addbibresource{\_references.bib}
-% \bibliography{refs} % Entries are in the refs.bib file
 
@@
 Sustainability in the Australian winegrowing industry involves complex, interacting factors.
-To address this, we developed a Bayesian Network (BN) model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes.
-The BN model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability.
+To address this, we developed a Bayesian Network model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes.
+The Bayesian Network model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability.
 A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use.
-This study underscores the potential of BNs as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
+This study underscores the potential of Bayesian Networks as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
 \end{abstract}
-
 \begin{document}
@@
 
+\flushbottom
+\maketitle
+
+\thispagestyle{empty}
+
 \section*{Introduction}
-
 The imperative for sustainability in agriculture has intensified as the sector strives to balance productivity with ecological preservation~(\cite{baianoOverviewSustainabilityWine2021,corboEnvironmentalSustainabilityPrograms2014}).
@@
 BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~(\cite{korbBayesianArtificialIntelligence2011}).
-BNs also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiements, outcomes from published literature, and so on.
+Bayesian Networks (BNs) also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiments, outcomes from published literature, and so on.
 In this study, the BNs integrated expert knowledge and region-specific data within a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing.
@@
 A primary question is how key factors impact the environment, and how these factors can be rigorously defined and quantified.
-Furthremore, the study delves into how factors change due to the unique characteristics of different winegrowing regions, using the Coonawarra region to illustrate how the relative influence of factors change.
+Furthermore, the study delves into how factors change due to the unique characteristics of different winegrowing regions, using the Coonawarra region to illustrate how the relative influence of factors change.
 Additionally, the study investigates how these factors interact with each other.
@@
 These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification.
-The most prominent way of informing the model was the construction of an initial strawman model to describe different relationships explored in the literature, which helped as a beginning point for the experts to discuss the specific applicability of relationships for different Australian contexts.
+The most prominent way of informing the model was the construction of an initial straw-man model to describe different relationships explored in the literature, which helped as a beginning point for the experts to discuss the specific applicability of relationships for different Australian contexts.
 The literature review was done using systematic search of terms, broadly based on key factors given from the industry panel, was conducted.
@@
 % % This is the query in a code-like format.
-% \begin{lstlisting}[language=]
-%     (Water OR Agrochemical OR Chemical OR Ground management OR Pest OR Disease OR Management OR Electricity OR Energy OR GHG OR Emissions OR Greenhouse gas emissions OR Environmental OR Environment OR Ecological OR Fertiliser OR Fertilizer OR Fuel OR Biofuel OR Price OR Nutrient OR Runoff OR Leeching OR Market OR Supply and demand OR Soil OR Organic carbon OR SOC OR Tractor OR Field OR Operations OR Weather OR Climate OR Yield OR Production)
-%     AND
-%     (Sustainability OR Sustainable OR Eco-friendly OR Environmentally friendly OR Green practices)
-%     AND
-%     (Viticulture OR Winegrowing OR Vineyard)
-% \end{lstlisting}\label{query}
+\begin{lstlisting}[language=]
+    (Water OR Agrochemical OR Chemical OR Ground management OR Pest
+    OR Disease OR Management OR Electricity OR Energy OR GHG
+    OR Emissions OR Greenhouse gas emissions OR Environmental
+    OR Environment OR Ecological OR Fertiliser OR Fertilizer OR Fuel
+    OR Biofuel OR Price OR Nutrient OR Runoff OR Leeching OR Market
+    OR Supply and demand OR Soil OR Organic carbon OR SOC OR Tractor
+    OR Field OR Operations OR Weather OR Climate OR Yield
+    OR Production)
+    AND
+    (Sustainability OR Sustainable OR Eco-friendly OR
+    Environmentally friendly OR Green practices)
+    AND
+    (Viticulture OR Winegrowing OR Vineyard)
+    \label{lst:query}
+\end{lstlisting}
 
@@
 
-Given the directed acyclic graph (DAC) structure of the BN, each quantification of a node only depends on the parent of that node, and is conditionally independent of the other nodes in the network collectively, then,
+Given the directed acyclic graph (DAG) structure of the BN, each quantification of a node only depends on the parent of that node, and is conditionally independent of the other nodes in the network collectively, then,
 
@@
 
-The Bayesian Network was constructed using a mixture of data and expert elicite, following the format recommended by~(\cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}).
-The process progressed iteratively through problem definition, structure, parameterization, and validation.
+The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by~(\cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}).
+The process progressed iteratively through problem definition, structure, parameterisation, and validation.
 Initially, experts were informed about the process to ensure a clear understanding of each step and to highlight common pitfalls, as well as how these would be addressed.
@@
 Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency.
-Communication included in-person and electronic one-on-ones and group sessions; with elicite of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.
+Communication included in-person and electronic one-on-ones and group sessions; with elicited of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.
 
@@
 
-To introduce new concepts and how they interacted, preliminary simplified versions (strawman examples) were provided to experts; with the intention of these examples to be examined, critiqued, and improved upon.
-The use of these strawman examples enabled a more engaged and effective review process.
+To introduce new concepts and how they interacted, preliminary simplified versions (straw-man examples) were provided to experts; with the intention of these examples to be examined, critiqued, and improved upon.
+The use of these straw-man examples enabled a more engaged and effective review process.
 Experts were initially able to interact with elements of the model and see how they worked together.
-The strawman examples were crafted from a foundation of literature and data to offer a basic, layman's understanding of key factors and concepts, serving as a starting point for further development and discussion.
+The straw-man examples were crafted from a foundation of literature and data to offer a basic, layman's understanding of key factors and concepts, serving as a starting point for further development and discussion.
 
@@
 Similarly, the convergent validity of the model was accomplished through the checking the alignment of the model to other research, which helped to further answer questions of concurrent validation.
-This process was undertaken after the regional models were developed in unison with the literature review and creation of leximancer concept map.
+This process was undertaken after the regional models were developed in unison with the literature review and creation of Leximancer concept map.
 It was found that other studies emphasised the same variables selected by our experts.
@@
 
-As discussed above the expert advisory panel proposed the development of a reigonal model to augment and focus the primary general model.
+As discussed above the expert advisory panel proposed the development of a regional model to augment and focus the primary general model.
 For specificity the panel proposed a case study of a specific and well understood region: Coonawarra in South Australia.
@@
 The Coonawarra BN was based on the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.
-Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for undervine operations and more purposeful undervine management, as well as the inclusion of further soil based factors that could be significant for particular sites.
+Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for under vine operations and more purposeful under vine management, as well as the inclusion of further soil based factors that could be significant for particular sites.
 
@@
     \textbf{Fertiliser use} & Total amount of nitrogen (synthetic and organic) used by a vineyard in a financial year (Kg/Ha) & \textbf{Low} & High \\
-    \textbf{Fuel use} & Total amount of fuel (diesel, petrol, lpg and biodiesel) used by a vineyard in a financial year (L/Ha) & \textbf{Low} & High \\
+    \textbf{Fuel use} & Total amount of fuel (diesel, petrol, LPG and bio-diesel) used by a vineyard in a financial year (L/Ha) & \textbf{Low} & High \\
     \textbf{Renewable Fuel} & Percentage of fuel used that is renewable. & High & \textbf{Low} \\
@@
 & \textbf{Yes} & No \\
-    \textbf{Market supply and demand} & The relationship between the quantity of winegrapes produced and the quantity that consumers wish to buy & High & \textbf{Low} \\
+    \textbf{Market supply and demand} & The relationship between the quantity of wine-grapes produced and the quantity that consumers wish to buy & High & \textbf{Low} \\
     \textbf{Pest and Disease Management} & The management of pests and diseases such as through the employ of fungicide and pesticides & \textbf{Yes} & No \\
@@
 
-The relationships between the facets in Table~\ref{tab:definitions}  as agreed by the industry panel, are depicted in the BN model in Fig~\ref{figure:generalBN}.
+\begin{figure}[h!]
+    \centering
+    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
+    \caption{The resultant Bayesian Network (BN) illustrating the relationships between vineyard factors and environmental impact in Australian winegrowing.
+The network's nodes are color-coded to indicate the source and nature of the data: Blue nodes represent expert-led ideas that are not directly supported by data, Green nodes are supported by data contained in Sustainable Winegrowing Australia's database, and Gold nodes correspond to variables with readily accessible public data.
+The terminal node is highlighted in pink.}\label{fig:generalBN}
+\end{figure}
+
+The relationships between the facets in Table~\ref{tab:definitions}  as agreed by the industry panel, are depicted in the BN model in Fig~\ref{fig:generalBN}.
 The BN highlights which factors are influenced by others in the form of an acyclic directed graph.
 Notably, the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
-It also illustrates the complex nature of variables such as water and their interrelatedness.
+It also illustrates the complex nature of variables such as water and their inter-relatedness.
 
@@
 %
-\begin{figure}[h!]
-    \centering
-    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
-    \caption{The resultant Bayesian Network (BN) illustrating the relationships between vineyard factors and environmental impact in Australian winegrowing.
-The network's nodes are color-coded to indicate the source and nature of the data: Blue nodes represent expert-led ideas that are not directly supported by data, Green nodes are supported by data contained in Sustainable Winegrowing Australia's database, and Gold nodes correspond to variables with readily accessible public data.
-The terminal node is highlighted in pink.}\label{fig:generalBN}
-\end{figure}
 
@@
 
-By mapping these relationships, the BN provides a visual and analytical framework that aids in identifying the most influential factors and understanding their interdependencies.
+By mapping these relationships, the BN provides a visual and analytical framework that aids in identifying the most influential factors and understanding their inter-dependencies.
 This, in turn, helps inform decisions toward more environmentally sustainable practices.
@@
 As part of this study, a comprehensive literature review was conducted to assess the current state of research on sustainability in the winegrowing industry and as part of the BNs validation.
-The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see~\ref{query}).
+The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see~\ref{lst:query}).
 The articles span a range of topics, including sustainability metrics, operational practices, and the influence of regulatory frameworks on environmental outcomes.
@@
 The most prominent concept was water (see Table~\ref{tab:lexi}).
-The critical importance of other variables is indicated by their comparative frequncy in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
+The critical importance of other variables is indicated by their comparative frequency in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
 % What are the factors of sustainability in the Australian winegrowing industry?
@@
 % Please add the following required packages to your document preamble:
-\begin{table}[h]
+\begin{table}[ht]
     \begin{tabular}{@{}lrr@{}}
     \toprule
-    \textbf{Concept} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
+
+    \textbf{Concept} & \textbf{Count} & \textbf{Relevance Percentage} \\
+    \midrule
     water & 1321 & 100 \\
@@
     \end{tabular}
-    \caption{Table~\ref{tab:lexi} Table~\ref{tab}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}\label{tab:lexi}
+    \caption{Table~\ref{tab:lexi} Table~\ref{tab:lexi}: Key Concepts Identified in the Bibliometric Analysis of sustainability in the Australian Winegrowing Industry.}\label{tab:lexi}
 \end{table}
@@
     \includegraphics[width=\linewidth]{Winegrowing-concept-map}
-    \caption{hello}\label{fig:lexi}
-        % TODO: add a caption the explains what the connection between concepts in lexi is and how words are selected and culled - what is a concept. Reference the Lexi proceedures followed too
+    \caption{Concept map generated by Leximancer illustrating key themes and their interconnections in the literature on sustainable winegrowing.}\label{fig:lexi}
 \end{figure}
@@
 The first decision would have the act of spraying cause a lower probability of disease to occur, and the second being that the presence of disease would be more likely to initiate the use of agrochemicals.
-The two arguments for the relationship between tractor passes and under vine management reflect this type of causal reversal, where they differed in the use of tractors to actively manage the undervine area or to leverage the tractor when it was already being used for other tasks to then manage the undervine as a consequence.
+The two arguments for the relationship between tractor passes and under vine management reflect this type of causal reversal, where they differed in the use of tractors to actively manage the under-vine area or to leverage the tractor when it was already being used for other tasks to then manage the undervine as a consequence.
 These types of differences in management perspectives can greatly effect the root decision that impacts the environmental even if they do not directly change the most sensitive or contributing factors, as in this case both models maintained similar sensitivities to agrochemical use, water, and climate.
@@
 Identified key factors impacting sustainability were examined with regard to Coonawarra.
-By comparing the generic Bayesian Network (Figure~\ref{fig:b}) model to the Coonawarra-specific model (Figure~\ref{fig:robyn} and Figure~\ref{fig:marcel}), we identified regional characteristics that influence these variations.
+By comparing the generic Bayesian Network (Figure~\ref{fig:generalBN}) model to the Coonawarra-specific model (Figure~\ref{fig:robyn} and Figure~\ref{fig:marcel}), we identified regional characteristics that influence these variations.
 In this case study, we altered the general Australian BN to model and analyse the complex interactions between various environmental factors affecting wine production in Coonawarra.
@@
 However, many of these considerations can also be caused by more granular variables that are not within these models, such as composting, soil depth and clay content.
-The inability to consider different activitiies at multiple scales without hte use of multiple models becomes a limiting factor.
+The inability to consider different activities at multiple scales without the use of multiple models becomes a limiting factor.
 
@@
 Many of these singular relationships are well-defined within literature studies such as those between climate and pest/disease~(\cite{olatinwoChapterWeatherbasedPest2014}).
-Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combatting external pressures such climate, water scarciy and disease~(\cite{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}).
+Furthermore, literature  highlights a growing need for data and more decision support tools to assist with combating external pressures such climate, water scarcity and disease~(\cite{naigeonDATADecisionmakingViticulture2023,stefaniniBayesianCausalModel2022,fincoCombiningPrecisionViticulture2022a,laurentLocalInfluenceClimate2022}).
 Tools such as Bayesian networks are becoming more applied to assist with the creation of decision support tools such as with water management~(\cite{carmonaUseParticipatoryObjectOriented2011}) or vineyard placement~(\cite{abbalDecisionSupportSystem2016}).
@@
 Additionally, the need to adapt to changing climate conditions can drive increased use of fuel and electricity, potentially exacerbating greenhouse gas emissions.
-The findings align with literature, with researchers highlighting how different operations contribute to climate change through greenhouse gas emmissions~(\cite{pilafidisAssessingEnergyUse2023,cechPesticideUseAssociated2022,zhangEstimatingEconomicEnvironmental2019}) and conversely how climate change increases pressure on farmers~(\cite{barnaEditorialImprovingSustainability2023,costaRoleSoilTemperature2023,atakClimateChangeAdaptive2024}), suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practice~(\cite{pereiraViticultureClimateChange2023}).
+The findings align with literature, with researchers highlighting how different operations contribute to climate change through greenhouse gas emissions~(\cite{pilafidisAssessingEnergyUse2023,cechPesticideUseAssociated2022,zhangEstimatingEconomicEnvironmental2019}) and conversely how climate change increases pressure on farmers~(\cite{barnaEditorialImprovingSustainability2023,costaRoleSoilTemperature2023,atakClimateChangeAdaptive2024}), suggesting future research should focus on integrated resource management, technological innovations to reduce energy consumption, and policy incentives to promote energy-efficient practice~(\cite{pereiraViticultureClimateChange2023}).
 This integrated perspective is crucial for developing effective strategies to enhance the sustainability of the winegrowing industry.
@@
 
-The relationships of nodes associated with operational and management  decisions illustrated how different drivers from nodes several edges away from environmetnal impact could still be driving forces through their causal influence of the primary contributing factors.
-Furthermore, extenral considerations such as market pressures, the demand for high-quality grapes through factors such as grape prices, were found to have an impact on the environment through how they influenced internal responses, such as the use of more water to increase yields as a response to price increases.
-The economic drivers of some of the decisions would be a great compliment in determinig how the priority of these decision might be made alongside their environmental concerns, and poses a potential avenue for further research.
+The relationships of nodes associated with operational and management  decisions illustrated how different drivers from nodes several edges away from environmental impact could still be driving forces through their causal influence of the primary contributing factors.
+Furthermore, external considerations such as market pressures, the demand for high-quality grapes through factors such as grape prices, were found to have an impact on the environment through how they influenced internal responses, such as the use of more water to increase yields as a response to price increases.
+The economic drivers of some of the decisions would be a great compliment in determining how the priority of these decision might be made alongside their environmental concerns, and poses a potential avenue for further research.
 
@@
 
-\section*{References}
-% Your references text goes here.
-% \bibliographystyle{plain}
-% \printbibliography
-% \bibliographystyle{plain} % We choose the "plain" reference style
-\bibliography{references} % Entries are in the refs.bib file
+\bibliography{sample}
+
+% \noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
+Use the cite command for an inline citation, e.g.
+
+% For data citations of datasets uploaded to e.g.
+\emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.
+
+% \section*{Acknowledgements (not compulsory)}
+
+% Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
+
+% \section*{Author contributions statement}
+
+% Must include all authors, identified by initials, for example:
+% A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.
+
+% \section*{Additional information}
+
+% To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).
+
+% The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper.
+This statement must be included in the submitted article file.
 

### 2024-12-03 article.tex
revising introduction, start of methods revision.

@@
-\documentclass[fleqn,10pt]{wlscirep}
+\documentclass[10pt,letterpaper]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{listings}
+\usepackage{biblatex}
 
-\title{A Bayesian Network Model based decision support tool for sustainability in the Australian Winegrowing Industry.}
+\addbibresource{references.bib}
 
-\author[1,2,3,*]{Bryce Boyd}
-\author[1]{Kate Helmsteadt}
-\author[2]{Mardi Longbottom}
-\author[1]{Kerrie Mengersen}
+\title{A Bayesian Network Model-based decision support tool for sustainability in the Australian Winegrowing Industry.}
 
-\affil[1]{QUT, Mathematical Sciences, Brisbane, Australia}
-\affil[2]{AWRI, Adelaide, Australia}
-\affil[3]{Food Agility CRC}
+\begin{document}
 
-\affil[*]{bryce.polley@awri.com.au}
+% \author[1,2,3,*]{Bryce Boyd}
+% \author[1]{Kate Helmsteadt}
+% \author[2]{Mardi Longbottom}
+% \author[1]{Kerrie Mengersen}
+
+% \affil[1]{QUT, Mathematical Sciences, Brisbane, Australia}
+% \affil[2]{AWRI, Adelaide, Australia}
+% \affil[3]{Food Agility CRC}
+
+% \affil[*]{bryce.polley@awri.com.au}
 
@@
 Sustainability in the Australian winegrowing industry involves complex, interacting factors.
-To address this, we developed a Bayesian Network model, integrating data and expert input to summarise key factors, their relationships, and impacts on vineyard outcomes.
-The Bayesian Network model was iteratively refined, involving variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability.
-A case study of the Coonawarra region highlighted regional differences while underscoring industry-wide concerns, such as agrochemical use.
-This study underscores the potential of Bayesian Networks as powerful tools for sustainability analysis in agriculture, offering valuable insights for sustainable vineyard management.
+To address this, we developed a Bayesian Network model, integrating data and expert input to summarise key factors, their relationships, and their impacts on vineyard outcomes.
+The Bayesian Network model was iteratively refined, utilising variable selection, structure definition, and probability estimation, with expert input ensuring industry relevance and regional adaptability.
+A case study of the Coonawarra and Riverland regions was conducted to highlight regional differences whilst emphasising industry-wide concerns, such as agrochemical use and water consumption.
+This study underscores the potential of Bayesian Networks as powerful tools for sustainability analysis in agriculture to connect industry concerns, analyses and literature, offering valuable insights for sustainable vineyard management.
 \end{abstract}
-\begin{document}
 
@@
 This is especially true for viticulture, the cultivation of grapevines for wine production, as it presents unique challenges and opportunities for sustainability, particularly due to its position as a luxury good amongst other agricultural industries~(\cite{longbottomExploringLinksSustainability2018,ferraraLifeCycleAssessment2018}).
-This study investigates sustainability practices in Australian winegrowing, using the application of Bayesian Networks (BNs) to create a broad model for Australian.
-This broad model was followed by a more specific case study looking at the Coonawarra winegrowing region.
-Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~(\cite{beaumelleBiodiversityConservationEcosystem2023}) criterion for assessing sustainability has become multifaceted and has led to the creation of many institutions with varying industry-specific frameworks for sustainability metrics~(\cite{baianoOverviewSustainabilityWine2021,montalvo-falconSustainabilityResearchWine2023, wayeCarbonFootprintsFood2008}).
-In this study we focus on the environmental aspect of sustainability through the use of `environmental impact' as the terminal node within the network, linking relevant factors through structures described by an expert panel.
+Due to the diverse nature of Sustainable practices and the complicated interactions with environmental, social and economic outcomes~(\cite{beaumelleBiodiversityConservationEcosystem2023}), the criterion for assessing sustainability has become multifaceted, leading to the creation of many institutions with varying industry-specific approaches to creating sustainability metrics~(\cite{baianoOverviewSustainabilityWine2021,montalvo-falconSustainabilityResearchWine2023, wayeCarbonFootprintsFood2008}).
+Whilst various sustainability frameworks exist, they are often limited in scope, failing to adapt to regional differences and requirements, and to capture the complex, interconnected nature of factors~\cite{santiniSustainabilityWineIndustry2013, christ2013critical}.
+Existing tools frequently focus on single metrics and relationships and cannot integrate regional variability or address the unique environmental challenges of Australian winegrowing~(\cite{baianoOverviewSustainabilityWine2021,leask2019sustainable, abbalDecisionSupportSystem2016}).
 
-BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems~(\cite{korbBayesianArtificialIntelligence2011}).
-Bayesian Networks (BNs) also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiments, outcomes from published literature, and so on.
-In this study, the BNs integrated expert knowledge and region-specific data within a structured framework to quantify the impacts of various factors on sustainability within Australian winegrowing.
-This methodology shed light on current sustainability practices, identified critical areas for intervention and facilitated evolution of the potential impact of various management action or climate scenarios.
+As the agricultural industry in Australia continues to be affected by international market demands, disease pressures, natural disasters and social change; the question of sustainability has continued to grow in importance ~(\cite{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}).
+The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry~(\cite{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}).
+It is essential to consider each factor concerning these perspectives, and to be explicit in how they are defined~(\cite{santiago-brownSustainabilityAssessmentWineGrape2015}).
 
-This research is guided by several fundamental inquiries aimed at enhancing our understanding of sustainability in viticulture.
-A primary question is how key factors impact the environment, and how these factors can be rigorously defined and quantified.
-Furthermore, the study delves into how factors change due to the unique characteristics of different winegrowing regions, using the Coonawarra region to illustrate how the relative influence of factors change.
+This study investigates sustainable practices in Australian winegrowing using Bayesian Networks (BNs), using a broad model for Australia to structure the connections between industry concerns.
+Collaboration between experts from different perspectives helps to reconcile opinions regarding other factors and their contribution to sustainable outcomes~(\cite{dichiaraCollaborativeApproachAchieving2024}).
+In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers~(\cite{dumbrellComparingAustralianPublic2024}).
+While there is a general agreement on broader regulatory needs, the industry requirements vary significantly between different wine regions due to climate, soil types and water resources~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}).
+To address this Regional-specific models were subsequently derived from this network's structure, adding conditional probabilities to compare different industry priorities between regions and to delve deeper into the intensity of connections between industry concerns by reflecting the strength of these relationships through a probabilistic network.
+
+BNs are probabilistic models that capture and analyse the interactions between multiple factors in complex systems.
+BNs also facilitate the integration of diverse types and sources of information, including expert knowledge, the results of prior experiments, outcomes from published literature, and so on~(\cite{korbBayesianArtificialIntelligence2011}).
+We have chosen to use BNs due to their adaptability to address regional concerns and model-specific scenarios, as well as because of their wide use in agricultural applications~\cite{abbalDecisionSupportSystem2016, carmonaUseParticipatoryObjectOriented2011, luDiseaseRiskForecasting2020, barton2008bayesian, cain2001planning}.
+In this study, we focus on the environmental aspect of sustainability through the use of `environmental impact' as the terminal node (node definitions are detailed in the results) within the network, linking relevant factors through structures described by an expert panel.
+Specialist knowledge and region-specific data were integrated into the BN within a structured framework to quantify the impacts of various factors on sustainability.
+This methodology shedding light on current sustainable practices, identifying critical areas for intervention and facilitating the creation of metrics to assess the evolution and impact of various management actions and climate scenarios.
+
+Several fundamental inquiries guided this research to enhance our understanding of sustainability in viticulture.
+The primary driving question being, how key factors impact the environment and how these factors can be rigorously defined and quantified.
+Furthermore, the study delves into how factors change due to the unique characteristics of different winegrowing regions, using the Coonawarra and Riverland regions to illustrate how the relative influence of factors changes.
 Additionally, the study investigates how these factors interact with each other.
-The final question is, how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.
-
-An industry panel comprising experts in viticulture and sustainability, was convened to guide the project.
-The panel acted as a catalyst in the early stages of the research to help explore the above questions.
-The panel input was supported by a comprehensive literature review, which established a foundational understanding of the current knowledge landscape and identified major concepts within sustainable winegrowing.
-To ensure a robust and comprehensive BN, a combination of qualitative and quantitative methods were employed in its creation via expert consultations and data analysis.
+The final question is how the findings from these Bayesian Network models compare with existing literature on sustainability in viticulture, aiming to connect industry perceptions to academic knowledge.
+To address these objectives, an industry panel of viticulturists and sustainability experts provided critical input supported by an extensive literature review.
+To ensure a robust and comprehensive BN, a combination of qualitative and quantitative methods was employed in its creation via expert consultations and data analysis.
 The study thus aimed to produce findings that are not only theoretically sound but also practically relevant and applicable to the viticulture industry.
@@
 
-In agriculture, the consideration of environment is critical to the success of the industry.
-The question of sustainability has continued to grow in importance as the industry is affected by international market demands, disease pressures, natural disasters and social change~(\cite{wineaustraliaNationalVintageReport2022,wineaustraliaNationalVintageReport2020,wineaustraliaNationalVintageReport2021,cassonMultidisciplinaryApproachAssess2022}).
-The question of sustainability requires the consideration of a multitude of factors, not only due to physical characteristics and differences between locations and habitats but also due to priorities driven by diverse perspectives including consumers, produces, the community, government and industry~(\cite{baianoOverviewSustainabilityWine2021,wayeCarbonFootprintsFood2008}).
-It is important to consider each factor with respect to these perspectives, and to be explicit in how they are defined~(\cite{santiago-brownSustainabilityAssessmentWineGrape2015}).
+Given the complexity of factors influencing sustainability, the adopted approach integrates a comprehensive literature review with expert elicitation and BN.
+The literature review was designed to identify key factors and their interactions, informed by insights from an expert panel specialising in viticulture and sustainability.
+Bayesian Networks were chosen to complement this as the primary modelling tool due to their ability to describe these relationships in a causal fashion and capture them probabilistically.
 
-Collaboration between experts from different perspectives helps to reconcile opinions regarding different factors and their contribution to sustainable outcomes~(\cite{dichiaraCollaborativeApproachAchieving2024}).
-In Australia, all of the above groups mentioned are united in the priority to reduce greenhouse gas emissions and resource use through approaches such as regulating chemicals, water use and fertilisers~(\cite{dumbrellComparingAustralianPublic2024}).
-While there is a general agreement on broader regulatory needs, the industry requirements vary greatly between different wine regions; due to climate, soil types and water resources~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012}).
-% old comment
-% KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this para out and absorb refs into the lit review.
-G, K and F seem quite relevant but this paragraph doesnt do them justice so expand or move.
-% 
-% Review further comments about this paragraph - its not a good piece of work but it is important to consider how impact and sustainability is or could be measured and interpretted.
-Perhaps go deeper like you did in your confirmation.
-Methods for measuring sustainability comprise a wide variety that of approaches with the use of index systems being common.
-The use of index systems is beneficial in comparing sustainability performance across different industries or geographic regions.
-As~\cite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating easier interpretation and comparison.
-Other approaches utilise the identification of key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment~(\cite{floresWhatSustainabilityWine2018}).
-The measuring of sustainability through can help to manage risk and promote resilience for industries through identifying sustainable goals and key factors of interest that contribute to positive outcomes~(\cite{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}).
-For instance, frameworks like MESMIS categorize sustainability measures into `descriptors' (guidelines), `indicators' (metrics for measuring changes), and `parameters' (limits for indicators)~(\cite{klemes_assessing_2015}).
-This structure allows for a more granular assessment of sustainability by linking broad guidelines to specific, measurable outcomes.
-By focusing on key indicators such as soil health, water usage, and biodiversity, the sustainability of wine production practices can be gauged with greater precision.
-These proxy measurements are crucial for understanding how specific actions or practices affect broader environmental outcomes, thereby enabling more targeted and effective sustainability efforts.
-Within this study we focus on measuring key factors and establishing how they interact, and ultimately effect the surrounding environment; the chosen method for this study is a Bayesian Network.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% End suggestion.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The expert panel guided the selection of regions as case studies, recommending regions that leveraged their specialised knowledge and favoured available data.
+The following subsections detail the literature review process, the construction and quantification of Bayesian Networks, and the validation and sensitivity analyses conducted to ensure robustness.
+
 \subsection*{Literature Review}
 
-The literature review was designed to assess existing knowledge on sustainability in viticulture with the aim of identifying key factors influencing sustainability and understanding their interactions.
-These findings were combined with the information derived from the expert consultations to inform the BN construction and quantification.
-The most prominent way of informing the model was the construction of an initial straw-man model to describe different relationships explored in the literature, which helped as a beginning point for the experts to discuss the specific applicability of relationships for different Australian contexts.
-The literature review was done using systematic search of terms, broadly based on key factors given from the industry panel, was conducted.
+The literature review was designed to assess existing knowledge on sustainability in viticulture to identify key factors influencing sustainability and understanding their interactions.
+The literature review was conducted using a systematic search of terms, based on key factors from the industry panel.
 The general query (adapted to different formats for various journals and bibliographic databases) used for the literature search was:
@@
 Articles were only excluded if they were not available in full text or were not written in English.
-In-depth reviews of sustainability within agriculture or winegrowing and methodological reviews within this context were also included.
+In-depth sustainability reviews within agriculture or winegrowing and methodological reviews within this context were also included.
 
@@
 The expert panel comprising specialists in viticulture and sustainability was engaged throughout the literature review process.
-The panel provided guidance on the selection of relevant articles, helped refine the inclusion criteria through their list of key factors.
+The panel guided the selection of relevant articles and helped refine the inclusion criteria through their list of critical factors.
 % By conducting a thorough literature review, this study aimed to build a solid foundation of existing knowledge, identify gaps, and position the findings from the Bayesian Network models within the broader context of sustainability research in viticulture.
-This approach ensured that the study's results were not only robust and scientifically sound but also practically relevant and actionable for industry stakeholders.
+This approach ensured that the study's results were robust and scientifically sound and practically relevant and actionable for industry stakeholders.
 
@@
 
-A BN is a graphical model, comprising of nodes and edges.
-Uniquely, Bayesian Networks contain the network's operations within the nodes themselves instead of across the edges.
-In the BN structure adopted in the study, these operations were encapsulated through a conditional probability table for each node, with connections between the nodes being defined by edges.
-This results in computational simplicity, since each node is dependent only on its parent and simplicity within the calculations are achieved through sum, multiplication and division operations
+% old comment
+% KM: I Suggest expanding this (the paragraph below) - split into measurement, methods, etc - or leave this part out and absorb refs into the lit review.
+G, K and F seem quite relevant, but this paragraph doesn't do them justice, so expand or move.
+% 
+% Review further comments about this paragraph - it's not a good piece of work, but it is essential to consider how impact and sustainability are or could be measured and interpreted.
+Perhaps go deeper like you did in your confirmation.
+% THIS IS WHERE KERRIES RESEARCGH GOOOEOEEESSSS
+Methods for measuring sustainability comprise a wide variety of approaches, with index systems being common.
+Index systems are beneficial in comparing sustainability performance across different industries or geographic regions.
+As~\cite{gehringerMappingSustainabilityMeasurement2024} notes, these systems provide a structured approach to evaluating sustainability by aggregating multiple indicators into a singular measure, facilitating more straightforward interpretation and comparison.
+Other approaches utilise identifying key factors, and their measurements as a proxy to indicate impact to, or the health of, the environment~(\cite{floresWhatSustainabilityWine2018}).
+The measuring of sustainability can help to manage risk and promote resilience for industries through identifying sustainable goals and critical factors of interest that contribute to positive outcomes~(\cite{klemesAssessingMeasuringEnvironmental2015, beckerSustainabilityScienceManaging2024}).
+For instance, frameworks like MESMIS categorize sustainability measures into `descriptors' (guidelines), `indicators' (metrics for measuring changes), and `parameters' (limits for indicators)~(\cite{klemes_assessing_2015}).
+This structure allows for a more granular sustainability assessment by linking broad guidelines to specific, measurable outcomes.
+By focusing on critical indicators such as soil health, water usage, and biodiversity, the sustainability of wine production practices can be gauged with greater precision.
+These proxy measurements are crucial for understanding how specific actions or practices affect broader environmental outcomes, enabling more targeted and effective sustainability efforts.
+Within this study, we focus on measuring key factors and establishing how they interact and ultimately affect the surrounding environment; the chosen method for this study is a Bayesian Network.
+%  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% End suggestion.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A BN is a graphical model comprising nodes and edges.
+Uniquely, Bayesian Networks contain the network's operations within the nodes instead of across the edges.
+In the BN structure adopted in the study, these operations were encapsulated through a conditional probability table for each node, with connections between the nodes defined by edges.
+This results in computational simplicity since each node is dependent only on its parent and simplicity within the calculations is achieved through sum, multiplication and division operations
 % .
 However, great complexity is introduced when a node is informed by many parents, which can also have many parents themselves.
-The change in a single parent node effects all children of the network; often resulting in intractable systems, especially when nodes may have numerous classes
+The change in a single parent node affects all children of the network, often resulting in intractable systems, especially when nodes may have numerous classes
 (\cite{korbBayesianArtificialIntelligence2011}).
-% The strength of this complexity over simple operations, is the ability to encapsulate incredibly complex systems with simple definitions.
+% The strength of this complexity over simple operations is the ability to encapsulate incredibly complex systems with simple definitions.
 
@@
 The ability to include perspectives from industry experts and create a causal structure.
-The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another; and ultimately a factor's relation direct or indirect, to a vineyard's environmental impact
+The graphical nature of the Bayesian Network also helps to illustrate factors within the model and communicate the complexity and relationships of factors to one another;and ultimately ,a factor's relation, direct or indirect, to a vineyard's environmental impact
 (\cite{pourretBayesianNetworksPractical2008}).
-Furthermore, data collected across Australia could also be used to help inform the model structure as well as quantify the associated conditional probabilities alongside expert opinion.
+Furthermore, data collected across Australia could also be used to help inform the model structure and quantify the associated conditional probabilities alongside expert opinion.
 
@@
 % Where we calculate the probability of an event A given an event B, as demonstrated by \cite{bayesLIIEssaySolving1763}.
-Within a Bayesian Network, an event can be considered any given node and its outcome one of the node's classes.
+Within a Bayesian Network, an event can be considered any given node, and its outcome is one of the node's classes.
 Events are connected by edges within the network, with each node containing the probability of an outcome given parent nodes' outcomes.
@@
 
-Given the directed acyclic graph (DAG) structure of the BN, each quantification of a node only depends on the parent of that node, and is conditionally independent of the other nodes in the network collectively, then,
+Given the directed acyclic graph (DAG) structure of the BN, each quantification of a node only depends on the parent of that node and is conditionally independent of the other nodes in the network collectively; then,
 
@@
 The ability to present different probable outcomes for various sets of events and their associated uncertainties enables the conduction of inference.
-This inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present.
-The sets of different outcomes then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods.
-One of the greatest abilities of this type of inference is Marginalization.
-In which, the outcome of a particular event can be determined irrespective of other outcomes.
-This type of marginalisation is intuitively represented as nodes conditional independence and illustrated inherently through the structure of the graph by its edges.
-Bayesian Networks created in this study were created using BayesFusion~(\cite{bayesfusionGeNIeModelerUSER2022}) to calculate the networks and their probabilities.
+This inference shows the difference between the likelihood of multiple outcomes with and without different evidence of prior nodes outcomes being present.
+The sets of different outcomes are then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods.
+One of the most remarkable abilities of this type of inference is Marginalization.
+The outcome of a particular event can be determined irrespective of other outcomes.
+This type of marginalisation is intuitively represented as nodes' conditional independence and illustrated inherently through the graph's structure by its edges.
+Bayesian Networks in this study were created using BayesFusion~(\cite{bayesfusionGeNIeModelerUSER2022}) to calculate the networks and their probabilities.
 % The Bayes fuse software was used both through the GUI interface and the SMILE API \cite{bayesfusionGeNIeModelerUSER2022} system using C++ (\cite{ISO:2012:III}).
@@
 
-The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by~(\cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}).
+The Bayesian Network was constructed using data and expert elicitation, following the format recommended by~(\cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}).
 The process progressed iteratively through problem definition, structure, parameterisation, and validation.
-Initially, experts were informed about the process to ensure a clear understanding of each step and to highlight common pitfalls, as well as how these would be addressed.
-Some of the common problems identified by both authors include a lack of understanding of the problem context, the introduction of complexity without value, incorrect arc directions, an excessive number of parent nodes, biased expert estimates, inconsistent probabilities, and an unwarranted certainty in estimates.
+Initially, experts were informed about the process to ensure a clear understanding of each step and highlight common pitfalls and how these would be addressed.
+Some common problems identified by both authors include a lack of knowledge of the problem context, the introduction of complexity without value, incorrect arc directions, an excessive number of parent nodes, biased expert estimates, inconsistent probabilities, and an unwarranted certainty in estimates.
 To address these issues, experts were kept well-informed of them, as well as variable definitions and problem scope.
-Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency.
-Communication included in-person and electronic one-on-ones and group sessions; with elicited of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.
+Open communication was maintained during the entire process to help answer questions regarding the model and process and to maintain transparency.
+Communication included in-person and electronic one-on-ones and group sessions;,with elicited oxpert knowledge being primarily conducted through a series of workshops with the panel of industry experts.
 
-Each workshop had a primary focus such as: scope, structure or parameterisation; with, prior concepts being built upon iteratively.
-The first important establishment was the scope of the network, and how well it could or couldn't be adapted to a wide variety of circumstances within the Australian winegrowing industry.
-Following this was the discussion around the structure of the network, which entailed the description of relationships and stricter definitions of each factor to one another.
-Finally, variables were paramatised using conditional probabilities.
+Each workshop had a primary focus, such as scope, structure or parameterisation, with prior concepts being built upon iteratively.
+The first critical establishment was the scope of the network and how well it could or couldn't be adapted to a wide variety of circumstances within the Australian winegrowing industry.
+Following this was the discussion around the network structure, which entailed the description of relationships and stricter definitions of each factor to one another.
+Finally, variables were parameterised using conditional probabilities.
 
-To introduce new concepts and how they interacted, preliminary simplified versions (straw-man examples) were provided to experts; with the intention of these examples to be examined, critiqued, and improved upon.
-The use of these straw-man examples enabled a more engaged and effective review process.
-Experts were initially able to interact with elements of the model and see how they worked together.
-The straw-man examples were crafted from a foundation of literature and data to offer a basic, layman's understanding of key factors and concepts, serving as a starting point for further development and discussion.
+To introduce new concepts and how they interacted, preliminary simplified versions (straw-man examples) were provided to experts, with the intention that these examples be examined, critiqued, and improved upon.
+Findings from the literature review were combined with data from Sustainable Winegrowing Australia to derive these initial straw-man models, which helped as a beginning point for the experts to discuss the specific applicability of relationships and significance of factors withinthe Australian context.
+Using these straw-man examples enabled a more engaged and effective review process.
+Experts were initially able to interact with model elements and see how they worked together.
+The straw-man examples were crafted from a foundation of literature and data to offer a basic layman's understanding of critical factors and concepts, serving as a starting point for further development and discussion.
 
@@
 As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network (\cite{korbBayesianArtificialIntelligence2011}).
-For reasons of comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes.
-The classes represented a positive or negative contribution to a vineyard's environmental outcome helping to reduce this complexity.
-Furthermore, the intricacy of variables, particularly water use, were overwhelmingly interrelated to operations across the vineyard.
-To attempt to capture this complexity but not dilute the ability to work with various scenarios experts were asked to provide key input into complex CPT cells and the CPT cells were interpolated.
+For comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes.
+The classes represented a positive or negative contribution to a vineyard's environmental outcome, helping to reduce this complexity.
+Furthermore, the intricacy of variables, particularly water use, was overwhelmingly interrelated to operations across the vineyard.
+To attempt to capture this complexity but not dilute the ability to work with various scenarios, experts were asked to provide critical input into complex CPT cells, and the CPT cells were interpolated.
 The experts then reviewed and amended or approved the derived CPTs.
@@
 This interpolation method utilised filling in cells between two anchored points.
-One point represented the case of all factors being true/positive and the other represented all factors being false/negative.
-The interpolation was achieved by designating each factor an attributed weight, where weights were indicative of a factor's overall influence to its child node.
-During workshop discussion participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.
+One point represented the case of all factors being true/positive, and the other represented all being false/negative.
+The interpolation was achieved by designating each factor an attributed weight, where weights indicated a factor's overall influence on its child node.
+During the workshop discussion, participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.
 
@@
 The values for $x$ and $y$ can be derived using the sum of the provided BN weights.
-An assumption of `smoothness' is taken between worst and best case scenarios when utilising this method.
-All possible combinations between all states being true (or ideal) and all being false (not ideal) are also mirrored such, with the only consideration being given, is that of how heavily weighted a variables state is compared to the others.
+An assumption of `smoothness' is taken between worst and best-case scenarios when utilising this method.
+All possible combinations between all states being accurate (or ideal) and all being false (not ideal) are also mirrored, with the only consideration being given, is that of how heavily weighted a variable state is compared to the others.
 
@@
 
-The method for validation sought to address criteria presented by~\cite{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
-Nomological validity refers to ensuring that the BN fits within a broader theoretical context, aligning with established literature.
+The validation method sought to address criteria presented by~\cite{pitchforthProposedValidationFramework2013}, who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity.
+Nomological validity ensures that the BN fits within a broader theoretical context, aligning with established literature.
 Face validity involves evaluating whether the model appears to be a valid representation based on expert judgment.
-Content validity checks that the model includes all relevant factors and relationships from both literature and expert knowledge, ensuring nothing critical is omitted.
-Concurrent validity is concerned with whether the BN or its components behave consistently when compared with other similar networks.
-Convergent validity assesses how closely the BN aligns with models that describe similar systems, while discriminant validity ensures that the BN is distinct from models representing different systems.
-Finally, predictive validity examines the BN's ability to accurately predict system behavior.Validation steps were partly incorporated during the process of constructing the Bayesian network itself.
-When considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario.
-The selection process for experts, encouraged diversity in their regional knowledge and expertise in order to broaden the ability to critique choices.
+Content validity checks that the model includes all relevant factors and relationships from literature and specialist knowledge, ensuring nothing critical is omitted.
+Concurrent validity concerns whether the BN or its components behave consistently when compared with similar networks.
+Convergent validity assesses how closely the BN aligns with models that describe identical systems, while discriminant validity ensures that the BN is distinct from models representing different systems.
+Finally, predictive validity examines the BN's ability to predict system behavior accurately.Validation steps were partly incorporated while constructing the Bayesian network itself.
+When considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region or scenario.
+The selection process for experts encouraged diversity in their regional knowledge and expertise itobroaden their ability to critique choices.
 Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions~(\cite{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}).
 
-The face and content validity of the network was questioned directly by the expert panel through the structure and conditional probability phases.
-This helped to avoid some overtly specific scenarios in favour of broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations.
-This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors~(\cite{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}).
-% Specifically, the question of water resources, which was central to the model and highly interrelated \cite{carmonaUseParticipatoryObjectOriented2011}.
+The face and content validity of the network were questioned directly by the expert panel through the structure and conditional probability phases.
+This helped avoid some overtly specific scenarios in favour of broader vineyard decisions whilst allowing the model to address these behaviours in the future by targeting a region and incorporating its considerations.
+This approach went hand in hand with the content validation, where it was found additional nodes needed to be added to the general model to reflect important regional factors~(\cite{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}).
+% Specifically, the question of water resources was central to the model and highly interrelated \cite{carmonaUseParticipatoryObjectOriented2011}.
 
-Similarly, the convergent validity of the model was accomplished through the checking the alignment of the model to other research, which helped to further answer questions of concurrent validation.
-This process was undertaken after the regional models were developed in unison with the literature review and creation of Leximancer concept map.
+Similarly, the convergent validity of the model was accomplished by checking the alignment of the model to other research, which helped to answer questions of concurrent validation further.
+This process was undertaken after the regional models were developed in unison with the literature review and creation of the Leximancer concept map.
 It was found that other studies emphasised the same variables selected by our experts.
@@
 
-The discriminant validation of the model was the most difficult, as the definitions of each node changed over the course of the model's inception.
+The discriminant validation of the model was the most difficult, as the definitions of each node changed throughout the model's inception.
 This brought the difficulty that nodes connected by edges would have to be reconsidered each time a definition changed.
-This issue was simply overcome through explicit definitions accessible to all participants, and by directly addressing issues caused by definitions before further development of the model.
-Again, the simplicity of binary state nodes helped to isolate definitions more distinctly, as well as employing methods such as node splitting, removal and adding additional nodes~(\cite{korbBayesianArtificialIntelligence2011}).
+This issue was overcome through explicit definitions accessible to all participants and by directly addressing problems caused by definitions before further development of the model.
+Again, the simplicity of binary state nodes helped to isolate definitions more distinctly and employ methods such as node splitting, removal and adding additional nodes~(\cite{korbBayesianArtificialIntelligence2011}).
 
-The factors within the BN had similar parent nodes to factors that appeared in other models from the literature (i.e yield generally utilised area, water, fuel as predictors), although there were key differences.
-The differences were primarily due to the consideration of nodes as factors that related and were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the environmental outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation~(\cite{laurentReviewIssuesMethods2021}).
-The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being able to be properly employed.
-Furthermore, the predictive validity was able to be well established through two methods, the use of a case study and the consideration of extreme outcomes.
+The factors within the BN had similar parent nodes to factors that appeared in other models from the literature (i.e.
+yield generally utilised area, water, and fuel as predictors), although there were key diWaternces.
+The differences were primarily due to the consideration of nodes as factors that related.
+They were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the ecological outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation~(\cite{laurentReviewIssuesMethods2021}).
+The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being properly employed.
+Furthermore, the predictive validity was established through two methods: the use of a case study and the consideration of extreme outcomes.
 
@@
 Sensitivity analysis is a crucial step in evaluating the robustness and reliability of a BN model.
-It involves assessing how variations in input parameters influences a selected variables resultant probability distribution (or posterior in this case).
-In this study, sensitivity analysis was used to visualise the impact of factors on the environmental impact node.
-This was used to provide insight into which factors had the most influence on environmental impact, the BNs terminal node.
-BNs facilitates sensitivity analyses by allowing for the systematic examination of how small changes in one or more input variables affect the probability distribution of a selected node.
-This is particularly important when reviewing the sensitivity analysis in the context of environmental impact as it adds to the understanding of how relationships between variables and their potential impacts can guide decision-making or improve model accuracy.
+It involves assessing how input parameter variations influence a selected variables resultant probability distribution (or posterior in this case).
+This study used sensitivity analysis to visualise the impact of factors on the environmental impact node.
+This was used to provide insight into which factors had the most influence on ecological impact, the BN's terminal node.
+BNs facilitate sensitivity analyses by systematically examining how small changes in one or more input variables affect the probability distribution of a selected node.
+This is particularly important when reviewing the sensitivity analysis in the context of environmental impact, as it adds to the understanding of how relationships between variables and their potential impacts can guide decision-making or improve model accuracy.
 
@@
 
-The process utilises two outward and one inward propagation across a junction tree, a data structure that represents the Bayesian network by organizing its nodes into a tree of cliques, where each clique is a subset of nodes that are fully connected within the network.
-Propagation refers to the method of passing messages (or updating beliefs) through this junction tree to ensure consistency across the network, allowing for the efficient calculation of probabilities.
-These propagations are essential for establishing the necessary cliques that allow for the calculation of the sensitivity function using the coefficients $\gamma$ and $\delta$.
+The process utilises two outward and one inward propagation across a junction tree, a data structure that represents the Bayesian network, by organizing its nodes into a tree of cliques, where each clique is a subset of fully connected nodes within the network.
+Propagation refers to passing messages (or updating beliefs) through this junction tree to ensure consistency across the network, allowing for the efficient calculation of probabilities.
+These propagations are essential for establishing the necessary cliques that allow for calculating the sensitivity function using the coefficients $\gamma$ and $\delta$.
 
@@
 where $\alpha$, $\beta$, $\gamma$ and $\delta$ are constants with respect to $x$.
-$y$ is the posterior marginal of interest, which refers to the probability distribution of a subset of variables (in this case, $y$) after taking into account the given evidence $e$, with respect to the parameter $x$ (a factor or state of a node within the BN).
+$y$ is the posterior marginal of interest, which refers to the probability distribution of a subset of variables (in this case, $y$) after taking into account the given evidence $e$, concerning the parameter $x$ (a factor or state of a node within the BN).
 
-% should I extrapolate on this method?
+% Should I extrapolate on this method?
 
@@
 
-The methodology is extendable to n-way sensitivity analysis, allowing for the examination of the joint effects of multiple parameters.
-This involves identifying the relevant parameters and their influence on the posterior marginals using the same propagation strategy multiple times.
+The methodology is extendable to n-way sensitivity analysis, allowing for examining the joint effects of multiple parameters.
+This involves identifying the relevant parameters and their influence on the posterior marginals using the same propagation strategy numerous times.
 
 By employing this method, the sensitivity analysis avoids the extensive computational demands of traditional brute-force approaches, which require numerous network evaluations.
-Instead, this approach ensures that all potential parameters are considered with minimal computational overhead; allowing the use of multiple scenarios based off different evidence.
+Instead, this approach ensures that all potential parameters are considered with minimal computational overhead, allowing the use of multiple scenarios based on different evidence.
 
@@
 Due to Coonawarra's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying BNs.
-Located in South Australia's Limestone Coast zone, Coonawarra is distinguished by its cooler climate and the unique soils shaped by the region's distinctive geology.
+Located in South Australia's Limestone Coast zone, Coonawarra is distinguished by its cooler climate and the unique soils shaped by its distinctive geology.
 This combination provides an exceptional foundation for viticulture, making Coonawarra a renowned wine-producing area.
-The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon~(\cite{hallidayAustralianWineEncyclopedia2009}).
-Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around sustainability practices to specific regional factors.
+The Coonawarra winegrowing region is renowned for its exceptional wine quality, notably its Cabernet Sauvignon~(\cite{hallidayAustralianWineEncyclopedia2009}).
+Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panel's overarching ideas around sustainability practices to specific regional factors.
 
-As discussed above the expert advisory panel proposed the development of a regional model to augment and focus the primary general model.
-For specificity the panel proposed a case study of a specific and well understood region: Coonawarra in South Australia.
-The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing.
-The Coonawarra BN was based on the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel.
-Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for under vine operations and more purposeful under vine management, as well as the inclusion of further soil based factors that could be significant for particular sites.
+As discussed above, the expert advisory panel proposed developing a regional model to augment and focus on the primary general model.
+For specificity, the panel suggested a case study of a specific and well-understood region: Coonawarra in South Australia.
+The choice of the area was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to wine growing.
+The Coonawarra BN was based on the original Bayesian Network's structure, with site-specific conditional probabilities being entered and scrutinised by the expert panel.
+Differences in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches, primarily differing between opportunity-based tractor use for under-vine operations and more purposeful under-vine management, as well as the inclusion of further soil-based factors that could be significant for particular sites.
 
@@
 
-The key factors identified by the industry panel and their agreed definitions are shown in Table~\ref{tab:definitions}.
-By utilising these definitions, each factor's contribution to sustainability were quantified and assessed by the industry panel.
+The critical factors identified by the industry panel and their agreed definitions are shown in Table~\ref{tab:definitions}.
+Using these definitions, the industry panel quantified and assessed each factor's contribution to sustainability.
 The quantification of each factor allowed for a systematic assessment of their impacts.
 For example, `Water Use' was quantified as `High' or `Low', enabling a straightforward assessment of its environmental impact.
-Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).
+Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable, with each being of the two general categories ideal and not ideal (low and high, respectively, for water use).
 
@@
 % Purpose: Develop the factors into well-defined and measurable impacts on sustainability.
-% Results: Use the agreed upon definitions to fully realise factors and their impact.
+% Results: Use the agreed-upon definitions to realise factors and their impact fully.
 % 
@@
     \textbf{Factor name} & Definition & \textbf{Ideal Class} & Not Ideal Class \\ \midrule
-    \textbf{Water use} & Total amount of water used by a vineyard in a financial year (ML/Ha) & \textbf{Low} & High \\
+    \textbf{Water use} & Total amount of water used by a vineyard in a financial year (ML/Ha) &Watertbf{Low} & High \\
     \textbf{Agrochemical type} & When selecting agrochemicals, those which are less hazardous to beneficial organisms and/or have a lower environmental impact are considered & \textbf{Yes} & No \\
@@
     \textbf{Water Price} & The cost per unit of water paid for by a vineyard & \textbf{Low} & High \\
-    \textbf{Water quality} & Water used for irrigation is assessed annually for quality (pH, chloride, sodium absorption ratio, electrical conductivity, soluble solids, hardness, microbial contamination).
+Watertextbf{Water quality} & Water used for irrigation is assessed annually for quaWater(pH, chloride, sodium absorption ratio, electrical conductivity, soluble solids, hardness, microbial contamination).
 Water that may case soil degradation or irrigation inefficiency is treated before use.
@@
 By applying these definitions, the study effectively translated the qualitative aspects of sustainability into usable metrics.
-This approach not only facilitated a comprehensive analysis of the factors but also identified their specific relationships.
-The use of these definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving sustainability; allowing each factor's contribution to be clearly understood and relationships explicitly defined.
-This was key within the construction of the BN, were the industry panel could easily refer to the specifics of each definition and thus how it might relate to other factors.
+This approach facilitated a comprehensive analysis of the factors and identified their specific relationships.
+These definitions enabled each of the factors' impacts to be linked and reviewed, demonstrating their importance in achieving sustainability, allowing each factor's contribution to be clearly understood and relationships explicitly defined.
+This was key within the construction of the BN, where the industry panel could easily refer to the specifics of each definition and, thus, how it might relate to other factors.
 
-\subsection*{Bayesian Network Structure for sustainability in Australian Winegrowing}
+\subsection*{Bayesian Network Structure for Sustainability in Australian Winegrowing}
 
@@
     \caption{The resultant Bayesian Network (BN) illustrating the relationships between vineyard factors and environmental impact in Australian winegrowing.
-The network's nodes are color-coded to indicate the source and nature of the data: Blue nodes represent expert-led ideas that are not directly supported by data, Green nodes are supported by data contained in Sustainable Winegrowing Australia's database, and Gold nodes correspond to variables with readily accessible public data.
+The network's nodes are colour-coded to indicate the source and nature of the data: Blue nodes represent expert-led ideas that are not directly supported by data, Green nodes are supported by data contained in Sustainable Winegrowing Australia's database, and Gold nodes correspond to variables with readily accessible public data.
 The terminal node is highlighted in pink.}\label{fig:generalBN}
@@
 
-The relationships between the facets in Table~\ref{tab:definitions}  as agreed by the industry panel, are depicted in the BN model in Fig~\ref{fig:generalBN}.
-The BN highlights which factors are influenced by others in the form of an acyclic directed graph.
-Notably, the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water.
-It also illustrates the complex nature of variables such as water and their inter-relatedness.
+The relationships between the facets in Table~\ref{tab:definitions}, as agreed by the industry panel, are depicted in the BN model in Fig~\ref{fig:generalBN}.
+The BN highlights which factors others influence in the form of an acyclic-directed graph.
+Notably, the key factors influencing environmental impact centre around agrochemical sprays, soil management, pest/disease and water.
+It also illustrates the complex nature of variables such as water and their interrelatedness.
 
-    % What are the primary factors that significantly impact sustainability in the Australian winegrowing industry?
-    %     Purpose: Identify the most influential variables directly affecting sustainability and those that are perceived to directly impact sustainability.
-    %     Results: Review the most influential factors and what they are related too. Compare this to the data in SWA.
+    % What are theWaterary factors that significantly impact sustainability in the Australian winegrowing industry?
+    %     Purpose: Identify the most influential variables directly affecting sustainability and those perceived to directly impact sustainability.
+    %     Results: Review the most influential factors and their relation. Compare this to the data in SWA.
 
@@
     %     Purpose: Explore and understand the causal and correlated relationships among the factors.
-    %     Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
+    %     Results: Use the generic BN to illustrate the agreed-upon relationships between discussed factors.
 %
 
-% The BN provided a comprehensive overview of how factors defined by the industry panel, would interact.
-Showing not only direct relationships but also how changes in one factor can propagate through the network to affect others.
-This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry.
+% The BN provided a comprehensive overview of how factors defined by the industry panel would interact.
+This shows not only direct relationships but also how changes in one factor can propagate through the network and affect others.
+This understanding is crucial for developing targeted interventions and policies to improve sustainability in the wine-growing industry.
 This network illustrates the complexity of interactions that determine sustainability in Australian winegrowing.
-Furthermore, the extent of relationships helps to intrinsically show the importance of variables such as water; which is prolific in how it is interconnected with other vineyard aspects.
+Furthermore, the extent of relationships helps to show the importance of variables such as water intrinsically, which is prolific in how it is interconnected with water vineyard aspects.
 
-Figure~\ref{fig:generalBN}, illustrates the intricate relationships between various vineyard factors and their impact on sustainability in the Australian winegrowing industry.
-The BN structure highlights the critical role of water, disease/pest management, and climate, which are depicted as central nodes with numerous connections to other variables.
-These connections underscore the importance of these factors as key drivers of environmental impact, influencing a wide number of other nodes within the network.
+Figure~\ref{fig:generalBN} illustrates the intricate relationships between various vineyard factors and their impact on sustainability in the Australian winegrowing industry.
+The BN structure highlights the critical role of water, disease/pest management, and climate, which are connected as central nodes with numerous connections to other variables.
+These connections underscore the importance of these factors as key drivers of environmental impact, influencing many other nodes within the network.
 
@@
 For instance, variables like fuel use and soil management emerge as child nodes within the network, representing operational decisions that respond to these external pressures.
-The BN effectively captures the complexity of these interactions, illustrating how decisions made at the operational level, such as the optimisation of fuel use or improving soil management practices, can serve as potential interventions to lessen environmental impact.
+The BN effectively captures the complexity of these interactions, illustrating how decisions made at the operational level, such as optimising fuel use or improving soil management practices, can serve as potential interventions to lessen environmental impact.
 These interventions are critical in pursuing more sustainable outcomes, mitigating the adverse effects of environmental stressors, and enhancing the resilience of the winegrowing system.
 
-By mapping these relationships, the BN provides a visual and analytical framework that aids in identifying the most influential factors and understanding their inter-dependencies.
+By mapping these relationships, the BN provides a visual and analytical framework that aids in identifying the most influential factors and understanding their interdependencies.
 This, in turn, helps inform decisions toward more environmentally sustainable practices.
@@
 
-As part of this study, a comprehensive literature review was conducted to assess the current state of research on sustainability in the winegrowing industry and as part of the BNs validation.
-The review included a total of 1321 articles, selected based on key words and publication dates outlined in the prior selection criteria (see~\ref{lst:query}).
+As part of this study, a comprehensive literature review was conducted to assess the current research on sustainability in the wine-growing industry and as part of the BNs validation.
+The review included 1321 articles, selected based on keywords and publication dates outlined in the prior selection criteria (see~\ref{lst:query}).
 The articles span a range of topics, including sustainability metrics, operational practices, and the influence of regulatory frameworks on environmental outcomes.
 
-The number of articles that contained key terms is outlined in Table~\ref{tab:lexi}.
-The bibliometric analysis using Leximancer revealed key concepts and their relevance to sustainability in the Australian winegrowing industry.
+Table~\ref{tab:lexi} outlines the number of articles containing key terms.
+The bibliometric analysis using Leximancer revealed vital concepts and their relevance to sustainability in the Australian wine-growing industry.
 The most prominent concept was water (see Table~\ref{tab:lexi}).
-The critical importance of other variables is indicated by their comparative frequency in articles relative to water (making water 100\%).This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with challenges and solutions outlined by the expert panel.
+The critical importaWaterf other variables is indicated by their comparative frequency in articles relative to water (making water 100\%).
+This review provided a foundation for comparing academic perspectives with industry practices, allowing for a nuanced analysis of how well the literature aligns with the challenges and solutions outlined by the expert panel.
 % What are the factors of sustainability in the Australian winegrowing industry?
-%     Purpose: Explore and understand the both the literature and industry perspectives on this.
-%     Results Literature review. Industry list of factors. Mind Map? Leximancer network.
-%     - Use the same words as the definitions in the search to show the parralels and differences.
+%     Purpose: Explore and understand both the literature and industry perspectives on this.
+%     Results in Literature review. Industry list of factors. Mind Map? Leximancer network.
+%     - Use the same words as the definitions in the search to show the parallels and differences.
 % Please add the following required packages to your document preamble:
@@
     change & 569 & 43 \\
-    %TODO: One of these should be something other than change!!! THey both cant be!!
+    %TODO: One of these should be something other than change!!! They both can't be!!
     grapevine & 565 & 43 \\
@@
 % Comparing this with the data from Sustainable Winegrowing Australia (SWA), it was evident that the factors identified in the BN align with the critical areas SWA focuses on, such as water use, greenhouse gas emissions, and agrochemical use.
-This alignment reinforces the importance of these factors and supports the findings of the BN analysis.
+This alignment reinforces these factors' importance and supports the BN analysis's findings.
 % What are the relationships between these factors in the Australian winegrowing industry?
@@
 
-The most significant concepts along with water, included change, climate, and disease.
-These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see Table~\ref{tab:lexi}).
+The most significant concepts, along with water, included change, climate, and disease.
+These highlight the focus on adapting to climate change and managing plant diseases, which are crucial for maintaining sustainable practices (see Table~\ref{tab:lexi}).
 Furthermore, change and climate were kept separate to illustrate the variety of different changes, such as in practice, legislation and resource abundance.
@@
 Figure~\ref{fig:lexi} also illustrates the connection between concepts through edges, and overlaying the most related concepts, change, grapevine, water and land as coloured areas on the diagram.
-With the most related concepts being of similar themes to that of the industry panel's Bayesian Network.
+With Waterost related concepts being of similar themes to that of the industry panel's Bayesian Network.
 
@@
 Notably the sensitivity of the Coonawarra models align with the focus of literature and analyses, focusing on  aspects such as disease, water, soil health and climate.
-The combination of agreeing with these primary concerns whilst highlighting their connection to operational variables such as tractor, and fuel use; is an important step to realising the benefits of combined efforts of prevention through scenario assessments.
+The combination of agrWater with these primary concerns whilst highlighting their connection to operational variables such as tractor, and fuel use; is an important step to realising the benefits of combined efforts of prevention through scenario assessments.
 Considering variables that are related to an operational standpoint as well as environmental Furthers the ability to show the consideration of environmental impact within vineyard operational decisions and how it may lower the costly use of agrochemicals and fuel.
@@
 
-Identified key factors impacting sustainability were examined with regard to Coonawarra.
+Identified key factors impacting Waterinability were examined with regard to Coonawarra.
 By comparing the generic Bayesian Network (Figure~\ref{fig:generalBN}) model to the Coonawarra-specific model (Figure~\ref{fig:robyn} and Figure~\ref{fig:marcel}), we identified regional characteristics that influence these variations.
@@
 % This is significant... (refering to below)
-As a factor, water emerged as the most interconnected variable for both BNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture.
+As a factor, water emerged as the most interconnected variable for WaterBNs, with edges connecting it to almost everything either directly or indirectly, illustrating its fundamental role in agriculture.
 Climate conditions also play a significant role, influencing water availability, quality and disease/pest pressures.
@@
 Environmental impact was particularly sensitive to management strategies (pest, disease, soil carbon and spray applications) in both BNs.
-These sensitive factors are closely linked to resource use variables (water, fuel and electricity), showing how targeted regulatory and operational interventions can influence multiple sustainability aspects beyond their immediate focus.
+These sensitive factors are closely linked to resource use variables (water, fuel and electricity), showing how targeted regWaterry and operational interventions can influence multiple sustainability aspects beyond their immediate focus.
 
 The Coonawarra-specific BNs both support the findings from the literature, with a more structured map of how factors interact compared to the Leximancer summary in Figure~\ref{fig:lexi}.
-The BN provides a detailed view of the relationships between factors, highlighting the central role of water and the interconnectedness of pest management, market pressures, and climate conditions.
+The BN provides a detailed view of the relationships between factors, highlighting the central role of water and the interconnectedness of pest management, mWater pressures, and climate conditions.
 Additionally, the BNs emphasise economic factors, such as market pressures and grape prices, and includes how they interact within a scope of secondary factors like fuel and electricity use.
@@
 % This refined approach ensures that your Results section directly addresses your research questions and clearly presents your findings.
-Let me know if there are specific details or sections you’d like further refined!
+Let me know if there are specific details or sections you'd like further refined!
 
@@
 
-By linking fuel and electricity use with well-studied factors like water and climate, the BN model broadens the scope of sustainability research in viticulture, emphasising the interconnected nature of these challenges.
-Integrating elements which play critical roles in vineyard operational decisions such as tractor, fuel and electricity use, which were more peripheral within the bibliometric analysis, to central themes like water, pests/disease and climate offered a holistic view of sustainability in winegrowing.
+By linking fuel and electricity use with well-studied factors like water and climate, the BN model broadens the scope of Waterinability research in viticulture, emphasising the interconnected nature of these challenges.
+Integrating elements which play critical roles in vineyard operational decisions such as tractor, fuel and electricity use, which were more peripheral within the bibliometric analysis, to central themes like water, pests/disease and climate offered a holistic viWater sustainability in winegrowing.
 The model demonstrated how fuel, tractor, and electricity use are intertwined with factors such as water and climate through propagation.
-Even though sustainability was not highly sensitive to such factors, they directly relate to operational decisions that can be influenced by growers over a season.
+Even though susWaterbility was not highly sensitive to such factors, they directly relate to operational decisions that can be influenced by growers over a season.
 For example, electricity and fuel use are crucial for irrigation systems, as well as fuel use and tractors required for operations linked to soil preparation, management, and pest/disease control actions.
 Notably these operational decisions can be preventative or reactionary within a season.
-With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (soil, water and disease) particularly all of which are connected to climate~(\cite{fragaClimateChangeNew2020,tofaloClimateChangeWine2023,naigeonDATADecisionmakingViticulture2023}).
+With many of these decisions being directly influenced by the central themes described in the bibliometric analysis (soil, water and disease) particularly all of which are conneWaterto climate~(\cite{fragaClimateChangeNew2020,tofaloClimateChangeWine2023,naigeonDATADecisionmakingViticulture2023}).
 Additionally, the need to adapt to changing climate conditions can drive increased use of fuel and electricity, potentially exacerbating greenhouse gas emissions.
@@
 The relationships of nodes associated with operational and management  decisions illustrated how different drivers from nodes several edges away from environmental impact could still be driving forces through their causal influence of the primary contributing factors.
-Furthermore, external considerations such as market pressures, the demand for high-quality grapes through factors such as grape prices, were found to have an impact on the environment through how they influenced internal responses, such as the use of more water to increase yields as a response to price increases.
-The economic drivers of some of the decisions would be a great compliment in determining how the priority of these decision might be made alongside their environmental concerns, and poses a potential avenue for further research.
+Furthermore, external considerations such as market pressures, the demand for high-quality grapes through factors such as grape prices, were found to have an impact on the environment through how they influenced internal responses, such as the use of more water to increase yields as a response to price increaWaterThe economic drivers of some of the decisions would be a great compliment in determining how the priority of these decision might be made alongside their environmental concerns, and poses a potential avenue for further research.
 
@@
 The findings highlight the critical role of water quality and availability, emphasising its critical influence on all operational decisions either directly or propagating through other factors.
-With this critical nature being due to water being the most interconnected factor, emphasising the importance efficient water management practices enhancing sustainability in viticulture.
+With this critical nature being due to water being the most interconnected factor, emphasisinWater importance efficient water management practices enhancing sustainability in viticulture.
 
@@
 
-\bibliography{sample}
+\printbibliography
 
